### 2016-05-04 paper/ms.tex
apj style

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

%=========================================================================
%		INTERNAL MACROS
%=========================================================================
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\lmmin}{{\ifmmode{{\log M_{\rm min}}}\else{${\log M_{\rm min}}$}\fi}}
\newcommand{\lmmax}{{\ifmmode{{\log M_{\rm max}}}\else{${\log M_{\rm max}}$}\fi}}

\newcommand{\Mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\dm}{{\ifmmode{{\Delta M}}\else{$\Delta M$}\fi}}
\newcommand{\dlm}{{\ifmmode{{\Delta \log M}}\else{$\Delta \log M$}\fi}}
\newcommand{\focc}{{\ifmmode{{f_{\rm occ}}}\else{${f_{\rm occ}}$}\fi}}

\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
%SAMPLES

%MY COMMANDS #############################################################
\newcommand{\sub}[1]{\mbox{\scriptsize{#1}}}
\newcommand{\dtot}[2]{ \frac{ d #1 }{d #2} }
\newcommand{\dpar}[2]{ \frac{ \partial #1 }{\partial #2} }
\newcommand{\pr}[1]{ \left( #1 \right) }
\newcommand{\corc}[1]{ \left[ #1 \right] }
\newcommand{\lla}[1]{ \left\{ #1 \right\} }
\newcommand{\bds}[1]{\boldsymbol{ #1 }}
\newcommand{\oiint}{\displaystyle\bigcirc\!\!\!\!\!\!\!\!\int\!\!\!\!\!\int}
\newcommand{\mathsize}[2]{\mbox{\fontsize{#1}{#1}\selectfont $#2$}}
\newcommand{\eq}[2]{\begin{equation} \label{eq:#1} #2 \end{equation}}
\newcommand{\lth}{$\lambda_{th}$ }
\newcommand{\reff}{{\ifmmode{r_{\mbox{\tiny eff}}}\else{$r_{\mbox{\tiny eff}}$}\fi}}
%#########################################################################

%TO DO COMMANDS. Highlight region that needs extra work  #############################################################
\newcommand{\todo}{\ifmmode \text{\Huge{\(\bullet\)}} \else {\Huge$\bullet$}\fi}
% \newcommand{\todo}{\ifmmode {\Huge \bullet} \else {\Huge$\bullet$}\fi}
\newcommand{\tido}{\ifmmode {\bullet} \else $\bullet$\fi}
\newcommand{\REFS}{(\todo REFS) }
\newcommand{\toref}{(\todo REFS)}
%#########################################################################

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Satellite allignments in galaxy pairs in the Illustris Simulation}
\author{
  Ver\'onica Arias \thanks{v.arias@uniandes.edu.co}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

\affil{
$^1$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
}

\begin{abstract}
Alineaciones.
\end{abstract}

\keywords{
Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
--- Dark Matter --- Methods: numerical 
}

\section{Introduction}

Observational evidence of planes is everywhere (where we can see them). MW, M31, Centaurus A.\\

Not so evident in simulations:\\

Millenium II Baumgardt, Ibata, Pawlowski\\

Clues Gillet está pero diferente\\

Plane claims:\\
Libeskind: preferential direction for accretion.\\
Sawala: planes are there when baryonic physics is included.\\
Buck: planes are easy to form at early times, when DM filaments are very thin. In high redshift galaxies galaxies, planes are everywhere.\\

Other explanations: Kroupa: tidal dwarfs\\
Fouquet\\

Following a bit on the claim by Sawala that barionic physics are important when looking for planes, WE look in Illustris and Elvis simulations to try and understand why barionic physics results in planar distribution of satellites.

\section{Sample Selection}

\begin{figure}
\centering
\includegraphics[width=\hsize]{v_r_pairs.pdf}\\
\caption{Halo pair samples used in this paper located in the
  plane of relative comoving velocity $V_{AB}$ versus relative
  distance $R_{AB}$ between the two halos in the pair.
  The R\&V sample is the closest to the separation and kinematic
  conditions observed in the Local Group.} 
\label{fig:samples}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\hsize]{v_circ_pairs.pdf}\\
\caption{Diference between the maximum circular velocity $V_{max}$ for the two
  halos in the pair as a function of $V_{max}$ for the massive halo in
  the pair.}
\label{fig:vcirc}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\hsize]{n_structure.pdf}\\
\caption{Number of bright substructures ($M_{B}<-9$) as a function of
  the number of dark substructures around the pair's sphere of influence.}
\label{fig:nstructure}
\end{figure}

\section{Method}
\label{Method}

\section{Results}
\label{Results}
\begin{figure}
\centering
\includegraphics[width=\hsize]{AxisRatio_RandomMean_VS_Luminous.pdf}\\
\caption{.}
\label{fig:StreamPlaneOrbit}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=\hsize]{Halo_pos_LRomulusRemus.pdf}\\
%\end{figure}

\section{Discussion} 
\section{Acknowledgements}
Gracias.
\bibliographystyle{apj}
\bibliography{Dwarfs}

\end{document}

### 2016-05-04 paper/ms.tex
new plot

@@
 \includegraphics[width=\hsize]{n_structure.pdf}\\
-\caption{Number of bright substructures ($M_{B}<-9$) as a function of
-  the number of dark substructures around the pair's sphere of influence.}
+\caption{Number of bright substructures ($M_{B}<-9$) and dark matter
+  substructures.}
 \label{fig:nstructure}
@@
 \centering
-\includegraphics[width=\hsize]{AxisRatio_RandomMean_VS_Luminous.pdf}\\
-\caption{.}
+\includegraphics[width=\hsize]{axratio_dark_bright.pdf}\\
+\caption{Axis ratio of luminous satellites versus the axis ratio for
+  dark subhalos.}
 \label{fig:StreamPlaneOrbit}

### 2016-05-06 paper/ms.tex
title
new plots in draft
new plots in paper

@@
 %=========================================================================
-\title{Satellite allignments in galaxy pairs in the Illustris Simulation}
+\title{Local Group Satellite Alignments in a Cosmological Context: Insights from the Illustris Simulation}
 \author{
@@
 
-\section{Method}
-\label{Method}
-
-\section{Results}
-\label{Results}
 \begin{figure}
@@
 \end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.48\hsize]{significance_full_dark.pdf}
+\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}\\
+\includegraphics[width=0.48\hsize]{significance_lg_dark.pdf}
+\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}\\
+\caption{Significance of alignments.}
+\label{fig:significance}
+\end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=\hsize]{r_u_alignment.pdf}\\
+\caption{Alignment of the mayor axis with the vector connecting the
+  two halos.}
+\label{fig:lg_alignment}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\hsize]{plane_width.pdf}\\
+\caption{Plane width for the best planes in the luminious and dark cases.}
+\label{fig:plane_width}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\hsize]{plane_width_n_dark.pdf}\\
+\caption{Plane width as a function of objects used to find the plane.}
+\label{fig:plane_width_nobjects}
+\end{figure}
+
+\section{Results}
+\label{Results}
+
+\section{Method}
+\label{Method}
 

### 2016-05-12 refs/ReviewPapers.tex
papers review version 1

\documentclass{article}
\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{2.0in}
%\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-1.0in}
%\addtolength{\textheight}{1.80in}
\addtolength{\textheight}{1.95in}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{sidecap}
\usepackage[pdftex]{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\decimalpoint

\begin{document}
\section{Evidencias observacionales de planos:}
\noindent The VPOS (Pawlowski et al 2012: https://arxiv.org/abs/1204.5176)\\
A vast thin plane of corrotating dwarf galaxies orbiting the Andromeda
Galaxy (Ibata et al 2013)\\
Corotation in SDSS data (Ibata et al 2014)\\
There was a reply to this paper (A new spin on disks of satellite
galaxies, Cuatun et al 2014)\\
Planes in Centaurus A (Tully et al 2015)\\
Varios papers de pawlowski que muestran que los nuevos sat\'elites de
MW estan en el plano, que el plano no se debe al Sdss footprint, que
los globular clusters tambien estan en el plano... etc,\\ 
Papers de Conn donde encuentra el plano\\

\section{B\'usqueda de planos en simulaciones:}
\noindent A comparison of the distribution of satellite galaxies
around Andromeda and the results of $\Lambda$CDM simulations (Bahl and
Baumgardt 2013) Encuentran planos en Millenium II.\\
A thousand shadows of Andromeda: rotating planes of satellites in the
Millennium-II cosmological simulation (Ibata et al 2013) dicen que el
paper de Bahl y Baumgardt est\'a mal y que no hay planos en millenium
II\\
Co-orbiting satellite galaxy structures are still in conflict with the
distribution of primordial dwarf galaxies (Pawlowski et al 2014)\\
Co-orbiting planes of sub-halos are similarly unlikely around paired
and isolated hosts (Pawlowski et al 2014)\\
Vast planes of satellites in a high resolution simulation of the Local
Group: comparison to Andromeda (Gillet et al 2014). finds a plnes
similar to that of M31 in Clues simulations.\\
Planes of satellite galaxies: when exceptions are the rule (Cautun et
al 2015) encuentra que 10 por ciento de los halos tienen planos
iguales o m\'as prominentes que los del LG.\\

\section{Posibles or\'igenes de los planos:}
\noindent Preferential accretion (Libeskind et al 20??)\\
Alignments with the cosmic web (Tempel et al 20??)\\
The vast thin plane of M31 co-rotating dwarfs: an additional fossil
signature of the M31 merger and of its considerable impact in the
whole Local Group (Hammer et al 2013) Major merger in M31-MW system
plane galaxies are tidal dwarfs (n-body simulations)\\
Kroupa tiene todo un carretazo de que las dwarfs son todas tidal
dwarfs\\
MIRAR lo que est\'a haciendo Pierre Alan Duc con tidal dwrafs porque en
una conferencia este a;o habl\'o de un posible escenario
intermedio...\\
Evidence for Early Filamentary Accretion from the Andromeda Galaxy's
Thin Plane of Satellites (Buck et al 2015)\\
Alignments between galaxies, satellite systems and haloes (Cautun et al
2016) NO LO HE LEIDO...

\section{Problemas con esas explicaciones:}
The Vast Polar Structure of the Milky Way and Filamentary Accretion of
Sub-Halos (Pawlowski et al 2012)\\
Paper de Collins (2013 y 2016) donde explica que no hay doferencias en
las propiedades de los on-plane y los off-plane satellites\\
Problemas con la estabilidad a largo plazo de los planos: Bowden et al
2012, Gonzales et al 2015...\\
The Plane Truth: Andromeda analog thin Planes of Satellites are not
kinematical coherent structures (Buck et al 2015)\\

\end{document}

### 2016-05-21 paper/ms.tex
new title
updated notebook and ms
ms
paper introduction: first part

@@
 %=========================================================================
-\title{Local Group Satellite Alignments in a Cosmological Context: Insights from the Illustris Simulation}
+\title{Satellite Alignments in Galaxy Pairs}
 \author{
@@
 
-Observational evidence of planes is everywhere (where we can see them). MW, M31, Centaurus A.\\
+%
+%Observational evidence of planes is everywhere (where we can see them). MW, M31, Centaurus A.\\
+%
+%Not so evident in simulations:\\
+%
+%Millenium II Baumgardt, Ibata, Pawlowski\\
+%
+%Clues Gillet está pero diferente\\
+%
+%Plane claims:\\
+%Libeskind: preferential direction for accretion.\\
+%Sawala: planes are there when baryonic physics is included.\\
+%Buck: planes are easy to form at early times, when DM filaments are very thin. In high redshift galaxies galaxies, planes are everywhere.\\
+%
+%Other explanations: Kroupa: tidal dwarfs\\
+%Fouquet\\
+%
+%
+%
+% 
+%Following a bit on the claim by Sawala that barionic physics are important when looking for planes, WE look in Illustris and Elvis simulations to try and understand why barionic physics results in planar distribution of satellites.
 
-Not so evident in simulations:\\
+%\subsection{Evidencias observacionales de planos:}
+\noindent Since the early works of (el que libeskind dice que habló de
+eso primero) and Lynden-Bell (1976), the observed anisotropic
+distribution of satellite galaxies in the Local Group has been a key
+point in the discussion of galaxy formation models within $\Lambda$CDM
+cosmology. These pioneer papers described that the then known satellite
+galaxies of the Milky May (MW) were distributed roughly following the plane
+that contained the Magelanic clouds and their stellar tails. This
+anisotropic distribution was further studied in the work of Pawlowski
+et. al. (2012), where they included all the known MW satellite galaxies (XXX
+more than in the original Lynden-Bell paper) as well as some MW globular
+clusters, and found that they are all contained in what they call a
+"Vast Plane Of Satellites" (VPOS). This structure is around 30kpc thick and
+is perpendicular to the stellar disc of the MW galaxy. This plane of
+satellites was considered a rarity until the PAndAS survey of the
+Andromeda (M31) galaxy and its halo (missing reference on the survey)
+provided a complete sample of the satellite galaxy population (above a
+XXXX magnitude) of our neighboring galaxy, allowing their consistent distance
+estimations (Conn et al 2012). In a groundbreaking work, Ibata et.
+al. (2013) found that 15 out of the 30 satellites are in a planar
+structure that is 15kpc thick and has an extension of 400kpc.
+Additionally, from line of sight velocity measurements, they
+found that the structure has an apparent coherent rotation, with the
+satellites south of M31 moving away from us and those north of M31
+coming towards us. This apparent organized rotation of satellite galaxies was also
+statistically found to occur in diametrically opposed 
+pairs of satellites from the SDSS (Ibata et al 2014), although this
+results were contested in a follow up paper by Cuatun et al (2014).
 
-Millenium II Baumgardt, Ibata, Pawlowski\\
+These discoveries of the planes in M31 and the MW were followed by the
+remark from Shaya et al (2013) that the other satellite galaxies in
+M31 could be part of a second plane, further reinforcing the idea that
+satellites in the local group are not isotropically distributed.
+Despite the challenges in estimating distances to the satellites
+galaxies, Tully et al. managed to go beyond the local group and found
+two planes of satellites galaxies in Centaurus A, making a clearer
+case for the planes of satellites>in all the galaxies where distance
+measurements could be performed evidence of satellite planar
+structures have been found.\\
 
-Clues Gillet está pero diferente\\
+These observed planes present a challenge for current galaxy formation
+models (Pawlowski et. al 2014)
 
-Plane claims:\\
-Libeskind: preferential direction for accretion.\\
-Sawala: planes are there when baryonic physics is included.\\
-Buck: planes are easy to form at early times, when DM filaments are very thin. In high redshift galaxies galaxies, planes are everywhere.\\
+%The VPOS (Pawlowski et al 2012: https://arxiv.org/abs/1204.5176)\\
+%A vast thin plane of corrotating dwarf galaxies orbiting the Andromeda
+%Galaxy (Ibata et al 2013)\\
+%Corotation in SDSS data (Ibata et al 2014)\\
+%There was a reply to this paper (A new spin on disks of satellite
+%galaxies, Cuatun et al 2014)\\
+    %Planes in Centaurus A (Tully et al 2015)\
+%paper con los dos planos MW yM31
+%>https://arxiv.org/pdf/1307.6210v1.pdf
+\
+%Varios papers de pawlowski que muestran que los nuevos sat\'elites de
+%MW estan en el plano, que el plano no se debe al Sdss footprint, que
+%los globular clusters tambien estan en el plano... etc,\\ 
+%Papers de Conn donde encuentra el plano\\
 
-Other explanations: Kroupa: tidal dwarfs\\
-Fouquet\\
+%\subsection{B\'usqueda de planos en simulaciones:}
+\noindent A comparison of the distribution of satellite galaxies
+around Andromeda and the results of $\Lambda$CDM simulations (Bahl and
+Baumgardt 2013) Encuentran planos en Millenium II.\\
+A thousand shadows of Andromeda: rotating planes of satellites in the
+Millennium-II cosmological simulation (Ibata et al 2013) dicen que el
+paper de Bahl y Baumgardt est\'a mal y que no hay planos en millenium
+II\\
+Co-orbiting satellite galaxy structures are still in conflict with the
+distribution of primordial dwarf galaxies (Pawlowski et al 2014)\\
+Co-orbiting planes of sub-halos are similarly unlikely around paired
+and isolated hosts (Pawlowski et al 2014)\\
+Vast planes of satellites in a high resolution simulation of the Local
+Group: comparison to Andromeda (Gillet et al 2014). finds a plnes
+similar to that of M31 in Clues simulations.\\
+Planes of satellite galaxies: when exceptions are the rule (Cautun et
+al 2015) encuentra que 10 por ciento de los halos tienen planos
+iguales o m\'as prominentes que los del LG.\\
 
-Following a bit on the claim by Sawala that barionic physics are important when looking for planes, WE look in Illustris and Elvis simulations to try and understand why barionic physics results in planar distribution of satellites.
+\subsection{Posibles or\'igenes de los planos:}
+\noindent Preferential accretion (Libeskind et al 20??)\\
+Alignments with the cosmic web (Tempel et al 20??)\\
+The vast thin plane of M31 co-rotating dwarfs: an additional fossil
+signature of the M31 merger and of its considerable impact in the
+whole Local Group (Hammer et al 2013) Major merger in M31-MW system
+plane galaxies are tidal dwarfs (n-body simulations)\\
+Kroupa tiene todo un carretazo de que las dwarfs son todas tidal
+dwarfs\\
+MIRAR lo que est\'a haciendo Pierre Alan Duc con tidal dwrafs porque en
+una conferencia este a;o habl\'o de un posible escenario
+intermedio...\\
+Evidence for Early Filamentary Accretion from the Andromeda Galaxy's
+Thin Plane of Satellites (Buck et al 2015)\\
+Alignments between galaxies, satellite systems and haloes (Cautun et al
+2016) NO LO HE LEIDO...
+
+\subsection{Problemas con esas explicaciones:}
+The Vast Polar Structure of the Milky Way and Filamentary Accretion of
+Sub-Halos (Pawlowski et al 2012)\\
+Paper de Collins (2013 y 2016) donde explica que no hay doferencias en
+las propiedades de los on-plane y los off-plane satellites\\
+Problemas con la estabilidad a largo plazo de los planos: Bowden et al
+2012, Gonzales et al 2015...\\
+The Plane Truth: Andromeda analog thin Planes of Satellites are not
+kinematical coherent structures (Buck et al 2015)\\
+
+\section{Illustris simulation}
 
 \section{Sample Selection}
+
+General Pair Sample.
+
+Reduced sample based on non interacting halos. Further sub-selection based on number of bright substructures.
+
+Reduced Local Group sample based on kinematic characteristics.
 
@@
 \centering
-\includegraphics[width=0.48\hsize]{significance_full_dark.pdf}
-\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}\\
-\includegraphics[width=0.48\hsize]{significance_lg_dark.pdf}
-\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}\\
+\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}
+\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}
 \caption{Significance of alignments.}

### 2016-05-23 paper/ms.tex
general sample

@@
 
-General Pair Sample.
+We select all halos with maximum circular velocities in the
+range 150 km s$^{-1}$ $<V_{\rm max}<$ 350 km s$^{1}$.
+We exclude sub-halos from this selection.
+From this set we construct a sample of pairs as follows.
+For each halo $A$ we find its closest halo $B$, if halo $A$ is also
+the closest to halo $B$, the two halos are considered as a pair. 
+Another way to phrase this selection is that pairs do not have
+neighbors closer than the pair's distance.
+There are $53$ pairs with those conditions in the simulation.
 
-Reduced sample based on non interacting halos. Further sub-selection based on number of bright substructures.
+We extract from the simulation spheres of $2$
+
+Reduced sample based on non interacting halos. Further sub-selection
+based on number of bright substructures.
 

### 2016-05-23 paper/ms.tex
samples

@@
 neighbors closer than the pair's distance.
+We exclude the pairs that are closer thn
 There are $53$ pairs with those conditions in the simulation.
 
-We extract from the simulation spheres of $2$
+We extract from the simulation spheres of $2$ \hMpc in radius around
+the pair's center of mass. 
+We use this information to exclude all the pairs that inc
+
+in this
+spherical volume a with a circular larger than $150$ km s$^{1}$. 
+This further reduces the sample to $49$ pairs
 

### 2016-05-24 paper/ms.tex
seleccion de la muestra

@@
 the pair's center of mass. 
-We use this information to exclude all the pairs that inc
+We use this information to exclude all the pairs that have separations
+smaller than the sum  of their virial radii, i.e. we exclude
+interacting pairs. 
+This reduces to $49$ the number of pairs in the sample.
 
-in this
-spherical volume a with a circular larger than $150$ km s$^{1}$. 
-This further reduces the sample to $49$ pairs
+We count the number of galaxies with $M_V<-9$ inside the virial
+radius of each halo, including the central galaxy.
+We only keep pairs where both halos have 5 bright galaxies at least. 
+This reduces the sample to $24$ pairs. 
+We call this sample the Full  Sample.
 
-Reduced sample based on non interacting halos. Further sub-selection
-based on number of bright substructures.
+From the Full Sample we build a second sample based on the pairs' kinematics. 
+Figure \ref{fig:samples} shows the comoving separation and relative
+speed between the two halos in the pair.
+The stars in the Figure represent the pairs with a separation in the
+range $0.75\hMpc <R_{AB}< 1.50\hMpc$ and relative velocity in the
+range $V_{AB}>100$ km s$^{-1}$, which are close to the Local Group
+Observed values.
+We call this sample the LG Sample.
 
-Reduced Local Group sample based on kinematic characteristics.
+The number of pairs in the Full Sample is consistent with previous
+calculations. 
+\cite{ForeroRomero2013} performed a study of the LG kinematics using a
+cosmological N-body simulation as a benchmark. 
+In their study, using criteria similar to ours to define the Full
+Sample, they found 1923 pairs in a volume of $250^3$ $h^{-3}$
+Mpc$^{3}$. 
+With the same number density we expect to find $52$ pairs in the
+volume of the Illustris simulation, which is very close to the actual
+number of $49$ pairs.
+
+In the same study they found 158 pairs with broad kinematic
+caracteristics, similar to the definition of our LG sample. 
+This represents a reduction of a factor of $12$ from their General
+Sample. 
+With those numbers in mind we would expect to keep at least $4$ pairs
+in the Illustris volume. 
+Given that our conditions are slightly more relaxed (we do not ask for
+isolation criteria from massive halos) we end up with a larger sample
+size, but still consistent with the fact that LG-like pairs are
+scarce.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\hsize]{v_circ_pairs.pdf}\\
-\caption{Diference between the maximum circular velocity $V_{max}$ for the two
-  halos in the pair as a function of $V_{max}$ for the massive halo in
-  the pair.}
-\label{fig:vcirc}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=\hsize]{v_circ_pairs.pdf}\\
+%\caption{Diference between the maximum circular velocity $V_{max}$ for the two
+%  halos in the pair as a function of $V_{max}$ for the massive halo in
+%  the pair.}
+%\label{fig:vcirc}
+%\end{figure}
 

### 2016-06-01 paper/ms.tex
sim papers

@@
 XXXX magnitude) of our neighboring galaxy, allowing their consistent distance
-estimations (Conn et al 2012). In a groundbreaking work, Ibata et.
+estimations (Conn et al. 2012). In a groundbreaking work, Ibata et
 al. (2013) found that 15 out of the 30 satellites are in a planar
@@
 statistically found to occur in diametrically opposed 
-pairs of satellites from the SDSS (Ibata et al 2014), although this
-results were contested in a follow up paper by Cuatun et al (2014).
+pairs of satellites from the SDSS (Ibata et al. 2014), although this
+results were contested in a follow up paper by Cuatun et al. (2014).
 
 These discoveries of the planes in M31 and the MW were followed by the
-remark from Shaya et al (2013) that the other satellite galaxies in
+remark from Shaya et al. (2013) that the other satellite galaxies in
 M31 could be part of a second plane, further reinforcing the idea that
@@
 two planes of satellites galaxies in Centaurus A, making a clearer
-case for the planes of satellites>in all the galaxies where distance
+case for the planes of satellites: in all the galaxies where distance
 measurements could be performed evidence of satellite planar
@@
 These observed planes present a challenge for current galaxy formation
-models (Pawlowski et. al 2014)
+models (Pawlowski et al. 2014)
 
@@
 neighbors closer than the pair's distance.
-We exclude the pairs that are closer thn
+We exclude the pairs that are closer than
 There are $53$ pairs with those conditions in the simulation.
@@
 From the Full Sample we build a second sample based on the pairs' kinematics. 
-Figure \ref{fig:samples} shows the comoving separation and relative
+Figure \ref{fig:samples} shows the co-moving separation and relative
 speed between the two halos in the pair.
@@
 In the same study they found 158 pairs with broad kinematic
-caracteristics, similar to the definition of our LG sample. 
+characteristics, similar to the definition of our LG sample. 
 This represents a reduction of a factor of $12$ from their General
@@
 Gracias.
+
+%\begin{wraptable}{l}{2\linewidth}
+%\centering
+%\begin{tabular}{|l|l|l|l|l|l|}
+%\hline
+%Bahl 2013       & MilleniumII & resolution & number of host halos& gas no        & planes yes? \\\hline
+%Ibata 2014      & MilleniumII & resolution & number of host halos& gas no        & planes no? \\\hline
+%Pawlowski 2015  & MilleniumII & resolution & number of host halos& gas no        & planes no? \\\hline
+%Gillet 2015     & CLUES       & resolution & number of host halos& gas yes and no& planes yes \\\hline
+%Cautun 201XXX   & ?           & resolution & number of host halos& gas ??????    & planes yes \\\hline
+%Buck            & their own   & resolution & number of host halos& gas no?       & planes yes \\\hline
+%Sawala          & Apostole?   & resolution & number of host halos& gas yes?      & planes yes \\\hline
+%Gonzalez        & their own?  & resolution & number of host halos& gas yes/no    & planes he does not care \\\hline
+%\end{tabular}
+%\end{wraptable}
+
+Simulation papers:
+\begin{itemize}
+\item{Bahl and Baumgardt 2013 "A comparison of the distribution (...)":\\
+MilleniumII and a semi-analytic model\\
+Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+PAndAS like field\\
+With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
+Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
+Conclusion: M31 like planes are not uncommon in MilleniumII simulations.
+Co-rotating structures are not stable structures.
+Plane of M31 could be a statistical fluctuation in an otherwise more spherical distribution.\\
+Simulation: Millenium II ()\\
+Gas: NO\\
+Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+Number of host halos: 1511 with orphan galaxies, 112 excluding orphan galaxies (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$), younger that 10 Gyr and satelites smaller than 7$\times 10^{10} M\odot$\\
+Planes: yes (40$\%$ with orphan galaxies 2$\%$ without)\\
+co-rotation: yes (in 2$\%$ of the halos ???)\\
+Stable: No\\
+Note: PAndAS data has satellites with baryonic masses down to 2.9$\times 10^{4} M\odot$ and they take that as a lower limit for their data.\\
+}
+\item{Ibata et al 2014 "A thousand shadows (...)":\\
+MilleniumII and a semi-analytic model (Guo)\\
+%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+Same analysis as in PAndAS data\\
+%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
+%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
+Conclusion: M31 like planes are NOT common in MilleniumII simulations.\\
+Simulation: Millenium II ()\\
+Gas: NO\\
+Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+Number of host halos: 679 (I assume with orphan galaxies) (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
+Planes: no (with orphan galaxies only 0.04$\%$ of the system fulfill the thinness, extension and co-rotation criteria, and NONE does if orphans are not included.
+If co-rotation is not included then $2\%$ fulfill the thinness and extension criteria)\\
+co-rotation: only 0.04$\%$ with orphans and NONE without orphans\\
+Note: they use the 679 host halos and study them from different viewing angles\\
+}
+\item{Pawlowski et al 2014 "Co-orbitingsatellite galaxy structures are still in conflict with (...)":\\
+MilleniumII and a semi-analytic model (Guo)\\
+%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+Same analysis as in PAndAS data\\
+Same analysis as in Wang et al. 2013\\
+%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
+%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
+Conclusion: M31 and MW like planes are NOT common in MilleniumII simulations.\\
+Simulation: Millenium II ()\\
+Gas: NO\\
+Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+Number of host halos:  1825 (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
+Planes: no (M31: 0.09$\%$ fulfill the thinness, extension and co-rotation criteria. MW: 0.2$\%$)\\
+Note: they use the host halos and study them from different viewing angles so they end up with 15000 samples.
+They always consider orphan galaxies for comparison purposes.
+For one test they randomize the sample and find M31 like planes in only 0.002 per cent of the cases and MW like planes in 0.06$\%$ of the cases.\\
+MIRAR Wang et al. 2013 que busca MWlike planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos
+}
+\item{Cautun et al. 2015 "Planes of satellite galaxies: when exceptions are the rule":\\
+MilleniumII and a semi-analytic model (Guo 2013)\\
+CoCo and a semi-analytic model (Guo 2015)\\
+%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+Conclusion: planar structures are very common in $\Lambda$CDM (10$\%$)\\
+Simulation 1: Millenium IIi rescaled to WMAP\\
+Simulation 2: CoCo (Higher resolution than MilleniumII)\\
+Gas: NO\\
+Resolution 1: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+Number of host halos:  2849 (MilleniumII) and 63 8COCO halos) (selection criteria: "we adopted a broader mass range to account for the large uncertainty in the mass measurements and also for possible systematic effects").\\
+Resolution 2: sub-halos $\approx$ 2$\times 10^6 M\odot$ (75 times higher mass resolution
+and four times better spatial resolution)\\
+Planes: yes (10$\%$)\\
+Note: They found a great variety of plane and the M31 plane lies in general within the scatter of the simulated planes however it seem to have an "unusually large radial extent".\\
+Note 2: they find that each halos has a different planar configuration showing that the low incidence of the M31 plane is not in contradiction with simulations.
+This contradicts the Pawlowski et al.
+2014 conclusions}
+\end{itemize}
+
 \bibliographystyle{apj}

### 2016-06-10 paper/ms.tex
papers de libeskind

@@
 
+\citep{2011MNRAS.411.1525L} Measure the infall direction of satellites
+in a DM only simulation of one pair of LG halos in a constrained
+simulation. There is a definite infall direction but it's not
+quantified in terms of the cosmic web.
+
+\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
+with respect to the V-web. They do it in a DM cosmological simulation
+(64 Mpch, 1024 3 particles). They find that infall is done along the
+e3 (i.e. filament) direction.
+
+\citep{2015MNRAS.450.2727T} They measure the angle between satellites
+and the direction defined by filaments (Bissous filament finder )to
+find a signal both in SDSS and the semi-analytic galaxies in the
+Millennium Simulation.
+
+\citep{2015ApJ...799..212L} Detection of alignment of satellites along
+the direction defined by filaments (velocity shear cosmic web) on the
+SDSS DR7.
+
+@ARTICLE{2014MNRAS.443.1274L,
+   author = {{Libeskind}, N.~I. and {Knebe}, A. and {Hoffman}, Y. and {Gottl{\"o}ber}, S.
+	},
+    title = "{The universal nature of subhalo accretion}",
+  journal = {\mnras},
+archivePrefix = "arXiv",
+   eprint = {1407.0394},
+ keywords = {galaxies: haloes, cosmology: theory, dark matter, large-scale structure of Universe},
+     year = 2014,
+    month = sep,
+   volume = 443,
+    pages = {1274-1280},
+      doi = {10.1093/mnras/stu1216},
+   adsurl = {http://adsabs.harvard.edu/abs/2014MNRAS.443.1274L},
+  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
+}
+
 \begin{figure}

### 2016-06-10 paper/ms.tex
remove bibtex info from ms

@@
 
-@ARTICLE{2014MNRAS.443.1274L,
-   author = {{Libeskind}, N.~I. and {Knebe}, A. and {Hoffman}, Y. and {Gottl{\"o}ber}, S.
-	},
-    title = "{The universal nature of subhalo accretion}",
-  journal = {\mnras},
-archivePrefix = "arXiv",
-   eprint = {1407.0394},
- keywords = {galaxies: haloes, cosmology: theory, dark matter, large-scale structure of Universe},
-     year = 2014,
-    month = sep,
-   volume = 443,
-    pages = {1274-1280},
-      doi = {10.1093/mnras/stu1216},
-   adsurl = {http://adsabs.harvard.edu/abs/2014MNRAS.443.1274L},
-  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
-}
-
 \begin{figure}

### 2016-06-10 paper/ms.tex
some more references

@@
 
+\citep{2012MNRAS.424...80P} Compare the kinematic structure of the MW
+satellites against DM only simulation of high resolutions halos from
+the Via Lactea and Aquarius projects.  Cannot find a similar kinematic
+structure (i.e. the orbital poles of the MW satellites) in the
+simulations.
+
 \citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
@@
 SDSS DR7.
+
+\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
+spatial anisotropy the 11 brightest satellites. THe anisotropy is
+quantified the reduced inertia tensor. Still the MW is more
+anisotropic than all but one of the 24 halos. The analysis is not very
+thorough and do not show the resulting distribution. Does not compare
+the results of using DM information only.
+
+\citep{2015ApJ...815...19P} argue that the result from
+\citep{2016MNRAS.457.1931S} is a produc of using a metric that ignores
+the radial position of the galaxies. They use the ELVIS suite to
+compare the two analysis methods: reduced vs. full inertia tensor.
+
+\citep{2016arXiv160501728S} Use the eagle simulation to study the
+alignment of satellites with respect to the central galaxy. They find
+a weak alignment. Around $20\%$ of the systems have a misalignment
+angle larger than the value observed for the Milky Way. They do not
+study DM only simulations and do not narrow down the signal to pairs.
+
+\citep{2016arXiv160601516L} Using SDSS DR10 studied galaxy pairs. They find
+that satellites tend to accumulate towards the companion galaxy. There
+are up to $\sim 10\%$ more satellites in the space between the pair
+than expected from an uniform distribution
 

### 2016-06-12 paper/ms.tex
updated tex
cosmic web description

@@
 %=========================================================================
-\title{Satellite Alignments in Galaxy Pairs}
+\title{The Spatial Distribution of Local Group Satellites in a
+  Cosmological Context}  
 \author{
@@
 \begin{abstract}
-Alineaciones.
+We focus on the spatial distribution of bright ($M_V<-8$) satellites and
+pairs of galaxies with similar masses, isolation and kinematic
+configurations as the Local Group. 
 \end{abstract}
@@
 
-\section{Illustris simulation}
+\subsection{Previous studies of Local Group satellites}
 
-\section{Sample Selection}
+\citep{2011MNRAS.411.1525L} Measure the infall direction of satellites
+in a DM only simulation of one pair of LG halos in a constrained
+simulation. There is a definite infall direction but it's not
+quantified in terms of the cosmic web.
+
+\citep{2012MNRAS.424...80P} Compare the kinematic structure of the MW
+satellites against DM only simulation of high resolutions halos from
+the Via Lactea and Aquarius projects.  Cannot find a similar kinematic
+structure (i.e. the orbital poles of the MW satellites) in the
+simulations.
+
+\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
+with respect to the V-web. They do it in a DM cosmological simulation
+(64 Mpch, 1024 3 particles). They find that infall is done along the
+e3 (i.e. filament) direction.
+
+\citep{2015MNRAS.450.2727T} They measure the angle between satellites
+and the direction defined by filaments (Bissous filament finder )to
+find a signal both in SDSS and the semi-analytic galaxies in the
+Millennium Simulation.
+
+\citep{2015ApJ...799..212L} Detection of alignment of satellites along
+the direction defined by filaments (velocity shear cosmic web) on the
+SDSS DR7.
+
+\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
+spatial anisotropy the 11 brightest satellites. THe anisotropy is
+quantified the reduced inertia tensor. Still the MW is more
+anisotropic than all but one of the 24 halos. The analysis is not very
+thorough and do not show the resulting distribution. Does not compare
+the results of using DM information only.
+
+\citep{2015ApJ...815...19P} argue that the result from
+\citep{2016MNRAS.457.1931S} is a produc of using a metric that ignores
+the radial position of the galaxies. They use the ELVIS suite to
+compare the two analysis methods: reduced vs. full inertia tensor.
+
+\citep{2016arXiv160501728S} Use the eagle simulation to study the
+alignment of satellites with respect to the central galaxy. They find
+a weak alignment. Around $20\%$ of the systems have a misalignment
+angle larger than the value observed for the Milky Way. They do not
+study DM only simulations and do not narrow down the signal to pairs.
+
+\citep{2016arXiv160601516L} Using SDSS DR10 studied galaxy pairs. They find
+that satellites tend to accumulate towards the companion galaxy. There
+are up to $\sim 10\%$ more satellites in the space between the pair
+than expected from an uniform distribution
+
+\section{Numerical Setup}
+
+\subsection{Illustris simulation}
+
+\subsection{Sample Selection}
 
@@
 
-\citep{2011MNRAS.411.1525L} Measure the infall direction of satellites
-in a DM only simulation of one pair of LG halos in a constrained
-simulation. There is a definite infall direction but it's not
-quantified in terms of the cosmic web.
-
-\citep{2012MNRAS.424...80P} Compare the kinematic structure of the MW
-satellites against DM only simulation of high resolutions halos from
-the Via Lactea and Aquarius projects.  Cannot find a similar kinematic
-structure (i.e. the orbital poles of the MW satellites) in the
-simulations.
-
-\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
-with respect to the V-web. They do it in a DM cosmological simulation
-(64 Mpch, 1024 3 particles). They find that infall is done along the
-e3 (i.e. filament) direction.
-
-\citep{2015MNRAS.450.2727T} They measure the angle between satellites
-and the direction defined by filaments (Bissous filament finder )to
-find a signal both in SDSS and the semi-analytic galaxies in the
-Millennium Simulation.
-
-\citep{2015ApJ...799..212L} Detection of alignment of satellites along
-the direction defined by filaments (velocity shear cosmic web) on the
-SDSS DR7.
-
-\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
-spatial anisotropy the 11 brightest satellites. THe anisotropy is
-quantified the reduced inertia tensor. Still the MW is more
-anisotropic than all but one of the 24 halos. The analysis is not very
-thorough and do not show the resulting distribution. Does not compare
-the results of using DM information only.
-
-\citep{2015ApJ...815...19P} argue that the result from
-\citep{2016MNRAS.457.1931S} is a produc of using a metric that ignores
-the radial position of the galaxies. They use the ELVIS suite to
-compare the two analysis methods: reduced vs. full inertia tensor.
-
-\citep{2016arXiv160501728S} Use the eagle simulation to study the
-alignment of satellites with respect to the central galaxy. They find
-a weak alignment. Around $20\%$ of the systems have a misalignment
-angle larger than the value observed for the Milky Way. They do not
-study DM only simulations and do not narrow down the signal to pairs.
-
-\citep{2016arXiv160601516L} Using SDSS DR10 studied galaxy pairs. They find
-that satellites tend to accumulate towards the companion galaxy. There
-are up to $\sim 10\%$ more satellites in the space between the pair
-than expected from an uniform distribution
-
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Cosmic Web environment}
+
+We place the pairs in our sample into the cosmic web as quantified by
+the deformation tensor.
+\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
+This method computes a cartesian grid the tensor $T_{ij}$,
+\begin{equation}
+T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j}
+\end{equation}
+%
+where $\phi$ is a pseudo-gravitational potential that follows the
+Poisson equation $\nabla^2\phi=-\delta$ and the $r_i$ coordinates
+correspond to a cartesian system with $i=1,2,3$.
+
+This tensor is and symmetric and can be diagonalized.
+Its eigenvalues ($\lambda_1 > \lambda_2 > \lambda_3$) and
+corresponding eigenvectors ($\hat{e}_1$, $\hat{e}_2$, $\hat{e}_3$)
+define the degree and direction of stability around the neighborhood
+where the tensor was computed. 
+This allows the classification of that region either as a peak,
+filaments, sheets and voids in the case of three, two, one or zero
+eigenvalues larger than a given threshold $\lambda_{th}$.
+
+In this study we compute these eigenvalues and eigenvectors over the
+dark matter component of the Illustris-3 simulation on a cubic mesh of
+$74$ cells on a side. 
+This resolution corresponds to $\sim 1$ Mpc h.
+We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
+scheme. 
+We proceed to smooth the density field with a gaussian window with a
+physical scale equal to the cell size.
+
+We choose this interpolation and smoothing scale for two reasons.
+First, because it corresponds to the typical pair separation in our
+sample.
+Second, because it allows a direct comparison with other results in
+the literature that used the same methodology to quantify the cosmic
+web environment for Local Group pairs in a cosmological context
+\citep{ForeroRomero2013,2015ApJ...799...45F}.
 

### 2016-06-13 paper/ms.tex
mas referencias

@@
 Sub-Halos (Pawlowski et al 2012)\\
-Paper de Collins (2013 y 2016) donde explica que no hay doferencias en
+Paper de Collins (2013 y 2016) donde explica que no hay diferencias en
 las propiedades de los on-plane y los off-plane satellites\\
@@
 \citep{2015MNRAS.450.2727T} They measure the angle between satellites
-and the direction defined by filaments (Bissous filament finder )to
+and the direction defined by filaments (Bissous filament finder) to
 find a signal both in SDSS and the semi-analytic galaxies in the
@@
 \citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
-spatial anisotropy the 11 brightest satellites. THe anisotropy is
+spatial anisotropy the 11 brightest satellites. The anisotropy is
 quantified the reduced inertia tensor. Still the MW is more
@@
 2014 conclusions}
+
+\item{Sawala et al. 2014 "The chosen few: the low mass halos that host faint galaxies":\\
+Conclusion: Some "effects make dwarf galaxies highly biased
+tracers of the underlying dark matter distribution."\\
+Simulation: 12 cosmological volumes as zoom" simulations
+extracted from the Dove simulation. They require that each box has to
+have two halos (MW and M31 like)\\
+Gas: Yes (they also compare their results with DM only simulations)\\
+Resolution : sub-halos 1 $\times 10^7 M\odot$\\
+Number of host halos:  2 times 12 (pairs of galaxies).\\
+Planes: They do not look for them\\}
+
+\item{Libeskind et al. 2012 "The universal nature of subhalo accretion":\\
+Conclusion: "the preferential infall of subhaloes is effectively universal
+in the sense that its always aligned with the axis of weakest collapse
+of the velocity shear tensor. It is the same shear tensor that
+dictates the structure of the cosmic web and hence the shear field
+emerges as the key factor that governs the local anisotropic pattern
+of structure formation."\\
+Simulation:DM-only N-body simulation of 10243 particles in a
+64h$^{-1}$ Mpc box.\\
+Gas: NO\\
+Resolution : particle 1.89 $\times 10^7 h^{-1} M\odot$\\
+Resolution : halos 1$\times 10^9 h^{-1} M\odot$\\
+Number of host halos:  not mentioned.\\
+Planes: They do not look for them. They look and find preferential
+directions for accretion\\}
+
+\item{Libeskind et al. 2015 "Planes of satellite galaxies and the
+cosmic web":\\
+Conclusion:"The analysis reveals that the Local Group and Centaurus A
+reside in a filament stretched by the Virgo cluster and compressed by
+the expansion of the Local Void. Four out of five thin planes of
+satellite galaxies are indeed closely aligned with the axis of
+compression induced by the Local Void. (...) "\\ 
+Simulation: Observational paper uses the cosmic flow data set.\\
+Gas: No aplica\\
+\\}
+
+\item{Tempel et al. 2015 "The alignment of satellite galaxies and
+cosmic filaments: observations and simulations":\\
+Conclusion:"A statistically significant alignment between satellite
+galaxy position and filament axis in observations is confirmed. We
+find a qualitatively compatible alignments by examining satellites and
+filaments similarly identified in the Millennium simulation,
+semi-analytical galaxy catalogue. We also examine the dependence of
+the alignment strength on galaxy properties such as colour, magnitude
+and (relative) satellite magnitude, finding that the alignment is
+strongest for the reddest and brightest central and satellite
+galaxies. "\\ 
+Simulation: MilleniumII compared to Observational data (SDSS).\\
+Gas: No\\
+Alignments: yes both in simulations and in observations\\
+Note: they make a statistical analysis of alignments in projected
+data.}
+
+\item{Sawala et al. 2015 "The APOSTLE simulations: solutions to the
+Local Group's cosmic puzzles":\\
+Conclusion: "Applying the Eagle code to the LG environment, we find
+that our simulations match the observed abundance of LG galaxies,
+including the satellite galaxies of the MW and Andromeda. Due to
+changes to the structure of halos and the evolution in the LG
+environment, the simulations reproduce the observed relation between
+stellar mass and velocity dispersion of individual dwarf spheroidal
+galaxies without necessitating the formation of cores in their dark
+matter profiles. Satellite systems form with a range of spatial
+anisotropies, including one similar to that of the MW, confirming that
+such a configuration is not unexpected in $\Lambda$CDM"\\ 
+Simulation: They use the EAGLE code to simulate the Apostole set of
+simulations (a suite of cosmological hydro-
+dynamic simulations of twelve volumes selected to match the kinematics
+of the Local Group (LG) members).\\
+halo selection:In particular, we focus
+on pairs of halos that match the separation, approach
+velocity, and relative tangential velocity of the Milky Way
+(MW) and Andromeda (M31). From a large cosmological
+simulation, we have selected twelve pairs of halos with combined
+virial masses of  2.3$\pm$0.6$\times 10^{12}M_\odot$, compatible
+with the most recent dynamical constraints\\ 
+Resolution : re-simulated each LG volume at several resolutions,
+both as dark matter only (DMO) simulations, and
+as hydrodynamic simulations\\
+Gas: Yes (they also compare with DM only simulations)\\
+planes: yes (they find "anisotropic configurations: BUT not typical ")\\
+Note: they select MW-M31-like pairs, including kinematical
+constraints\\}
+
+\item{ Gillet et al. 2015: "Vast planes of satellites in a high resolution simulation of
+the Local Group: comparison to Andromeda":\\
+CLUES project and a semi-analytic model\\
+Conclusion: "The structure of the simulated satellite systems is
+strongly non-random and contains planes of satellites, predominantly
+co-rotating, with, in some cases, sizes comparable to the plane
+observed in M31 by Ibata et al.. However the latter is slightly richer
+in satellites, slightly thinner and has stronger co-rotation, which
+makes it stand out as overall more exceptional than the simulated
+planes, when compared to a random population" \\
+Simulation: CLUES\\
+Gas: NO\\
+Resolution : DM particle 2.1 $\times 10^5 h^{-1} M\odot$\\
+Resolution : gas particle 4.42 $\times 10^4 h^{-1} M\odot$\\
+Resolution : halos $4.2\times 10^6 h^{-1} M\odot$\\
+Number of host halos: 2 (one pair)\\
+Planes: yes\\
+co-rotation: kind of\\
+Stable: No\\
+note: they use 5 different methods to choose the satellites and 3
+different volumes.\\
+}
+
+\item{ Pawlowski et al. 2012: "Can filamentary accretion explain the
+orbital poles of the Milky Way satellites?":\\
+Aquarius and Via Lactea Simulations\\
+Conclusion: they find that the simulations cannot reproduce the
+angular momentum coherence of the satellites in the MW and that "this
+indicates that the formation as tidal dwarf galaxies in a single
+encounter is a viable, if not the only, process to explain the
+phase-space distribution of the MW satellite galaxies." \\
+Simulation: Aquarius and Via Lactea\\
+Gas: NO\\
+Resolution : ?\\
+Number of host halos: 8\\
+Planes: they look for alignments in the orbital poles and found none
+in the cosmological simulations\\
+co-rotation: no\\
+note: they compare what they find in simulations with an isotropic
+distribution and with merger scenarios.\\
+}
+
+\item{ Pawlowski et al. 2014: "Co-orbiting planes of sub-halos are
+similarly unlikely around paired and isolated hosts":\\
+They use the Elvis simulations to study the satellite population of
+paired vs isolated galaxies.\\
+Conclusion: The observed flattening and the observed orbital alignment
+are each reproduced by only 0.2 to 2 per cent of paired and isolated
+systems incorporating the obscuration of satellites by randomly
+oriented galactic discs.\\
+Simulation: Elvis\\
+Gas: NO\\
+Resolution : ?\\
+Number of host halos: 24 paired and 24 isolated host halos (4800
+analyzed realizations).\\
+Planes: 0.2 to 2 per cent\\
+co-rotation: 0.2 to 2 per cent\\
+note: co-rotation and alignments together are only observed in ONE of
+4800 realizations.\\
+}
 \end{itemize}

### 2016-06-13 paper/ms.tex
mas referencias 2

@@
 For one test they randomize the sample and find M31 like planes in only 0.002 per cent of the cases and MW like planes in 0.06$\%$ of the cases.\\
-MIRAR Wang et al. 2013 que busca MWlike planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos
+MIRAR Wang et al. 2013 que busca MW-like planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos
 }
@@
 }
+
+\item{Buck et al 2015 "EVIDENCE FOR EARLY FILAMENTARY ACCRETION FROM THE ANDROMEDA GALAXY'S THIN PLANE
+OF SATELLITES":\\
+They use zoom in cosmological simulations to study the possible formation of thin planes of satellite galaxies.\\
+Conclusion: "We show that it is possible to obtain a thin, extended, rotating plane of satellites resembling the one in
+Andromeda in cosmological collisionless simulations based on the Cold Dark Matter model. Our new
+high resolution simulations show a correlation between the formation time of the dark matter halo
+and the thickness of the plane of satellites." (...) "Our high resolution simulations show a correlation between the formation time of the dark matter halo
+and the thickness of the plane of satellites. Our simulations have a high incidence of satellite planes
+as thin, extended, and as rich as the one in Andromeda and with a very coherent kinematic structure
+when we select high concentration/early forming halos."\\
+Simulation: 21 high resolution "zoom-in" Dark Matter only simulations. Andromeda-mass haloes in the mass range
+(7,4$\times 10^{11} < M_{200}M_\odot < 2,2 \times 10^{12}$).\\
+Gas: NO\\
+Resolution : resolve substructure down to $10^7 h^{-1}M\odot$\\
+Number of host halos: 21\\
+Planes: yes\\
+co-rotation: yes\\
+note: \\
+}
+
+\item{Buck et al 2016 "Simulated $\Lambda$CDM analogues of the thin Plane of Satellites
+around the Andromeda galaxy are not kinematically
+coherent structures":\\
+They use zoom in cosmological simulation of high concentration haloes to study the dynamics of the satellite population.\\
+Conclusion: "Thus we conclude that the line-of-sight velocity is not well suited as a proxy for the kinematical coherence of the plane.
+Analysis of the kinematics of our planes shows a fraction of 30$\%$ chance aligned
+satellites. Tracking the satellites in the plane back in time reveals that these planes
+are a transient feature and not kinematically coherent as would appear at first sight.
+Thus we expect some of the satellites in the plane around Andromeda to have high
+velocities perpendicular to the plane."\\
+Simulation: 21 high resolution "zoom-in" Dark Matter only simulations. Andromeda-mass haloes in the mass range
+(7,4$\times 10^{11} < M_{200}M_\odot < 2,2 \times 10^{12}$).\\
+Gas: NO\\
+Resolution : resolve substructure down to $10^7 h^{-1}M\odot$\\
+Number of host halos: 21\\
+Planes: yes\\
+co-rotation: yes (when they look at angular momenta they find MW like co-rotation.
+When they look at line-of-sight velocities they find that 30$\%$ of the satellites are not co-rotating despited the apparent co-rotation form the line-of-sight velocity).\\
+note: \\
+}
+
+%\item{ :\\
+%Conclusion: \\
+%Simulation: \\
+%Gas: \\
+%Resolution : \\
+%Number of host halos: \\
+%Planes: \\
+%co-rotation: \\
+%note: \\
+%}
+
 \end{itemize}

### 2016-06-14 paper/ms.tex
intro new paragraph

@@
 \noindent Since the early works of (el que libeskind dice que habló de
-eso primero) and Lynden-Bell (1976), the observed anisotropic
+eso primero) and \cite{1976MNRAS.174..695L}, the observed anisotropic
 distribution of satellite galaxies in the Local Group has been a key
@@
 that contained the Magelanic clouds and their stellar tails. This
-anisotropic distribution was further studied in the work of Pawlowski
+anisotropic distribution was further studied in the work of \cite{}Pawlowski
 et. al. (2012), where they included all the known MW satellite galaxies (XXX
@@
 
-These observed planes present a challenge for current galaxy formation
-models (Pawlowski et al. 2014)
+These observed planes and their apparent co-rotation seem to challenge current galaxy formation models (Pawlowski et al. 2014). 
+A few months after the discovery of the M31 plane of satellites, Bahl and Baumgardt (2013) looked for similar structures in the MilleniummII dark matter only cosmological simulations, and found that planar structures are common (they found them in around 2 per cent of host halos).
+Nevertheless these results were contradicted by the works of Ibata el al.
+(2014) and Pawlowski et al.
+(2014) who, analyzing the same cosmological simulations with methods closer to those used to analyze the observational data, found that planar structures such as that observed in M31 are extremely rare (less than 0.02 per cent or 0.004 per cent respectively).\\
 

### 2016-08-16 paper/ms.tex
paper: intro y results

--- 2016-06-13 paper/ms.tex
@@
 
-%
-%Observational evidence of planes is everywhere (where we can see them). MW, M31, Centaurus A.\\
-%
-%Not so evident in simulations:\\
-%
-%Millenium II Baumgardt, Ibata, Pawlowski\\
-%
-%Clues Gillet está pero diferente\\
-%
-%Plane claims:\\
-%Libeskind: preferential direction for accretion.\\
-%Sawala: planes are there when baryonic physics is included.\\
-%Buck: planes are easy to form at early times, when DM filaments are very thin. In high redshift galaxies galaxies, planes are everywhere.\\
-%
-%Other explanations: Kroupa: tidal dwarfs\\
-%Fouquet\\
-%
-%
-%
-% 
-%Following a bit on the claim by Sawala that barionic physics are important when looking for planes, WE look in Illustris and Elvis simulations to try and understand why barionic physics results in planar distribution of satellites.
-
-%\subsection{Evidencias observacionales de planos:}
-\noindent Since the early works of (el que libeskind dice que habló de
-eso primero) and Lynden-Bell (1976), the observed anisotropic
+Since the early works of (el que libeskind dice que habló de
+eso primero) and \cite{1976MNRAS.174..695L}, the observed anisotropic
 distribution of satellite galaxies in the Local Group has been a key
@@
 
-These observed planes present a challenge for current galaxy formation
-models (Pawlowski et al. 2014)
+These observed planes and their apparent co-rotation seem to challenge
+current galaxy formation models (Pawlowski et al. 2014).
+\cite{2012MNRAS.424...80P} compared the kinematic structure of the MW
+satellites against DM only simulation of high resolution halos from
+the Via Lactea and Aquarius projects and could not find find a similar
+kinematic structure (i.e. the orbital poles of the MW satellites) in
+the simulations. Additionally, a few months after the discovery of the
+M31 plane of satellites, Bahl and Baumgardt (2013) looked for similar
+structures in the MilleniummII dark matter only cosmological
+simulations, and found that planar structures are common (they found
+them in around 2 per cent of host halos). Nevertheless these results
+were contradicted by the works of Ibata el al. (2014) and Pawlowski et
+al. (2014) who, analyzing the same cosmological simulations with
+methods closer to those used to analyze the observational data, found
+that planar structures such as that observed in M31 are extremely rare
+(less than 0.02 per cent or 0.004 per cent respectively). But
+satellite galaxies are not particularly good tracers of the underlying
+dark matter structure (Sawala 2014), and indeed anisotropic
+distributions of the satellites have been found in the APOSTOLE
+simulations that include baryonic physics \citep{2016MNRAS.457.1931S},
+although the Milky Way remains an extreme case. These results were
+contested by \cite{2015ApJ...815...19P} who claim that the
+anisotropies found are a product of using a metric that ignores the
+radial position of the galaxies. %Sawalla et al. 2014
+In CLUES, a high resolution constrained Local Group simulation,
+Gillet et al. (2015) found M31-like planes but again, the observed M31 plane
+remains an extreme case, and this seems to be corroborated by Cautun
+et al. (2015), who, despite finding a great variety of planes in
+simulations remarks that the observed M31 plane has an "unusually large
+radial extent".\\
 
-%The VPOS (Pawlowski et al 2012: https://arxiv.org/abs/1204.5176)\\
-%A vast thin plane of corrotating dwarf galaxies orbiting the Andromeda
-%Galaxy (Ibata et al 2013)\\
-%Corotation in SDSS data (Ibata et al 2014)\\
-%There was a reply to this paper (A new spin on disks of satellite
-%galaxies, Cuatun et al 2014)\\
-    %Planes in Centaurus A (Tully et al 2015)\
-%paper con los dos planos MW yM31
-%>https://arxiv.org/pdf/1307.6210v1.pdf
-\
-%Varios papers de pawlowski que muestran que los nuevos sat\'elites de
-%MW estan en el plano, que el plano no se debe al Sdss footprint, que
-%los globular clusters tambien estan en el plano... etc,\\ 
-%Papers de Conn donde encuentra el plano\\
+In addition to these plane-finding efforts in cosmological simulations,
+many works have focused on the possible formation processes that led
+to planar structures and on the alignments  of these structures with
+the cosmic web. In a pioneer work \cite{2011MNRAS.411.1525L} measured
+the infall direction of satellites in a DM only constrained simulation of one pair
+of LG halos and found that there is a definite infall direction. 
+% but it's not quantified in terms of the cosmic web.
+Using cosmological dark matter only simulations
+\cite{2014MNRAS.443.1274L} showed that the preferential infall
+direction was along cosmic filaments, result that was also obtained by 
+\cite{2015ApJ...799..212L}. This result was further
+confirmed by \cite{2015MNRAS.450.2727T}, who measure the angle between
+satellites and the direction defined by filaments (Bissous filament
+finder) to find a signal both in the SDSS galaxy catalog and in the
+semi-analytic galaxies in the Millennium Simulation. Additionally, 
+an analysis of the cosmic flow data set by Libeskind et al. (2015) 
+reveals that four out of the fives satellite planes observed in the 
+Local Group are aligned with a filament. 
+Additionally, \cite{2016arXiv160601516L} use the SDSS DR10 catalog to study galaxy pairs and find that satellites tend to accumulate towards the companion galaxy: There
+are up to $\sim 10\%$ more satellites in the space between the pair
+than expected from an uniform distribution.
 
-%\subsection{B\'usqueda de planos en simulaciones:}
-\noindent A comparison of the distribution of satellite galaxies
-around Andromeda and the results of $\Lambda$CDM simulations (Bahl and
-Baumgardt 2013) Encuentran planos en Millenium II.\\
-A thousand shadows of Andromeda: rotating planes of satellites in the
-Millennium-II cosmological simulation (Ibata et al 2013) dicen que el
-paper de Bahl y Baumgardt est\'a mal y que no hay planos en millenium
-II\\
-Co-orbiting satellite galaxy structures are still in conflict with the
-distribution of primordial dwarf galaxies (Pawlowski et al 2014)\\
-Co-orbiting planes of sub-halos are similarly unlikely around paired
-and isolated hosts (Pawlowski et al 2014)\\
-Vast planes of satellites in a high resolution simulation of the Local
-Group: comparison to Andromeda (Gillet et al 2014). finds a plnes
-similar to that of M31 in Clues simulations.\\
-Planes of satellite galaxies: when exceptions are the rule (Cautun et
-al 2015) encuentra que 10 por ciento de los halos tienen planos
-iguales o m\'as prominentes que los del LG.\\
+Early filamentary accretion has been proposed as the formation mechanism for the Andromeda thin plane of satellites (Buck et al 2015), with early formed galaxies accreting their mass via cold thin filaments.
+This formation mechanism results naturally in thin planes, but a follow up work shows that these are not kinematically coherent structures (Buck et al.
+2015).
+These results are from dark matter only simulations, so it would be interesting to see if they still hold for simulations that include baryonic physics, since it was shown by Gonzales et al 2015 that satellites acrreted via filaments are destroyed faster than those that are not.
 
-\subsection{Posibles or\'igenes de los planos:}
-\noindent Preferential accretion (Libeskind et al 20??)\\
-Alignments with the cosmic web (Tempel et al 20??)\\
-The vast thin plane of M31 co-rotating dwarfs: an additional fossil
-signature of the M31 merger and of its considerable impact in the
-whole Local Group (Hammer et al 2013) Major merger in M31-MW system
-plane galaxies are tidal dwarfs (n-body simulations)\\
-Kroupa tiene todo un carretazo de que las dwarfs son todas tidal
-dwarfs\\
-MIRAR lo que est\'a haciendo Pierre Alan Duc con tidal dwrafs porque en
-una conferencia este a;o habl\'o de un posible escenario
-intermedio...\\
-Evidence for Early Filamentary Accretion from the Andromeda Galaxy's
-Thin Plane of Satellites (Buck et al 2015)\\
-Alignments between galaxies, satellite systems and haloes (Cautun et al
-2016) NO LO HE LEIDO...
-
-\subsection{Problemas con esas explicaciones:}
-The Vast Polar Structure of the Milky Way and Filamentary Accretion of
-Sub-Halos (Pawlowski et al 2012)\\
-Paper de Collins (2013 y 2016) donde explica que no hay diferencias en
-las propiedades de los on-plane y los off-plane satellites\\
-Problemas con la estabilidad a largo plazo de los planos: Bowden et al
-2012, Gonzales et al 2015...\\
-The Plane Truth: Andromeda analog thin Planes of Satellites are not
-kinematical coherent structures (Buck et al 2015)\\
-
-\subsection{Previous studies of Local Group satellites}
-
-\citep{2011MNRAS.411.1525L} Measure the infall direction of satellites
-in a DM only simulation of one pair of LG halos in a constrained
-simulation. There is a definite infall direction but it's not
-quantified in terms of the cosmic web.
-
-\citep{2012MNRAS.424...80P} Compare the kinematic structure of the MW
-satellites against DM only simulation of high resolutions halos from
-the Via Lactea and Aquarius projects.  Cannot find a similar kinematic
-structure (i.e. the orbital poles of the MW satellites) in the
-simulations.
-
-\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
-with respect to the V-web. They do it in a DM cosmological simulation
-(64 Mpch, 1024 3 particles). They find that infall is done along the
-e3 (i.e. filament) direction.
-
-\citep{2015MNRAS.450.2727T} They measure the angle between satellites
-and the direction defined by filaments (Bissous filament finder) to
-find a signal both in SDSS and the semi-analytic galaxies in the
-Millennium Simulation.
-
-\citep{2015ApJ...799..212L} Detection of alignment of satellites along
-the direction defined by filaments (velocity shear cosmic web) on the
-SDSS DR7.
-
-\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
-spatial anisotropy the 11 brightest satellites. The anisotropy is
-quantified the reduced inertia tensor. Still the MW is more
-anisotropic than all but one of the 24 halos. The analysis is not very
-thorough and do not show the resulting distribution. Does not compare
-the results of using DM information only.
-
-\citep{2015ApJ...815...19P} argue that the result from
-\citep{2016MNRAS.457.1931S} is a produc of using a metric that ignores
-the radial position of the galaxies. They use the ELVIS suite to
-compare the two analysis methods: reduced vs. full inertia tensor.
-
-\citep{2016arXiv160501728S} Use the eagle simulation to study the
+In a more general numerical study,   
+\cite{2016arXiv160501728S} use the eagle simulation to study the
 alignment of satellites with respect to the central galaxy. They find
 a weak alignment. Around $20\%$ of the systems have a misalignment
-angle larger than the value observed for the Milky Way. They do not
-study DM only simulations and do not narrow down the signal to pairs.
+angle larger than the value observed for the Milky Way.
 
-\citep{2016arXiv160601516L} Using SDSS DR10 studied galaxy pairs. They find
-that satellites tend to accumulate towards the companion galaxy. There
-are up to $\sim 10\%$ more satellites in the space between the pair
-than expected from an uniform distribution
+Planes in simulations tend to be transient structures (not
+kinematically coherent) and that poses two problems: one is why do we
+see planes in all the galaxies were we can actually make the
+measurements if they are transient? Problem with the MW plane for which
+some of the dwarfs have proper motion measurements. Another problem:
+explicación de Buck 2015 sería rara entonces...
 
@@
 \subsection{Illustris simulation}
+
+In this work we use the publicly available results from the Illustris
+simulation (Vogelsberger et al. 2014). This cosmological simulation, performed using
+the quasi-Lagrangian code AREPO, follows the coupled evolution of dark
+matter and gas, and includes parametrizations to account for the effects of
+gas cooling, photoionization, star formation, stellar feedback, black
+hole and super massive black hole feedback. Vogelsberger et al. 2014 use a $75 Mpc/h$
+simulation box, with $\Lambda$CDM cosmology initial conditions
+starting at a redshift $z=127$ and consistent with WMAP-9 measurments.
 
@@
 scarce.  
+%no me es muy claro este ultimo parrafo. En nuestros samples pasamos de 49 a 24 (o sea se redujo en un factor 2 en vez de un factor 12)
 
@@
 \subsection{Cosmic Web environment}
-
+%me parece que la palabra "place" puede ser confusa. 
 We place the pairs in our sample into the cosmic web as quantified by
@@
 
+\subsection{Characterization of spatial distributions}
+\label{Method}
+In this paper, our aim is to study alignments: of the
+satellite population with the cosmic web, of the dark matter halos
+with the axis that unites them, etc...
+To do this, we fitted a triaxial spheroid to both the satellite (bright) and the dark matter (dark) subhalo distributions, to get both their semi-major and semi-minor axis.
+With this geometrical information we can study the alignments of the two distributions with the cosmic web, and also with the vector that unites the halo pair that host these substructures.
+%Jaime, falta el plot de alineaciones con la cosmic web
+
+\section{Results}
+\label{Results}
+
+Some papers claim that once baryonic physics is included more planar distributions are found.
+First we investigate if there is a difference in the bright and dark distribution in terms of their flatness.
+In Figure \ref{fig:StreamPlaneOrbit} we can see that indeed the bright distribution is flatter than the dark distribution.
 \begin{figure}
@@
 
-\begin{figure*}
+We then try to fit planes to both the dark and bright distributions in order to test if it is indeed easier to find thinner planes in the bright distribution. 
+We find that the bright planes are thinner.
+\begin{figure}
 \centering
-\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}
-\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}
-\caption{Significance of alignments.}
-\label{fig:significance}
-\end{figure*}
+\includegraphics[width=\hsize]{plane_width.pdf}\\
+\caption{Plane width for the best planes in the luminious and dark cases.}
+\label{fig:plane_width}
+\end{figure}
+But is there a physical reason for that?
+Apparently not, since the thinness of the fitted planes seems to be only due to number of objects: number of bright satellites is smaller than of dark sub-halos and that results naturally in thinner fitted planes.
+%pregunta para Jaime: en tu código dark quiere decir dm only subhalos o todos los subhalos (dm only y bright)?
+%podríamos hacer como un test extra el plot que yo tenía en mis plot de antes, que es cojer al azar entre los dark un numero de subhalos igual al de bright y ver los anchos de los planos.
+
+\begin{figure}
+\centering
+\includegraphics[width=\hsize]{plane_width_n_dark.pdf}\\
+\caption{Plane width as a function of objects used to find the plane.}
+\label{fig:plane_width_nobjects}
+\end{figure}
+
+A second test is to look if there is any evidence of alignments between the distribution of satellites and the axis that unites the main halos that form the pair.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=\hsize]{plane_width.pdf}\\
-\caption{Plane width for the best planes in the luminious and dark cases.}
-\label{fig:plane_width}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\hsize]{plane_width_n_dark.pdf}\\
-\caption{Plane width as a function of objects used to find the plane.}
-\label{fig:plane_width_nobjects}
-\end{figure}
-
-\section{Results}
-\label{Results}
-
-\section{Method}
-\label{Method}
+\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}
+\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}
+\caption{Significance of alignments for both samples.}
+\label{fig:significance}
+\end{figure*}
 
@@
 \section{Discussion}
+Difference between bright and dark distributions are only due to number.\\
+We find significant alignments between distributions and H1H2 axis. But this alignments are the opposite as the one observed for the Local Group!!!
+
 \section{Acknowledgements}
@@
 
-Simulation papers:
-\begin{itemize}
-\item{Bahl and Baumgardt 2013 "A comparison of the distribution (...)":\\
-MilleniumII and a semi-analytic model\\
-Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
-PAndAS like field\\
-With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
-Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
-Conclusion: M31 like planes are not uncommon in MilleniumII simulations.
+%Simulation papers:
+%%\item {ya}
+%%\item{Bahl and Baumgardt 2013 "A comparison of the distribution (...)":\\
+%%MilleniumII and a semi-analytic model\\
+%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+%%PAndAS like field\\
+%%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
+%%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
+%%Conclusion: M31 like planes are not uncommon in MilleniumII simulations.
 Co-rotating structures are not stable structures.
 Plane of M31 could be a statistical fluctuation in an otherwise more spherical distribution.\\
-Simulation: Millenium II ()\\
-Gas: NO\\
-Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
-Number of host halos: 1511 with orphan galaxies, 112 excluding orphan galaxies (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$), younger that 10 Gyr and satelites smaller than 7$\times 10^{10} M\odot$\\
-Planes: yes (40$\%$ with orphan galaxies 2$\%$ without)\\
-co-rotation: yes (in 2$\%$ of the halos ???)\\
-Stable: No\\
-Note: PAndAS data has satellites with baryonic masses down to 2.9$\times 10^{4} M\odot$ and they take that as a lower limit for their data.\\
-}
-\item{Ibata et al 2014 "A thousand shadows (...)":\\
-MilleniumII and a semi-analytic model (Guo)\\
-%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
-Same analysis as in PAndAS data\\
-%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
-%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
-Conclusion: M31 like planes are NOT common in MilleniumII simulations.\\
-Simulation: Millenium II ()\\
-Gas: NO\\
-Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
-Number of host halos: 679 (I assume with orphan galaxies) (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
-Planes: no (with orphan galaxies only 0.04$\%$ of the system fulfill the thinness, extension and co-rotation criteria, and NONE does if orphans are not included.
+%%Simulation: Millenium II ()\\
+%%Gas: NO\\
+%%Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+%%Number of host halos: 1511 with orphan galaxies, 112 excluding orphan galaxies (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$), younger that 10 Gyr and satelites smaller than 7$\times 10^{10} M\odot$\\
+%%Planes: yes (40$\%$ with orphan galaxies 2$\%$ without)\\
+%%co-rotation: yes (in 2$\%$ of the halos ???)\\
+%%Stable: No\\
+%%Note: PAndAS data has satellites with baryonic masses down to 2.9$\times 10^{4} M\odot$ and they take that as a lower limit for their data.\\
+%%}
+%%\item {ya}
+%%\item{Ibata et al 2014 "A thousand shadows (...)":\\
+%%MilleniumII and a semi-analytic model (Guo)\\
+%%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+%%Same analysis as in PAndAS data\\
+%%%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
+%%%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
+%%Conclusion: M31 like planes are NOT common in MilleniumII simulations.\\
+%%Simulation: Millenium II ()\\
+%%Gas: NO\\
+%%Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+%%Number of host halos: 679 (I assume with orphan galaxies) (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
+%%Planes: no (with orphan galaxies only 0.04$\%$ of the system fulfill the thinness, extension and co-rotation criteria, and NONE does if orphans are not included.
 If co-rotation is not included then $2\%$ fulfill the thinness and extension criteria)\\
-co-rotation: only 0.04$\%$ with orphans and NONE without orphans\\
-Note: they use the 679 host halos and study them from different viewing angles\\
-}
-\item{Pawlowski et al 2014 "Co-orbitingsatellite galaxy structures are still in conflict with (...)":\\
-MilleniumII and a semi-analytic model (Guo)\\
-%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
-Same analysis as in PAndAS data\\
-Same analysis as in Wang et al. 2013\\
-%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
-%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
-Conclusion: M31 and MW like planes are NOT common in MilleniumII simulations.\\
-Simulation: Millenium II ()\\
-Gas: NO\\
-Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
-Number of host halos:  1825 (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
-Planes: no (M31: 0.09$\%$ fulfill the thinness, extension and co-rotation criteria. MW: 0.2$\%$)\\
-Note: they use the host halos and study them from different viewing angles so they end up with 15000 samples.
+%%co-rotation: only 0.04$\%$ with orphans and NONE without orphans\\
+%%Note: they use the 679 host halos and study them from different viewing angles\\
+%%}
+%%\item {ya}
+%%\item{Pawlowski et al 2014 "Co-orbitingsatellite galaxy structures are still in conflict with (...)":\\
+%%MilleniumII and a semi-analytic model (Guo)\\
+%%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+%%Same analysis as in PAndAS data\\
+%%Same analysis as in Wang et al. 2013\\
+%%%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
+%%%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
+%%Conclusion: M31 and MW like planes are NOT common in MilleniumII simulations.\\
+%%Simulation: Millenium II ()\\
+%%Gas: NO\\
+%%Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+%%Number of host halos:  1825 (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
+%%Planes: no (M31: 0.09$\%$ fulfill the thinness, extension and co-rotation criteria. MW: 0.2$\%$)\\
+%%Note: they use the host halos and study them from different viewing angles so they end up with 15000 samples.
 They always consider orphan galaxies for comparison purposes.
 For one test they randomize the sample and find M31 like planes in only 0.002 per cent of the cases and MW like planes in 0.06$\%$ of the cases.\\
-MIRAR Wang et al. 2013 que busca MWlike planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos
-}
-\item{Cautun et al. 2015 "Planes of satellite galaxies: when exceptions are the rule":\\
-MilleniumII and a semi-analytic model (Guo 2013)\\
-CoCo and a semi-analytic model (Guo 2015)\\
-%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
-Conclusion: planar structures are very common in $\Lambda$CDM (10$\%$)\\
-Simulation 1: Millenium IIi rescaled to WMAP\\
-Simulation 2: CoCo (Higher resolution than MilleniumII)\\
-Gas: NO\\
-Resolution 1: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
-Number of host halos:  2849 (MilleniumII) and 63 8COCO halos) (selection criteria: "we adopted a broader mass range to account for the large uncertainty in the mass measurements and also for possible systematic effects").\\
-Resolution 2: sub-halos $\approx$ 2$\times 10^6 M\odot$ (75 times higher mass resolution
-and four times better spatial resolution)\\
-Planes: yes (10$\%$)\\
-Note: They found a great variety of plane and the M31 plane lies in general within the scatter of the simulated planes however it seem to have an "unusually large radial extent".\\
-Note 2: they find that each halos has a different planar configuration showing that the low incidence of the M31 plane is not in contradiction with simulations.
+%%MIRAR Wang et al. 2013 que busca MW-like planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos
+%%}
+%%\item {ya}
+%%\item{Cautun et al. 2015 "Planes of satellite galaxies: when exceptions are the rule":\\
+%%MilleniumII and a semi-analytic model (Guo 2013)\\
+%%CoCo and a semi-analytic model (Guo 2015)\\
+%%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
+%%Conclusion: planar structures are very common in $\Lambda$CDM (10$\%$)\\
+%%Simulation 1: Millenium IIi rescaled to WMAP\\
+%%Simulation 2: CoCo (Higher resolution than MilleniumII)\\
+%%Gas: NO\\
+%%Resolution 1: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
+%%Number of host halos:  2849 (MilleniumII) and 63 8COCO halos) (selection criteria: "we adopted a broader mass range to account for the large uncertainty in the mass measurements and also for possible systematic effects").\\
+%%Resolution 2: sub-halos $\approx$ 2$\times 10^6 M\odot$ (75 times higher mass resolution
+%%and four times better spatial resolution)\\
+%%Planes: yes (10$\%$)\\
+%%Note: They found a great variety of plane and the M31 plane lies in general within the scatter of the simulated planes however it seem to have an "unusually large radial extent".\\
+%%Note 2: they find that each halos has a different planar configuration showing that the low incidence of the M31 plane is not in contradiction with simulations.
 This contradicts the Pawlowski et al.
 2014 conclusions}
+%%
+%%\item{Sawala et al. 2014 "The chosen few: the low mass halos that host faint galaxies":\\
+%%Conclusion: Some "effects make dwarf galaxies highly biased
+%%tracers of the underlying dark matter distribution."\\
+%%Simulation: 12 cosmological volumes as zoom" simulations
+%%extracted from the Dove simulation. They require that each box has to
+%%have two halos (MW and M31 like)\\
+%%Gas: Yes (they also compare their results with DM only simulations)\\
+%%Resolution : sub-halos 1 $\times 10^7 M\odot$\\
+%%Number of host halos:  2 times 12 (pairs of galaxies).\\
+%%Planes: They do not look for them\\}
 
-\item{Sawala et al. 2014 "The chosen few: the low mass halos that host faint galaxies":\\
-Conclusion: Some "effects make dwarf galaxies highly biased
-tracers of the underlying dark matter distribution."\\
-Simulation: 12 cosmological volumes as zoom" simulations
-extracted from the Dove simulation. They require that each box has to
-have two halos (MW and M31 like)\\
-Gas: Yes (they also compare their results with DM only simulations)\\
-Resolution : sub-halos 1 $\times 10^7 M\odot$\\
-Number of host halos:  2 times 12 (pairs of galaxies).\\
-Planes: They do not look for them\\}
+%                            \begin{itemize}
+%                            \item{Libeskind et al. 2012 "The universal nature of subhalo accretion":\\
+%                            Conclusion: "the preferential infall of subhaloes is effectively universal
+%                            in the sense that its always aligned with the axis of weakest collapse
+%                            of the velocity shear tensor. It is the same shear tensor that
+%                            dictates the structure of the cosmic web and hence the shear field
+%                            emerges as the key factor that governs the local anisotropic pattern
+%                            of structure formation."\\
+%                            Simulation:DM-only N-body simulation of 10243 particles in a
+%                            64h$^{-1}$ Mpc box.\\
+%                            Gas: NO\\
+%                            Resolution : particle 1.89 $\times 10^7 h^{-1} M\odot$\\
+%                            Resolution : halos 1$\times 10^9 h^{-1} M\odot$\\
+%                            Number of host halos:  not mentioned.\\
+%                            Planes: They do not look for them. They look and find preferential
+%                            directions for accretion\\}
+%                            
+%                            %%\item{Libeskind et al. 2015 "Planes of satellite galaxies and the
+%                            %%cosmic web":\\
+%                            %%Conclusion:"The analysis reveals that the Local Group and Centaurus A
+%                            %%reside in a filament stretched by the Virgo cluster and compressed by
+%                            %%the expansion of the Local Void. Four out of five thin planes of
+%                            %%satellite galaxies are indeed closely aligned with the axis of
+%                            %%compression induced by the Local Void. (...) "\\ 
+%                            %%Simulation: Observational paper uses the cosmic flow data set.\\
+%                            %%Gas: No aplica\\
+%                            %%\\}
+%                            
+%                            %%\item{Tempel et al. 2015 "The alignment of satellite galaxies and
+%                            %%cosmic filaments: observations and simulations":\\
+%                            %%Conclusion:"A statistically significant alignment between satellite
+%                            %%galaxy position and filament axis in observations is confirmed. We
+%                            %%find a qualitatively compatible alignments by examining satellites and
+%                            %%filaments similarly identified in the Millennium simulation,
+%                            %%semi-analytical galaxy catalogue. We also examine the dependence of
+%                            %%the alignment strength on galaxy properties such as colour, magnitude
+%                            %%and (relative) satellite magnitude, finding that the alignment is
+%                            %%strongest for the reddest and brightest central and satellite
+%                            %%galaxies. "\\ 
+%                            %%Simulation: MilleniumII compared to Observational data (SDSS).\\
+%                            %%Gas: No\\
+%                            %%Alignments: yes both in simulations and in observations\\
+%                            %%Note: they make a statistical analysis of alignments in projected
+%                            %%data.}
+%                            
+%                            %%\item{Sawala et al. 2015 "The APOSTLE simulations: solutions to the
+%                            %%Local Group's cosmic puzzles":\\
+%                            %%Conclusion: "Applying the Eagle code to the LG environment, we find
+%                            %%that our simulations match the observed abundance of LG galaxies,
+%                            %%including the satellite galaxies of the MW and Andromeda. Due to
+%                            %%changes to the structure of halos and the evolution in the LG
+%                            %%environment, the simulations reproduce the observed relation between
+%                            %%stellar mass and velocity dispersion of individual dwarf spheroidal
+%                            %%galaxies without necessitating the formation of cores in their dark
+%                            %%matter profiles. Satellite systems form with a range of spatial
+%                            %%anisotropies, including one similar to that of the MW, confirming that
+%                            %%such a configuration is not unexpected in $\Lambda$CDM"\\ 
+%                            %%Simulation: They use the EAGLE code to simulate the Apostole set of
+%                            %%simulations (a suite of cosmological hydro-
+%                            %%dynamic simulations of twelve volumes selected to match the kinematics
+%                            %%of the Local Group (LG) members).\\
+%                            %%halo selection:In particular, we focus
+%                            %%on pairs of halos that match the separation, approach
+%                            %%velocity, and relative tangential velocity of the Milky Way
+%                            %%(MW) and Andromeda (M31). From a large cosmological
+%                            %%simulation, we have selected twelve pairs of halos with combined
+%                            %%virial masses of  2.3$\pm$0.6$\times 10^{12}M_\odot$, compatible
+%                            %%with the most recent dynamical constraints\\ 
+%                            %%Resolution : re-simulated each LG volume at several resolutions,
+%                            %%both as dark matter only (DMO) simulations, and
+%                            %%as hydrodynamic simulations\\
+%                            %%Gas: Yes (they also compare with DM only simulations)\\
+%                            %%planes: yes (they find "anisotropic configurations: BUT not typical ")\\
+%                            %%Note: they select MW-M31-like pairs, including kinematical
+%                            %%constraints\\}
+%                            %%
+%                            %%\item{ Gillet et al. 2015: "Vast planes of satellites in a high resolution simulation of
+%                            %%the Local Group: comparison to Andromeda":\\
+%                            %%CLUES project and a semi-analytic model\\
+%                            %%Conclusion: "The structure of the simulated satellite systems is
+%                            %%strongly non-random and contains planes of satellites, predominantly
+%                            %%co-rotating, with, in some cases, sizes comparable to the plane
+%                            %%observed in M31 by Ibata et al.. However the latter is slightly richer
+%                            %%in satellites, slightly thinner and has stronger co-rotation, which
+%                            %%makes it stand out as overall more exceptional than the simulated
+%                            %%planes, when compared to a random population" \\
+%                            %%Simulation: CLUES\\
+%                            %%Gas: NO\\
+%                            %%Resolution : DM particle 2.1 $\times 10^5 h^{-1} M\odot$\\
+%                            %%Resolution : gas particle 4.42 $\times 10^4 h^{-1} M\odot$\\
+%                            %%Resolution : halos $4.2\times 10^6 h^{-1} M\odot$\\
+%                            %%Number of host halos: 2 (one pair)\\
+%                            %%Planes: yes\\
+%                            %%co-rotation: kind of\\
+%                            %%Stable: No\\
+%                            %%note: they use 5 different methods to choose the satellites and 3
+%                            %%different volumes.\\
+%                            %%}
+%                            
+%                            %%\item{ Pawlowski et al. 2012: "Can filamentary accretion explain the
+%                            %%orbital poles of the Milky Way satellites?":\\
+%                            %%Aquarius and Via Lactea Simulations\\
+%                            %%Conclusion: they find that the simulations cannot reproduce the
+%                            %%angular momentum coherence of the satellites in the MW and that "this
+%                            %%indicates that the formation as tidal dwarf galaxies in a single
+%                            %%encounter is a viable, if not the only, process to explain the
+%                            %%phase-space distribution of the MW satellite galaxies." \\
+%                            %%Simulation: Aquarius and Via Lactea\\
+%                            %%Gas: NO\\
+%                            %%Resolution : ?\\
+%                            %%Number of host halos: 8\\
+%                            %%Planes: they look for alignments in the orbital poles and found none
+%                            %%in the cosmological simulations\\
+%                            %%co-rotation: no\\
+%                            %%note: they compare what they find in simulations with an isotropic
+%                            %%distribution and with merger scenarios.\\
+%                            %%}
+%                            
+%                            \item{ Pawlowski et al. 2014: "Co-orbiting planes of sub-halos are
+%                            similarly unlikely around paired and isolated hosts":\\
+%                            They use the Elvis simulations to study the satellite population of
+%                            paired vs isolated galaxies.\\
+%                            Conclusion: The observed flattening and the observed orbital alignment
+%                            are each reproduced by only 0.2 to 2 per cent of paired and isolated
+%                            systems incorporating the obscuration of satellites by randomly
+%                            oriented galactic discs.\\
+%                            Simulation: Elvis\\
+%                            Gas: NO\\
+%                            Resolution : ?\\
+%                            Number of host halos: 24 paired and 24 isolated host halos (4800
+%                            analyzed realizations).\\
+%                            Planes: 0.2 to 2 per cent\\
+%                            co-rotation: 0.2 to 2 per cent\\
+%                            note: co-rotation and alignments together are only observed in ONE of
+%                            4800 realizations.\\
+%                            }
+%                            
+%                            \item{Buck et al 2015 "EVIDENCE FOR EARLY FILAMENTARY ACCRETION FROM THE ANDROMEDA GALAXY'S THIN PLANE
+%                            OF SATELLITES":\\
+%                            They use zoom in cosmological simulations to study the possible formation of thin planes of satellite galaxies.\\
+%                            Conclusion: "We show that it is possible to obtain a thin, extended, rotating plane of satellites resembling the one in
+%                            Andromeda in cosmological collisionless simulations based on the Cold Dark Matter model. Our new
+%                            high resolution simulations show a correlation between the formation time of the dark matter halo
+%                            and the thickness of the plane of satellites." (...) "Our high resolution simulations show a correlation between the formation time of the dark matter halo
+%                            and the thickness of the plane of satellites. Our simulations have a high incidence of satellite planes
+%                            as thin, extended, and as rich as the one in Andromeda and with a very coherent kinematic structure
+%                            when we select high concentration/early forming halos."\\
+%                            Simulation: 21 high resolution "zoom-in" Dark Matter only simulations. Andromeda-mass haloes in the mass range
+%                            (7,4$\times 10^{11} < M_{200}M_\odot < 2,2 \times 10^{12}$).\\
+%                            Gas: NO\\
+%                            Resolution : resolve substructure down to $10^7 h^{-1}M\odot$\\
+%                            Number of host halos: 21\\
+%                            Planes: yes\\
+%                            co-rotation: yes\\
+%                            note: \\
+%                            }
+%                            
+%                            \item{Buck et al 2016 "Simulated $\Lambda$CDM analogues of the thin Plane of Satellites
+%                            around the Andromeda galaxy are not kinematically
+%                            coherent structures":\\
+%                            They use zoom in cosmological simulation of high concentration haloes to study the dynamics of the satellite population.\\
+%                            Conclusion: "Thus we conclude that the line-of-sight velocity is not well suited as a proxy for the kinematical coherence of the plane.
+%                            Analysis of the kinematics of our planes shows a fraction of 30$\%$ chance aligned
+%                            satellites. Tracking the satellites in the plane back in time reveals that these planes
+%                            are a transient feature and not kinematically coherent as would appear at first sight.
+%                            Thus we expect some of the satellites in the plane around Andromeda to have high
+%                            velocities perpendicular to the plane."\\
+%                            Simulation: 21 high resolution "zoom-in" Dark Matter only simulations. Andromeda-mass haloes in the mass range
+%                            (7,4$\times 10^{11} < M_{200}M_\odot < 2,2 \times 10^{12}$).\\
+%                            Gas: NO\\
+%                            Resolution : resolve substructure down to $10^7 h^{-1}M\odot$\\
+%                            Number of host halos: 21\\
+%                            Planes: yes\\
+%                            co-rotation: yes (when they look at angular momenta they find MW like co-rotation.
+When they look at line-of-sight velocities they find that 30$\%$ of the satellites are not co-rotating despited the apparent co-rotation form the line-of-sight velocity).\\
+%                            note: \\
+%                            }
+%                            
+%                            %\item{ :\\
+%                            %Conclusion: \\
+%                            %Simulation: \\
+%                            %Gas: \\
+%                            %Resolution : \\
+%                            %Number of host halos: \\
+%                            %Planes: \\
+%                            %co-rotation: \\
+%                            %note: \\
+%                            %}
+%                            
+%                            \end{itemize}
+%
 
-\item{Libeskind et al. 2012 "The universal nature of subhalo accretion":\\
-Conclusion: "the preferential infall of subhaloes is effectively universal
-in the sense that its always aligned with the axis of weakest collapse
-of the velocity shear tensor. It is the same shear tensor that
-dictates the structure of the cosmic web and hence the shear field
-emerges as the key factor that governs the local anisotropic pattern
-of structure formation."\\
-Simulation:DM-only N-body simulation of 10243 particles in a
-64h$^{-1}$ Mpc box.\\
-Gas: NO\\
-Resolution : particle 1.89 $\times 10^7 h^{-1} M\odot$\\
-Resolution : halos 1$\times 10^9 h^{-1} M\odot$\\
-Number of host halos:  not mentioned.\\
-Planes: They do not look for them. They look and find preferential
-directions for accretion\\}
+%\subsection{Problemas con esas explicaciones:}
+%The Vast Polar Structure of the Milky Way and Filamentary Accretion of
+%Sub-Halos (Pawlowski et al 2012)\\
+%Paper de Collins (2013 y 2016) donde explica que no hay diferencias en
+%las propiedades de los on-plane y los off-plane satellites\\
 
-\item{Libeskind et al. 2015 "Planes of satellite galaxies and the
-cosmic web":\\
-Conclusion:"The analysis reveals that the Local Group and Centaurus A
-reside in a filament stretched by the Virgo cluster and compressed by
-the expansion of the Local Void. Four out of five thin planes of
-satellite galaxies are indeed closely aligned with the axis of
-compression induced by the Local Void. (...) "\\ 
-Simulation: Observational paper uses the cosmic flow data set.\\
-Gas: No aplica\\
-\\}
+%Problemas con la estabilidad a largo plazo de los planos: Bowden et al
+%2012, Gonzales et al 2015...\\
+%The Plane Truth: Andromeda analog thin Planes of Satellites are not
+%kinematical coherent structures (Buck et al 2015)\\
 
-\item{Tempel et al. 2015 "The alignment of satellite galaxies and
-cosmic filaments: observations and simulations":\\
-Conclusion:"A statistically significant alignment between satellite
-galaxy position and filament axis in observations is confirmed. We
-find a qualitatively compatible alignments by examining satellites and
-filaments similarly identified in the Millennium simulation,
-semi-analytical galaxy catalogue. We also examine the dependence of
-the alignment strength on galaxy properties such as colour, magnitude
-and (relative) satellite magnitude, finding that the alignment is
-strongest for the reddest and brightest central and satellite
-galaxies. "\\ 
-Simulation: MilleniumII compared to Observational data (SDSS).\\
-Gas: No\\
-Alignments: yes both in simulations and in observations\\
-Note: they make a statistical analysis of alignments in projected
-data.}
+%Others have had more success in finding planes
 
-\item{Sawala et al. 2015 "The APOSTLE simulations: solutions to the
-Local Group's cosmic puzzles":\\
-Conclusion: "Applying the Eagle code to the LG environment, we find
-that our simulations match the observed abundance of LG galaxies,
-including the satellite galaxies of the MW and Andromeda. Due to
-changes to the structure of halos and the evolution in the LG
-environment, the simulations reproduce the observed relation between
-stellar mass and velocity dispersion of individual dwarf spheroidal
-galaxies without necessitating the formation of cores in their dark
-matter profiles. Satellite systems form with a range of spatial
-anisotropies, including one similar to that of the MW, confirming that
-such a configuration is not unexpected in $\Lambda$CDM"\\ 
-Simulation: They use the EAGLE code to simulate the Apostole set of
-simulations (a suite of cosmological hydro-
-dynamic simulations of twelve volumes selected to match the kinematics
-of the Local Group (LG) members).\\
-halo selection:In particular, we focus
-on pairs of halos that match the separation, approach
-velocity, and relative tangential velocity of the Milky Way
-(MW) and Andromeda (M31). From a large cosmological
-simulation, we have selected twelve pairs of halos with combined
-virial masses of  2.3$\pm$0.6$\times 10^{12}M_\odot$, compatible
-with the most recent dynamical constraints\\ 
-Resolution : re-simulated each LG volume at several resolutions,
-both as dark matter only (DMO) simulations, and
-as hydrodynamic simulations\\
-Gas: Yes (they also compare with DM only simulations)\\
-planes: yes (they find "anisotropic configurations: BUT not typical ")\\
-Note: they select MW-M31-like pairs, including kinematical
-constraints\\}
+%The VPOS (Pawlowski et al 2012: https://arxiv.org/abs/1204.5176)\\
+%A vast thin plane of corrotating dwarf galaxies orbiting the Andromeda
+%Galaxy (Ibata et al 2013)\\
+%Corotation in SDSS data (Ibata et al 2014)\\
+%There was a reply to this paper (A new spin on disks of satellite
+%galaxies, Cuatun et al 2014)\\
+    %Planes in Centaurus A (Tully et al 2015)\
+%paper con los dos planos MW yM31
+%>https://arxiv.org/pdf/1307.6210v1.pdf
+\
+%Varios papers de pawlowski que muestran que los nuevos sat\'elites de
+%MW estan en el plano, que el plano no se debe al Sdss footprint, que
+%los globular clusters tambien estan en el plano... etc,\\ 
+%Papers de Conn donde encuentra el plano\\
 
-\item{ Gillet et al. 2015: "Vast planes of satellites in a high resolution simulation of
-the Local Group: comparison to Andromeda":\\
-CLUES project and a semi-analytic model\\
-Conclusion: "The structure of the simulated satellite systems is
-strongly non-random and contains planes of satellites, predominantly
-co-rotating, with, in some cases, sizes comparable to the plane
-observed in M31 by Ibata et al.. However the latter is slightly richer
-in satellites, slightly thinner and has stronger co-rotation, which
-makes it stand out as overall more exceptional than the simulated
-planes, when compared to a random population" \\
-Simulation: CLUES\\
-Gas: NO\\
-Resolution : DM particle 2.1 $\times 10^5 h^{-1} M\odot$\\
-Resolution : gas particle 4.42 $\times 10^4 h^{-1} M\odot$\\
-Resolution : halos $4.2\times 10^6 h^{-1} M\odot$\\
-Number of host halos: 2 (one pair)\\
-Planes: yes\\
-co-rotation: kind of\\
-Stable: No\\
-note: they use 5 different methods to choose the satellites and 3
-different volumes.\\
-}
+%\subsection{B\'usqueda de planos en simulaciones:}
+%\noindent A comparison of the distribution of satellite galaxies
+%around Andromeda and the results of $\Lambda$CDM simulations (Bahl and
+%Baumgardt 2013) Encuentran planos en Millenium II.\\
+%A thousand shadows of Andromeda: rotating planes of satellites in the
+%Millennium-II cosmological simulation (Ibata et al 2013) dicen que el
+%paper de Bahl y Baumgardt est\'a mal y que no hay planos en millenium
+%II\\
+%Co-orbiting satellite galaxy structures are still in conflict with the
+%distribution of primordial dwarf galaxies (Pawlowski et al 2014)\\
+%**** Co-orbiting planes of sub-halos are similarly unlikely around paired
+%**** and isolated hosts (Pawlowski et al 2014)\\
+%Vast planes of satellites in a high resolution simulation of the Local
+%Group: comparison to Andromeda (Gillet et al 2014). They find planes
+%similar to that of M31 in Clues simulations.\\
+%Planes of satellite galaxies: when exceptions are the rule (Cautun et
+%al 2015) encuentra que 10 por ciento de los halos tienen planos
+%iguales o m\'as prominentes que los del LG.\\
 
-\item{ Pawlowski et al. 2012: "Can filamentary accretion explain the
-orbital poles of the Milky Way satellites?":\\
-Aquarius and Via Lactea Simulations\\
-Conclusion: they find that the simulations cannot reproduce the
-angular momentum coherence of the satellites in the MW and that "this
-indicates that the formation as tidal dwarf galaxies in a single
-encounter is a viable, if not the only, process to explain the
-phase-space distribution of the MW satellite galaxies." \\
-Simulation: Aquarius and Via Lactea\\
-Gas: NO\\
-Resolution : ?\\
-Number of host halos: 8\\
-Planes: they look for alignments in the orbital poles and found none
-in the cosmological simulations\\
-co-rotation: no\\
-note: they compare what they find in simulations with an isotropic
-distribution and with merger scenarios.\\
-}
+%\subsection{Posibles or\'igenes de los planos:}
+%\noindent Preferential accretion (Libeskind et al 20??)\\
+%Alignments with the cosmic web (Tempel et al 20??)\\
 
-\item{ Pawlowski et al. 2014: "Co-orbiting planes of sub-halos are
-similarly unlikely around paired and isolated hosts":\\
-They use the Elvis simulations to study the satellite population of
-paired vs isolated galaxies.\\
-Conclusion: The observed flattening and the observed orbital alignment
-are each reproduced by only 0.2 to 2 per cent of paired and isolated
-systems incorporating the obscuration of satellites by randomly
-oriented galactic discs.\\
-Simulation: Elvis\\
-Gas: NO\\
-Resolution : ?\\
-Number of host halos: 24 paired and 24 isolated host halos (4800
-analyzed realizations).\\
-Planes: 0.2 to 2 per cent\\
-co-rotation: 0.2 to 2 per cent\\
-note: co-rotation and alignments together are only observed in ONE of
-4800 realizations.\\
-}
-\end{itemize}
+%The vast thin plane of M31 co-rotating dwarfs: an additional fossil
+%signature of the M31 merger and of its considerable impact in the
+%whole Local Group (Hammer et al 2013) Major merger in M31-MW system
+%plane galaxies are tidal dwarfs (n-body simulations)\\
+%Kroupa tiene todo un carretazo de que las dwarfs son todas tidal
+%dwarfs\\
+%MIRAR lo que est\'a haciendo Pierre Alan Duc con tidal dwrafs porque en
+%una conferencia este a;o habl\'o de un posible escenario
+%intermedio...\\
+
+%nevertheless the
+%anisotropy and dynamical coherence observed in the Milky Way and M31
+%satellite population is still extreme compared with that of the
+%systems found in the numerical simulations.
+
+% Pawlowski 2015   
+%but those observed in the Milky Way or in M31 tend to be outliers either in thikness or in their extent.
+
+%But satellite galaxies are not particularly good tracers of the underlying dark matter structure (Sawala 2014), and indeed planar structures and anisotropies have been found in the APOSTOLE simulations that include baryonic physics \citep{2016MNRAS.457.1931S}, %Sawalla et al.
+2014
+%in CLUES which is a hight resolution constrained Local Group simulation (Gillet et al. 2015;  Cautun et al. 2015).
+%Nevertheless the anisotropy and dynamical coherence observed in the Milky Way and M31 satellite population is still extreme compared with that of the systems found in the numerical simulations \citep{2015ApJ...815...19P}.% Pawlowski 2015
+%but those observed in the Milky Way or in M31 tend to be outliers either in thikness or in their exte
+
+%\subsection{Previous studies of Local Group satellites}
+%Libeskind 2011
+%\citep{2011MNRAS.411.1525L} Measure the infall direction of satellites
+%in a DM only simulation of one pair of LG halos in a constrained
+%simulation. There is a definite infall direction but it's not
+%quantified in terms of the cosmic web.
+%%Pawlowski 2012
+%\citep{2012MNRAS.424...80P} Compare the kinematic structure of the MW
+%satellites against DM only simulation of high resolutions halos from
+%the Via Lactea and Aquarius projects.  Cannot find a similar kinematic
+%structure (i.e. the orbital poles of the MW satellites) in the
+%simulations. 
+%%Libeskind 2014
+%\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
+%with respect to the V-web. They do it in a DM cosmological simulation
+%(64 Mpch, 1024 3 particles). They find that infall is done along the
+%e3 (i.e. filament) direction.
+%%Tempel 2015
+%\citep{2015MNRAS.450.2727T} They measure the angle between satellites
+%and the direction defined by filaments (Bissous filament finder) to
+%find a signal both in SDSS and the semi-analytic galaxies in the
+%Millennium Simulation.  
+%%Lee y Choi 2015
+%\citep{2015ApJ...799..212L} Detection of alignment of satellites along
+%the direction defined by filaments (velocity shear cosmic web) on the
+%SDSS DR7.
+%%Sawala 2016
+%\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
+%spatial anisotropy the 11 brightest satellites. The anisotropy is
+%quantified the reduced inertia tensor. Still the MW is more
+%anisotropic than all but one of the 24 halos. The analysis is not very
+%thorough and do not show the resulting distribution. Does not compare
+%the results of using DM information only. 
+%Pawlowski 2015
+%\citep{2015ApJ...815...19P} argue that the result from
+%\citep{2016MNRAS.457.1931S} is a product of using a metric that ignores
+%the radial position of the galaxies. They use the ELVIS suite to
+%compare the two analysis methods: reduced vs. full inertia tensor. 
+%Shao 2016
+
+%%%Alignments between galaxies, satellite systems and halos (Shiao et al
+%%%2016)
+%%%Libeskind 2014
+%%\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
+%%with respect to the V-web. They do it in a DM cosmological simulation
+%%(64 Mpch, 1024 3 particles). They find that infall is done along the
+%%e3 (i.e. filament) direction.
+%Libeskind 2011
+
+%%%Tempel 2015
+%%\citep{2015MNRAS.450.2727T} They measure the angle between satellites
+%%and the direction defined by filaments (Bissous filament finder) to
+%%find a signal both in SDSS and the semi-analytic galaxies in the
+%%Millennium Simulation.
+
+%%%Lee y Choi 2015
+%%\citep{2015ApJ...799..212L} Detection of alignment of satellites along
+%%the direction defined by filaments (velocity shear cosmic web) on the
+
+%They do not
+%study DM only simulations and do not narrow down the signal to pairs. 
+%Libeskind 2016
+%\citep{2016arXiv160601516L} Using SDSS DR10 studied galaxy pairs. They find
+%that satellites tend to accumulate towards the companion galaxy. There
+%are up to $\sim 10\%$ more satellites in the space between the pair
+%than expected from an uniform distribution
+
+%The Illustris page says:
+%Simulation Details
+
+%We follow the coupled dynamics of DM and gas with the robust, accurate, and efficient quasi-Lagrangian code AREPO.
+In this approach, an unstructured Voronoi tessellation of the simulation volume allows for dynamic and adaptive spatial discretization, where a set of mesh generating points are moved along with the gas flow.
+This mesh is used to solve the equations of ideal hydrodynamics using a second order, finite volume, directionally un-split Godunov-type scheme, with an exact Riemann solver.
+The gravitational force is calculated with a split Tree-PM approach, where long-range forces are calculated from a particle-mesh method, and short-range forces are calculated with a hierarchical octree algorithm.
+Our galaxy formation model is based on the inclusion of several additional astrophysical processes:
+
+%    Gas cooling and photo-ionization: the cooling function is calculated as a function of gas density, temperature, metallicity, UV radiation field, and AGN radiation field.
+The UV background is a spatially uniform, time dependent field for which reionization completes at z~6.
+%    Star formation and ISM model: our subgrid model for the ISM puts dense gas above 0.13 particles per cubic cm on an effective equation of state, assuming a two-phase medium of cold clouds embedded in a tenuous, hot phase.
+Star formation occurs stochastically following the KS-law and with a Chabrier IMF.
+%    Stellar evolution: stellar populations return mass to the gas phase through stellar winds and supernova.
+We track and follow the rates associated with SN Ia, SN II, and AGB stars.
+The evolving abundances of nine elements (H, He, C, N, O, Ne, Mg, Si, Fe) are independently considered and advected.
+%    Stellar feedback: we employ a kinetic stellar feedback scheme, which generates a wind with velocity scaled to the local DM dispersion, and mass loading inferred from the available SN energy for energy-driven winds (1051 erg per SNII).
+The metal enrichment of winds is modulated such that only 40% of local ISM metals are driven away by these galactic winds.
+%    Black holes and SMBH feedback: we seed new BHs with a mass of 105 solar masses in all FoF groups which become more massive than 7x1010 solar masses.
+The feedback of SMBHs includes both quasar-mode and radio-mode regimes, and a consideration of the radiation field of AGNs, which heats surrounding halo gas, modifying its ionization state and net cooling rate.
+%
+%Resolution table ()
+%
+%The initial conditions assume a LCDM cosmology consistent with WMAP-9 measurements, from which a linear power spectrum is used to create a random realization in a periodic box with side length 75 Mpc/h = 106.5 Mpc, at a starting redshift of 127.
+A series of simulations are run at different resolutions, and a second set is run with only dark matter.
+The main simulation initially has 18203 = 6,028,568,000 hydrodynamic cells, and the same number of DM particles and MC tracers (see table for more details, including mass resolutions and gravitational softening lengths).
+Evolving the main simulation to z=0 used 8,192 compute cores, a peak memory of 25 TB, and 19 million CPU hours.
 
@@
 \end{document}
+
+\grid

### 2016-09-13 paper/ms.tex
paper con results casi listo

@@
 2015).
-These results are from dark matter only simulations, so it would be interesting to see if they still hold for simulations that include baryonic physics, since it was shown by Gonzales et al 2015 that satellites acrreted via filaments are destroyed faster than those that are not.
+These results are from dark matter only simulations, so it would be interesting to see if they still hold for simulations that include baryonic physics, since it was shown by Gonzales et al 2015 that satellites accreted via filaments are destroyed faster than those that are not.
+So far, the planes found in simulations tend to be transient structures (XXXXXXX) and that poses two problems: one is why do we
+see planes in all the three galaxies were we can actually make the
+measurements if they are transient? 
+The second is that these findings seem to be at odds with the observed rotational coherence of the MW satellites for which proper motion measurements exist (Pawlowski et al. 2015).
+%Problem with the MW plane for which
+%some of the dwarfs have proper motion measurements. Another problem:
+%explicación de Buck 2015 sería rara entonces...
 
 In a more general numerical study,   
-\cite{2016arXiv160501728S} use the eagle simulation to study the
+\cite{2016arXiv160501728S} use the EAGLE simulation to study the
 alignment of satellites with respect to the central galaxy. They find
@@
 angle larger than the value observed for the Milky Way.
+In this work, we continue these approach of studying more generally the alignments between the satellites population, the dark matter substructures and the main host halos in the illustris simulation.
+This paper is organized as follows.
+In Section \ref{NumericalSetup} we describe the numerical setup, the sample selection criteria, the method to determine the cosmic web environment and the method to quantify alignments. 
+The alignments and lack thereof obtained are presented in Section \ref{Results} and compared with the Local Group observations.
+Finally, these results are discussed more broadly in Section \ref{Discussion}.
 
-Planes in simulations tend to be transient structures (not
-kinematically coherent) and that poses two problems: one is why do we
-see planes in all the galaxies were we can actually make the
-measurements if they are transient? Problem with the MW plane for which
-some of the dwarfs have proper motion measurements. Another problem:
-explicación de Buck 2015 sería rara entonces...
-
-\section{Numerical Setup}
+\section{Numerical Setup}\label{NumericalSetup}
 
@@
 \caption{Halo pair samples used in this paper located in the
-  plane of relative comoving velocity $V_{AB}$ versus relative
+  plane of relative co-moving velocity $V_{AB}$ versus relative
   distance $R_{AB}$ between the two halos in the pair.
@@
 \label{Method}
-In this paper, our aim is to study alignments: of the
+In this paper, our main aim is to study alignments: of the
 satellite population with the cosmic web, of the dark matter halos
@@
 With this geometrical information we can study the alignments of the two distributions with the cosmic web, and also with the vector that unites the halo pair that host these substructures.
-%Jaime, falta el plot de alineaciones con la cosmic web
+Additionally, we calculate the axis ratio of the distributions to determine its "flatness" and look for differences between dark and bright distributions and between substructure in the full sample and in the LG sample.
 
@@
 
-Some papers claim that once baryonic physics is included more planar distributions are found.
-First we investigate if there is a difference in the bright and dark distribution in terms of their flatness.
-In Figure \ref{fig:StreamPlaneOrbit} we can see that indeed the bright distribution is flatter than the dark distribution.
+\subsection{Alignments of the galaxy pairs with the cosmic web}
+\label{AlignmentsGalCosmicWeb}
+Alignments between galaxies and the cosmic web were investigated by \citep{ForeroRomero2013} who found that the axis that unites halo pairs similar to the MW-M31 pair tends to align with the $\hat e_3$ vector.
+We investigated this alignment on both our Full and LG samples. 
+In Figure \ref{fig:alignment_e3_cosmicweb} we plot the integrated probability of the dot product between the $\hat e_3$ vector and the vector that unites the galaxy pair ($\hat r_{AB}$). 
+This integrated probability shows that $\hat e_3$ and $\hat r_{AB}$ tend to be aligned, which is consistent with the literature results mentioned above. 
+It is also interesting to note that the full sample shows a stronger alignment than that of the LG sample.
+Since there is an alignment between $\hat e_3$ and $\hat r_{AB}$, in the following we will investigate the alignments of the distribution of satellites and of the dark substructures with $\hat r_{AB}$.\\
+\begin{figure}
+\centering
+\includegraphics[width=\hsize]{r_tweb_e3_alignment.pdf}\\
+\caption{.}
+\label{fig:alignment_e3_cosmicweb}
+\end{figure}
+
+\subsection{Comparison between the satellite and the dark substructure distributions}
+\label{DarkBright}
+In the comparisons between observations and simulations, the plane-finding efforts have often been made in dark matter only simulations (Citar a Baumgartdt, Ibata, Pawlowsky cautun, buck etc...), and Sawalla et al.
+claims that once baryonic physics is included more planar distributions are found.
+We wanted to test if this holds true in the Illustris simulation, that also includes baryonic physics.
+So we first investigate if there is a difference in the bright and dark distribution in terms of their flatness.
+This flatness was quantified using the ratio of the semi-minor and semi-major axis of the triaxial distributions of both the bright satellite galaxies and the dark subhalos. 
+In Figure \ref{fig:StreamPlaneOrbit} we can see the integrated probability of the axis ratios for the different halo pairs in both our full and LG samples. 
+We find that indeed the bright distributions are flatter than the distributions that include also the dark substructure.
+This is in agreement with claims that the inclusion of baryonic physics results in more planar structures. 
+However, this result alone is not enough to infer anything about the mechanisms behind the formation of these flatter distribution or if this increased flatness corresponds to the planes of satellite galaxies observed in the Local Group.\\
 \begin{figure}
@@
 
-We then try to fit planes to both the dark and bright distributions in order to test if it is indeed easier to find thinner planes in the bright distribution. 
-We find that the bright planes are thinner.
+\subsection{Plane fitting: plane width versus object number}
+\label{DarkBright}
+We then fit planes to both the dark and bright distributions in order to test if it is indeed easier to find thinner planes in the bright distribution. 
+We first fit planes to all the bright satellites for each halo in both the Full and LG samples and then repeat the process for the distributions that includes also the dark substructure.
+We then calculate the plane width of the best fit plane. %de pronto acá deberia explicar mejor el metodo de plane fitting
+In Figure \ref{fig:plane_width} the integrated probability plot of the plane width for the different halo pairs shows that bright planes are thinner that dark planes in both our full and LG samples and the difference between the bright and dark distributions is starker than for the axis ratios.
+This again is in agreement with the idea that planes planes in simulations occur naturally when baryonic physics are included, but again this result alone is not enough to infer anything about the mechanisms behind their formation.\\
+
 \begin{figure}
@@
 \end{figure}
-But is there a physical reason for that?
-Apparently not, since the thinness of the fitted planes seems to be only due to number of objects: number of bright satellites is smaller than of dark sub-halos and that results naturally in thinner fitted planes.
+
+To test if there is a physical reason for the difference in plane width between the bright and dark distributions or if this difference is due to a sampling effect, we look at the plane width as a function of number of objects in the plane.
+Since the bright satellites are a sub-sample of the dark distribution (that includes also the dark substructure), the number objects in "bright" planes is larger than that of "dark" planes for each given halo.
+In Figure \ref{fig:plane_width_nobjects} we can see that there is a strong correlation between the number of objects in the fitted plane and its width.
+Fewer objects are fitted by thinner planes.
+And in general, there are fewer brigth satellites, so the differences between the width of bright and dark distributions can be attributed to the number of objects and does not seem to be the result of other processes.
+
+{\color{red} Icluir acá gráficas de dark vs bright con el mismo numero?}
 %pregunta para Jaime: en tu código dark quiere decir dm only subhalos o todos los subhalos (dm only y bright)?
-%podríamos hacer como un test extra el plot que yo tenía en mis plot de antes, que es cojer al azar entre los dark un numero de subhalos igual al de bright y ver los anchos de los planos.
 
@@
 
-A second test is to look if there is any evidence of alignments between the distribution of satellites and the axis that unites the main halos that form the pair.
+\subsection{Alignments of the distributions with their environment}
+\label{AlignemntH1H2_sats}
+
+From the comparison between the number of objects and the plane width we could conclude that there is not a physical mechanism behind the Local Group planar structures and that these are just due to the small number of satellites we observe.
+Nevertheless, these observed structures have, besides their special spatial configuration, a dynamical coherence that demands a better explanation for their formation mechanism (Pawlowski et al.
+2014, Ibata et al.
+2013 ...).
+Preferential accretion of the satellites and of the dark substructure has been explored as a possible formation mechanism of the observed Local Group planes of satellites. 
+This mechanism would likely leave an imprint in the alignment between the distribution of satellites and dark substructure and the favoured accretion direction.     
+In this work we study the alignment between the semi-major axis of the distribution and the axis that unites the halo pair. 
+In Figure \ref{fig:lg_alignment} we plot the dot product of the semimajor axis and the axis that unites the two halos unit vectors, for each halo pair in both sub-samples. 
+%second test is to look if there is any evidence of alignments between the distribution of satellites and the axis that unites the main halos that form the pair.
 
@@
 \section{Discussion}
+\label{Discussion}
 Difference between bright and dark distributions are only due to number.\\

### 2017-07-04 paper/ms.tex
updated makefile

@@
-\documentclass{emulateapj}
-\submitted{{\it Submitted for publication in ApJ}}
-\usepackage{multirow,color,wrapfig,ulem}
-\usepackage {graphicx}
-\usepackage{graphics}
-\usepackage[dvips]{epsfig}
-
-%=========================================================================
-%		INTERNAL MACROS
-%=========================================================================
-\def\be{\begin{equation}}
-\def\ee{\end{equation}}
-\def\ba{\begin{eqnarray}}
-\def\ea{\end{eqnarray}}
-
 % To highlight comments 
@@
 \definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
-\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
-\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
-\newcommand{\before}[1]{\textcolor{red}{ #1}}
-\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
-
-\newcommand{\LCDM}{$\Lambda$CDM~}
-\newcommand{\beq}{\begin{eqnarray}}  
-\newcommand{\eeq}{\end{eqnarray}}  
-\newcommand{\zz}{$z\sim 3$} 
-\newcommand{\avg}[1]{\langle{#1}\rangle}  
-\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
 \newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
@@
 \newcommand{\focc}{{\ifmmode{{f_{\rm occ}}}\else{${f_{\rm occ}}$}\fi}}
+\newcommand{\hs}{{\hspace{1mm}}}  
+\newcommand{\tol}{Tololo 1214-277}
+\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
+\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
+\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
+\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
+\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
+\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
+\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
+%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\vek}[1]{\bm{#1}}
+%\newcommand{\lya}{Ly$\alpha$}
+\newcommand{\hb}{H$\beta$}
+\newcommand{\ha}{H$\alpha$}
+\newcommand{\oiii}{[OIII]}
+\newcommand{\oii}{[OII]}
+\newcommand{\nii}{[NII]}
+\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
+\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
+\newcommand{\es}{erg s$^{-1}$}
+\newcommand{\esa}{erg s$^{-1}$}
+\newcommand{\kms}{km s$^{-1}$}
 
-\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\lya}{{Lyman$\alpha$~}}
-\newcommand{\clara}{{\texttt{CLARA}}~}
-\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
-%SAMPLES
-
-%MY COMMANDS #############################################################
-\newcommand{\sub}[1]{\mbox{\scriptsize{#1}}}
-\newcommand{\dtot}[2]{ \frac{ d #1 }{d #2} }
-\newcommand{\dpar}[2]{ \frac{ \partial #1 }{\partial #2} }
-\newcommand{\pr}[1]{ \left( #1 \right) }
-\newcommand{\corc}[1]{ \left[ #1 \right] }
-\newcommand{\lla}[1]{ \left\{ #1 \right\} }
-\newcommand{\bds}[1]{\boldsymbol{ #1 }}
-\newcommand{\oiint}{\displaystyle\bigcirc\!\!\!\!\!\!\!\!\int\!\!\!\!\!\int}
-\newcommand{\mathsize}[2]{\mbox{\fontsize{#1}{#1}\selectfont $#2$}}
-\newcommand{\eq}[2]{\begin{equation} \label{eq:#1} #2 \end{equation}}
-\newcommand{\lth}{$\lambda_{th}$ }
-\newcommand{\reff}{{\ifmmode{r_{\mbox{\tiny eff}}}\else{$r_{\mbox{\tiny eff}}$}\fi}}
-%#########################################################################
-
-%TO DO COMMANDS. Highlight region that needs extra work  #############################################################
-\newcommand{\todo}{\ifmmode \text{\Huge{\(\bullet\)}} \else {\Huge$\bullet$}\fi}
-% \newcommand{\todo}{\ifmmode {\Huge \bullet} \else {\Huge$\bullet$}\fi}
-\newcommand{\tido}{\ifmmode {\bullet} \else $\bullet$\fi}
-\newcommand{\REFS}{(\todo REFS) }
-\newcommand{\toref}{(\todo REFS)}
-%#########################################################################
-
-\begin{document}
-%=========================================================================
-%		FRONT MATTER
-%=========================================================================
-\title{The Spatial Distribution of Local Group Satellites in a
-  Cosmological Context}  
-\author{
-  Ver\'onica Arias \thanks{v.arias@uniandes.edu.co}$^{1}$,
-  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
-}
-
-\affil{
-$^1$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
-}
-
-\begin{abstract}
-We focus on the spatial distribution of bright ($M_V<-8$) satellites and
-pairs of galaxies with similar masses, isolation and kinematic
-configurations as the Local Group. 
-\end{abstract}
-
-\keywords{
-Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
---- Dark Matter --- Methods: numerical 
-}
-
-\section{Introduction}
-
-Since the early works of (el que libeskind dice que habló de
-eso primero) and \cite{1976MNRAS.174..695L}, the observed anisotropic
+Since the early works of (el que libeskind dice que habl\'o de
+eso primero) and %\cite{1976MNRAS.174..695L}, the observed anisotropic
 distribution of satellite galaxies in the Local Group has been a key
@@
 that contained the Magelanic clouds and their stellar tails. This
-anisotropic distribution was further studied in the work of \cite{}Pawlowski
+anisotropic distribution was further studied in the work of Pawlowski
 et. al. (2012), where they included all the known MW satellite galaxies (XXX
@@
 measurements could be performed evidence of satellite planar
-structures have been found.\\
+structures have been found.
 
@@
 \centering
-\includegraphics[width=\hsize]{v_r_pairs.pdf}\\
+\includegraphics[width=0.5\textwidth]{v_r_pairs.pdf}
 \caption{Halo pair samples used in this paper located in the
@@
 \begin{figure}
-\centering
-\includegraphics[width=\hsize]{n_structure.pdf}\\
+\includegraphics[width=\hsize]{n_structure.pdf}
 \caption{Number of bright substructures ($M_{B}<-9$) and dark matter
@@
 \begin{figure}
-\centering
 \includegraphics[width=\hsize]{r_tweb_e3_alignment.pdf}\\
@@
 \begin{figure}
-\centering
 \includegraphics[width=\hsize]{axratio_dark_bright.pdf}\\
@@
 \begin{figure}
-\centering
 \includegraphics[width=\hsize]{plane_width.pdf}\\
@@
 \begin{figure}
-\centering
 \includegraphics[width=\hsize]{plane_width_n_dark.pdf}\\
@@
 \begin{figure}
-\centering
 \includegraphics[width=\hsize]{r_u_alignment.pdf}\\
@@
 \begin{figure*}
-\centering
 \includegraphics[width=0.48\hsize]{significance_full_bright.pdf}
@@
 
-\bibliographystyle{apj}
+\bibliographystyle{mn2e}
 \bibliography{Dwarfs}
@@
 \end{document}
-
-\grid

### 2017-07-04 paper/paper.tex
empezando de cero

\documentclass[useAMS,usenatbib,usegraphicx]{mn2e} 
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{hyperref}
\newcommand{\apj}{ApJ}  
\newcommand{\jcap}{JCAP}  
\newcommand{\apjs}{ApJS}  
\newcommand{\pasa}{PASA}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}

\begin{document}

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellites in a cosmological context]{
The Spatial Distribution of Local Group Satellites in a
  Cosmological Context}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

\maketitle

\begin{abstract}
We focus on the spatial distribution of bright ($M_V<-8$) satellites and
pairs of galaxies with similar masses, isolation and kinematic
configurations as the Local Group. 
\end{abstract}

\begin{keywords}Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
--- Dark Matter --- Methods: numerical 
\end{keywords}

\section{Introduction}
\cite{2012MNRAS.424...80P} 
\bibliographystyle{mn2e}
\bibliography{Dwarfs}

\end{document}

### 2017-07-04 paper/ms.tex
new references

@@
 Finally, these results are discussed more broadly in Section \ref{Discussion}.
-
-\section{Numerical Setup}\label{NumericalSetup}
-
-\subsection{Illustris simulation}
-
-In this work we use the publicly available results from the Illustris
-simulation (Vogelsberger et al. 2014). This cosmological simulation, performed using
-the quasi-Lagrangian code AREPO, follows the coupled evolution of dark
-matter and gas, and includes parametrizations to account for the effects of
-gas cooling, photoionization, star formation, stellar feedback, black
-hole and super massive black hole feedback. Vogelsberger et al. 2014 use a $75 Mpc/h$
-simulation box, with $\Lambda$CDM cosmology initial conditions
-starting at a redshift $z=127$ and consistent with WMAP-9 measurments.
 

### 2017-07-04 paper/paper.tex
new references

@@
 \newcommand{\pasj}{PASJ}    
+\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}
 
@@
 %=========================================================================
-\title[LG satellites in a cosmological context]{
-The Spatial Distribution of Local Group Satellites in a
-  Cosmological Context}
+\title[LG satellite alignments]{
+Local Group Satellite Alignments in a Cosmological Context}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 \section{Introduction}
+
+\section{Numerical Setup}
+\label{sec:NumericalSetup}
+
+\subsection{Illustris simulation}
+
+We use publicly available data from the Illustris Project 
+\citep{2014MNRAS.444.1518V}. 
+This suite of cosmological simulations, performed using the quasi-Lagrangian
+code AREPO \citep{2010MNRAS.401..791S}, follow the coupled evolution of dark 
+matter and gas and includes parametrizations to account for the effects of
+gas cooling, photoionization, star formation, stellar feedback, black
+hole and super massive black hole feedback.
+
+The simulation volume is a cubic box of $75$ \hMpc\ on a side.
+The cosmological parameters are correspond to a $\Lambda$CDM cosmology
+consistent with WMAP-9 measurements \citep{2013ApJS..208...19H}.
+
 \cite{2012MNRAS.424...80P} 

### 2017-07-05 paper/paper.tex
data from the illustris project

@@
 \newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
+\newcommand{\Mpc}{{\ifmmode{{\rm Mpc}}\else{Mpc}\fi}}  
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
+\newcommand{\Msun}{{\ifmmode{{\rm{M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
 
@@
 
-\section{Numerical Setup}
+\section{Data and Algorithms}
 \label{sec:NumericalSetup}
 
-\subsection{Illustris simulation}
+\subsection{Data from the Illustris Project}
 
@@
 The simulation volume is a cubic box of $75$ \hMpc\ on a side.
-The cosmological parameters are correspond to a $\Lambda$CDM cosmology
+The cosmological parameters correspond to a $\Lambda$CDM cosmology
 consistent with WMAP-9 measurements \citep{2013ApJS..208...19H}.
 
-\cite{2012MNRAS.424...80P} 
+We extract halo and galaxy information from the Illustris-1 simulation
+which has the highest resolution in the current release of the
+Illustris Project.
+Illustris-1 has $1820^3$ dark matter particles and $1820^3$ initial gas
+volumen elements. 
+This corresponds to a dark matter particle mass of
+$6.3\times 10^6$\Msun\ and a minimum mass for the baryonic volume
+element of $8.0\times 10^7$\Msun. 
+The corresponding spatial resolution is $1.4$ kpc for the dark matter
+gravitational softening and $0.7$ kpc for the typical size of the
+smallest gas cell size.
+
+We compute the cosmic web from the DM information in the
+Illustris-3 simulation which share the same structure information with
+Illustris-1 on scales of $1$ \Mpc.  
+Illustris-3 has $455^3$ DM particles, corresponding to
+$4.0\times 10^8$ \Msun in DM particle mass and $5.7$ kpc for the DM
+gravitational softwning lentgh.
+
 \bibliographystyle{mn2e}

### 2017-07-05 paper/paper.tex
pair samples

@@
 \newcommand{\Msun}{{\ifmmode{{\rm{M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
+\newcommand{\kms}{{\ifmmode{{\rm{km\ s}^{-1}}}\else{km $\rm{s}^{-1}$}\fi}}
 
@@
 
+\subsection{Galaxy Pair Selection}
+
+We build two samples of galaxy pairs. 
+The first is a general sample of isolated pairs (IP) and the
+second sample correspond to Local Group pairs (LGP).
+The halos in these samples only include the DM halos with maximum
+circular velocities in the range $ 150\ \kms <V_{\rm max}< 350\ \kms$. We
+exclude sub-halos from this selection.
+
+From this set of DM halos we construct the IP sample as follows.
+For each halo $A$ we find its closest halo $B$, if halo $A$ is also
+the closest to halo $B$, the two halos are considered as a pair. 
+Another way to phrase this selection is that pairs do not have
+neighbors closer than the pair's distance.
+We exclude the pairs that have overlapping virial radii. 
+We use this information to exclude all the pairs that have separations
+smaller than the sum of their virial radii, i.e. we exclude
+We find $49$ pairs with those conditions.
+
+We then count the number of galaxies with $M_V<-9$ inside the virial
+radius of each halo, including the central galaxy.
+We only keep pairs where both halos have at least 5 bright galaxies. 
+This reduces the sample to $24$ pairs.  
+This is the IP sample.
+
+We build the LGP sample by keeping the pairs in the IP sample with
+a separation between its brightest galaxies of $0.75\ \Mpc <R_{AB}< 1.50\ \Mpc$
+and a relative radial velocity (including the Hubble flow) of $V_{AB}<-100$ km s$^{-1}$.
+These intervals are close to the Local Group observed values.
+
 \bibliographystyle{mn2e}

### 2017-07-05 paper/paper.tex
new plot

@@
 a separation between its brightest galaxies of $0.75\ \Mpc <R_{AB}< 1.50\ \Mpc$
-and a relative radial velocity (including the Hubble flow) of $V_{AB}<-100$ km s$^{-1}$.
+and a negative relative radial velocity (including the Hubble flow) 
 These intervals are close to the Local Group observed values.
+The LGP sample is reduced to $12$ pairs.
+
+Figure \ref{fig:samples} show the results for the IP and LGP samples
+in the plane of radial velocity versus distance.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{v_r_pairs.pdf}
+\caption{Halo pair samples used in this paper located in the
+  plane of relative radial velocity $V_{r,AB}$ versus 
+  distance $R_{AB}$ between the two halos in the pair.
+  The IP sample (24 pairs) is a general pair sample, while the LGP
+  sample (12 pairs) resemples the separation and kinematic
+  conditions observed in the Local Group.} 
+\label{fig:samples}
+\end{figure}
 

### 2017-07-06 paper/ms.tex
cosmic web

@@
 \newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
-%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
+\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
 \newcommand{\dd}{\mathrm{d}}
@@
 
-\subsection{Sample Selection}
-
-We select all halos with maximum circular velocities in the
-range 150 km s$^{-1}$ $<V_{\rm max}<$ 350 km s$^{1}$.
-We exclude sub-halos from this selection.
-From this set we construct a sample of pairs as follows.
-For each halo $A$ we find its closest halo $B$, if halo $A$ is also
-the closest to halo $B$, the two halos are considered as a pair. 
-Another way to phrase this selection is that pairs do not have
-neighbors closer than the pair's distance.
-We exclude the pairs that are closer than
-There are $53$ pairs with those conditions in the simulation.
-
-We extract from the simulation spheres of $2$ \hMpc  in radius around
-the pair's center of mass. 
-We use this information to exclude all the pairs that have separations
-smaller than the sum of their virial radii, i.e. we exclude
-interacting pairs. 
-This reduces to $49$ the number of pairs in the sample.
-
-We count the number of galaxies with $M_V<-9$ inside the virial
-radius of each halo, including the central galaxy.
-We only keep pairs where both halos have 5 bright galaxies at least. 
-This reduces the sample to $24$ pairs. 
-We call this sample the Full Sample.
-
-From the Full Sample we build a second sample based on the pairs' kinematics. 
-Figure \ref{fig:samples} shows the co-moving separation and relative
-speed between the two halos in the pair.
-The stars in the Figure represent the pairs with a separation in the
-range $0.75\hMpc <R_{AB}< 1.50\hMpc$ and relative velocity in the
-range $V_{AB}>100$ km s$^{-1}$, which are close to the Local Group
-Observed values.
-We call this sample the LG Sample.
-
-The number of pairs in the Full Sample is consistent with previous
-calculations. 
-\cite{ForeroRomero2013} performed a study of the LG kinematics using a
-cosmological N-body simulation as a benchmark. 
-In their study, using criteria similar to ours to define the Full
-Sample, they found 1923 pairs in a volume of $250^3$ $h^{-3}$
-Mpc$^{3}$. 
-With the same number density we expect to find $52$ pairs in the
-volume of the Illustris simulation, which is very close to the actual
-number of $49$ pairs.
-
-In the same study they found 158 pairs with broad kinematic
-characteristics, similar to the definition of our LG sample. 
-This represents a reduction of a factor of $12$ from their General
-Sample. 
-With those numbers in mind we would expect to keep at least $4$ pairs
-in the Illustris volume. 
-Given that our conditions are slightly more relaxed (we do not ask for
-isolation criteria from massive halos) we end up with a larger sample
-size, but still consistent with the fact that LG-like pairs are
-scarce.  
 %no me es muy claro este ultimo parrafo. En nuestros samples pasamos de 49 a 24 (o sea se redujo en un factor 2 en vez de un factor 12)
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{v_r_pairs.pdf}
-\caption{Halo pair samples used in this paper located in the
-  plane of relative co-moving velocity $V_{AB}$ versus relative
-  distance $R_{AB}$ between the two halos in the pair.
-  The R\&V sample is the closest to the separation and kinematic
-  conditions observed in the Local Group.}
-\label{fig:samples}
-\end{figure}
 

### 2017-07-06 paper/paper.tex
new titles
cosmic web

@@
 %=========================================================================
-\title[LG satellite alignments]{
-Local Group Satellite Alignments in a Cosmological Context}
+\title[LG satellite alignments]{Satellite Alignments in the Local Group}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 
-\section{Data and Algorithms}
+\section{Local Group Analogues in the Illustris Simulation}
 \label{sec:NumericalSetup}
-
-\subsection{Data from the Illustris Project}
 
@@
 
-\subsection{Galaxy Pair Selection}
+\subsection{Sample Selection: Local Group Analogues}
 
@@
 
+\section{Cosmic Web Calculations}
+
+We also find the place IS and LGS pairs into the cosmic web as quantified by the deformation tensor
+\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
+This method computes a cartesian grid the tensor 
+\begin{equation}
+T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
+\end{equation}
+%
+where $\phi$ is a pseudo-gravitational potential that follows the
+Poisson equation $\nabla^2\phi=-\delta$, with $\delta$ the DM matter
+overdentisy, and the $r_i$ coordinates correspond to a cartesian
+system with $i=1,2,3$.
+
+This tensor can be diagonalized.
+Its eigenvalues ($\lambda_1 > \lambda_2 > \lambda_3$) and
+corresponding eigenvectors ($\hat{e}_1$, $\hat{e}_2$, $\hat{e}_3$)
+define the degree and direction of stability around the neighborhood
+where the tensor is computed. 
+This allows the classification of that region either as a peak,
+filament, sheet or voids in the case of three, two, one or zero
+eigenvalues larger than a given threshold $\lambda_{\rm th}$.
+
+In this study we compute these eigenvalues and eigenvectors over the
+dark matter component of the Illustris-3 simulation on a cubic mesh of
+$74$ cells on a side. 
+This resolution corresponds to $\sim 1$ \hMpc.
+We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
+scheme, then smooth the density field with a gaussian window with a
+physical scale equal to the cell size.
+
+We choose this interpolation and smoothing scale for two reasons.
+First, because it corresponds to the typical pair separation in our
+sample, making each halo in the pair share the same environment.
+Second, because it allows a direct comparison with previous results in
+the literature that used the same methodology to quantify the cosmic
+web environment for Local Group pairs in a cosmological context
+\citep{ForeroRomero2013,2015ApJ...799...45F}.
+
 \bibliographystyle{mn2e}
@@
 
+%% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P
 \end{document}

### 2017-07-06 paper/ms.tex
inertia tensor

@@
 
-\subsection{Cosmic Web environment}
-%me parece que la palabra "place" puede ser confusa. 
-We place the pairs in our sample into the cosmic web as quantified by
-the deformation tensor.
-\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
-This method computes a cartesian grid the tensor $T_{ij}$,
-\begin{equation}
-T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j}
-\end{equation}
-%
-where $\phi$ is a pseudo-gravitational potential that follows the
-Poisson equation $\nabla^2\phi=-\delta$ and the $r_i$ coordinates
-correspond to a cartesian system with $i=1,2,3$.
-
-This tensor is and symmetric and can be diagonalized.
-Its eigenvalues ($\lambda_1 > \lambda_2 > \lambda_3$) and
-corresponding eigenvectors ($\hat{e}_1$, $\hat{e}_2$, $\hat{e}_3$)
-define the degree and direction of stability around the neighborhood
-where the tensor was computed. 
-This allows the classification of that region either as a peak,
-filaments, sheets and voids in the case of three, two, one or zero
-eigenvalues larger than a given threshold $\lambda_{th}$.
-
-In this study we compute these eigenvalues and eigenvectors over the
-dark matter component of the Illustris-3 simulation on a cubic mesh of
-$74$ cells on a side. 
-This resolution corresponds to $\sim 1$ Mpc h.
-We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
-scheme. 
-We proceed to smooth the density field with a gaussian window with a
-physical scale equal to the cell size.
-
-We choose this interpolation and smoothing scale for two reasons.
-First, because it corresponds to the typical pair separation in our
-sample.
-Second, because it allows a direct comparison with other results in
-the literature that used the same methodology to quantify the cosmic
-web environment for Local Group pairs in a cosmological context
-\citep{ForeroRomero2013,2015ApJ...799...45F}.
-
 \subsection{Characterization of spatial distributions}
@@
 with the axis that unites them, etc...   
-To do this, we fitted a triaxial spheroid to both the satellite (bright) and the dark matter (dark) subhalo distributions, to get both their semi-major and semi-minor axis. 
-With this geometrical information we can study the alignments of the two distributions with the cosmic web, and also with the vector that unites the halo pair that host these substructures.
-Additionally, we calculate the axis ratio of the distributions to determine its "flatness" and look for differences between dark and bright distributions and between substructure in the full sample and in the LG sample.
+To do this, we fitted a triaxial spheroid to both the satellite
+(bright) and the dark matter (dark) subhalo distributions, to get both
+their semi-major and semi-minor axis.   
+With this geometrical information we can study the alignments of the
+two distributions with the cosmic web, and also with the vector that
+unites the halo pair that host these substructures. 
+Additionally, we calculate the axis ratio of the distributions to
+determine its "flatness" and look for differences between dark and
+bright distributions and between substructure in the full sample and
+in the LG sample.
 

### 2017-07-06 paper/paper.tex
inertia tensor

@@
 radius of each halo, including the central galaxy.
-We only keep pairs where both halos have at least 5 bright galaxies. 
-This reduces the sample to $24$ pairs.  
+We only keep pairs where both halos have at least 5 bright galaxies, 
+reducing the sample to $24$ pairs.  
 This is the IP sample.
@@
 \section{Cosmic Web Calculations}
+\label{sec:CosmicWeb}
 
@@
 where $\phi$ is a pseudo-gravitational potential that follows the
-Poisson equation $\nabla^2\phi=-\delta$, with $\delta$ the DM matter
+Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
 overdentisy, and the $r_i$ coordinates correspond to a cartesian
@@
 Second, because it allows a direct comparison with previous results in
-the literature that used the same methodology to quantify the cosmic
+the literature that used the same setup to quantify the cosmic
 web environment for Local Group pairs in a cosmological context
 \citep{ForeroRomero2013,2015ApJ...799...45F}.
+
+\section{Satellite Spatial Distribution and Alignment}
+\label{sec:SpatialMeasurements}
+
+We characterize the satellite spatial distribution in two ways. 
+First, by computing the inertia tensor defined as
+
+\begin{equation}
+{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
+  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
+\end{equation}
+%
+where $k$ indexes the set of satellites of interest
+$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the
+positions pof the host DM halo, $\bf{1}$ is the unit matrix,  and
+${\bf r}^T$ is the transposed vector $\bf{r}$. 
+We finally compute the eigenvalues and eigenvector of this tensor.
 

### 2017-07-10 paper/paper.tex
sample selection

@@
 
-We build two samples of galaxy pairs. 
-The first is a general sample of isolated pairs (IP) and the
-second sample correspond to Local Group pairs (LGP).
-The halos in these samples only include the DM halos with maximum
-circular velocities in the range $ 150\ \kms <V_{\rm max}< 350\ \kms$. We
-exclude sub-halos from this selection.
+We build a sample of Local Group Analgues (LGA) by performing a selection on
+the stellar mass and isolation properties of the galaxies in the
+simulation. The conditions to select LGA galaxies are the following.
 
-From this set of DM halos we construct the IP sample as follows.
-For each halo $A$ we find its closest halo $B$, if halo $A$ is also
+\begin{itemize}
+\item {\bf Stellar mass}. LGA galaxy pairs are composed by galaxies with stellar mass in the
+range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
+\item {\bf Dominant pairs}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
 the closest to halo $B$, the two halos are considered as a pair. 
@@
 neighbors closer than the pair's distance.
-We exclude the pairs that have overlapping virial radii. 
-We use this information to exclude all the pairs that have separations
-smaller than the sum of their virial radii, i.e. we exclude
-We find $49$ pairs with those conditions.
+\item {\bf Separation}. The distance between the galaxies' center of
+  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
+\item {\bf Isolation}. For each galaxy in the pair there cannot be a galaxy more
+  massive than the lightest galaxy in the pair within a radius of $2$
+  Mpc. 
+\end{itemize}
 
-We then count the number of galaxies with $M_V<-9$ inside the virial
-radius of each halo, including the central galaxy.
-We only keep pairs where both halos have at least 5 bright galaxies, 
-reducing the sample to $24$ pairs.  
-This is the IP sample.
-
-We build the LGP sample by keeping the pairs in the IP sample with
-a separation between its brightest galaxies of $0.75\ \Mpc <R_{AB}< 1.50\ \Mpc$
-and a negative relative radial velocity (including the Hubble flow) 
-These intervals are close to the Local Group observed values.
-The LGP sample is reduced to $12$ pairs.
-
-Figure \ref{fig:samples} show the results for the IP and LGP samples
-in the plane of radial velocity versus distance.
+We find $19$ pairs of galaxies fulfilling these conditions.
+Figure \ref{fig:samples} shows the radial velocity versus distance for
+the LGA pairs.
 
@@
 
+% referencia posiciones satellites
+% http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P
+
 \bibliographystyle{mn2e}

### 2017-07-10 paper/paper.tex
plane width + table with interesting quantities

@@
 Illustris-1 on scales of $1$ \Mpc.  
-Illustris-3 has $455^3$ DM particles, corresponding to
+Illustris-3 has $456^3$ DM particles, corresponding to
 $4.0\times 10^8$ \Msun in DM particle mass and $5.7$ kpc for the DM
@@
 range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
-\item {\bf Dominant pairs}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
+\item {\bf Dominant pair}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
 the closest to halo $B$, the two halos are considered as a pair. 
 Another way to phrase this selection is that pairs do not have
-neighbors closer than the pair's distance.
+neighbors closer than the pair's separation.
 \item {\bf Separation}. The distance between the galaxies' center of
@@
 
-We characterize the satellite spatial distribution in two ways. 
+We characterize the bright ($M_V<-9$) satellite spatial distribution
+with four different metrics.
+
+\begin{enumerate}
+\item{The inertia tensor}.
+\item{Fitting planes}.
+\item{Velocity Anisotropy}.
+\item{Alignment with the cosmic web}. 
+\end{enumerate}
+
+I what follows we describe the details of implementation of each
+metric.
+
+\subsection{Inertia Tensor}
+\label{sub:inertia}
 First, by computing the inertia tensor defined as
@@
 
+\subsection{Plane fitting}
+\label{sub:planes}
+
+We fit satellite planes around each galaxy in the pair by randomly
+generating 10000 unit vectors over the  sphere, each vector
+representing the direction perpendicular to a plane passing through
+the main galaxy's center of mass. 
+We compute the dot product of the unit vector with the position vector
+for each satellite, this scalar gives us the satellite distance to the
+plane. 
+The best plane is determined by the vector that gives the lowest
+position satellite distance dispersion. 
+We take the dispersion value as a measure of the plane's width.
+For comparison we also store the value and direction giving the
+highest distance dispersion.
+
+\subsection{Velocity Anisotropy}
+\label{sub:beta}
+
+The velocity anisotropy paramenter, $\beta$ is defined as
+
+\begin{equation}
+  \beta = 1 - \frac{\sum_i v^2_{\rm{tan}; i}}{2\sum_i v^{2}_{\rm{rad};i}},
+\label{eq:beta}
+\end{equation}
+% 
+where $v_{\rm{tan/rad};i}$ correspond to the tangential/radial
+velocity of the $i$-th satellite with respect to the central galaxy.
+
+\begin{table*}
+  \centering
+\begin{tabular}{lll}
+\hline\hline
+Symbol & Units & Description\\\hline
+$M_{\star}$ & $10^{10}$\Msun & Stellar mass\\
+$N_s$ & & Number of satellites with $M_V<-9$\\
+$a > b> c$ & & Inertia tensor eigenvalues. \\
+$\hat{s}_1$, $\hat{s}_2$, $\hat{s}_3$ & & Inertia tensor eigenvectors. \\
+$\beta$  &  & Satellite Velocity Anisotropy\\
+$\sigma_s$ & kpc & Plane width\\
+$\lambda_1>\lambda_2>\lambda_3$ &  & Hessian Matrix
+eigenvalues\\
+$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ & - & Hessian Matrix
+eigenvectors\\ 
+$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
+
+\hline\hline
+\end{tabular}
+  \caption{Overview of the parameters computed for each central galaxy
+    and its satellite system.
+  \label{tab:models}}
+\end{table*}
+
 \bibliographystyle{mn2e}
@@
 
+%% Alignments between galaxies, satellite systems and haloes
+%% https://arxiv.org/pdf/1605.01728.pdf
+
+%% The tangential velocity excess of the Milky Way satellites
+%% https://arxiv.org/pdf/1612.01529.pdf
+
 %% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P

### 2017-07-11 paper/paper.tex
references
alignments

@@
 
-We also find the place IS and LGS pairs into the cosmic web as quantified by the deformation tensor
+We place the LGA pairs into the cosmic web as quantified by the
+deformation tensor  
 \citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
@@
 %
-where $\phi$ is a pseudo-gravitational potential that follows the
+where $\phi$ is a pseudo-gravitational potential that satisfies the
 Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
@@
 ${\bf r}^T$ is the transposed vector $\bf{r}$. 
-We finally compute the eigenvalues and eigenvector of this tensor.
+We finally compute the eigenvalues, $a>b>c$, and corresponding
+eigenvectors, $\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$, of this tensor.
+In the case of a sheet-like configuration the vector perpendicular to
+the sheet would be signaled by, $\hat{I}_a$, the eigenvector of the
+largest eigenvalue.
 
@@
 We take the dispersion value as a measure of the plane's width.
-For comparison we also store the value and direction giving the
+For comparison we store the value and direction giving the
 highest distance dispersion.
+We denote by $\hat{p}$ the unit vector defining the direction
+perpendicular to the best plane.
 
@@
 $\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
-
 \hline\hline
@@
 \end{table*}
+
+\subsection{Cosmic Web Alignment}
+\label{sub:webalignment}
+
+\cite{2015ApJ...799...45F} showed tha LGA pairs present alignments
+with the cosmic web.
+The strongest alignment is between the eigenvector associated  with the smallest
+eigenvalue, $\hat{e}_3$, and the vector $\hat{r}_{AB} $connecting the two halos in
+the pair. 
+The eigenvector $\hat{e}_3$ indicates the direction along
+which the cosmic web filament lies and in the case of being on a local
+sheet it is a vector lying on the pancakes' plane.
+
+Following \cite{} we want to find the cosmic web preferential
+direction towards which the vectors $\hat{r}_{AB}$, $\hat{s}_3$ and
 
@@
 
+%% Tambien deberiamos sacar las alineaciones con el momentum angular
+%% de las estrellas de las galaxias principales.
+
 %% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P

### 2017-07-11 paper/paper.tex
table

@@
 %=========================================================================
-\title[LG satellite alignments]{Satellite Alignments in the Local Group}
+\title[LG satellite alignments]{Local Group Satellite Alignments}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 \section{Introduction}
+
+\section{Observational Characterists of Andromeda and the Milky Way}
+\label{sec:obs}
 
@@
 \begin{itemize}
-\item {\bf Stellar mass}. LGA galaxy pairs are composed by galaxies with stellar mass in the
+\item LGA galaxy pairs are composed by galaxies with stellar mass in the
 range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
-\item {\bf Dominant pair}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
+\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
 the closest to halo $B$, the two halos are considered as a pair. 
@@
 neighbors closer than the pair's separation.
-\item {\bf Separation}. The distance between the galaxies' center of
+\item The distance between the galaxies' center of
   mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
-\item {\bf Isolation}. For each galaxy in the pair there cannot be a galaxy more
+\item For each galaxy in the pair there cannot be a galaxy more
   massive than the lightest galaxy in the pair within a radius of $2$
@@
 
-We find $19$ pairs of galaxies fulfilling these conditions.
+We find $19$ pairs with these conditions.
 Figure \ref{fig:samples} shows the radial velocity versus distance for
@@
 \citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
-This method computes a cartesian grid the tensor 
+This method computes a cartesian grid the tidal tensor 
 \begin{equation}
@@
 Symbol & Units & Description\\\hline
-$M_{\star}$ & $10^{10}$\Msun & Stellar mass\\
+$M_{\star}$ & $10^{10}$\Msun & Stellar mass of the central galaxy\\
 $N_s$ & & Number of satellites with $M_V<-9$\\
 $a > b> c$ & & Inertia tensor eigenvalues. \\
-$\hat{s}_1$, $\hat{s}_2$, $\hat{s}_3$ & & Inertia tensor eigenvectors. \\
+$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
 $\beta$  &  & Satellite Velocity Anisotropy\\
 $\sigma_s$ & kpc & Plane width\\
-$\lambda_1>\lambda_2>\lambda_3$ &  & Hessian Matrix
+$\lambda_1>\lambda_2>\lambda_3$ &  & Tidal tensor
 eigenvalues\\
-$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ & - & Hessian Matrix
+$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ &  & Tidal tensor
 eigenvectors\\ 
@@
 
-Following \cite{} we want to find the cosmic web preferential
-direction towards which the vectors $\hat{r}_{AB}$, $\hat{s}_3$ and
+Following \cite{2014MNRAS.443.1090F} we compute the closest cosmic web
+eigenvalue  towards which the vectors $\hat{r}_{AB}$, $\hat{p}$ and
+$\hat{I}_a$ are aligned.
 

### 2017-07-11 code/readfileRandom.py
removing old scripts

@@ -1,556 +1,0 @@
-import numpy as np
-import scipy as sp
-import scipy.stats
-import pdb
-import matplotlib.pyplot as plt		# paquete para graficar
-import matplotlib.cm as cm
-from scipy.interpolate import interp1d
-
-def loading_snapshot(snap_name,i):
-	data = np.loadtxt(snap_name)
-	x = data[:,1]
-	y = data[:,2]
-	z = data[:,3]
-	vx = data[:,4]
-	vy = data[:,5]
-	vz = data[:,6]
-	vmax = data[:,7]
-	Mag  = data[:,8]
-	return x, y, z, vx, vy, vz, vmax, Mag
-
-#finds the 2 main halos 
-def MainHalos(x, y, z, vx, vy, vz, vmax, Mag):
-        max_vmax = np.amax(vmax)
-        max_vmax = np.amax(vmax)
-        indexH = np.where(vmax >= max_vmax)
-        index = np.where(vmax < max_vmax)
-        index = index[0]
-	return x[index], y[index], z[index], vx[index], vy[index], vz[index], vmax[index], Mag[index], x[indexH], y[indexH], z[indexH], vx[indexH], vy[indexH], vz[indexH], vmax[indexH], Mag[indexH]  
-
-# determines which subhalos "belong" to which main halo
-def AllCriteria(x, y, z, vx, vy, vz, vmax, Mag, dist_a, dist_b, DistTreshold, MagTresholdUPPER, MagTresholdLOWER):
-        index = np.where((dist_a < dist_b)*(dist_a < DistTreshold)*(Mag<MagTresholdUPPER)*(Mag>MagTresholdLOWER)) 
-        index = index[0]
-	return x[index], y[index], z[index], vx[index], vy[index], vz[index], vmax[index], Mag[index] 
-
-#selects subhalos above a certain vmax
-def vmaxCut(x, y, z, vx, vy, vz, vmax, Mag, dist_a, dist_b, DistTreshold, MagTresholdUPPER, MagTresholdLOWER, vmaxTresholdLOWER):
[…]

### 2017-07-11 code/readfileRandom_Allroutines.py

@@ -1,479 +1,0 @@
-import numpy as np
-import scipy as sp
-import scipy.stats
-import pdb
-import matplotlib.pyplot as plt		# paquete para graficar
-import matplotlib.cm as cm
-
-def loading_snapshot(snap_name,i):
-	data = np.loadtxt(snap_name)
-	x = data[:,1]
-	y = data[:,2]
-	z = data[:,3]
-	vx = data[:,4]
-	vy = data[:,5]
-	vz = data[:,6]
-	vmax = data[:,7]
-	Mag  = data[:,8]
-	return x, y, z, vx, vy, vz, vmax, Mag
-
-def CalculateAngularMomentum(x, y, z, vx, vy, vz, Numb):
-	posHalo_modulus=np.zeros([Numb])
-	#velHalo=np.zeros([Numb])
-	#L_Halo=np.zeros([Numb])
-	L_Halo_modulus=np.zeros([Numb])
-	for j in range (Numb):
-		posHalo = 10.**(-3)*np.array([x[j],y[j],z[j]])
-		print "posHalo" , posHalo
-		posHalo_modulus[j] = 10.**(-3)*np.sqrt(x[j]*x[j]+y[j]*y[j]+z[j]*z[j])
-		print "posHalo_modulus" , posHalo_modulus[j]
-        	velHalo = np.array([vx[j],vy[j],vz[j]])
-        	#velHalo_modulus[j] = np.sqrt(vx[j]*vx[j]+vy[j]*vy[j]+vz[j]*vz[j])
-		print "velHalo" , velHalo
-        	L_Halo  = np.cross(posHalo, velHalo)  
-		print "L_Halo" , L_Halo
-		L_Halo_modulus[j] = np.sqrt((L_Halo*L_Halo).sum())
-		print "j", j ,"L_Halo_modulus[j]", L_Halo_modulus[j] 
-	#HaloVY_H1.append(velH1_Y)
-	#posHaloH1.append(posHalo_modulus)
-	#L_haloH1.append(L_halo_modulus)
-	## kinetic energy per unit mass
-	#VelVel = ((velHalo*velHalo).sum())	
-	#K_halo = 0.5*VelVel
-	#K_haloH1.append(K_halo)
-	return L_Halo_modulus[j], posHalo_modulus[j] 
-
-def MainHalos(x, y, z, vx, vy, vz, vmax, Mag):
-        max_vmax = np.amax(vmax)
-        max_vmax = np.amax(vmax)
[…]

### 2017-07-18 paper/paper.tex
condition on bright sats
new mnras style

@@
-\documentclass[useAMS,usenatbib,usegraphicx]{mn2e} 
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
+
 %=========================================================================
@@
 \usepackage{color}
+\usepackage{caption}
 \usepackage{hyperref}
-\newcommand{\apj}{ApJ}  
-\newcommand{\jcap}{JCAP}  
-\newcommand{\apjs}{ApJS}  
-\newcommand{\pasa}{PASA}  
-\newcommand{\apjl}{ApJL}  
-\newcommand{\aj}{AJ}  
-\newcommand{\mnras}{MNRAS}  
-\newcommand{\mnrassub}{MNRAS accepted}  
-\newcommand{\aap}{A\&A}  
-\newcommand{\aaps}{A\&AS}  
-\newcommand{\araa}{ARA\&A}  
-\newcommand{\nat}{Nature}  
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}    
-\newcommand{\pasj}{PASJ}    
-\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
-\newcommand{\Mpc}{{\ifmmode{{\rm Mpc}}\else{Mpc}\fi}}  
+\usepackage{bm}
+%Non reposionated tables
+
+%=========================================================================
+%		INTERNAL MACROS
+%=========================================================================
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\ba{\begin{eqnarray}}
+\def\ea{\end{eqnarray}}
+
+% To highlight comments 
+\definecolor{red}{rgb}{1,0.0,0.0}
+\newcommand{\red}{\color{red}}
+\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
+\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
+\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
+\newcommand{\before}[1]{\textcolor{red}{ #1}}
+\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
+\newcommand{\hs}{{\hspace{1mm}}}  
+\newcommand{\tol}{Tololo 1214-277}
+\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
+\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
+\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
+\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
+\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
+\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
+\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\vek}[1]{\bm{#1}}
+\newcommand{\hb}{H$\beta$}
+\newcommand{\ha}{H$\alpha$}
+\newcommand{\oiii}{[OIII]}
+\newcommand{\oii}{[OII]}
+\newcommand{\nii}{[NII]}
+\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
+\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
+\newcommand{\es}{erg s$^{-1}$}
+\newcommand{\esa}{erg s$^{-1}$}
+\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
 \newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
 \newcommand{\Msun}{{\ifmmode{{\rm{M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
-\newcommand{\kms}{{\ifmmode{{\rm{km\ s}^{-1}}}\else{km $\rm{s}^{-1}$}\fi}}
+
+\newcommand{\jefr}[1]{\textcolor{darkgreen}{\bf JEFR: \textit{#1}}}
 
@@
 
-The simulation volume is a cubic box of $75$ \hMpc\ on a side.
+The simulation volume is a cubic box of $75$ \Mpch\ on a side.
 The cosmological parameters correspond to a $\Lambda$CDM cosmology
@@
 Illustris-3 simulation which share the same structure information with
-Illustris-1 on scales of $1$ \Mpc.  
+Illustris-1 on scales of $1$ Mpc.  
 Illustris-3 has $456^3$ DM particles, corresponding to
@@
   Mpc. 
+\item Each galaxy in the pair must have at least $5$ satellites
+  brighter than  $M_V<-9$.
 \end{itemize}
 
-We find $19$ pairs with these conditions.
+We find $11$ pairs with these conditions.
 Figure \ref{fig:samples} shows the radial velocity versus distance for
@@
 $74$ cells on a side. 
-This resolution corresponds to $\sim 1$ \hMpc.
+This resolution corresponds to $\sim 1$ \Mpch.
 We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
@@
 
-\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 \bibliography{Dwarfs}

### 2017-07-18 paper/paper.tex
new figure

@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.5\textwidth]{v_r_pairs.pdf}
-\caption{Halo pair samples used in this paper located in the
-  plane of relative radial velocity $V_{r,AB}$ versus 
-  distance $R_{AB}$ between the two halos in the pair.
-  The IP sample (24 pairs) is a general pair sample, while the LGP
-  sample (12 pairs) resemples the separation and kinematic
-  conditions observed in the Local Group.} 
-\label{fig:samples}
-\end{figure}
+\includegraphics[width=0.31\textwidth]{nsat.pdf}
+\includegraphics[width=0.31\textwidth]{mstar.pdf}
+\includegraphics[width=0.31\textwidth]{vmax.pdf}
+\caption{Numer of satellites, stellar mass, vmax\label{fig:general}}
+\end{figure*}
+%\caption{Halo pair samples used in this paper located in the
+%  plane of relative radial velocity $V_{r,AB}$ versus 
+%  distance $R_{AB}$ between the two halos in the pair.
+%  The IP sample (24 pairs) is a general pair sample, while the LGP
+%  sample (12 pairs) resemples the separation and kinematic
+%  conditions observed in the Local Group.}
 

### 2017-07-20 paper/paper.tex
caption

@@
 We find $11$ pairs with these conditions.
-Figure \ref{fig:samples} shows the radial velocity versus distance for
-the LGA pairs.
+Figure \ref{fig:general} shows the stellar masses, maximum circular
+velocities and the number of bright satellites for all the pairs in
+the sample.
 
@@
 \centering
-\includegraphics[width=0.31\textwidth]{nsat.pdf}
 \includegraphics[width=0.31\textwidth]{mstar.pdf}
 \includegraphics[width=0.31\textwidth]{vmax.pdf}
-\caption{Numer of satellites, stellar mass, vmax\label{fig:general}}
+\includegraphics[width=0.31\textwidth]{nsat.pdf}
+\caption{Basic characteristics for the 11 pairs selected to be Local
+  Group Analogues (circles). From left to right: stellar mass, maximum circular
+  velocity and number of bright ($M_V<-9$) satellites.
+  Galaxy A is the galaxy with the higher stellar mass.
+  The squares represent the same characteristics for the observed
+  Local Group. 
+\label{fig:general}}
 \end{figure*}
-%\caption{Halo pair samples used in this paper located in the
-%  plane of relative radial velocity $V_{r,AB}$ versus 
-%  distance $R_{AB}$ between the two halos in the pair.
-%  The IP sample (24 pairs) is a general pair sample, while the LGP
-%  sample (12 pairs) resemples the separation and kinematic
-%  conditions observed in the Local Group.}
 

### 2017-07-26 paper/paper.tex
new plot in paper
cum ditro beta
new plots into the paper
remove cosmic web

@@
 
-We compute the cosmic web from the DM information in the
-Illustris-3 simulation which share the same structure information with
-Illustris-1 on scales of $1$ Mpc.  
-Illustris-3 has $456^3$ DM particles, corresponding to
-$4.0\times 10^8$ \Msun in DM particle mass and $5.7$ kpc for the DM
-gravitational softwning lentgh.
-
 \subsection{Sample Selection: Local Group Analogues}
@@
 
-\section{Cosmic Web Calculations}
-\label{sec:CosmicWeb}
-
-We place the LGA pairs into the cosmic web as quantified by the
-deformation tensor  
-\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
-This method computes a cartesian grid the tidal tensor 
-\begin{equation}
-T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
-\end{equation}
-%
-where $\phi$ is a pseudo-gravitational potential that satisfies the
-Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
-overdentisy, and the $r_i$ coordinates correspond to a cartesian
-system with $i=1,2,3$.
-
-This tensor can be diagonalized.
-Its eigenvalues ($\lambda_1 > \lambda_2 > \lambda_3$) and
-corresponding eigenvectors ($\hat{e}_1$, $\hat{e}_2$, $\hat{e}_3$)
-define the degree and direction of stability around the neighborhood
-where the tensor is computed. 
-This allows the classification of that region either as a peak,
-filament, sheet or voids in the case of three, two, one or zero
-eigenvalues larger than a given threshold $\lambda_{\rm th}$.
-
-In this study we compute these eigenvalues and eigenvectors over the
-dark matter component of the Illustris-3 simulation on a cubic mesh of
-$74$ cells on a side. 
-This resolution corresponds to $\sim 1$ \Mpch.
-We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
-scheme, then smooth the density field with a gaussian window with a
-physical scale equal to the cell size.
-
-We choose this interpolation and smoothing scale for two reasons.
-First, because it corresponds to the typical pair separation in our
-sample, making each halo in the pair share the same environment.
-Second, because it allows a direct comparison with previous results in
-the literature that used the same setup to quantify the cosmic
-web environment for Local Group pairs in a cosmological context
-\citep{ForeroRomero2013,2015ApJ...799...45F}.
-
 \section{Satellite Spatial Distribution and Alignment}
@@
 \item{Velocity Anisotropy}.
-\item{Alignment with the cosmic web}. 
 \end{enumerate}
@@
 $\sigma_s$ & kpc & Plane width\\
-$\lambda_1>\lambda_2>\lambda_3$ &  & Tidal tensor
-eigenvalues\\
-$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ &  & Tidal tensor
-eigenvectors\\ 
 $\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
@@
 
-\subsection{Cosmic Web Alignment}
-\label{sub:webalignment}
+\section{Results}
+\label{sec:results}
 
-\cite{2015ApJ...799...45F} showed tha LGA pairs present alignments
-with the cosmic web.
-The strongest alignment is between the eigenvector associated  with the smallest
-eigenvalue, $\hat{e}_3$, and the vector $\hat{r}_{AB} $connecting the two halos in
-the pair. 
-The eigenvector $\hat{e}_3$ indicates the direction along
-which the cosmic web filament lies and in the case of being on a local
-sheet it is a vector lying on the pancakes' plane.
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth]{planes.pdf}
+\caption{
+Plane width as a function of the number of bright satellites.
+Wider planes are expected as the satellite number increases.
+\label{fig:planes}}
+\end{figure}
 
-Following \cite{2014MNRAS.443.1090F} we compute the closest cosmic web
-eigenvalue  towards which the vectors $\hat{r}_{AB}$, $\hat{p}$ and
-$\hat{I}_a$ are aligned.
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth]{beta.pdf}
+\caption{
+Cumulative distribution for the gelocity anisotropy $\beta$.
+\label{fig:beta}}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.48\textwidth]{mu_ri_cum.pdf}
+\includegraphics[width=0.48\textwidth]{mu_ri_scatter.pdf}
+\caption{
+Cumulative distribution for the gelocity anisotropy $\beta$.
+\label{fig:mu_ri}}
+\end{figure*}
 

### 2017-08-09 paper/paper.tex
alignment bootstrap + normalized planes
updated plots in paper
plane fitting

@@
 \centering
-\includegraphics[width=0.31\textwidth]{mstar.pdf}
-\includegraphics[width=0.31\textwidth]{vmax.pdf}
-\includegraphics[width=0.31\textwidth]{nsat.pdf}
+\includegraphics[width=0.30\textwidth]{mstar.pdf}
+\includegraphics[width=0.30\textwidth]{vmax.pdf}
+\includegraphics[width=0.30\textwidth]{nsat.pdf}
 \caption{Basic characteristics for the 11 pairs selected to be Local
@@
 We fit satellite planes around each galaxy in the pair by randomly
-generating 10000 unit vectors over the  sphere, each vector
-representing the direction perpendicular to a plane passing through
+generating 10000 unit vectors homogeneously distributed over the
+sphere.
+Each vector represents the direction perpendicular to a plane passing through
 the main galaxy's center of mass. 
-We compute the dot product of the unit vector with the position vector
-for each satellite, this scalar gives us the satellite distance to the
+We compute the dot product of this unit vector with the position vector
+for each satellite, this gives us the satellite distances to the
 plane. 
 The best plane is determined by the vector that gives the lowest
-position satellite distance dispersion. 
-We take the dispersion value as a measure of the plane's width.
-For comparison we store the value and direction giving the
-highest distance dispersion.
-We denote by $\hat{p}$ the unit vector defining the direction
+sample standard deviation in the satellite distances to the plane.
+In the set of unit vectors to be considered we also include the vector
+$\hat{I}_a$, which provides the exact solution in the case of $3$
+satallites. 
+We take the sample standard deviation as a measure of the plane's width
+and denote by $\hat{p}$ the unit vector defining the direction
 perpendicular to the best plane.
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=0.48\textwidth]{planes.pdf}
+\includegraphics[width=0.48\textwidth]{planes_normalized.pdf}
 \caption{
@@
 \label{fig:planes}}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.48\textwidth]{beta.pdf}
+\includegraphics[width=0.45\textwidth]{beta.pdf}
+\includegraphics[width=0.45\textwidth]{beta_scatter.pdf}
 \caption{
@@
 \label{fig:beta}}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{mu_ip_scatter.pdf}
+\includegraphics[width=0.45\textwidth]{mu_ri_scatter.pdf}
+\includegraphics[width=0.45\textwidth]{mu_rp_scatter.pdf}
+\centering
+\caption{A}
 \end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.48\textwidth]{mu_ri_cum.pdf}
-\includegraphics[width=0.48\textwidth]{mu_ri_scatter.pdf}
-\caption{
-Cumulative distribution for the gelocity anisotropy $\beta$.
-\label{fig:mu_ri}}
-\end{figure*}
 
@@
 %% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P
+
+%M31 mass
+%% https://arxiv.org/abs/1410.0017
+
+%MW mass
+%https://arxiv.org/abs/1407.1078
+
 \end{document}

### 2017-09-22 paper/paper.tex
plane center
new plot in paper
updated paper plots

@@
 %=========================================================================
-\title[LG satellite alignments]{Local Group Satellite Alignments}
+\title[Satellites in the MW and M31]{Joint Satellite Distributions in the Milky Way and Andromeda}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 \centering
-\includegraphics[width=0.30\textwidth]{mstar.pdf}
-\includegraphics[width=0.30\textwidth]{vmax.pdf}
-\includegraphics[width=0.30\textwidth]{nsat.pdf}
-\caption{Basic characteristics for the 11 pairs selected to be Local
-  Group Analogues (circles). From left to right: stellar mass, maximum circular
-  velocity and number of bright ($M_V<-9$) satellites.
-  Galaxy A is the galaxy with the higher stellar mass.
-  The squares represent the same characteristics for the observed
-  Local Group. 
+\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
+\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
+\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
+\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
 \label{fig:general}}
@@
 perpendicular to the best plane.
+We also store the median of the satellite distances to the plane as a
+measure of the plane's location with respect to the central galaxy.
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.48\textwidth]{planes.pdf}
-\includegraphics[width=0.48\textwidth]{planes_normalized.pdf}
-\caption{
-Plane width as a function of the number of bright satellites.
-Wider planes are expected as the satellite number increases.
-\label{fig:planes}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.45\textwidth]{beta.pdf}
-\includegraphics[width=0.45\textwidth]{beta_scatter.pdf}
-\caption{
-Cumulative distribution for the gelocity anisotropy $\beta$.
-\label{fig:beta}}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[width=0.45\textwidth]{mu_ip_scatter.pdf}
-\includegraphics[width=0.45\textwidth]{mu_ri_scatter.pdf}
-\includegraphics[width=0.45\textwidth]{mu_rp_scatter.pdf}
-\centering
-\caption{A}
-\end{figure}
-
 \bibliographystyle{mnras}

### 2017-09-24 paper/paper.tex
updated randomized points presentation
paper text

@@
 
-\section{Observational Characterists of Andromeda and the Milky Way}
+\section{Observational Data}
 \label{sec:obs}
@@
 \centering
+\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
 \includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
+\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
 \includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
-\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
-\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
@@
 
-We characterize the bright ($M_V<-9$) satellite spatial distribution
-with four different metrics.
-
-\begin{enumerate}
-\item{The inertia tensor}.
-\item{Fitting planes}.
-\item{Velocity Anisotropy}.
-\end{enumerate}
-
-I what follows we describe the details of implementation of each
-metric.
-
-\subsection{Inertia Tensor}
-\label{sub:inertia}
-First, by computing the inertia tensor defined as
+We use the inertia tensor to characterize the satellites.
+This tensor is defined as
 
@@
 largest eigenvalue. 
+We measure the width of the satellite distribution as the standard
+deviation of all satellite distances to the plane defined by the
+vector $\hat{I}_a$.
 
@@
 % http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P
-
-\subsection{Plane fitting}
-\label{sub:planes}
-
-We fit satellite planes around each galaxy in the pair by randomly
-generating 10000 unit vectors homogeneously distributed over the
-sphere.
-Each vector represents the direction perpendicular to a plane passing through
-the main galaxy's center of mass. 
-We compute the dot product of this unit vector with the position vector
-for each satellite, this gives us the satellite distances to the
-plane. 
-The best plane is determined by the vector that gives the lowest
-sample standard deviation in the satellite distances to the plane.
-In the set of unit vectors to be considered we also include the vector
-$\hat{I}_a$, which provides the exact solution in the case of $3$
-satallites. 
-We take the sample standard deviation as a measure of the plane's width
-and denote by $\hat{p}$ the unit vector defining the direction
-perpendicular to the best plane.
-We also store the median of the satellite distances to the plane as a
-measure of the plane's location with respect to the central galaxy.
-
-\subsection{Velocity Anisotropy}
-\label{sub:beta}
-
-The velocity anisotropy paramenter, $\beta$ is defined as
-
-\begin{equation}
-  \beta = 1 - \frac{\sum_i v^2_{\rm{tan}; i}}{2\sum_i v^{2}_{\rm{rad};i}},
-\label{eq:beta}
-\end{equation}
-% 
-where $v_{\rm{tan/rad};i}$ correspond to the tangential/radial
-velocity of the $i$-th satellite with respect to the central galaxy.
 
@@
 Symbol & Units & Description\\\hline
-$M_{\star}$ & $10^{10}$\Msun & Stellar mass of the central galaxy\\
-$N_s$ & & Number of satellites with $M_V<-9$\\
+$\hat{r}_{AB}$& & Unit vector along the direction connecting two
+dominant galaxies\\
+$N_s$ & & Number of satellites\\
 $a > b> c$ & & Inertia tensor eigenvalues. \\
 $\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
-$\beta$  &  & Satellite Velocity Anisotropy\\
-$\sigma_s$ & kpc & Plane width\\
-$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
+$\sigma_s$ & kpc & Ellipsoid width\\
+
 \hline\hline

### 2017-09-25 paper/paper.tex
+1 paragraph in the paper

@@
 \begin{abstract}
-We focus on the spatial distribution of bright ($M_V<-8$) satellites and
-pairs of galaxies with similar masses, isolation and kinematic
-configurations as the Local Group. 
+We quantify the joint spatial distribution of satellites around the Milky way and Andromeda.
 \end{abstract}
@@
 
-\section{Local Group Analogues in the Illustris Simulation}
+\section{Local Group Satellites in the Illustris Simulation}
 \label{sec:NumericalSetup}
@@
 This suite of cosmological simulations, performed using the quasi-Lagrangian
-code AREPO \citep{2010MNRAS.401..791S}, follow the coupled evolution of dark 
+code AREPO \citep{2010MNRAS.401..791S}, followed the coupled evolution of dark 
 matter and gas and includes parametrizations to account for the effects of
@@
 hole and super massive black hole feedback. 
-
 The simulation volume is a cubic box of $75$ \Mpch\ on a side.
@@
 
-\subsection{Sample Selection: Local Group Analogues}
+The smallest satellites are barely resolved in stellar mass at magnitudes of
+$M_V=9$, however its dark matter structure is sampled with at least
+$100$ particles. 
+We find that all considered halos have at least $XX$ subhalos above
+a maximum circular velocity of $15$\kms.
+For this reason we select the satellite galaxy samples from the
+DM subhalo population and not from the galaxies with photometry.
+We chose in two different ways the sub-halo samples. 
+First, we rank the halos by decreasing order of its maximum circular
+velocity and select the first $N_p$ halos in the list.
+Second, we select all satellites above maximum circular velocity of
+$20$\kms to randmbly subsample $N_p$ subhalos.
 
@@
   Mpc. 
-\item Each galaxy in the pair must have at least $5$ satellites
-  brighter than  $M_V<-9$.
 \end{itemize}

### 2017-09-25 paper/paper.tex
+1 paragraph

@@
 
-We build a sample of Local Group Analgues (LGA) by performing a selection on
-the stellar mass and isolation properties of the galaxies in the
-simulation. The conditions to select LGA galaxies are the following.
+We build a sample of Local Group Analgues (LGA) by selecting first all
+galaxies with  an stellar mass in the range $1\times10^{10}\Msun
+<M_{\star}<1.5 \times 10^{11} \Msun$.
+Then we consider the following criteria for all galaxies in that
+sample.
 
 \begin{itemize}
-\item LGA galaxy pairs are composed by galaxies with stellar mass in the
-range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
 \item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
-the closest to halo $B$, the two halos are considered as a pair. 
-Another way to phrase this selection is that pairs do not have
-neighbors closer than the pair's separation.
-\item The distance between the galaxies' center of
-  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
-\item For each galaxy in the pair there cannot be a galaxy more
-  massive than the lightest galaxy in the pair within a radius of $2$
-  Mpc. 
+the closest to halo $B$, the two are considered as a pair. 
+\item With $d_{AB}$ the distance between the two galaxies and
+  $M_{\star,min}$ the lowest stellar mass in the two galaxies, we
+  discard pairs that have any other galaxy $C$ with stellar mas
+  $M_{\star}>M_{\star, min}$ closer than $3\times d_{AB}$ from any of
+  the pair's members.
+\item The distance $d_{AB}>700$ kpc. 
+\item The radial velocity between the two galaxies is $120\kms <V_{AB, radial}<0\kms$
 \end{itemize}
 
-We find $11$ pairs with these conditions.
-Figure \ref{fig:general} shows the stellar masses, maximum circular
-velocities and the number of bright satellites for all the pairs in
-the sample.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
-\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
-\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
-\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:general}}
-\end{figure*}
+We find $XX$ pairs with these conditions.
 
@@
 $\sigma_s$ & kpc & Ellipsoid width\\
-
 \hline\hline
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
+\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
+\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
+\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:general}}
+\end{figure*}
+
 \bibliographystyle{mnras}
@@
 %% https://arxiv.org/pdf/1605.01728.pdf
-
-%% The tangential velocity excess of the Milky Way satellites
-%% https://arxiv.org/pdf/1612.01529.pdf
-
-%% Tambien deberiamos sacar las alineaciones con el momentum angular
-%% de las estrellas de las galaxias principales.
-
-%% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P
 

### 2017-09-26 paper/paper.tex
edit paragraph

@@
   the pair's members. 
-\item The distance $d_{AB}>700$ kpc. 
-\item The radial velocity between the two galaxies is $120\kms <V_{AB, radial}<0\kms$
+\item The distance $d_{AB}$ greater than $700$ kpc.
+\item The radial velocity between the two galaxies is $-120\ \kms <v_{AB,r}<0\ \kms$. 
 \end{itemize}
@@
 
-\section{Satellite Spatial Distribution and Alignment}
+\section{Satellite Spatial Distribution}
 \label{sec:SpatialMeasurements}
 
-We use the inertia tensor to characterize the satellites.
-This tensor is defined as
+We base all our results on the description provide by the inertia
+tensor defined by the satellites's positions.
 
@@
 where $k$ indexes the set of satellites of interest
-$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the
-positions pof the host DM halo, $\bf{1}$ is the unit matrix,  and
+$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
+of the satelites's geometric center $\bf{r}_{0}\equiv 1/N_s\sum_{k\in
+  V} \bf{r}_i$, $\bf{1}$ is the unit matrix,  and  
 ${\bf r}^T$ is the transposed vector $\bf{r}$.
-We finally compute the eigenvalues, $a>b>c$, and corresponding
-eigenvectors, $\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$, of this tensor.
-In the case of a sheet-like configuration the vector perpendicular to
-the sheet would be signaled by, $\hat{I}_a$, the eigenvector of the
-largest eigenvalue. 
-We measure the width of the satellite distribution as the standard
-deviation of all satellite distances to the plane defined by the
-vector $\hat{I}_a$.
+
+From this tensor we compute its eigenvalues,
+$\lambda_1>\lambda_2>\lambda_3$, and corresponding eigenvectors,
+$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$.
+We define the size of its three ellipsoidal axis as
+$a=\sqrt{\lambda_1}$, $b=\sqrt{\lambda_2}$ and $c=\sqrt{\lambda_3}$.
+
+We define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
+planar satellite distribution. 
+We also define the width of the planar satellite distribution,
+$\sigma_p$ as the standard deviation of all satellite distances to the
+plane defined by the $\hat{n}$.
 
@@
 % http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P
-
-\begin{table*}
-  \centering
-\begin{tabular}{lll}
-\hline\hline
-Symbol & Units & Description\\\hline
-$\hat{r}_{AB}$& & Unit vector along the direction connecting two
-dominant galaxies\\
-$N_s$ & & Number of satellites\\
-$a > b> c$ & & Inertia tensor eigenvalues. \\
-$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
-$\sigma_s$ & kpc & Ellipsoid width\\
-\hline\hline
-\end{tabular}
-  \caption{Overview of the parameters computed for each central galaxy
-    and its satellite system.
-  \label{tab:models}}
-\end{table*}
-
-\section{Results}
-\label{sec:results}
 
@@
 \end{figure*}
+
+\section{Results}
+\label{sec:results}
+
+\begin{table*}
+  \centering
+\begin{tabular}{lll}
+\hline\hline
+Symbol & Units & Description\\\hline
+$\hat{r}_{AB}$& & Unit vector along the direction connecting two
+dominant galaxies\\
+$N_s$ & & Number of satellites\\
+$a > b> c$ & kpc & Inertia tensor eigenvalues. \\
+$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
+$\sigma_s$ & kpc & Ellipsoid width\\
+\hline\hline
+\end{tabular}
+  \caption{Overview of the parameters computed for each central galaxy
+    and its satellite system.
+  \label{tab:models}}
+\end{table*}
 

### 2017-09-26 paper/paper.tex
typos

@@
 %=========================================================================
-\title[Satellites in the MW and M31]{Joint Satellite Distributions in the Milky Way and Andromeda}
+\title[Satellites in the MW and M31]{Joint Satellite Distributions in
+  the Local Group}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 \item The distance $d_{AB}$ greater than $700$ kpc.
-\item The radial velocity between the two galaxies is $-120\ \kms <v_{AB,r}<0\ \kms$. 
+\item The relative radial velocity between the two galaxies, including
+  the Hubble flow, is $-120\ \kms <v_{AB,r}<0\ \kms$. 
 \end{itemize}
 
-We find $XX$ pairs with these conditions.
+We find 32 pairs with these conditions. Figure shows the physical 
+properties (stellar masses, maximum circular velocities, radial
+velocities and separation) in those pairs.
 
@@
 $\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
-of the satelites's geometric center $\bf{r}_{0}\equiv 1/N_s\sum_{k\in
+of the satelites's geometric center ${\bf r}_{0}\equiv \frac{1}{N_s}\sum_{k\in
   V} \bf{r}_i$, $\bf{1}$ is the unit matrix,  and  
@@
 
+\subsection{Satellites in the Local Group}
+
+\subsection{Satellites in the Illustris Simulation}
+
 \begin{table*}
@@
 $a > b> c$ & kpc & Inertia tensor eigenvalues. \\
-$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
+$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$ & & Inertia tensor eigenvectors. \\
 $\sigma_s$ & kpc & Ellipsoid width\\

### 2017-09-27 paper/paper.tex
+1 paragraph on results

@@
 
+We compare the two satellite distributions by always keeping the same
+number of satellites around each galaxy.
+This means that the magnitude cut corresponding to the faintest
+satellite included in the sample is different in each case.
+We make this choice for two reasons. 
+First to always be sure that there is a non-zero number of satellites to make the computations. 
+Second, to be able to compare the two halos at a fixed number of
+satellites.
+
+We test the shape and alignment statistics for 11 up 25 satellites.
+The lowest number corresponds to the number of classical Milky Way
+satellites.
+We compare the resuls of the satellite distributions with the average
+of from 10000 randomized version of the same satellites.
+The spherical randomization is done as described in Section X.
+
+Figure \ref{fig:general} summarized the results. 
+The left column shows
+
 \subsection{Satellites in the Illustris Simulation}

### 2017-10-02 paper/paper.tex
one more plot
+1 paragraph alignments + cosmic web

@@
 
+We characterize the alignment between the satellite plane and the
+vector connecting the two dominant galaxies as $\mu=|\hat{r}_{AB}\cdot
+\hat{n}|$. 
+It has been shown that LG pair separation vector is aligned along the
+filaments in  which they are typically embeded
+\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
+matter arrangements are aligned with the plane itself. 
+Characterizing the satellite alignments with $\mu$ thus provide
+information about how satellites are distributed with respect to the
+cosmic web.
+
 % referencia posiciones satellites
@@
 \centering
-\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
-\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
-\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
-\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
+\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
+\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
+\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
+\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:general}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
+\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
+\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
+\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems

### 2017-10-02 paper/paper.tex
+1 paragraph distributions

@@
 
+\subsection{Parameter Distributions}
+
+We charaterize the $\mu$ distribution by a power law probability
+density distribution
+\begin{equation}
+P(\mu) = \frac{1}{\alpha}\mu^{\alpha-1}.
+\end{equation}
+We estimate the $\alpha$ using a bayesian approach, such as that
+the likelihood of being $\alpha$ the power value given the observed values of $\{\mu_i\}$
+  can be written as:
+
+\begin{equation}
+\mathcal{L}(\alpha|\{\mu_i\})=\frac{1}{Z_\alpha}\prod_{i=1}^{N_s}
+\frac{1}{\alpha}\mu_i^{\alpha-1}, 
+\end{equation}
+%
+where $Z_{\alpha}$ is a constant such as $\int_{0}^{\infty}
+{\mathcal L}(\alpha|\{\mu_i\}) {\rm d}\alpha=1$. 
+We report as $\hat{\alpha}$ the value of $\alpha$ 
+maximizing the likelihood,
+
+We characterize the distributions for the plane width and axis ratio
+$b/a$, $b/c$ through a gaussian
+\begin{equation}
+P(x)  = \frac{1}{\sqrt{2\pi \sigma^2}} \exp{\left[-\frac{1}{2}\left(\frac{x-x_m}{\sigma}\right)^2\right]}
+\end{equation}
+In this case the maximum likelihood values for the parameter estimates
+$\hat{x_m}$ and $\hat{\sigma}$ correspond to the mean and standard
+deviation, respectively.
+
+We summarize the results from the Illustris simulation by reporting
+the maximum likelihood parameter estimates. 
+In turn we use this us to estimate the probability of finding the
+observed values in the Local Group and compare it against the highest
+probabilty values.
+
 % referencia posiciones satellites
@@
 
-We compare the two satellite distributions by always keeping the same
-number of satellites around each galaxy.
+We compare the satellite distributions in the MW and M31 at fixed
+satellite number.
 This means that the magnitude cut corresponding to the faintest

### 2017-10-03 paper/paper.tex
new plots
+1 paragraph

@@
 \centering
+\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
+\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
+\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
+\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:sampling}}
+\end{figure*}
+
+\begin{figure*}
+\centering
 \includegraphics[width=0.7\textwidth]{scatter_width.pdf}
@@
 
-We test the shape and alignment statistics for 11 up 25 satellites.
+We test the shape and alignment statistics for 11 up 15 satellites.
 The lowest number corresponds to the number of classical Milky Way
 satellites.
-We compare the resuls of the satellite distributions with the average
-of from 10000 randomized version of the same satellites.
-The spherical randomization is done as described in Section X.
+The upper limit corresponds to the minimum number of satellites that
+can be resolved in the simulations for both halos in each pair. 
+In the case of simulations we rank the subhalos by their maximum
+circular velocity. 
+We do not use their stellar properties because this represents the
+lower resolution limit for the hydrodynamics; most of these subhalos
+only have one stellar particle belonging to them. 
+In contrast, the detected sub-halos have at least 35 dark matter
+particles to determine their properties.
 
-Figure \ref{fig:general} summarized the results. 
-The left column shows
+We build two different kinds of statistics from these satellites
+First, we compute the shape and alignments for a varying number of
+satellites $11\leq N_{s}\leq 15$ keeping their ranking in
+$V_{mag}$/$V_{max}$. 
+This allows us to estimate the variation expected by changing the
+satellite number. 
+The second kind of statistics are computed for a fixed number of
+satellites $N_{s}=11$ randomly selected from the top $15$ ranked
+satellites. 
+We perform this bootstrapping $10$ times for each pair. 
+This allows us to estimate the variation expected by randomly sampling
+the satellites from a parent distribution.
+
+Figure \ref{fig:sampling} summarized the results.
 

### 2017-10-04 paper/paper.tex
nuevo orden
updated plot order
+1 paragraph

@@
 
-We find 32 pairs with these conditions. Figure shows the physical 
+We find 27 pairs with these conditions. Figure shows the physical 
 properties (stellar masses, maximum circular velocities, radial
@@
 
-% referencia posiciones satellites
-% http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
-\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
-\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
-\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:sampling}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:general}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:general}}
-\end{figure*}
-
-\section{Results}
-\label{sec:results}
-
-\subsection{Satellites in the Local Group}
+\subsection{Satellite samples}
 
@@
 satellites $11\leq N_{s}\leq 15$ keeping their ranking in
-$V_{mag}$/$V_{max}$. 
+$M_V$ or $V_{max}$. 
 This allows us to estimate the variation expected by changing the
@@
 
-Figure \ref{fig:sampling} summarized the results.
+% referencia posiciones satellites
+% http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P
 
-\subsection{Satellites in the Illustris Simulation}
+\begin{figure*}
+\centering
+\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
+\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
+\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
+\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:lg_scatter}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
+\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
+\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
+\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:general}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
+\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
+\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
+\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:general}}
+\end{figure*}
+
+\section{Results}
+\label{sec:results}
+
+\subsection{Distributions in the Local Group}
+
+Figure \ref{fig:lg_scatter} summarizes our main results for the
+observed LG satellite distributions.
+In all panels the diagonal line corresponds to the 1:1 ratio.
+
+Here we can see that the mean values of the \texttt{Ranked} and
+\texttt{Bootstrapped} samples are similar within the scatter in each
+sample. 
+The scatter is itself tends to be larger in the \texttt{Bootstrapped}
+sample. 
+This allows to stablish the LG uncertainties to be used in the next
+sections to compare it against the distributions derived from the
+Illustris simulation.
+
+There is a third sample in Figure \ref{fig:lg_scatter}. 
+It corresponds to the set of \texttt{Random} points that were generated
+by randomizing the angular positions of the satellites in the
+\texttt{Bootstrapped} samples. 
+This allows us to understand the importance of intrinsic satellite's
+radial profile distribution in driving the results.
 

### 2017-10-06 paper/paper.tex
titulo
+1 paragrap mu

@@
 \newcommand{\tol}{Tololo 1214-277}
+\newcommand{\rank}{\texttt{Ranked}}
+\newcommand{\boot}{\texttt{Bootstrapped}}
+\newcommand{\rand}{\texttt{Random}}
 \newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
@@
 %=========================================================================
-\title[Satellites in the MW and M31]{Joint Satellite Distributions in
-  the Local Group}
+\title[Satellites in the MW and M31]{Local Group Satellite Distributions in
+ the Illustris Simulation}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 observed LG satellite distributions.
-In all panels the diagonal line corresponds to the 1:1 ratio.
-
-Here we can see that the mean values of the \texttt{Ranked} and
-\texttt{Bootstrapped} samples are similar within the scatter in each
-sample. 
-The scatter is itself tends to be larger in the \texttt{Bootstrapped}
-sample. 
-This allows to stablish the LG uncertainties to be used in the next
-sections to compare it against the distributions derived from the
-Illustris simulation.
+We see that the \rank\ and \boot\ samples are consistent 
+withing the scatter provided by each sample.
+We use the median and standard deviation in each sample to define the
+most probable value and its associated uncertaintiy.
+This allows us to compare the observational values gainst the
+distributions derived from the Illustris simulation.
 
 There is a third sample in Figure \ref{fig:lg_scatter}. 
-It corresponds to the set of \texttt{Random} points that were generated
-by randomizing the angular positions of the satellites in the
-\texttt{Bootstrapped} samples. 
-This allows us to understand the importance of intrinsic satellite's
-radial profile distribution in driving the results.
+It corresponds to the set of \rand\ points generated
+by randomizing the angular positions of the satellites in each pair in
+the \boot\ sample. 
+This provides a baseline to understand the importance 
+of intrinsic satellite's radial profile distribution in driving the
+results.
+
+The upper left panel in Figure \ref{fig:lg_scatter} shows that the
+planar satellite distributions are located perpendicular to the line
+connecting the two galaxies. 
+It is remarkable that this alignment is almost perfect for both
+satellite distributions. 
+The points in the \rand\ simply highlights the expected result for a
+random angular distribution is a flat distribution in the range
+$0\leq\mu\leq 1$.
 

### 2017-10-06 paper/paper.tex
+1 paragraph on LG width

@@
 
+The upper right panel shows two interesting things. 
+First, the MW satellite plane is thiner than its M31
+counterpart. 
+This is in principle unexepected since M31 is more
+massive than the MW and it should have a broader satellite
+distribution. 
+The second interesting point is that the MW satellite plane is also
+thiner than the spherical randomized expectation, while the M31 plane
+is right within the expectation of the randomized satellites. 
+This is a another piece of evidence showing the highly structured
+satellite distribution in the MW in comparison to M31. 
+The fact that the \rand\ samples also show a trend towards thinner MW
+planes means that the radial satellite distribution in concentrated in
+the MW than it is in M31.
+
+The lower two panels re-inforce the picture of a highly structured.
+
 \begin{table*}

### 2017-10-06 paper/paper.tex
+1 paragraph LG distributions

@@
 
-\subsection{Distributions in the Local Group}
+\subsection{Satellite distributions in the Local Group}
 
@@
 
-The lower two panels re-inforce the picture of a highly structured.
+The lower left panel re-inforce the picture of a highly structured
+MW. 
+It corresponds to the $c/a$ ratio and shows the same trends observed
+in for the plane width. 
+First, the ratio is lower for the MW than it is for M31; second, the
+ratio for the MW is also lower than the expectation for the randomized
+sample while the results for M31 is within the expectations from \rand.  
+In this case the median value of the \rand\ distributions follow the
+$1:1$ line as expected.
+The lower right panel does not show any surprises. 
+All the distributions from \rank, \boot\ and \rand\ are consistent
+both for the MW and M31.
 

### 2017-10-06 paper/paper.tex
updated plots in paper

@@
 \centering
-\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
-\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
-\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
-\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{LG_scatter_mu.pdf}
+\includegraphics[width=0.35\textwidth]{LG_scatter_width.pdf}
+\includegraphics[width=0.35\textwidth]{LG_scatter_ca_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{LG_scatter_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
@@
 \centering
+\includegraphics[width=0.35\textwidth]{distribution_random_mu.pdf}
+\includegraphics[width=0.35\textwidth]{distribution_random_width.pdf}
+\includegraphics[width=0.35\textwidth]{distribution_random_ca_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{distribution_random_ba_ratio.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:lg_distribution}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
 \includegraphics[width=0.7\textwidth]{scatter_width.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
 \includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
@@
 \centering
+\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
 \includegraphics[width=0.7\textwidth]{distribution_width.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
 \includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}

### 2017-10-07 paper/paper.tex
+1 paragraph

@@
 satellites. 
-We perform this bootstrapping $10$ times for each pair. 
+We perform this bootstrapping $5$ times for each pair. 
 This allows us to estimate the variation expected by randomly sampling
@@
 
-The lower left panel re-inforce the picture of a highly structured
+The lower left panel re-inforces the picture of a highly structured
 MW. 
@@
 both for the MW and M31.
+
+We can quantify the degree at which the observed satellite distributions are 
+different from their spherically randomized counterparts.
+Figure \ref{fig:lg_distributions} shows the probability distributions
+from the \rand\ pairs with an overplot of the LG values.
+The upper left panel shows the power law distribution for $\mu$. The
+results are not perfectly horizontal because the optimal power value
+$\hat{alpha}$ is slightly different from $1$, the uncertainties in
+this value are naturally consistent with the unit value expected for
+an homogeneous distribution. 
+In this case all values are equiprobable.
+In the case of the $b/a$ ratio (lower right panel) both the MW and M31
+are consistent with the \rand\ distribution.
+
+For all the other cases the Milky Way
 

### 2017-10-07 paper/paper.tex
+1 paragraphs

@@
 \section{Introduction}
+
+In Section we list the sources of the observatinal and
+simulated data to be used throughout the paper.
+Next, in Section we describe the methods we use to quantify and
+characterize the satellite distributions.
+In section we present our results. 
+First we describe the observed satellite distributions and compare
+them against the expectation of an spherical randomization of its
+satellites. We then compute the expectation from the Illustris Simulation. 
+In Section we discuss the implication of our results to finally
+summarize in Section.
 
@@
 different from their spherically randomized counterparts.
-Figure \ref{fig:lg_distributions} shows the probability distributions
+Figure \ref{fig:lg_distribution} shows the probability distributions
 from the \rand\ pairs with an overplot of the LG values.
@@
 In the case of the $b/a$ ratio (lower right panel) both the MW and M31
-are consistent with the \rand\ distribution.
+are consistent with the average values expected from \rand\ distribution.
+Remarkably, the plane width and $c/a$ ratio for the MW are significantly 
+different from the \rand\ expected values, while the M31 values are
+sistematically within the expectations.
 
-For all the other cases the Milky Way
+The comparison of the observed satellite distribution against its onw
+version, but spherically randomized, tells us that the MW satellite
+planar structure is remarkably different from a random distribution,
+while for the M31 distribution there isn't a significant difference
+from the random expectation.
+
+\subsection{Satellite distributions in the Illustris Simulation}
+
+In the previous section we saw how the MW cannot be concealed with its
+randomized satellite distribution, while M31 is fully consistent with
+it. 
+We now quantify whether the MW and M31 are consistent with the
+expectations from the Illustris Simulation.
+We show here the results from the \rank\ sample. 
+The results from the \boot\ sample ara avaialble in the appendix.
 

### 2017-10-07 paper/paper.tex
all main plots

@@
 \centering
-\includegraphics[width=0.35\textwidth]{LG_scatter_mu.pdf}
-\includegraphics[width=0.35\textwidth]{LG_scatter_width.pdf}
-\includegraphics[width=0.35\textwidth]{LG_scatter_ca_ratio.pdf}
-\includegraphics[width=0.35\textwidth]{LG_scatter_ba_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_random_ranked_mu.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_random_ranked_width.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_random_ranked_ca_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_random_ranked_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
@@
 \centering
-\includegraphics[width=0.35\textwidth]{distribution_random_mu.pdf}
-\includegraphics[width=0.35\textwidth]{distribution_random_width.pdf}
-\includegraphics[width=0.35\textwidth]{distribution_random_ca_ratio.pdf}
-\includegraphics[width=0.35\textwidth]{distribution_random_ba_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{distro_random_ranked_mu.pdf}
+\includegraphics[width=0.35\textwidth]{distro_random_ranked_width.pdf}
+\includegraphics[width=0.35\textwidth]{distro_random_ranked_ca_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{distro_random_ranked_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:lg_distribution}}
+\label{fig:lg_scatter}}
 \end{figure*}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_ranked_mu.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_ranked_width.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_ranked_ca_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{scatter_ranked_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:general}}
+\label{fig:lg_scatter}}
 \end{figure*}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{distro_ranked_mu.pdf}
+\includegraphics[width=0.35\textwidth]{distro_ranked_width.pdf}
+\includegraphics[width=0.35\textwidth]{distro_ranked_ca_ratio.pdf}
+\includegraphics[width=0.35\textwidth]{distro_ranked_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:general}}
+\label{fig:lg_scatter}}
 \end{figure*}

### 2017-10-20 paper/paper.tex
new plots

--- 2017-10-07 paper/paper.tex
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=0.35\textwidth]{LG_scatter_mu.pdf}
-\includegraphics[width=0.35\textwidth]{LG_scatter_width.pdf}
-\includegraphics[width=0.35\textwidth]{LG_scatter_ca_ratio.pdf}
-\includegraphics[width=0.35\textwidth]{LG_scatter_ba_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_random_ranked_width.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_ranked_width.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_norm_width.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
 \label{fig:lg_scatter}}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=0.35\textwidth]{distribution_random_mu.pdf}
-\includegraphics[width=0.35\textwidth]{distribution_random_width.pdf}
-\includegraphics[width=0.35\textwidth]{distribution_random_ca_ratio.pdf}
-\includegraphics[width=0.35\textwidth]{distribution_random_ba_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_random_ranked_ca_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_ranked_ca_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_norm_ca_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:lg_distribution}}
-\end{figure*}
+\label{fig:lg_scatter}}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
-\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_random_ranked_ba_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_ranked_ba_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_norm_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:general}}
-\end{figure*}
+\label{fig:lg_scatter}}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
-\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_random_ranked_mu.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_ranked_mu.pdf}
+\includegraphics[width=0.45\textwidth]{scatter_norm_mu.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:general}}
-\end{figure*}
+\label{fig:lg_scatter}}
+\end{figure}
 

### 2017-10-24 paper/paper.tex
updated fig size

@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.45\textwidth]{scatter_random_ranked_width.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_ranked_width.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_norm_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_random_ranked_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_width.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
 \label{fig:lg_scatter}}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.45\textwidth]{scatter_random_ranked_ca_ratio.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_ranked_ca_ratio.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_norm_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ca_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
 \label{fig:lg_scatter}}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.45\textwidth]{scatter_random_ranked_ba_ratio.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_ranked_ba_ratio.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_norm_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
 \label{fig:lg_scatter}}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.45\textwidth]{scatter_random_ranked_mu.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_ranked_mu.pdf}
-\includegraphics[width=0.45\textwidth]{scatter_norm_mu.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
 \caption{Basic characteristics for the MW and M31 satellite systems
 \label{fig:lg_scatter}}
-\end{figure}
+\end{figure*}
 

### 2017-10-25 paper/paper.tex
new plots
new plot, expected number
caption

@@
 %=========================================================================
-\title[Satellites in the MW and M31]{Local Group Satellite Distributions in
- the Illustris Simulation}
+\title[Satellites in the MW and M31]{Joint 
+  satellite distribution of isolated galaxy pairs}  
 \author[J.E. Forero-Romero \& V. Arias]
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
+\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
+\caption{Basic characteristics for the MW and M31 satellite systems
+\label{fig:lg_scatter}}
+\end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.47\textwidth]{expected_numbers.pdf}
+\caption{Probability distribution for the expected number of pairs
+  showing the same degree of atipicality as the Local Group. The two
+  distributions correspond to different numbers of initial isolated
+  pairs. On average $1\%$ of the isolated pairs should present
+  satellite distributions as atypical as the Local Group.
+\label{fig:expected_number}}
+\end{figure}
+
 \section{Results}

### 2017-10-26 paper/paper.tex
caption

@@
 \includegraphics[width=0.32\textwidth]{scatter_norm_width.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
+\caption{Plane width characterization in the Local Group and the
+  Isolated Pairs. In all panels the horizontal axis corresponds to the
+  M31 or the most massive halo in the pair and the vertical axis to
+  the MW or the least massive halo in the pair.
+The panel on the left shows the plane width in physical units
+comparing the results of five measurements from the observations
+(stars) and the result of spherically randomizing the satellite
+positions (circles). 
+The panel in the middle compares the average from the observations
+(star) and the average from each one of the Isolated Pairs (circles
+with error bars).
+The panel on the right has the same information as the middle panel,
+only that this time each point has been normalized (median substracted
+and normalized by the standar deviation) to the results of its
+randomization. 
+The main message of this series of plots is that the MW has a
+significantly thiner plane both compared to the result of its own
+satellite spherical randomization (left panel) and the expectation from
+simulations (middle panel). 
+This low value is $2-\sigma$ away from what is expected in a spherical
+distribution. 
+In the M31 their satellites are in agreement with the expectations
+both from an spherical distribution and the results form the
+simulations. 
 \label{fig:lg_scatter}}

### 2017-10-26 paper/paper.tex
caption

@@
 simulations (middle panel). 
-This low value is $2-\sigma$ away from what is expected in a spherical
+This low value is $2\sigma$ away from what is expected in a spherical
 distribution. 
@@
 simulations. 
-\label{fig:lg_scatter}}
+A second conclusion is that the spherically averaged plane width
+MW (seen in the point cloud in the left panel) is smaller than the
+average expectation from simulations. 
+\label{fig:scatter_width}}
 \end{figure*}
@@
 \includegraphics[width=0.32\textwidth]{scatter_norm_ca_ratio.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:lg_scatter}}
+\caption{Same layout as in Figure \ref{fig:scatter_width}. 
+This time for the $c/a$ axis ratio. 
+The message holds in this case as for the plane width.
+The MW is has a significantly low $c/a$ value compared to the
+expectation from a spherical distribution and simulations. 
+This low value is also $2\sigma$ away from the expactations for an
+spherical distribution.
+M31 is consistent both with an spherical distribution and the results
+from simulations.
+However, in this case the axis ratio in the spherically averaged case
+is completeley consistent with the expectation from simulations.
+\label{fig:scatter_ca_ration}}
 \end{figure*}
@@
 \includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:lg_scatter}}
+\caption{Same layout as in Figure \ref{fig:scatter_width}. 
+Ths time for the $b/a$ axis ratio.
+\label{fig:scatter_ba_ration}}
 \end{figure*}

### 2017-10-26 paper/paper.tex
caption

@@
 %=========================================================================
-\title[Satellites in the MW and M31]{Joint 
-  satellite distribution of isolated galaxy pairs}  
+\title[No Title]{No Title}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 MW (seen in the point cloud in the left panel) is smaller than the
-average expectation from simulations. 
+average expectation from simulations, while for M31 the spherical
+average is consistent with simulations. 
 \label{fig:scatter_width}}

### 2017-10-26 paper/paper.tex
caption
+1 caption

@@
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
-Ths time for the $b/a$ axis ratio.
+This time for the $b/a$ axis ratio. In this case both the MW and M31
+are consistent with the results of a spherical distribution and the
+simulations. 
 \label{fig:scatter_ba_ration}}
@@
 \includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:lg_scatter}}
+\caption{Same layout as in Figure \ref{fig:scatter_width}. 
+This time for $\mu$ the absolute value of the dot product between the
+vector connecting the main galaxies and the vector perpendicular to
+the satellite plane.
+In this case both the MW and M31 show a strong alignment.
+Apparently this result is outside the expectations from the
+simulations and atypical compared to the spherical results. 
+However, this is not the case. The $\mu$ distributions in the
+randomization and the simulation are consistent with a uniform
+distribution.
+Under such circumstances the result of $\mu\approx 1$ is as likely as
+any other result.
+\label{fig:scatter_mu}}
 \end{figure*}

### 2017-10-26 paper/paper.tex
caption

@@
 distribution.
-Under such circumstances the result of $\mu\approx 1$ is as likely as
-any other result.
+Under such circumstances $\mu\approx 1$ is as likely as
+any other value.
 \label{fig:scatter_mu}}
@@
 \includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
-\caption{Basic characteristics for the MW and M31 satellite systems
-\label{fig:lg_scatter}}
+\caption{Correlations between the normalized values for the plane
+  width, $c/a$ ratio and $b/a$ ratio. 
+The star corresponds to the LG, black circles with errorbars are the
+results from simulations and the gray cloud is the resul from the
+multivariate gaussian model.
+Upper raw summarizes the results for M31 and the lower raw for the MW.
+This simplified description allows us to quantify how atypical is the
+LG compared to the simulation results. 
+\label{fig:correlations}}
 \end{figure*}

### 2017-10-26 paper/paper.tex
abstract

@@
 \begin{abstract}
-We quantify the joint spatial distribution of satellites around the Milky way and Andromeda.
+We quantify the joint spatial distribution of the brightest satellites
+around the Milky way and M31. 
+We find that the satellites in MW show a distribution significantly
+thinner and flattened compared to the expectaions of a random
+spherical distribution and simulations based on the Lambda Cold Dark
+Matter paradigm.
+In turn, M31 is completely consistent with the expectations from a
+spherical satellite distribution and LCDM simulations.
+The satellite planes in the MW and M31 are almost perpendicular to the line
+connecting the two galaxies. None of the pairs in the simulation show
+a similar degree of alignment. 
+However, the simulations are consistent with a random uniform
+distribution, making the result from the observations consistent with
+these theoretical expectations.
+This special satellite distribution in the Milky Way makes the Local
+Group an atypical pair in the expected cosmological context.
+We summarize these results in a simple multivariate Gaussian
+model to estimate that only $1\%$ of the pairs with isolation
+and dynamical characteristics similar to the LG are expected to have
+satellite distributions with the same degree of atipicality. 
 \end{abstract}
@@
 
-In Section we list the sources of the observatinal and
+In Section we list the sources of the observational and
 simulated data to be used throughout the paper.
@@
 In section we present our results. 
-First we describe the observed satellite distributions and compare
-them against the expectation of an spherical randomization of its
-satellites. We then compute the expectation from the Illustris Simulation. 
-In Section we discuss the implication of our results to finally
-summarize in Section.
+In the discussion section we quantify the correlations between the main
+plane properties as described by the simulations.
+We use this results to quantify the degree of atipicality of the LG
+and estimate the volume that has to probed in simulations in order to
+find a pair with a satellite distribution as atipical as the LG. 
+Finally, we summarize our conclusions in Section .
 
@@
 
-The smallest satellites are barely resolved in stellar mass at magnitudes of
-$M_V=9$, however its dark matter structure is sampled with at least
-$100$ particles. 
-We find that all considered halos have at least $XX$ subhalos above
-a maximum circular velocity of $15$\kms.
-For this reason we select the satellite galaxy samples from the
-DM subhalo population and not from the galaxies with photometry.
-We chose in two different ways the sub-halo samples. 
-First, we rank the halos by decreasing order of its maximum circular
-velocity and select the first $N_p$ halos in the list.
-Second, we select all satellites above maximum circular velocity of
-$20$\kms to randmbly subsample $N_p$ subhalos.
-
-We build a sample of Local Group Analgues (LGA) by selecting first all
-galaxies with  an stellar mass in the range $1\times10^{10}\Msun
+We buid a sample of Isolated Pairs that resemble the conditions
+in the LG.
+To construct this sample we select first all galaxies with  an stellar mass in the range $1\times10^{10}\Msun
 <M_{\star}<1.5 \times 10^{11} \Msun$.
-Then we consider the following criteria for all galaxies in that
-sample.
+Then we consider the following criteria for all galaxies in that set.
 
@@
   $M_{\star,min}$ the lowest stellar mass in the two galaxies, we
-  discard pairs that have any other galaxy $C$ with stellar mas
+  discard pairs that have any other galaxy $C$ with stellar mass
   $M_{\star}>M_{\star, min}$ closer than $3\times d_{AB}$ from any of
   the pair's members. 
-\item The distance $d_{AB}$ greater than $700$ kpc.
+\item The distance $d_{AB}$ is greater than $700$ kpc.
 \item The relative radial velocity between the two galaxies, including
@@
 
-We find 27 pairs with these conditions. Figure shows the physical 
-properties (stellar masses, maximum circular velocities, radial
-velocities and separation) in those pairs.
+We find 27 pairs with these conditions. We show in the Appendix A the
+physical  properties (stellar masses, maximum circular velocities,
+radial velocities and separation) in those pairs. 
+We then select the pairs where in both halos there are at least 15
+detected subhalos. 
+We end up with a total of 20 pairs that fulfill these criteria.
+
+Although Illustris-1 has stellar particles, we do not use their
+properties to select the satelite population because the smallest
+galaxies are barely resolved in stellar mass at magnitudes of
+$M_V=9$. We prefer using the dark matter information as the smallest
+sub-halos are sampled with $100$ particles. 
+For this reason we select the satellite galaxy samples from the
+
+We chose the satellite samples by ranking the subhalos in decreasing
+order of its maximum circular velocity and select the first $N_p$
+halos in the list. 
+The results in the main body of the paper correspond to $11\leq
+N_p\leq 15$.
 
@@
 multivariate gaussian model.
-Upper raw summarizes the results for M31 and the lower raw for the MW.
+Upper/lower row summarizes the results for M31/M31.
 This simplified description allows us to quantify how atypical is the
@@
 
+Prospects for observational measurement: DESI.
+
 \bibliographystyle{mnras}

### 2017-10-26 paper/paper.tex
inertia tensor

@@
 This special satellite distribution in the Milky Way makes the Local
-Group an atypical pair in the expected cosmological context.
+Group an atypical pair in the cosmological context provided by
+simulations. 
 We summarize these results in a simple multivariate Gaussian
@@
 
-We base all our results on the description provide by the inertia
+We base all our results on the description provided by the inertia
 tensor defined by the satellites's positions.
@@
 $\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
-of the satelites's geometric center ${\bf r}_{0}\equiv \frac{1}{N_s}\sum_{k\in
-  V} \bf{r}_i$, $\bf{1}$ is the unit matrix,  and  
+of the central galaxy $\bf{1}$ is the unit matrix,  and  
 ${\bf r}^T$ is the transposed vector $\bf{r}$. 
+We use $\bf{r}_0$ as the position of the central galaxy, and not the
+satellites' geometrical center, to allow for a fair comparison once
+the angular positions of the satellites are randomized around this
+point.
 

### 2017-10-26 paper/paper.tex
inertia tensor

@@
 
+It has been shown that LG pair separation vector is aligned along the
+filaments in  which they are typically embeded
+\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
+matter arrangements are aligned with the plane itself. 
+Characterizing the satellite alignments with $\mu$ thus provide
+information about how satellites are distributed with respect to the
+cosmic web.
+
 In Section we list the sources of the observational and
@@
 $\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$.
-We define the size of its three ellipsoidal axis as
+We define the size of the three ellipsoidal axis as
 $a=\sqrt{\lambda_1}$, $b=\sqrt{\lambda_2}$ and $c=\sqrt{\lambda_3}$.
+We also define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
+planar satellite distribution. 
+We also define the width, $w$, of the planar satellite distribution,
+$\sigma_p$ as the standard deviation of all satellite distances to the
+plane defined by the vector $\hat{n}$. 
+Finally, we characterize the alignment between the satellite plane and the
+vector connecting the two dominant galaxies by $\mu=|\hat{r}_{AB}\cdot
+\hat{n}|$.
 
-We define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
-planar satellite distribution. 
-We also define the width of the planar satellite distribution,
-$\sigma_p$ as the standard deviation of all satellite distances to the
-plane defined by the $\hat{n}$.
-
-We characterize the alignment between the satellite plane and the
-vector connecting the two dominant galaxies as $\mu=|\hat{r}_{AB}\cdot
-\hat{n}|$. 
-It has been shown that LG pair separation vector is aligned along the
-filaments in  which they are typically embeded
-\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
-matter arrangements are aligned with the plane itself. 
-Characterizing the satellite alignments with $\mu$ thus provide
-information about how satellites are distributed with respect to the
-cosmic web.
-
-\subsection{Parameter Distributions}
-
-We charaterize the $\mu$ distribution by a power law probability
-density distribution
-\begin{equation}
-P(\mu) = \frac{1}{\alpha}\mu^{\alpha-1}.
-\end{equation}
-We estimate the $\alpha$ using a bayesian approach, such as that
-the likelihood of being $\alpha$ the power value given the observed values of $\{\mu_i\}$
-  can be written as:
-
-\begin{equation}
-\mathcal{L}(\alpha|\{\mu_i\})=\frac{1}{Z_\alpha}\prod_{i=1}^{N_s}
-\frac{1}{\alpha}\mu_i^{\alpha-1}, 
-\end{equation}
-%
-where $Z_{\alpha}$ is a constant such as $\int_{0}^{\infty}
-{\mathcal L}(\alpha|\{\mu_i\}) {\rm d}\alpha=1$. 
-We report as $\hat{\alpha}$ the value of $\alpha$ 
-maximizing the likelihood,
-
-We characterize the distributions for the plane width and axis ratio
-$b/a$, $b/c$ through a gaussian
-\begin{equation}
-P(x)  = \frac{1}{\sqrt{2\pi \sigma^2}} \exp{\left[-\frac{1}{2}\left(\frac{x-x_m}{\sigma}\right)^2\right]}
-\end{equation}
-In this case the maximum likelihood values for the parameter estimates
-$\hat{x_m}$ and $\hat{\sigma}$ correspond to the mean and standard
-deviation, respectively.
-
-We summarize the results from the Illustris simulation by reporting
-the maximum likelihood parameter estimates. 
-In turn we use this us to estimate the probability of finding the
-observed values in the Local Group and compare it against the highest
-probabilty values.
+To summarize we characterize the satellite distribution by for
+quantities obtained from the inertia tensor: 
+\begin{itemize}
+\item Plane width, $w$.
+\item $c/a$ axis ratio.
+\item $b/a$ axis ratio.
+\item $\mu$ as a measure of plane alignment.
+\end{itemize}
 

### 2017-10-26 paper/paper.tex
satellite sample

@@
 $M_V=9$. We prefer using the dark matter information as the smallest
-sub-halos are sampled with $100$ particles. 
+sub-halos are sampled with at least $35$ particles. 
 For this reason we select the satellite galaxy samples from the
@@
 
-\section{Satellite Spatial Distribution}
+\section{Building, Characterizing and Comparing Satellites Spatial Distributions}
 \label{sec:SpatialMeasurements}
 
+\subsection{Building Satellite Samples}
+
+We compare the joint satellite distributions in the MW and M31 at fixed
+satellite number, $N_s$.
+This means that the magnitude cut corresponding to the faintest
+satellite included in the sample is different in each case.
+We make this choice for two reasons. 
+First, to be sure that there is a non-zero number of satellites in the
+simulations to make the computations.  
+Second, to rule out the influence of satellite numbers in the
+statistics.
+
+We compute the satellite statistics fo 11 up to 15 satellites.
+The lowest bound corresponds to the number of classical Milky Way
+satellites.
+The upper limit corresponds to the maximum number of satellites that
+can be resolved in both halos for most of the isolated pairs in Illustris-1.
+In simulations we rank the subhalos by their maximum
+circular velocity, in observations we rank the satellites by its $M_V$
+magnitude.
+
+We also use two kinds of satellite distributions. 
+The first keeps the positions for the satellites fixed as provided in
+the observations/simulations; the second randomizes the angular positions of
+the satellites around the central galaxy while keeping its radial
+distance fixed. The randomization process is done 100 times for each
+galaxy.
+
+\subsection{Describing Samples with the Inertia Tensor}
 We base all our results on the description provided by the inertia
@@
 \begin{equation}
-{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
+{\bf{\bar{I}}} = \sum_{k=1}^{N_s}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
   (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
@@
 
-\subsection{Satellite samples}
+\subsection{Comparing Satellite Samples}
 
-We compare the satellite distributions in the MW and M31 at fixed
-satellite number.
-This means that the magnitude cut corresponding to the faintest
-satellite included in the sample is different in each case.
-We make this choice for two reasons. 
-First to always be sure that there is a non-zero number of satellites to make the computations. 
-Second, to be able to compare the two halos at a fixed number of
-satellites.
-
-We test the shape and alignment statistics for 11 up 15 satellites.
-The lowest number corresponds to the number of classical Milky Way
-satellites.
-The upper limit corresponds to the minimum number of satellites that
-can be resolved in the simulations for both halos in each pair. 
-In the case of simulations we rank the subhalos by their maximum
-circular velocity. 
-We do not use their stellar properties because this represents the
-lower resolution limit for the hydrodynamics; most of these subhalos
-only have one stellar particle belonging to them. 
-In contrast, the detected sub-halos have at least 35 dark matter
-particles to determine their properties.
-
-We build two different kinds of statistics from these satellites
-First, we compute the shape and alignments for a varying number of
-satellites $11\leq N_{s}\leq 15$ keeping their ranking in
-$M_V$ or $V_{max}$. 
-This allows us to estimate the variation expected by changing the
-satellite number. 
-The second kind of statistics are computed for a fixed number of
-satellites $N_{s}=11$ randomly selected from the top $15$ ranked
-satellites. 
-We perform this bootstrapping $5$ times for each pair. 
-This allows us to estimate the variation expected by randomly sampling
-the satellites from a parent distribution.
+\subsection{Describing joint satellite distributions}
 

### 2017-10-26 paper/paper.tex
results from scratch

@@
 is completeley consistent with the expectation from simulations.
-\label{fig:scatter_ca_ration}}
+\label{fig:scatter_ca_ratio}}
 \end{figure*}
@@
 simulations. 
-\label{fig:scatter_ba_ration}}
+\label{fig:scatter_ba_ratio}}
 \end{figure*}
@@
 
-\subsection{Satellite distributions in the Local Group}
+\subsection{Plane Width}
 
-Figure \ref{fig:lg_scatter} summarizes our main results for the
-observed LG satellite distributions.
-We see that the \rank\ and \boot\ samples are consistent 
-withing the scatter provided by each sample.
-We use the median and standard deviation in each sample to define the
-most probable value and its associated uncertaintiy.
-This allows us to compare the observational values gainst the
-distributions derived from the Illustris simulation.
-
-There is a third sample in Figure \ref{fig:lg_scatter}. 
-It corresponds to the set of \rand\ points generated
-by randomizing the angular positions of the satellites in each pair in
-the \boot\ sample. 
-This provides a baseline to understand the importance 
-of intrinsic satellite's radial profile distribution in driving the
-results.
-
-The upper left panel in Figure \ref{fig:lg_scatter} shows that the
-planar satellite distributions are located perpendicular to the line
-connecting the two galaxies. 
-It is remarkable that this alignment is almost perfect for both
-satellite distributions. 
-The points in the \rand\ simply highlights the expected result for a
-random angular distribution is a flat distribution in the range
-$0\leq\mu\leq 1$.
-
-The upper right panel shows two interesting things. 
-First, the MW satellite plane is thiner than its M31
-counterpart. 
-This is in principle unexepected since M31 is more
-massive than the MW and it should have a broader satellite
-distribution. 
-The second interesting point is that the MW satellite plane is also
-thiner than the spherical randomized expectation, while the M31 plane
-is right within the expectation of the randomized satellites. 
-This is a another piece of evidence showing the highly structured
-satellite distribution in the MW in comparison to M31. 
-The fact that the \rand\ samples also show a trend towards thinner MW
-planes means that the radial satellite distribution in concentrated in
-the MW than it is in M31.
-
-The lower left panel re-inforces the picture of a highly structured
-MW. 
-It corresponds to the $c/a$ ratio and shows the same trends observed
-in for the plane width. 
-First, the ratio is lower for the MW than it is for M31; second, the
-ratio for the MW is also lower than the expectation for the randomized
-sample while the results for M31 is within the expectations from \rand.  
-In this case the median value of the \rand\ distributions follow the
-$1:1$ line as expected.
-The lower right panel does not show any surprises. 
-All the distributions from \rank, \boot\ and \rand\ are consistent
-both for the MW and M31.
-
-We can quantify the degree at which the observed satellite distributions are 
-different from their spherically randomized counterparts.
-Figure \ref{fig:lg_distribution} shows the probability distributions
-from the \rand\ pairs with an overplot of the LG values.
-The upper left panel shows the power law distribution for $\mu$. The
-results are not perfectly horizontal because the optimal power value
-$\hat{alpha}$ is slightly different from $1$, the uncertainties in
-this value are naturally consistent with the unit value expected for
-an homogeneous distribution. 
-In this case all values are equiprobable.
-In the case of the $b/a$ ratio (lower right panel) both the MW and M31
-are consistent with the average values expected from \rand\ distribution.
-Remarkably, the plane width and $c/a$ ratio for the MW are significantly 
-different from the \rand\ expected values, while the M31 values are
-sistematically within the expectations.
-
-The comparison of the observed satellite distribution against its onw
-version, but spherically randomized, tells us that the MW satellite
-planar structure is remarkably different from a random distribution,
-while for the M31 distribution there isn't a significant difference
-from the random expectation.
+Figure \ref{fig:scatter_width} summarizes the main results for the plane
+width distributions.
+The panel on the left compares the results for the MW and M31
+observations against its randomized version. 
+The most interesting outcome is that the MW plane width is smaller
+than $95\%$ of the planes computed from the randomized distribution,
+while the M31 plane width is consistent with the same distribution.
 

### 2017-10-27 paper/paper.tex
new plots

@@
 around the Milky way and M31. 
-We find that the satellites in MW show a distribution significantly
-thinner and flattened compared to the expectaions of a random
-spherical distribution and simulations based on the Lambda Cold Dark
-Matter paradigm.
-In turn, M31 is completely consistent with the expectations from a
-spherical satellite distribution and LCDM simulations.
-The satellite planes in the MW and M31 are almost perpendicular to the line
-connecting the two galaxies. None of the pairs in the simulation show
-a similar degree of alignment. 
-However, the simulations are consistent with a random uniform
-distribution, making the result from the observations consistent with
-these theoretical expectations.
-This special satellite distribution in the Milky Way makes the Local
+We use the Illustris-1 and ELVIS simulations to show that the
+MW satellite distribution is significantly thinner and more oblate
+than the expectations from the Lambda Cold Dark Matter (LCDM)
+paradigm. In contrast, the satellites in M31 are fully consistent with the
+average expectations from simulations.
+We also find that the satellite planes in the MW and M31 are almost perpendicular to the line
+connecting the two galaxies. While none of the pairs in the simulations show
+a similar degree of alignment, these alignments are consistent with a
+random uniform distribution, making the result from the observations
+consistent with these theoretical expectations.
+The special satellite distribution in the Milky Way makes the Local
 Group an atypical pair in the cosmological context provided by
-simulations. 
-We summarize these results in a simple multivariate Gaussian
-model to estimate that only $1\%$ of the pairs with isolation
+LCDM simulations. 
+We estimate that only $0.5\%$ to $1\%$ of the pairs with isolation
 and dynamical characteristics similar to the LG are expected to have
-satellite distributions with the same degree of atipicality. 
+satellite distributions with the same degree of atipicality, making
+the LG a $3\sigma$ outlier in a sample of simulated galaxy pairs.
 \end{abstract}
@@
 
-\section{Local Group Satellites in the Illustris Simulation}
-\label{sec:NumericalSetup}
+\section{Data from the ELVIS simulation}
+\label{sim:ELVIS}
+
+\section{Data from the Illustris Simulation}
+\label{sec:illustris}
 
@@
 
-We find 27 pairs with these conditions. We show in the Appendix A the
-physical  properties (stellar masses, maximum circular velocities,
-radial velocities and separation) in those pairs. 
+We find 27 pairs with these conditions. 
 We then select the pairs where in both halos there are at least 15
-detected subhalos. 
-We end up with a total of 20 pairs that fulfill these criteria.
+detected subhalos, thus discarding pairs with halos with the lowest
+mass.
+We end up with a total of 20 pairs that fulfill these criteria,
+Appendix A shows the physical  properties (stellar masses, maximum
+circular velocities, radial velocities and separation) in those pairs.
 
@@
 \includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_width.pdf}
 \caption{Plane width characterization in the Local Group and the
@@
 \includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 \includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 \includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_mu.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
-\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_M31.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
 \caption{Correlations between the normalized values for the plane
@@
 
+\subsection{$c/a$ axis ratio}
+
+\subsection{$b/a$ axis ratio}
+
+\subsection{s}
+
 \subsection{Satellite distributions in the Illustris Simulation}
@@
 The results from the \boot\ sample ara avaialble in the appendix.
+
+\section{Discussion}
+\subsection{Gaussian Model}
+
+\begin{equation*}
+\begin{bmatrix}
+1.6  & 1.2 & 7.3\times10^{-1} & 7.9\times 10^{-2} & 1.0\times 10^{-1}
+& 6.5\times 10^{-2}\\
+ 1.2  & 1.2 & 3.5\times10^{-1} & 8.9\times 10^{-3} & 1.5\times 10^{-2} &-7.4\times10^{-2}\\
+ 7.3\times10^{-1} & 3.5\times10^{-1} & 0.668 & 0.102 &-0.00331 & 0.151\\
+ 7.9\times 10^{-2}  & 8.9\times 10^{-3} & 0.102 & 0.474   & 0.695 &-0.127\\
+ 1.0\times 10^{-1}  & 1.5\times 10^{-2} &-0.003  &0.695  &1.48 &-0.695\\
+ 6.5\times 10^{-2} & -7.4\times10^{-2} & 0.151 &-0.127 &-0.695 & 0.607
+\end{bmatrix}
+\end{equation*}
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_width.pdf}\\
+\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}\\
+\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}\\
+\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_mu.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_mu.pdf}
+\caption{Same layout as in Figure \ref{fig:scatter_width}. 
+This time for the $b/a$ axis ratio. In this case both the MW and M31
+are consistent with the results of a spherical distribution and the
+simulations. 
+\label{fig:scatter_ba_ratio}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_M31.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_MW.pdf}
+\caption{Correlations between the normalized values for the plane
+  width, $c/a$ ratio and $b/a$ ratio. 
+The star corresponds to the LG, black circles with errorbars are the
+results from simulations and the gray cloud is the resul from the
+multivariate gaussian model.
+Upper/lower row summarizes the results for M31/M31.
+This simplified description allows us to quantify how atypical is the
+LG compared to the simulation results. 
+\label{fig:correlations}}
+\end{figure*}
+
 \end{document}

### 2017-10-27 paper/paper.tex
abstract

@@
 We quantify the joint spatial distribution of the brightest satellites
-around the Milky way and M31. 
+around the Milky Way (MW) and M31, the dominant galaxies in the Local
+Group (LG).
 We use the Illustris-1 and ELVIS simulations to show that the
@@
 a similar degree of alignment, these alignments are consistent with a
-random uniform distribution, making the result from the observations
-consistent with these theoretical expectations.
+random uniform distribution, making the observations
+consistent with theoretical expectations.
 The special satellite distribution in the Milky Way makes the Local
@@
 
-\section{Data from the ELVIS simulation}
+\section{Data from the ELVIS project}
 \label{sim:ELVIS}
 
-\section{Data from the Illustris Simulation}
+\section{Data from the Illustris project}
 \label{sec:illustris}
@@
 
-\begin{equation*}
-\begin{bmatrix}
-1.6  & 1.2 & 7.3\times10^{-1} & 7.9\times 10^{-2} & 1.0\times 10^{-1}
-& 6.5\times 10^{-2}\\
- 1.2  & 1.2 & 3.5\times10^{-1} & 8.9\times 10^{-3} & 1.5\times 10^{-2} &-7.4\times10^{-2}\\
- 7.3\times10^{-1} & 3.5\times10^{-1} & 0.668 & 0.102 &-0.00331 & 0.151\\
- 7.9\times 10^{-2}  & 8.9\times 10^{-3} & 0.102 & 0.474   & 0.695 &-0.127\\
- 1.0\times 10^{-1}  & 1.5\times 10^{-2} &-0.003  &0.695  &1.48 &-0.695\\
- 6.5\times 10^{-2} & -7.4\times10^{-2} & 0.151 &-0.127 &-0.695 & 0.607
-\end{bmatrix}
-\end{equation*}
-
 \begin{table*}
@@
 %https://arxiv.org/abs/1407.1078
+\appendix
 

### 2017-10-27 paper/paper.tex
caption

@@
 %=========================================================================
-\title[No Title]{No Title}
+\title[LG as an outlier]{We are not the 99 percent: the Local Group as an
+  outlier in galaxy pairs' satellite distributions}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 consistent with theoretical expectations.
-The special satellite distribution in the Milky Way makes the Local
-Group an atypical pair in the cosmological context provided by
-LCDM simulations. 
+The special MW satellite distribution makes the LG an atypical pair in
+the cosmological context provided by LCDM simulations. 
 We estimate that only $0.5\%$ to $1\%$ of the pairs with isolation
@@
 \includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
-\caption{Correlations between the normalized values for the plane
-  width, $c/a$ ratio and $b/a$ ratio. 
-The star corresponds to the LG, black circles with errorbars are the
-results from simulations and the gray cloud is the resul from the
-multivariate gaussian model.
-Upper/lower row summarizes the results for M31/M31.
-This simplified description allows us to quantify how atypical is the
-LG compared to the simulation results. 
-\label{fig:correlations}}
+\caption{Correlations between the multivariate gaussian model built on
+  the normalized values for the plane width $w$, $c/a$ ratio and $b/a$ ratio. 
+Left/right panel correspond to M31/MW. 
+The contour levels in the 2D histograms correspond to the $1\sigma$,
+$2\sigma$ and $3\sigma$ contours in two dimensions. 
+The dahsed vertical lines in the histograms along the diagonal
+correspond to the $1\sigma$ boundaries in one dimension.
+The results for the gaussian model are built from $10^6$ point
+realizations in the six-dimensional space spaned by the variables of
+interest. 
+The correlation matrix and the mean values are computed from the
+results in the Illustris-1 simulation.
+The cross indicates the LG values.
+This plot clearly shows how the M31 results are well within the
+expectations from simulations while MW has an unusual low value for
+the plane width and the $c/a$ axis ration.
+Similar results from the ELVIS data are presented in Figure
+\ref{fig:correlations_elvis}.
+\label{fig:correlations_illustris}}
 \end{figure*}
@@
 
-\subsection{s}
-
-\subsection{Satellite distributions in the Illustris Simulation}
-
-In the previous section we saw how the MW cannot be concealed with its
-randomized satellite distribution, while M31 is fully consistent with
-it. 
-We now quantify whether the MW and M31 are consistent with the
-expectations from the Illustris Simulation.
-We show here the results from the \rank\ sample. 
-The results from the \boot\ sample ara avaialble in the appendix.
+\subsection{Plane alignment}
 
@@
 \subsection{Gaussian Model}
-
-\begin{table*}
-  \centering
-\begin{tabular}{lll}
-\hline\hline
-Symbol & Units & Description\\\hline
-$\hat{r}_{AB}$& & Unit vector along the direction connecting two
-dominant galaxies\\
-$N_s$ & & Number of satellites\\
-$a > b> c$ & kpc & Inertia tensor eigenvalues. \\
-$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$ & & Inertia tensor eigenvectors. \\
-$\sigma_s$ & kpc & Ellipsoid width\\
-\hline\hline
-\end{tabular}
-  \caption{Overview of the parameters computed for each central galaxy
-    and its satellite system.
-  \label{tab:models}}
-\end{table*}
 
@@
 %https://arxiv.org/abs/1407.1078
+\newpage
 \appendix
 
+\section{Results from ELVIS}
 \begin{figure*}
 \centering
-\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_width.pdf}\\
-\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}\\
-\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}\\
-\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_mu.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_mu.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_width.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_mu.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_width.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_mu.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 LG compared to the simulation results. 
-\label{fig:correlations}}
+\label{fig:correlations_elvis}}
 \end{figure*}

### 2017-10-27 paper/paper.tex
updated captions + results from the gaussian model

@@
 \begin{abstract}
-We quantify the joint spatial distribution of the brightest satellites
+In this paper we quantify the joint spatial distribution of the brightest satellites
 around the Milky Way (MW) and M31, the dominant galaxies in the Local
 Group (LG).
-We use the Illustris-1 and ELVIS simulations to show that the
-MW satellite distribution is significantly thinner and more oblate
-than the expectations from the Lambda Cold Dark Matter (LCDM)
-paradigm. In contrast, the satellites in M31 are fully consistent with the
-average expectations from simulations.
-We also find that the satellite planes in the MW and M31 are almost perpendicular to the line
-connecting the two galaxies. While none of the pairs in the simulations show
-a similar degree of alignment, these alignments are consistent with a
-random uniform distribution, making the observations
-consistent with theoretical expectations.
-The special MW satellite distribution makes the LG an atypical pair in
-the cosmological context provided by LCDM simulations. 
-We estimate that only $0.5\%$ to $1\%$ of the pairs with isolation
+We use the Illustris-1 and ELVIS simulations to quantify how the 
+unusual satellite distribution in the MW  makes the LG an atypical pair in
+the broader cosmological context provided by LCDM simulations. 
+We find that only $0.05\%$ to $0.25\%$ of the pairs with isolation
 and dynamical characteristics similar to the LG are expected to have
 satellite distributions with the same degree of atipicality, making
-the LG a $3\sigma$ outlier in a sample of simulated galaxy pairs.
+the LG a $3\sigma$ outlier.
 \end{abstract}
@@
 
-\section{Observational Data}
+\label{Data Samples}
+
+\subsection{Observational Data}
 \label{sec:obs}
 
-\section{Data from the ELVIS project}
+\subsection{Data from the ELVIS project}
 \label{sim:ELVIS}
 
-\section{Data from the Illustris project}
+\subsection{Data from the Illustris project}
 \label{sec:illustris}
@@
 sub-halos are sampled with at least $35$ particles. 
-For this reason we select the satellite galaxy samples from the
-
 We chose the satellite samples by ranking the subhalos in decreasing
@@
 halos in the list. 
-The results in the main body of the paper correspond to $11\leq
-N_p\leq 15$.
+The results presented here correspond to $11\leq N_p\leq 15$.
 
@@
 the satellites around the central galaxy while keeping its radial
-distance fixed. The randomization process is done 100 times for each
+distance fixed. The randomization process is done 1000 times for each
 galaxy.
@@
 The panel on the left shows the plane width in physical units
-comparing the results of five measurements from the observations
-(stars) and the result of spherically randomizing the satellite
-positions (circles). 
+comparing the results from observations
+(stars) against the result of spherically randomizing the satellite
+positions while keeping its radial distance (circles). 
 The panel in the middle compares the average from the observations
@@
 In this case both the MW and M31 show a strong alignment.
-Apparently this result is outside the expectations from the
+Apparently the LG is outside the expectations from
 simulations and atypical compared to the spherical results. 
@@
 expectations from simulations while MW has an unusual low value for
-the plane width and the $c/a$ axis ration.
-Similar results from the ELVIS data are presented in Figure
+the plane width and the $c/a$ axis ratio.
+Equivalent results from the ELVIS data are presented in Figure
 \ref{fig:correlations_elvis}.
@@
 \caption{Probability distribution for the expected number of pairs
-  showing the same degree of atipicality as the Local Group. The two
-  distributions correspond to different numbers of initial isolated
-  pairs. On average $1\%$ of the isolated pairs should present
+  showing the same degree of atipicality as the Local Group if drawn
+  from a sample of 2000 isolated pairs. 
+  The distributions correspond to results derived from Illustris-1
+  and ELVIS data.
+  On average between $0.05\%$ and $0.25\%$ of the isolated pairs should present
   satellite distributions as atypical as the Local Group.
@@
 \section{Discussion}
-\subsection{Gaussian Model}
+\subsection{Outlier characterization with a Multivariate Gaussian Model}
 
@@
 
+\section{Physical Characteristics of the Isolated Pairs samples}
+
 \section{Results from ELVIS}
@@
 \includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_mu.pdf}
-\caption{Same layout as in Figure \ref{fig:scatter_width}. 
-This time for the $b/a$ axis ratio. In this case both the MW and M31
-are consistent with the results of a spherical distribution and the
-simulations. 
-\label{fig:scatter_ba_ratio}}
+\caption{ELVIs results for the quantities presented for the Illustris-1
+  simulation in Figures  \ref{fig:scatter_width},
+  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio} and
+  \ref{fig:scatter_mu}.
+Upper row corresponds to the raw values from observations and
+simulated pairs, while the second row normalizes the same values to
+the mean and standard deviation on its spherically randomized
+counterparts. 
+\label{fig:scatter_elvis}}
 \end{figure*}
@@
 \includegraphics[width=0.45\textwidth]{gaussian_model_elvis_MW.pdf}
-\caption{Correlations between the normalized values for the plane
-  width, $c/a$ ratio and $b/a$ ratio. 
-The star corresponds to the LG, black circles with errorbars are the
-results from simulations and the gray cloud is the resul from the
-multivariate gaussian model.
-Upper/lower row summarizes the results for M31/M31.
-This simplified description allows us to quantify how atypical is the
-LG compared to the simulation results. 
+\caption{
+Same layout as Figure \ref{fig:correlations_illustris}, this time
+computed from the ELVIS data.
 \label{fig:correlations_elvis}}

### 2017-10-28 paper/paper.tex
new table + abstract

@@
 \usepackage{amssymb} 
+\usepackage{multirow}
+
 \usepackage{graphicx}
@@
 We use the Illustris-1 and ELVIS simulations to quantify how the 
-unusual satellite distribution in the MW  makes the LG an atypical pair in
-the broader cosmological context provided by LCDM simulations. 
+unusual satellite distribution in the MW  makes the LG an atypical pair.
+A crucial aspect in our analysis is that we define the atypicallity as
+the degree at which a satellite distribution deviates from sphericity and
+not as a deviation from simulations.
 We find that only $0.05\%$ to $0.25\%$ of the pairs with isolation
@@
 
+M31 observations
+
+\begin{table*}
+  \centering
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|c|c|}
+    \hline
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
+    % \hline
+    % \textbf{Inactive Modes} & \textbf{Description}\\
+    \cline{2-9}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
+    %\hhline{~--}
+    \hline
+    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $65\pm 11$   & $45\pm 8$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
+    $c/a$ ratio & $0.67\pm 0.03$ & $0.53\pm 0.03$ & $0.75\pm0.07$ & $0.72\pm 0.07$ & $0.72\pm 0.01$ & $0.72\pm 0.01$ & $0.73\pm 0.01$& $0.69\pm 0.01$ \\ \hline
+    $b/a$ ratio & $0.90\pm 0.03$ & $0.88\pm 0.01$ & $0.90\pm0.04$ & $0.90\pm 0.04$ & $0.89\pm 0.01$ & $0.89\pm 0.01$ & $0.89\pm0.01$& $0.90\pm 0.01$\\ \hline
+  \end{tabular}
+  \caption{Mode Transition Times}
+\end{table*}
+
 \section{Discussion}

### 2017-10-28 paper/paper.tex
abstract titulo

@@
 \title[LG as an outlier]{We are not the 99 percent: the Local Group as an
-  outlier in galaxy pairs' satellite distributions}
+  extreme outlier in satellite distributions}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 \begin{abstract}
-In this paper we quantify the joint spatial distribution of the brightest satellites
-around the Milky Way (MW) and M31, the dominant galaxies in the Local
-Group (LG).
-We use the Illustris-1 and ELVIS simulations to quantify how the 
-unusual satellite distribution in the MW  makes the LG an atypical pair.
-A crucial aspect in our analysis is that we define the atypicallity as
-the degree at which a satellite distribution deviates from sphericity and
-not as a deviation from simulations.
-We find that only $0.05\%$ to $0.25\%$ of the pairs with isolation
+In this paper we quantify the joint spatial distribution of the
+brightest satellites around the Milky Way (MW) and M31, the dominant
+galaxies in the Local Group (LG).
+We use the Illustris-1 and ELVIS simulations to quantify the
+expected deviations from statistically spherical satellite
+distributions in the Lambda Cold Dark Matter paradigm. 
+We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
 and dynamical characteristics similar to the LG are expected to have
-satellite distributions with the same degree of atipicality, making
-the LG a $3\sigma$ outlier.
+satellite distributions with the same degree deviation form
+sphericity, making the LG a $3\sigma$ outlier.  
 \end{abstract}

### 2017-10-28 paper/paper.tex
updated plots

@@
 \title[LG as an outlier]{We are not the 99 percent: the Local Group as an
-  extreme outlier in satellite distributions}
+  extreme outlier in ellipsoidal satellite distributions}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 and dynamical characteristics similar to the LG are expected to have
-satellite distributions with the same degree deviation form
-sphericity, making the LG a $3\sigma$ outlier.  
+satellite distributions with the same degree of deviation from
+sphericity.
+This makes the LG a $3\sigma$ outlier, with all the weight lying on
+the extremly planar (width of $22\pm 2$kpc and mayor-to-minor axis
+ration of $c/a=0.53\pm0.03$) satellite distribution in the MW. 
 \end{abstract}
@@
     \hline
-    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $65\pm 11$   & $45\pm 8$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
-    $c/a$ ratio & $0.67\pm 0.03$ & $0.53\pm 0.03$ & $0.75\pm0.07$ & $0.72\pm 0.07$ & $0.72\pm 0.01$ & $0.72\pm 0.01$ & $0.73\pm 0.01$& $0.69\pm 0.01$ \\ \hline
-    $b/a$ ratio & $0.90\pm 0.03$ & $0.88\pm 0.01$ & $0.90\pm0.04$ & $0.90\pm 0.04$ & $0.89\pm 0.01$ & $0.89\pm 0.01$ & $0.89\pm0.01$& $0.90\pm 0.01$\\ \hline
+    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
+    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
+    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
   \end{tabular}

### 2017-10-30 paper/paper.tex
mu

@@
 %=========================================================================
-\title[LG as an outlier]{We are not the 99 percent: the Local Group as an
-  extreme outlier in ellipsoidal satellite distributions}
+\title[LG as an outlier]{We are not the 99 percent: quantifying the
+  atypical satellite distributions in the Local Group}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 This makes the LG a $3\sigma$ outlier, with all the weight lying on
-the extremly planar (width of $22\pm 2$kpc and mayor-to-minor axis
-ration of $c/a=0.53\pm0.03$) satellite distribution in the MW. 
+the extremly planar MW satellite distribution.
 \end{abstract}
@@
 
-Figure \ref{fig:scatter_width} summarizes the main results for the plane
+Figure \ref{fig:scatter_width} summarizes the results for the plane
 width distributions.
@@
 
-M31 observations
+Figure \ref{fig:scatter_mu} summarizes the Illustris results for the
+alignments between the vector normal to the plane and the vector
+connecting the two dominant galaxies.
+The corresponding results for the ELVIS data are shown in Figure
+\ref{fig:scatter_elvis}.
+
+The first striking impression from the left panel in Figure
+\ref{fig:scatter_mu} is that the observations are cornered in
+a region of strong alignment, $\mu\approx 1$, for both galaxies. 
+In other words, the planes are almost perpendicular to the direction
+connecting the two galaxies. 
+The result for the spherical randomization corresponds to a uniform
+distribution $0\leq \mu\leq 1$ as shown in the same panel.
+
+The middle panel tells a similar story for the results from
+Illustris. That is, there isn't a prefered alignment direction from
+the simulation. This also holds for ELVIS data.
+We quantify this visual impresion by performing a K-S test where the
+null hypothesis corresponds to an uniform distribution. 
+The results from the K-S test do not allow us to discard the null
+hypotesis.
+
+This information allows us to properly understand the results on the
+right panel in Figure \ref{fig:scatter_mu}.
+That panel shows the results for the normalized values to the mean and
+standard deviation computed from spherically randomized
+ditributions.
+In this case the LG $\mu$ value has the same probability as any other value
+(because it is consistent with an uniform distribution) and the apparent
+large distance from the Illustris data must not be interpreted as an
+the LG having an atypical alignment.
+
+We defer to the Section \ref{sec:discussion} our discussion on how
+this
 

### 2017-10-30 paper/paper.tex
mu
title

@@
 %=========================================================================
-\title[LG as an outlier]{We are not the 99 percent: quantifying the
-  atypical satellite distributions in the Local Group}
+\title[LG as an outlier]{We are not the 99 percent: quantifying
+  bright satellite distributions in the Local Group}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 We defer to the Section \ref{sec:discussion} our discussion on how
-this
+this can be reconciled with other studies that show preferential
+infall satellite directions in LCDM simulations.
 

### 2017-11-01 paper/paper.tex
+1 paragraph

@@
 \subsection{$c/a$ axis ratio}
+Figure \ref{fig:scatter_ca_ratio} shows the results for the minor to
+major axis ratio. 
+Corresponding in the ELVIS data are in the appendix in Figure
+\ref{fig:scatter_elvis}.
+
+The left panel shows the results for the LG compared against its
+spherically randomized version.
+As expected the $c/a$ ratio in the MW is significantly lower as the
+measured values for spherical distributions. 
+On the other hand the ratio for M31 is lower than the mean of the
+spherical values but still well within its variance.
+In contrast to the results for the plane width, this time the
+randomized values have symmetrical expectations between the two
+galaxies.
+
+The midle panel
 

### 2017-11-01 paper/paper.tex
+1 paragraph

@@
 
-The midle panel
+The middle panel shows the LG compared against the results from
+Illustris. In this case we find a similar trend. The MW is atypical
+and M31 is within the variance from the simulation data.
+This time, however, there is a single MW-like galaxy out of the total
+of 20 that shows an $c/a$ as small as the MW.
+The only assymetry evident between the simulated halos is in the
+dispersion, the $c/a$ distribution for the massive halos seems to be
+wider than it is for the less massive partner.
 

### 2017-11-01 paper/paper.tex
+1 paragraph

@@
 
+The right panel shows the normalized results. 
+This highlights the two results mentioned above.
+First, the MW shows a low $c/a$ ration $2.5$ standard deviations away
+from the mean value of the spherical distribution; this contrasts the
+results for M31 which are close to $1$ standard deviation away.
+Second, the less massive halos in the Illustris simulation present a
+smaller dispersion in their deviations from sphericity than the
+its masssive partner.
+
+These
+
 \subsection{$b/a$ axis ratio}

### 2017-11-01 paper/paper.tex
+ 1 paragraph

@@
 The most interesting outcome is that the MW plane width is smaller
-than $95\%$ of the planes computed from the randomized distribution,
+than $\approx 98\%$ of the planes computed from the randomized distribution,
 while the M31 plane width is consistent with the same distribution.
@@
 This highlights the two results mentioned above.
-First, the MW shows a low $c/a$ ration $2.5$ standard deviations away
+First, the MW shows a low $c/a$ ration close to two standard deviations away
 from the mean value of the spherical distribution; this contrasts the
@@
 its masssive partner.
-
-These
+The MW axis ratio smaller than $\approx 98\%$ of the randomized
+satellite distributions.   and its atipicallity is only comparable to
+one halo in the Illustris  simulation (none in the ELVIS simulation).
 

### 2017-11-01 paper/paper.tex
+1 paragraph

@@
 
+Figure \ref{fig:scatter_ba_ratio} shows the results for the minor to
+major axis ratio. 
+Corresponding in the ELVIS data are in the appendix in Figure
+\ref{fig:scatter_elvis}.
+In all cases of comparison (against randomized distribution,
+comparasion against simulations and degree of deviation from
+sphericity) the results for both the MW and M31 do not seem atypical
+or deviated from the expectations for an spherical dsitribution.
+
 \subsection{Plane alignment}

### 2017-11-02 paper/paper.tex
+1 paragraph

@@
 \subsection{Comparing Satellite Samples}
+
+We compare every satellite distribution against its own spherically
+randomized distribution.
+We keep fixed the radial position of every satellite
+with respect to the central galaxy and then randomizing its angular
+position. 
+We repeat this procedure 1000 times for each satellite distribution
+and proceed to measure the quantities mentioned in the last section:
+$w$, $c/a$, $b/a$ and $mu$.
+For each quantity we compute an average and standard deviation from
+the 1000 random samples. 
+This allows us to build a normalized version of all quantities of
+interest by substracting the mean and dividing between the standard
+deviation of the randomized samples.
+
+This allows us to make a first comparison. 
+The observed/simulated
+distribution against its randomized version. 
+The second intermediate comparison we make are observations against
+simulations.
+The final comparison is between the normalized quantities, both
+observed and simulated.
+
+The comparison between the normalized quantities is the one that
+carries the important information about the deviations from spheriticy.
 

### 2017-11-02 paper/paper.tex
+1 paragraph

@@
 \begin{abstract}
-In this paper we quantify the joint spatial distribution of the
+In this paper we quantify the deviations from sphericity in the spatial distribution of the
 brightest satellites around the Milky Way (MW) and M31, the dominant
@@
 We use the Illustris-1 and ELVIS simulations to quantify the
-expected deviations from statistically spherical satellite
-distributions in the Lambda Cold Dark Matter paradigm. 
+same deviations from sphericity in the Lambda Cold Dark Matter paradigm. 
 We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
@@
 The comparison between the normalized quantities is the one that
-carries the important information about the deviations from spheriticy.
+carries the important information about the deviations from
+spheriticy. 
+We do not want to directly compare how the results observations
+deviate from simulations but to compare the deviations from
+asphericity in observations and simulations.
+
+It
 

### 2017-11-02 paper/paper.tex
+1 paragraph

@@
 
-It
+\subsection{Describing joint satellite distributions}
 
-\subsection{Describing joint satellite distributions}
+After building the normalized variables with the simulated data we
+perform  a Kolmogorov-Smirnov test with the null hypothesis of belongig
+to a normal distribution with mean and standard deviation computed
+from the mean and standard deviation from the data itself. 
+We find that the distributions for $w$, $c/a$ and $b/a$ cannot reject
+the null hypothesis. 
+Only the distribution for $\mu$ corresponds to a
+uniform distribution.
+
+We then build a multivariate normal distribution for $$
 

### 2017-11-02 paper/paper.tex
+1 paragraph

@@
 
-We then build a multivariate normal distribution for $$
+We then build a multivariate normal distribution for the two halos and
+the three variables consistent with a unidimensional normal
+distribution using the vector of mean values and covariance matrix.
+This means that our final covariance matrix is $6\times 6$ and takes
+into account the correlations internal to a single galaxy and with its
+partner.
+
+This
 

### 2017-11-02 paper/paper.tex
+1 paragraph

@@
 
-\subsection{Data from the ELVIS project}
-\label{sim:ELVIS}
-
 \subsection{Data from the Illustris project}
@@
 circular velocities, radial velocities and separation) in those pairs. 
+This corresponds to a pair number density of $2 \times10^{-5}$
+pairs Mpc$^{-3}$
 
@@
 The results presented here correspond to $11\leq N_p\leq 15$.
+
+\subsection{Data from the ELVIS project}
+\label{sim:ELVIS}
+
+For a detailed description of the ELVIS project and data we refer the
+reader to. 
+Here we summarize the elements relevant to our discussion.
+The data we use from the ELVIS project comes from the resimulation of
+dark matter halo pairs selected in dark matter only cosmological simulations.
+The parent cosmological boxes have a cosmology consistent with the
+Wilkinson Microwave Anisotropy Probe 7 results.
+They used the results from 50 simulation boxes of side lenght $70.4$
+Mpc to select pairs with kinematic characteristics similar to the LG.
+These selection criteria included the following
+\begin{itemize}
+\item The virial mass of each host must be in the range 
+$1\times
+  10^{12} M_{\odot}< M_{vir}<3\times 10^{12}M_{\odot}$ 
+\item The total pair mass must be in the range
+$2\times
+  10^{12} M_{\odot}< M_{vir}<5\times 10^{12}M_{\odot}$ 
+\item The center of mass separation is in the range $0.6\leq d\leq1$
+  Mpc.
+\item The relative radial velocity is negative.
+\item No halos more massive than the least massive halo within $2.8$
+  Mpc and no halos with $M_{vir}>7\times 10^{13}$ within $7$ Mpc of
+  the pairs' center of mass.
+\end{itemize}
+
+This corresponds to a pair number density of $8 \times10^{-6}$ pairs
+Mpc$^{-3}$, this is a factor $2.4$ lower than the pair number density
+we find in Illustris-1.
+There were a total of 146 pairs that met those criteria, but only $12$
+were chosen for resimulation. 
+Additionally, the selected pairs have a relative tangential velocity
+less than $75$ \kms.
 
@@
 
-This
+This compact description allows us to generate samples consistent with
+the simulations used in their construction.
+Finally, we use those generated samples to estimate how commoon are
+the deviations from sphericity that we measure in the observational
+data.
 

### 2017-11-02 paper/paper.tex
+1 paragraph

@@
 were chosen for resimulation. 
-Additionally, the selected pairs have a relative tangential velocity
-less than $75$ \kms.
+Additionally, the selected pairs for resimulation have a relative
+tangential velocity less than $75$ \kms. 
+In this paper we only use the results from the $12$ resimulated pairs.
 
@@
 and proceed to measure the quantities mentioned in the last section:
-$w$, $c/a$, $b/a$ and $mu$.
+$w$, $c/a$, $b/a$ and $\mu$.
 For each quantity we compute an average and standard deviation from
@@
 
+\subsection{Multivariate Distributions}
+
+\begin{table*}
+  \centering
+  \begin{tabular}{c|c|c|c|c|c|c|}
+    \hline
+        & M31 & M31 &M31 & MW & MW &MW\\
+        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
+M31 $w$ & & & & & & \\ 
+M31 $c/a$ & & & & & & \\ 
+M31 $b/a$ & & & & & & \\ 
+MW $w$ & & & & & & \\ 
+MW $c/a$ & & & & & & \\ 
+MW $b/a$ & & & & & & \\ 
+  \end{tabular}
+  \begin{tabular}{c|c|c|c|c|c|c|}
+    \hline
+        & M31 & M31 &M31 & MW & MW &MW\\
+        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
+M31 $w$ & & & & & & \\ 
+M31 $c/a$ & & & & & & \\ 
+M31 $b/a$ & & & & & & \\ 
+MW $w$ & & & & & & \\ 
+MW $c/a$ & & & & & & \\ 
+MW $b/a$ & & & & & & \\ 
+  \end{tabular}
+
+  \caption{Correlation matrix for the normalized values of $w$, $c/a$
+    and $b/a$ computed from the $20$ pairs in the Illustris-1
+    simulation (left) and the ELVIS project (right).}
+\end{table*}
+
+\section{Discussion}
+
 \begin{table*}
@@
 \section{Discussion}
+
 \subsection{Outlier characterization with a Multivariate Gaussian Model}

### 2017-11-02 paper/paper.tex
add covariances in text

@@
 
-\begin{table*}
-  \centering
-  \begin{tabular}{c|c|c|c|c|c|c|}
-    \hline
-        & M31 & M31 &M31 & MW & MW &MW\\
-        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
-M31 $w$ & & & & & & \\ 
-M31 $c/a$ & & & & & & \\ 
-M31 $b/a$ & & & & & & \\ 
-MW $w$ & & & & & & \\ 
-MW $c/a$ & & & & & & \\ 
-MW $b/a$ & & & & & & \\ 
-  \end{tabular}
-  \begin{tabular}{c|c|c|c|c|c|c|}
-    \hline
-        & M31 & M31 &M31 & MW & MW &MW\\
-        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
-M31 $w$ & & & & & & \\ 
-M31 $c/a$ & & & & & & \\ 
-M31 $b/a$ & & & & & & \\ 
-MW $w$ & & & & & & \\ 
-MW $c/a$ & & & & & & \\ 
-MW $b/a$ & & & & & & \\ 
-  \end{tabular}
-
-  \caption{Correlation matrix for the normalized values of $w$, $c/a$
-    and $b/a$ computed from the $20$ pairs in the Illustris-1
-    simulation (left) and the ELVIS project (right).}
-\end{table*}
-
 \section{Discussion}
@@
 
+Illustris
+\begin{verbatim}
+[[ 0.8344  0.7849  0.4186 -0.1155  0.0340 -0.1614]
+ [ 0.7849  1.1698 -0.1568 -0.0793  0.0362 -0.1213]
+ [ 0.4186 -0.1568  0.9606 -0.1151 -0.0150 -0.1098]
+ [-0.1155 -0.0793 -0.1151  0.7873  0.6339  0.4006]
+ [ 0.0340  0.0362 -0.0150  0.6339  0.6932  0.0652]
+ [-0.1614 -0.1213 -0.1098  0.4006  0.0652  0.6100]]
+\end{verbatim}
+
+\begin{verbatim}
+[-0.1852 -0.4152    -0.2002 -0.1786 -0.4072 -0.2394]
+\end{verbatim}
+
+ELVIS
+\begin{verbatim}
+[[ 1.6051  1.2207  0.7062  0.0833  0.1063  0.0812]
+ [ 1.2207  1.0872  0.3584  0.0298  0.1085 -0.0324]
+ [ 0.7062  0.3584  0.6363  0.0904  0.0194  0.1601]
+ [ 0.0833  0.0298  0.0904  0.4534  0.6138 -0.1159]
+ [ 0.1063  0.1085  0.0194  0.6138  1.2120 -0.6372]
+ [ 0.0812 -0.0324  0.1601 -0.1159 -0.6372  0.6475]]
+\end{verbatim}
+
+\begin{verbatim}
+[-0.1803 -0.2829 -0.2205 -0.3292 -0.7484 -0.0863]
+\end{verbatim}
 \end{document}

### 2017-11-03 paper/paper.tex
some pagragraphs

@@
 \section{Introduction}
+
+The presence of a Vast Polar Structure of satellites around the Milky
+Way has been stablished in the last decade.
+The question whether this configuration is atypical in the observable
+universe cannot be proberly addressed given the current limits in
+observations. 
+So far it has only been possible to contraint that $5\%$ of the
+Milky-Way like galaxies in the Universe have two bright satellite
+galaxies as is the case of the Milky Way and its Large and Small
+Magellanic Clouds.
+
+The closest system that could help us in providing a baseline for
+comparison is the Andromeda galaxy, M31. 
+Its close enough that an observational
+
+This has prompted a discussion on whether the current dominant
+paradigm for galaxy formation based on a Cold Dark Matter cosmology in
+a expanding universe described by General Relativity with a
+Cosmological Constant, so-called Lambda Cold Dark Matter (LCDM) model
+can account for the existence of such a structure.
 

### 2017-11-03 paper/paper.tex
some pagragraphs

@@
 Way has been stablished in the last decade.
+This structure can be easily described by global quantities of the
+brightest
+
 The question whether this configuration is atypical in the observable
@@
 comparison is the Andromeda galaxy, M31. 
-Its close enough that an observational
+Its close enough that an observational study of its satellite
+population is possible, with the great advantage of having a
+perpective from a distance and not from within, as is the case for our
+Galaxy. 
+These studies also found a planar satellite
+distributions.
+This time not in the whole distribution, but in a subset of $15$
+satellites out of an homogeneous sample of $27$ satellites.
 
-This has prompted a discussion on whether the current dominant
-paradigm for galaxy formation based on a Cold Dark Matter cosmology in
+This has prompted a discussion on whether this satellite distributions
+are easily found in structure formation simulations done in the
+current dominant paradigm for galaxy formation.
+This paradigm, based on a Cold Dark Matter cosmology in
 a expanding universe described by General Relativity with a
-Cosmological Constant, so-called Lambda Cold Dark Matter (LCDM) model
-can account for the existence of such a structure.
+Cosmological Constant, is the so-called Lambda Cold Dark Matter
+(LCDM).
+
+The consensus is that these structures are hard to find in
+simulations. 
+Some studies have focused on the study of individual dark matter halos
+that could host galaxies like the MW or M31, while some other studies
+have tried to simulate the formation of galaxy pairs resembling both
+the MW and M31.
+The transition from studying individual halos to pairs has been
+motivated by the realization that
 

### 2017-11-03 paper/paper.tex
some pagragraphs

@@
 The transition from studying individual halos to pairs has been
-motivated by the realization that
+motivated by the hypotesis hat the location of the Local Group in
+the cosmic web should play a determinant role in building up planar
+satellite distributions through preferential alignments and accretions
+histories of galaxies.
+
+To
 

### 2017-11-03 paper/paper.tex
some pagragraphs

@@
 
-To
-
-It has been shown that LG pair separation vector is aligned along the
-filaments in  which they are typically embeded
-\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
-matter arrangements are aligned with the plane itself. 
-Characterizing the satellite alignments with $\mu$ thus provide
-information about how satellites are distributed with respect to the
-cosmic web.
+Studies of the Local Group in an explicit cosmological context have
+also renewed the interest on performing constrained simulations that
+could reproduce the observed large scale structure of the Universe,
+This has also motivated the study of the two dominant galaxies in the 
+Local Group as a pair in a cosmological context.
 
@@
 plane defined by the vector $\hat{n}$.
-Finally, we characterize the alignment between the satellite plane and the
+
+It has been shown that LG pair separation vector is aligned along the
+filaments in  which they are typically embeded
+\citep{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
+matter arrangements are aligned with the plane itself. 
+Characterizing the satellite alignments with $\mu$ thus provide
+information about how satellites are distributed with respect to the
+cosmic web. 
+For that reason we also characterize the alignment between the satellite plane and the
 vector connecting the two dominant galaxies by $\mu=|\hat{r}_{AB}\cdot

### 2017-11-03 paper/paper.tex
some pagragraphs

@@
 This has also motivated the study of the two dominant galaxies in the 
-Local Group as a pair in a cosmological context.
+Local Group as a pair in a cosmological context finding that the LG
+itself has relatively uncommon kinematic configuration in the context
+of LCDM and a strong preference to lie along filaments.
+
+The aim of our work is to put together some of these pieces in a 
+simple framework to quantify how atypical is the satellite
+distribution found in the Local Group.
+Some of the explicit characteristics we want to keep in our treatment
+of the problem are the (i) cosmological context, (ii) the LG as a pair
+of galaxies and (iii) a simple and robust description for the
+satellites.
+
+The first condition constrains the kind of simulations we use. 
+We either results from fully cosmological simulations or resimulations
+of cosmological sub-volumes. 
+The second condition constraints the kind of samples we want to
+use. We build explicit samples of pairs that resemble the kinematic
+structure of the MW and M31. 
+The third condition motivates to only use the inertia tensor as a
+description for the satellites positions, while droping any
+information that might come from 3D velocities (high uncertainties) or
+involved algorithms for plane fitting.
+
+Finally,
 
@@
 
-\label{Data Samples}
+\section{Data samples}
 

### 2017-11-03 paper/paper.tex
text +pdf

@@
 %=========================================================================
-\title[LG as an outlier]{We are not the 99 percent: quantifying
-  bright satellite distributions in the Local Group}
+\title[LG satellites asphericity ]{We are not the 99 percent: quantifying
+  asphericity in the Local Group satellites' distributions}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 
-Finally,
+Finally, to compute the odds of finding the LG satellite distributions 
+in LCDM simulations, we do not make a direct search for the exact
+observed values into simulations because, as we show in Section, the
+LG is itself rare and we do not have enough simulated systems to
+perform such a brute force solution. 
+We also avoid this direct comparison for a second reason. 
+We do not want to implicitly use either LCDM or observations as what
+is considered normal or standard and compute the deviations from that
+point. 
+Our approach is different. 
+We set as a point of reference an spherical satellite
+distribution to quantify how both simulations and observations
+deviate from the spherical distribution.
+Simulations help us to construct an explicit probability distribution
+for deviations from sphericity in LCDM.
+Then we compute the odds of finding n satellite distributions that
+deviates from sphericity as much as the LG does.
 
@@
 characterize the satellite distributions.
-In section we present our results. 
+In section we present the results. 
 In the discussion section we quantify the correlations between the main

### 2017-11-03 paper/paper.tex
remove mu information

@@
 
-It has been shown that LG pair separation vector is aligned along the
-filaments in  which they are typically embeded
-\citep{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
-matter arrangements are aligned with the plane itself. 
-Characterizing the satellite alignments with $\mu$ thus provide
-information about how satellites are distributed with respect to the
-cosmic web. 
-For that reason we also characterize the alignment between the satellite plane and the
-vector connecting the two dominant galaxies by $\mu=|\hat{r}_{AB}\cdot
-\hat{n}|$.
-
 To summarize we characterize the satellite distribution by for
@@
 \item $b/a$ axis ratio.
-\item $\mu$ as a measure of plane alignment.
 \end{itemize}
@@
 and proceed to measure the quantities mentioned in the last section:
-$w$, $c/a$, $b/a$ and $\mu$.
+$w$, $c/a$ and $b/a$.
 For each quantity we compute an average and standard deviation from
@@
 the null hypothesis.
-Only the distribution for $\mu$ corresponds to a
-uniform distribution.
 
@@
 \label{fig:scatter_ba_ratio}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_mu.pdf}
-\caption{Same layout as in Figure \ref{fig:scatter_width}. 
-This time for $\mu$ the absolute value of the dot product between the
-vector connecting the main galaxies and the vector perpendicular to
-the satellite plane.
-In this case both the MW and M31 show a strong alignment.
-Apparently the LG is outside the expectations from
-simulations and atypical compared to the spherical results. 
-However, this is not the case. The $\mu$ distributions in the
-randomization and the simulation are consistent with a uniform
-distribution.
-Under such circumstances $\mu\approx 1$ is as likely as
-any other value.
-\label{fig:scatter_mu}}
 \end{figure*}
@@
 or deviated from the expectations for an spherical dsitribution.
-
-\subsection{Plane alignment}
-
-Figure \ref{fig:scatter_mu} summarizes the Illustris results for the
-alignments between the vector normal to the plane and the vector
-connecting the two dominant galaxies.
-The corresponding results for the ELVIS data are shown in Figure
-\ref{fig:scatter_elvis}.
-
-The first striking impression from the left panel in Figure
-\ref{fig:scatter_mu} is that the observations are cornered in
-a region of strong alignment, $\mu\approx 1$, for both galaxies. 
-In other words, the planes are almost perpendicular to the direction
-connecting the two galaxies. 
-The result for the spherical randomization corresponds to a uniform
-distribution $0\leq \mu\leq 1$ as shown in the same panel.
-
-The middle panel tells a similar story for the results from
-Illustris. That is, there isn't a prefered alignment direction from
-the simulation. This also holds for ELVIS data.
-We quantify this visual impresion by performing a K-S test where the
-null hypothesis corresponds to an uniform distribution. 
-The results from the K-S test do not allow us to discard the null
-hypotesis.
-
-This information allows us to properly understand the results on the
-right panel in Figure \ref{fig:scatter_mu}.
-That panel shows the results for the normalized values to the mean and
-standard deviation computed from spherically randomized
-ditributions.
-In this case the LG $\mu$ value has the same probability as any other value
-(because it is consistent with an uniform distribution) and the apparent
-large distance from the Illustris data must not be interpreted as an
-the LG having an atypical alignment.
-
-We defer to the Section \ref{sec:discussion} our discussion on how
-this can be reconciled with other studies that show preferential
-infall satellite directions in LCDM simulations.
 

### 2017-11-04 paper/paper.tex
without mu data and plots

@@
 \centering
-\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_width.pdf}
-\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
-\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_mu.pdf}
-\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_width.pdf}
-\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
-\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_mu.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
 \caption{ELVIs results for the quantities presented for the Illustris-1
   simulation in Figures  \ref{fig:scatter_width},
-  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio} and
-  \ref{fig:scatter_mu}.
+  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
 Upper row corresponds to the raw values from observations and

### 2017-11-04 paper/paper.tex
paper

@@
 %=========================================================================
-\title[LG satellites asphericity ]{We are not the 99 percent: quantifying
-  asphericity in the Local Group satellites' distributions}
+\title[LG satellites distribution asphericity]{We are not the 99 percent: quantifying
+  asphericity in the distribution of Local Group satellites}
 \author[J.E. Forero-Romero \& V. Arias]
@@
 
-\section{Discussion}
-
 \subsection{Outlier characterization with a Multivariate Gaussian Model}
@@
 Prospects for observational measurement: DESI.
+
+\section{Conclusions}
+
+In this paper we develop and demostrate a method to quantify the
+asphericity of the satellite distribution in the Local Group.
+The method uses as a basic condition the spherical randomization of
+satellite positions (observed or simulated). 
+The scalars describing the satellite distribution in each galaxy are
+then normalized to the mean value and standard deviation in the
+randomized samples.
+
+In observations we limit our analysis to the 11 brightest satellites 
+in the Milky Way and Andromeda. 
+For numerical data we use the Illustris-1 and the ELVIS simulations.
+
+We find that the deviation from aesphericity in the LG is only
+expected in $1\pm3$ pairs out of a sample of $2000$ isolated pairs. 
+This places the LG as a $3\sigma$ outlier. 
+The weight to explain this atypical result is not distributed equally
+between the MW and M31. While M31 presents a fully typical asphericity
+in the expectations from LCDM, the MW shows aspherical deviations in
+plane width and the major-to-minor axis ratio highly atypical in the
+framework of LCDM. 
+We estimate that with the M31 $XX$ out of $2000$ pairs show normalized
+characteristics larget r equal than M31, while this number drops to 
+$XX$ for the MW.
 

### 2017-11-04 paper/paper.tex
conclusions

@@
 randomized samples. 
-
 In observations we limit our analysis to the 11 brightest satellites 
@@
 $XX$ for the MW.
+
+The method we present to quantify how atypical is the LG is robust to
+the numerical simulations used to define the LCDM expectations. 
+Quantifying the degree of asphericity highlights the atypicality of
+the Milky Way stressing the stark difference with M31 and its more
+typical nature. 
+This atypical distribution also adds up to the presence of two bright
+satellite galaxies, which is also uncommon both in simulations and
+observations.
+
+The extension of the framework we present in this paper to describe
+outliers found as a second order deviation (i.e. fiding a \emph{subset} of
+satellites in M31 that are in a plane or \emph{adding} velocity
+information) could also be possible along the line of work presented
+by, that avoid finding in observations the exact observed distribution
+and instead focuse in defining atypicallity.
+
+The quantitative study we present allows us to estimate  the volumes 
+that cosmological simulations have to probe in order to study similar
+LG configurations.
+Such atypical satellite distribution should be seen as an opportunity
+to constraint in high detail the initial conditions and environment
+that allowed such pattern to emerge.
 

### 2017-11-04 paper/paper.tex
abstract

@@
 \begin{abstract}
-In this paper we quantify the deviations from sphericity in the spatial distribution of the
+In this paper we quantify the asphericity in the spatial distribution of the
 brightest satellites around the Milky Way (MW) and M31, the dominant
 galaxies in the Local Group (LG).
-We use the Illustris-1 and ELVIS simulations to quantify the
-same deviations from sphericity in the Lambda Cold Dark Matter paradigm. 
+We use the Illustris-1 and ELVIS simulations to quantify asphericity
+in the Lambda Cold Dark Matter paradigm.  
+We build explicit probability distributions of
+finding an aspherical satellite distribution, allowing for an easy
+reproducibility of the results presented here and a standarized method
+to compare probability distributions derived from different
+simulations. 
 We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
@@
 the extremly planar MW satellite distribution.
+
 \end{abstract}

### 2017-11-04 paper/paper.tex
abstract

@@
 \begin{abstract}
-In this paper we quantify the asphericity in the spatial distribution of the
+Here we quantify the asphericity in the spatial distribution of the
 brightest satellites around the Milky Way (MW) and M31, the dominant

### 2017-11-07 paper/paper.tex
table caption

@@
   \end{tabular}
-  \caption{Mode Transition Times}
+  \caption{Mean values and standard deviations for the different
+    quantities describing satellite distributions: plane width, $c/a$
+    ratio and $b/a$ ratio. The first colum refers to the results from
+    observational data, the second column uses the spherically
+    randomized version of the observational data. 
+    The third column summarizes the results from the 20 pairs in
+    Illustris-1 and the last column corresponds to the 12 pairs in the
+    ELVIS project.}
 \end{table*}

### 2017-11-07 paper/paper.tex
updated definitions

@@
 We define the size of the three ellipsoidal axis as
-$a=\sqrt{\lambda_1}$, $b=\sqrt{\lambda_2}$ and $c=\sqrt{\lambda_3}$.
+$a=\lambda_1$, $b=\lambda_2$ and $c=\lambda_3$.
 We also define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
@@
 We also define the width, $w$, of the planar satellite distribution,
-$\sigma_p$ as the standard deviation of all satellite distances to the
-plane defined by the vector $\hat{n}$.
+as the standard deviation of all satellite distances to the plane
+defined by the vector $\hat{n}$.
 
@@
 \centering
-\includegraphics[width=0.32\textwidth]{scatter_random_ranked_width.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_width.pdf}
 \caption{Plane width characterization in the Local Group and the
@@
 \centering
-\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ca_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 \centering
-\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ba_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_ba_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 \newpage
+
 \appendix
@@
 
+\section{Covariance Matrices and Mean value vectors}
 Illustris

### 2017-11-10 paper/paper.tex
transition
+2 paragraphs

@@
 \label{sec:obs}
+
+We use three dimentional positions as reported by. 
+The appendix includes the tables with the values we use in our
+computations.
+For each central galaxy we use the 15 brightest satellites within a
+distance of $300$kpc to the central galaxy.
+The satellites for the MW are: 
+THe satellites for M31 are:
 
@@
 partner. 
+We compute the preferred covariance matrix and the mean distribution values
+with a jackknife technique. 
+That is, out of the the $n$ pairs we have, we perfom $n$ different
+covariance and mean value measurement using only $n-1$ pairs. 
+The reported covariance and mean values correspond to the average of
+all measurements, the corresponding standard deviation also help us to
+estimate the uncertainty on every reported coefficient.
 
-This compact description allows us to generate samples consistent with
-the simulations used in their construction.
-Finally, we use those generated samples to estimate how commoon are
-the deviations from sphericity that we measure in the observational
-data.
+This compact description allows us to generate samples of size $N$
+that are consistent by construction with their parent
+simulation. Finally, we use the generated samples to estimate how
+commoon are the deviations from sphericity that we measure in the observational
+data.  We use a single-tail test in this comparison, meaning that we
+always measure the fraction of points with values smaller than the
+treshold value.
 
@@
 
+This is all the information that is needed to compute the fraction of
+pairs that are expected to share the same asphericity as the LG.
+We start the Discussion section by describing the results of
+performing such a computation.
+
 \section{Discussion}
@@
 \end{table*}
-
-\subsection{Outlier characterization with a Multivariate Gaussian Model}
-
-Prospects for observational measurement: DESI.
 

### 2017-11-22 paper/paper.tex
new plot
abstract

@@
 galaxies in the Local Group (LG).
-We use the Illustris-1 and ELVIS simulations to quantify asphericity
-in the Lambda Cold Dark Matter paradigm.  
-We build explicit probability distributions of
-finding an aspherical satellite distribution, allowing for an easy
-reproducibility of the results presented here and a standarized method
-to compare probability distributions derived from different
-simulations. 
-We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
+We build explicit probability distributions of finding an aspherical
+satellite distribution. 
+This allows us to estimate the atipicallity of the satellite
+distributions in the LG even when the underlying simulations
+do not have enough systems that resemble the LG features.
+This is also standarized method to compare different simulations and
+is also convenient for reproducibility and comparison 
+We demonstrate the method using the Illustris-1 and ELVIS simulations.
+We find significant differences between the two simulations. 
+In the case of Illustris-1 $0.05\%$ to $0.25\%$ of the pairs with isolation
 and dynamical characteristics similar to the LG are expected to have
@@
 sphericity.
-This makes the LG a $3\sigma$ outlier, with all the weight lying on
-the extremly planar MW satellite distribution.
+In the ELVIS simulations this fractions drops dramatically to
+$0.001\%$ of the pairs.
+This makes the LG a $3\sigma$ outlier in LCDM simulations, with all
+the weight lying on the extremly planar MW satellite distribution.
 
@@
 \includegraphics[width=0.47\textwidth]{expected_numbers.pdf}
+\includegraphics[width=0.47\textwidth]{expected_numbers_flip.pdf}
 \caption{Probability distribution for the expected number of pairs

### 2017-11-26 paper/paper.tex
new results from illustrisdm

@@
 is also convenient for reproducibility and comparison 
-We demonstrate the method using the Illustris-1 and ELVIS simulations.
-We find significant differences between the two simulations. 
-In the case of Illustris-1 $0.05\%$ to $0.25\%$ of the pairs with isolation
-and dynamical characteristics similar to the LG are expected to have
-satellite distributions with the same degree of deviation from
-sphericity.
-In the ELVIS simulations this fractions drops dramatically to
-$0.001\%$ of the pairs.
-This makes the LG a $3\sigma$ outlier in LCDM simulations, with all
-the weight lying on the extremly planar MW satellite distribution.
+We demonstrate the method using three different simulations:
+Illustris-1,  Illustris-1-DarkMatter and ELVIS simulations.
+Although there are significant differences between the three
+simulations, we find that at most of $0.20\%$ the pairs are expected
+to have satellite distributions with the same degree of deviation from
+sphericity as the Local Group.
+The three simulations show that the satellite
+distribution in M31 is common while the very planar MW satellite
+distribution is hard to find; we expect that between $19\%$ to $24\%$
+of the pairs have halo similar to M31, while only $0.80\%$ are similar
+to the MW.
 
@@
 \centering
-\includegraphics[width=0.47\textwidth]{expected_numbers.pdf}
-\includegraphics[width=0.47\textwidth]{expected_numbers_flip.pdf}
+\includegraphics[width=0.47\textwidth]{expected_numbers_n_M31.pdf}
+\includegraphics[width=0.47\textwidth]{expected_numbers_n_MW.pdf}
 \caption{Probability distribution for the expected number of pairs

### 2017-11-26 paper/paper.tex
results form illustrisdm in the paper

@@
 \includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
 \caption{Plane width characterization in the Local Group and the
@@
 \includegraphics[width=0.30\textwidth]{scatter_random_ranked_ca_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_ca_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ca_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ca_ratio.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 \includegraphics[width=0.30\textwidth]{scatter_random_ranked_ba_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_ba_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ba_ratio.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ba_ratio.pdf}
 \caption{Same layout as in Figure \ref{fig:scatter_width}. 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_M31.pdf}
-\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustrisdm_M31.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustrisdm_MW.pdf}
 \caption{Correlations between the multivariate gaussian model built on
@@
 \includegraphics[width=0.47\textwidth]{expected_numbers_n_MW.pdf}
-\caption{Probability distribution for the expected number of pairs
-  showing the same degree of atipicality as the Local Group if drawn
-  from a sample of 2000 isolated pairs. 
-  The distributions correspond to results derived from Illustris-1
+\caption{Probability distribution for the expected number of M31 and
+  MW halos  showing the same degree of atipicality as the Local Group if drawn
+  from a sample of 10000 isolated pairs. 
+  The distributions correspond to results derived from Illustris-DM, Illustris,
   and ELVIS data.
-  On average between $0.05\%$ and $0.25\%$ of the isolated pairs should present
-  satellite distributions as atypical as the Local Group.
+  In the most optimistic case (Illustris-DM), $1\%$ of the pairs have
+  two halos with properties similar to the LG. In the case of
+  Illustris this percentage drops to $0.1\%$ and $0.01\%$ for ELVIS.
 \label{fig:expected_number}}

### 2017-12-03 paper/paper.tex
covariance data illustris
illustrisdm cov
elvis cov
updated abstract

@@
 \begin{abstract}
-Here we quantify the asphericity in the spatial distribution of the
+We quantify the asphericity in the spatial distribution of the
 brightest satellites around the Milky Way (MW) and M31, the dominant
 galaxies in the Local Group (LG).
-We build explicit probability distributions of finding an aspherical
-satellite distribution. 
-This allows us to estimate the atipicallity of the satellite
-distributions in the LG even when the underlying simulations
-do not have enough systems that resemble the LG features.
-This is also standarized method to compare different simulations and
-is also convenient for reproducibility and comparison 
+We use this approach on simulations to build an explicit probability
+distribution of finding an aspherical  satellite  distribution around
+galaxies similar to the Milky Way and M31. 
+This probability distribution allows us to estimate the atipicallity
+of the satellite distributions in the LG even when the underlying
+simulations do not have enough systems that resemble the LG satellite
+anisotropy. 
+This methodology is straightforward to implement, allowing
+for an straighforward quantification of aspherical satellite
+distributions both in simulations and observations.
 We demonstrate the method using three different simulations:
 Illustris-1,  Illustris-1-DarkMatter and ELVIS simulations. 
-Although there are significant differences between the three
-simulations, we find that at most of $0.20\%$ the pairs are expected
-to have satellite distributions with the same degree of deviation from
-sphericity as the Local Group.
-The three simulations show that the satellite
-distribution in M31 is common while the very planar MW satellite
-distribution is hard to find; we expect that between $19\%$ to $24\%$
-of the pairs have halo similar to M31, while only $0.80\%$ are similar
-to the MW.
-
+We find as a common trend that at most of $0.20\%$ the pairs are
+expected  to have satellite distributions with the same degree of
+deviation from sphericity as the Local Group.
+The three simulations show that the satellite distribution in M31 is
+common while the very planar MW satellite distribution is hard to
+find.
+We show that in these simulations between $19\%$ to $24\%$ of the pairs
+have a halo with a satellite distribution similar to M31, while only
+$0.80\%$, at most, have a satellite distribution as planar as the MW.
+This characteristic places the LG as at the level of a 3-$\sigma$
+outlier in context provided by LCDM simulations.
 \end{abstract}
@@
 \section{Covariance Matrices and Mean value vectors}
-Illustris
+Illustris M31
+
+Covariance
 \begin{verbatim}
-[[ 0.8344  0.7849  0.4186 -0.1155  0.0340 -0.1614]
- [ 0.7849  1.1698 -0.1568 -0.0793  0.0362 -0.1213]
- [ 0.4186 -0.1568  0.9606 -0.1151 -0.0150 -0.1098]
- [-0.1155 -0.0793 -0.1151  0.7873  0.6339  0.4006]
- [ 0.0340  0.0362 -0.0150  0.6339  0.6932  0.0652]
- [-0.1614 -0.1213 -0.1098  0.4006  0.0652  0.6100]]
+[[ 0.83+/-0.03  0.78+/-0.04  0.41+/-0.04]
+ [ 0.78+/-0.04  1.16+/-0.05 -0.15+/-0.05]
+ [ 0.41+/-0.04 -0.15+/-0.05  0.96+/-0.04]]
+\end{verbatim}
+
+Mean
+
+\begin{verbatim}
+[-0.18+/-0.04 -0.41+/-0.05  -0.20+/-0.05]
+\end{verbatim}
+
+Illustris MW
+\begin{verbatim}
+[[ 0.78+/-0.06  0.63+/-0.07  0.40+/-0.03]
+ [ 0.63+/-0.07  0.69+/-0.08   0.06+/-0.02]
+ [ 0.40+/-0.03  0.06+/-0.02   0.61+/-0.04]]
+\end{verbatim}
+
+Mean
+\begin{verbatim}
+[-0.17+/-0.04 -0.40+/-0.04 -0.23+/-0.04]
+\end{verbatim}
+
+IllustrisDM M31
+
+Covariance
+\begin{verbatim}
+[[ 1.50+/-0.08  1.27+/-0.08  0.64+/-0.04]
+ [ 1.27+/-0.08  1.31+/-0.08  0.28+/-0.04]
+ [ 0.64+/-0.04  0.28+/-0.04  0.70+/-0.04]]
+\end{verbatim}
+
+Mean
+\begin{verbatim}
+[-0.37+/-0.05 -0.55+/-0.05  -0.13+/-0.03]
+\end{verbatim}
+
+IllustrisDM M31
+
+Covariance
+\begin{verbatim}
+[[ 1.03+/-0.05  0.94+/-0.05  0.36+/-0.03 ]
+ [ 0.94+/-0.05  1.24+/-0.07 -0.18+/-0.04]
+ [ 0.36+/-0.03  -0.18+/-0.04  0.86+/0.03]]
+\end{verbatim}
+
+Mean
+\begin{verbatim}
+[-0.45+/-0.04 -0.61+/-0.05 -0.31+/-0.04]
+\end{verbatim}
+
+ELVIS M31
+
+Covariance
+\begin{verbatim}
+[[ 1.60+/-0.19  1.22+/-0.14  0.70+/-0.09]
+ [ 1.22+/-0.14  1.08+/-0.10  0.35+/-0.05]
+ [ 0.70+/-0.09  0.35+/-0.05  0.63+/-0.10]]
+\end{verbatim}
+
+Mean
+\begin{verbatim}
+[-0.18+/-0.08 -0.28+/-0.07 -0.22+/-0.05]
+\end{verbatim}
+
+ELVIS MW
+Covariance
+\begin{verbatim}
+[[ 0.45+/-0.04    0.61+/-0.09 -0.11+/-0.09 ]
+ [ 0.61+/-0.09  1.21+/-0.17 -0.63+/-0.09]
+ [-0.11+/-0.05  -0.63+/-0.09  0.64+/-0.06]]
 \end{verbatim}
@@
 \begin{verbatim}
-[-0.1852 -0.4152    -0.2002 -0.1786 -0.4072 -0.2394]
+[-0.32+/-0.04 -0.74+/-0.07 -0.08+/-0.05]
 \end{verbatim}
 
-ELVIS
-\begin{verbatim}
-[[ 1.6051  1.2207  0.7062  0.0833  0.1063  0.0812]
- [ 1.2207  1.0872  0.3584  0.0298  0.1085 -0.0324]
- [ 0.7062  0.3584  0.6363  0.0904  0.0194  0.1601]
- [ 0.0833  0.0298  0.0904  0.4534  0.6138 -0.1159]
- [ 0.1063  0.1085  0.0194  0.6138  1.2120 -0.6372]
- [ 0.0812 -0.0324  0.1601 -0.1159 -0.6372  0.6475]]
-\end{verbatim}
-
-\begin{verbatim}
-[-0.1803 -0.2829 -0.2205 -0.3292 -0.7484 -0.0863]
-\end{verbatim}
 \end{document}

### 2017-12-03 paper/paper.tex
abstract

@@
 galaxies in the Local Group (LG).
-We use this approach on simulations to build an explicit probability
-distribution of finding an aspherical  satellite  distribution around
-galaxies similar to the Milky Way and M31. 
-This probability distribution allows us to estimate the atipicallity
+We use the same approach on simulations to build an explicit probability
+distribution for this asphericity around galaxies similar to the MW and M31.   
+This allows us to estimate the atipicallity
 of the satellite distributions in the LG even when the underlying
-simulations do not have enough systems that resemble the LG satellite
-anisotropy. 
-This methodology is straightforward to implement, allowing
-for an straighforward quantification of aspherical satellite
-distributions both in simulations and observations.
+simulations do not have enough systems that fully resemble the LG.
 We demonstrate the method using three different simulations:
-Illustris-1,  Illustris-1-DarkMatter and ELVIS simulations. 
-We find as a common trend that at most of $0.20\%$ the pairs are
+Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
+We find as a common trend that at most of $0.2\%$ the pairs are
 expected  to have satellite distributions with the same degree of
-deviation from sphericity as the Local Group.
-The three simulations show that the satellite distribution in M31 is
-common while the very planar MW satellite distribution is hard to
-find.
-We show that in these simulations between $19\%$ to $24\%$ of the pairs
-have a halo with a satellite distribution similar to M31, while only
-$0.80\%$, at most, have a satellite distribution as planar as the MW.
-This characteristic places the LG as at the level of a 3-$\sigma$
-outlier in context provided by LCDM simulations.
+deviation from sphericity as the Local Group; between $19\%$ to $24\%$
+of the pairs have a halo with a satellite distribution as aspherical
+as in M31, while only $0.80\%$, at most, have a satellite distribution
+as planar as in the MW. These results place the LG at the level of a
+3-$\sigma$ outlier in context provided by LCDM simulations. 
 \end{abstract}

### 2017-12-13 paper/paper.tex
new plots

@@
 Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
-We find as a common trend that at most of $0.2\%$ the pairs are
+We find as a common trends that at most of $1\%$ the pairs are
 expected  to have satellite distributions with the same degree of
-deviation from sphericity as the Local Group; between $19\%$ to $24\%$
+deviation from sphericity as the Local Group; between $38\%$ to $59\%$
 of the pairs have a halo with a satellite distribution as aspherical
-as in M31, while only $0.80\%$, at most, have a satellite distribution
-as planar as in the MW. These results place the LG at the level of a
-3-$\sigma$ outlier in context provided by LCDM simulations. 
+as  in M31; and at most $2\%$ have a satellite distribution
+as planar as in the MW. 
+These results place the LG close to the level of a 3$\sigma$ outlier
+in context provided by LCDM simulations.  
 \end{abstract}

### 2018-01-22 paper/paper.tex
edits in abstract

@@
 galaxies in the Local Group (LG).
-We use the same approach on simulations to build an explicit probability
-distribution for this asphericity around galaxies similar to the MW and M31.   
+We use simulations to build an explicit probability distribution for the
+asphericity around galaxies similar to the LG in the Lambda Cold Dark
+Matter paradigm.
 This allows us to estimate the atipicallity
@@
 Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
-We find as a common trends that at most of $1\%$ the pairs are
-expected  to have satellite distributions with the same degree of
-deviation from sphericity as the Local Group; between $38\%$ to $59\%$
-of the pairs have a halo with a satellite distribution as aspherical
-as  in M31; and at most $2\%$ have a satellite distribution
-as planar as in the MW. 
-These results place the LG close to the level of a 3$\sigma$ outlier
+We find as a common trends in thse simulations that: i) at most of
+$1\%$ the pairs are expected  to have satellite distributions with the
+same degree of deviation from sphericity as the Local Group; ii) between
+$38\%$ to $59\%$ of the pairs have a halo with a satellite
+distribution as aspherical as  in M31; and iii) at most $2\%$ have a
+satellite distribution as planar as in the MW. 
+These results place the LG close to the level of a 3-$\sigma$ outlier
 in context provided by LCDM simulations.  

### 2018-01-22 paper/paper.tex
editing conclusions

@@
 asphericity of the satellite distribution in the Local Group.
-The method uses as a basic condition the spherical randomization of
-satellite positions (observed or simulated). 
-The scalars describing the satellite distribution in each galaxy are
-then normalized to the mean value and standard deviation in the
-randomized samples. 
+The method uses as a reference point the spherically randomized data
+of the system under study.
+We first measure the width and axis ratios for the satellite
+distribution of interest. Then, we measure the same quantities for the spherical
+randomizations, to finally renormalize the initial results to the mean
+value and standard deviation from the randomized samples.
+
+We do not look for planes  or coherent kinematical structures in the
+interest of keeping our study simple and robust.
 In observations we limit our analysis to the 11 brightest satellites 
 in the Milky Way and Andromeda. 
-For numerical data we use the Illustris-1 and the ELVIS simulations.
+For numerical data we use the Illustris-1, Illustris-1-DM and the
+ELVIS simulations.
 

### 2018-01-24 paper/paper.tex
edit abstract

@@
 asphericity around galaxies similar to the LG in the Lambda Cold Dark
-Matter paradigm.
+Matter (LCDM) paradigm.
 This allows us to estimate the atipicallity
@@
 Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
-We find as a common trends in thse simulations that: i) at most of
+We find three common trends in these simulations. First, at most of
 $1\%$ the pairs are expected to have satellite distributions with the
-same degree of deviation from sphericity as the Local Group; ii) between
+same degree of deviation from sphericity as the Local Group; second, between
 $38\%$ to $59\%$ of the pairs have a halo with a satellite
-distribution as aspherical as  in M31; and iii) at most $2\%$ have a
-satellite distribution as planar as in the MW. 
+distribution as aspherical as  in M31; and third, at most $2\%$ of the
+pairs have a satellite distribution as planar as in the MW. 
+The M31 galaxy turns out to have a rather typical distribution 
+in the LCDM context, for its brightest satellites, while the MW is
+atypical in this respect. 
 These results place the LG close to the level of a 3-$\sigma$ outlier
-in context provided by LCDM simulations.
+in the LCDM paradigm.
+We summarize our results in terms of mean values and covariance
+matrices. This approach will facilitate the direct comparison of the
+results from different numerical setups and choices to select LG pairs
+in simulations. 
 \end{abstract}
 
-\begin{keywords}Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
---- Dark Matter --- Methods: numerical 
+\begin{keywords}Galaxies: halos --- Galaxies: statistics --- Dark
+  Matter --- Methods: numerical  
 \end{keywords}

### 2018-01-24 paper/paper.tex
edit

@@
 asphericity of the satellite distribution in the Local Group.
+We build up on the suggestions made in \cite{XX}.
+We do not look for planes  or coherent kinematical structures in the
+interest of keeping the method straightforward and robust.
+
 The method uses as a reference point the spherically randomized data
@@
 We first measure the width and axis ratios for the satellite
-distribution of interest. Then, we measure the same quantities for the spherical
-randomizations, to finally renormalize the initial results to the mean
-value and standard deviation from the randomized samples.
+distribution of interest. 
+Then, we measure the same quantities for spherically
+randomized data. 
+Finally, renormalize the initial results to the mean value and
+standard deviation from the randomized samples.
 
-We do not look for planes  or coherent kinematical structures in the
-interest of keeping our study simple and robust.
-In observations we limit our analysis to the 11 brightest satellites 
-in the Milky Way and Andromeda. 
-For numerical data we use the Illustris-1, Illustris-1-DM and the
-ELVIS simulations.
+The normalized quantities for different systems are well reproduced by
+a multivariate gaussian distribution. 
+We fit the parameters of this gaussian to the results from 
+LG samples coming from three different simulations: ELVIS, Illustris1
+and Illustris-DarkMatter.
+We finally compare the observational results against the distributions
+derived from the simulations.
 
-We find that the deviation from aesphericity in the LG is only
-expected in $1\pm3$ pairs out of a sample of $2000$ isolated pairs. 
+We find that in the best case (Illustris1-DarkMatter) the deviation from aesphericity in the observed LG is only
+expected in $3\pm2$ pairs out of a sample of $10^4$ isolated pairs. 
 This places the LG as a $3\sigma$ outlier. 

### 2018-01-24 paper/paper.tex
edit

@@
 Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
-We find three common trends in these simulations. First, at most of
+Detailed results differ greatly among the simulations, suggesting a
+strong influence of resolution, modelled physics and criteria to select
+LG pairs.
+However, there are three common trends in these simulations. First, at most of
 $1\%$ the pairs are expected to have satellite distributions with the
-same degree of deviation from sphericity as the Local Group; second, between
+same asphericity as the Local Group; second, between
 $38\%$ to $59\%$ of the pairs have a halo with a satellite
@@
 pairs have a satellite distribution as planar as in the MW. 
-The M31 galaxy turns out to have a rather typical distribution 
-in the LCDM context, for its brightest satellites, while the MW is
-atypical in this respect. 
+The brightest satellites in M31 galaxy turn out to have a rather typical distribution 
+in the LCDM context, while the MW is atypical in this respect. 
 These results place the LG close to the level of a 3-$\sigma$ outlier
@@
 We summarize our results in terms of mean values and covariance
-matrices. This approach will facilitate the direct comparison of the
-results from different numerical setups and choices to select LG pairs
-in simulations. 
+matrices. 
+This approach facilitates the comparison between asphericity results
+from different numerical setups and choices to select LG pairs in
+simulations.  
 \end{abstract}
@@
 
+The spatial distribution of satellite galaxies around our Milky Way and the
+M31 galaxy provides a stringent test for structure formation theories
+in a explicit cosmological context. 
 The presence of a Vast Polar Structure of satellites around the Milky
 Way has been stablished in the last decade.
-This structure can be easily described by global quantities of the
-brightest
+This structure is present in the $11$ brightest "classical" dwarf
+galaxies and has been confirmed as fainter satellites have been
+detected. 
+In the case of M31,  observational studies have found a planar satellite
+distribution in a subset of $15$ satellites out of an homogeneous
+sample of $27$ satellites. 
+Using only the $11$ brightest satellites (as a comparison with the MW)
+there does not seem to be any structure.
 
 The question whether this configuration is atypical in the observable
-universe cannot be proberly addressed given the current limits in
+Universe cannot be proberly addressed given the current limits in
 observations. 
@@
 
-The closest system that could help us in providing a baseline for
-comparison is the Andromeda galaxy, M31. 
-Its close enough that an observational study of its satellite
-population is possible, with the great advantage of having a
-perpective from a distance and not from within, as is the case for our
-Galaxy. 
-These studies also found a planar satellite
-distributions.
-This time not in the whole distribution, but in a subset of $15$
-satellites out of an homogeneous sample of $27$ satellites.
+However, the tipicallity of satellite distributions can be addressed
+in simulations.
+Most of the studies have been performed in the currently preferred
+paradigm, which is based on a Cold Dark Matter cosmology in a expanding
+Universe described by General Relativity including a Cosmological
+Constant, the so-called Lambda Cold Dark Matter (LCDM).
+The broad consensus is that these highly structured satellite distributions
+are hard to find in simulations.  
+There are still disagreements on the precise degree of atypicallity
+and the conditions required to simulate
 
-This has prompted a discussion on whether this satellite distributions
-are easily found in structure formation simulations done in the
-current dominant paradigm for galaxy formation.
-This paradigm, based on a Cold Dark Matter cosmology in
-a expanding universe described by General Relativity with a
-Cosmological Constant, is the so-called Lambda Cold Dark Matter
-(LCDM).
-
-The consensus is that these structures are hard to find in
-simulations. 
 Some studies have focused on the study of individual dark matter halos

### 2018-01-24 paper/paper.tex
new data in table

@@
 There are still disagreements on the precise degree of atypicallity
-and the conditions required to simulate
+and the conditions required to simulate satellite distributions closer
 
@@
   \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|c|c|}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
     \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
     % \hline
     % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-9}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
+    \cline{2-5}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
     %\hhline{~--}
     \hline
-    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
-    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
-    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
+    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
+    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
+    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
   \end{tabular}
   \caption{Mean values and standard deviations for the different
-    quantities describing satellite distributions: plane width, $c/a$
-    ratio and $b/a$ ratio. The first colum refers to the results from
+    quantities describing satellite distribution: plane width, $c/a$
+    ratio and $b/a$ ratio. 
+    The first colum refers to the results from
     observational data, the second column uses the spherically
@@
     Illustris-1 and the last column corresponds to the 12 pairs in the
+    ELVIS project.}
+\end{table*}
+
+\begin{table*}
+  \centering
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
+    \hline
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-DM}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
+    % \hline
+    % \textbf{Inactive Modes} & \textbf{Description}\\
+    \cline{2-7}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
+    %\hhline{~--}
+    \hline
+    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
+    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
+    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
+  \end{tabular}
+  \caption{Mean values and standard deviations for the different
+    quantities describing satellite distributions: plane width, $c/a$
+    ratio and $b/a$ ratio. 
+    The first column summarize the results from the 24 pairs in
+    Illustris-1-DM, the second column from the 20 pairs in
+    Illustris-1 and the third column from the 12 pairs in the
     ELVIS project.}

### 2018-01-24 paper/paper.tex
results

@@
 
+\begin{table*}
+  \centering
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
+    \hline
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
+    % \hline
+    % \textbf{Inactive Modes} & \textbf{Description}\\
+    \cline{2-5}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
+    %\hhline{~--}
+    \hline
+    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
+    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
+    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
+  \end{tabular}
+  \caption{Mean values and standard deviations for the different
+    quantities describing satellite distribution: plane width, $c/a$
+    ratio and $b/a$ ratio. 
+    The first colum refers to the results from
+    observational data, the second column uses the spherically
+    randomized version of the observational data. \label{table:observations}}
+\end{table*}
+
+\begin{table*}
+  \centering
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
+    \hline
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-DM}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
+    % \hline
+    % \textbf{Inactive Modes} & \textbf{Description}\\
+    \cline{2-7}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
+    %\hhline{~--}
+    \hline
+    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
+    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
+    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
+  \end{tabular}
+  \caption{Mean values and standard deviations for the different
+    quantities describing satellite distributions: plane width, $c/a$
+    ratio and $b/a$ ratio. 
+    The first column summarize the results from the 24 pairs in
+    Illustris-1-DM, the second column from the 20 pairs in
+    Illustris-1 and the third column from the 12 pairs in the
+    ELVIS project.\label{table:simulations}}
+\end{table*}
+
 % referencia posiciones satellites
@@
 
+Table \ref{table:observations} and Table \ref{table:simulations}
+summarize the mean values and uncertainties for the plane width, $c/a$
+ratio and $b/a$ ratio in the observations and simulations, respectively. 
+The uncertainty in the observations is computed over the results with
+different number of satellites, while in the observations it
+corresponds to the standard deviation over different halos. 
+In the following subsections we describe in detail the results for the
+distributions.
+
 \subsection{Plane Width}
@@
 \section{Discussion}
-
-\begin{table*}
-  \centering
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
-    \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-5}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
-    %\hhline{~--}
-    \hline
-    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
-    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
-    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
-  \end{tabular}
-  \caption{Mean values and standard deviations for the different
-    quantities describing satellite distribution: plane width, $c/a$
-    ratio and $b/a$ ratio. 
-    The first colum refers to the results from
-    observational data, the second column uses the spherically
-    randomized version of the observational data. 
-    The third column summarizes the results from the 20 pairs in
-    Illustris-1 and the last column corresponds to the 12 pairs in the
-    ELVIS project.}
-\end{table*}
-
-\begin{table*}
-  \centering
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
-    \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-DM}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-7}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
-    %\hhline{~--}
-    \hline
-    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
-    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
-    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
-  \end{tabular}
-  \caption{Mean values and standard deviations for the different
-    quantities describing satellite distributions: plane width, $c/a$
-    ratio and $b/a$ ratio. 
-    The first column summarize the results from the 24 pairs in
-    Illustris-1-DM, the second column from the 20 pairs in
-    Illustris-1 and the third column from the 12 pairs in the
-    ELVIS project.}
-\end{table*}
 

### 2018-01-24 paper/paper.tex
edit

@@
 sample of $27$ satellites. 
-Using only the $11$ brightest satellites (as a comparison with the MW)
-there does not seem to be any structure.
+However, taking into account the $11$ brightest satellites (as a
+comparison with the MW) there does not seem to be any planar structure.
 
-The question whether this configuration is atypical in the observable
-Universe cannot be proberly addressed given the current limits in
-observations. 
+The question whether this kind of planar configurations are atypical
+in the observable Universe cannot be properly addressed given the
+current limits in observations. 
 So far it has only been possible to contraint that $5\%$ of the
@@
 
+\begin{table*}
+  \centering
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
+    \hline
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
+    % \hline
+    % \textbf{Inactive Modes} & \textbf{Description}\\
+    \cline{2-5}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
+    %\hhline{~--}
+    \hline
+    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
+    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
+    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
+  \end{tabular}
+  \caption{Results from observations. Mean values and standard deviations for the different
+    quantities describing satellite distribution: plane width, $c/a$
+    ratio and $b/a$ ratio. 
+    The first colum refers to the results from
+    observational data, the second column uses the spherically
+    randomized version of the observational data. \label{table:observations}}
+\end{table*}
+
+\begin{table*}
+  \centering
+  \renewcommand{\arraystretch}{1.2}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
+    \hline
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-DM}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
+    % \hline
+    % \textbf{Inactive Modes} & \textbf{Description}\\
+    \cline{2-7}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
+    %\hhline{~--}
+    \hline
+    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
+    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
+    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
+  \end{tabular}
+  \caption{Results from simulations. Mean values and standard deviations for the different
+    quantities describing satellite distributions: plane width, $c/a$
+    ratio and $b/a$ ratio. 
+    The first column summarize the results from the 24 pairs in
+    Illustris-1-DM, the second column from the 20 pairs in
+    Illustris-1 and the third column from the 12 pairs in the
+    ELVIS project.\label{table:simulations}}
+\end{table*}
+
 \subsection{Describing Samples with the Inertia Tensor}
@@
 treshold value.
-
-\begin{table*}
-  \centering
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
-    \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-5}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
-    %\hhline{~--}
-    \hline
-    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
-    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
-    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
-  \end{tabular}
-  \caption{Mean values and standard deviations for the different
-    quantities describing satellite distribution: plane width, $c/a$
-    ratio and $b/a$ ratio. 
-    The first colum refers to the results from
-    observational data, the second column uses the spherically
-    randomized version of the observational data. \label{table:observations}}
-\end{table*}
-
-\begin{table*}
-  \centering
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
-    \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-DM}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-7}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
-    %\hhline{~--}
-    \hline
-    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
-    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
-    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
-  \end{tabular}
-  \caption{Mean values and standard deviations for the different
-    quantities describing satellite distributions: plane width, $c/a$
-    ratio and $b/a$ ratio. 
-    The first column summarize the results from the 24 pairs in
-    Illustris-1-DM, the second column from the 20 pairs in
-    Illustris-1 and the third column from the 12 pairs in the
-    ELVIS project.\label{table:simulations}}
-\end{table*}
 

### 2018-01-24 paper/paper.tex
edit

@@
 We demonstrate the method using three different simulations:
-Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
+Illustris-1,  Illustris-1-Dark and ELVIS. 
 Detailed results differ greatly among the simulations, suggesting a
@@
 
-We extract halo and galaxy information from the Illustris-1 simulation
-which has the highest resolution in the current release of the
+We extract halo and galaxy information from the Illustris-1 and
+Illustris-1-Dark simulations, the former simulation includes
+hydrodynamics and star formation prescriptions while the latter only
+includes dark matter physics.
+These simulations have the highest resolution in the current release of the
 Illustris Project.
 Illustris-1 has $1820^3$ dark matter particles and $1820^3$ initial gas
-volumen elements. 
+volumen elements, while Illustris-1-Dark has $1820^3$ dark matter particles.
 This corresponds to a dark matter particle mass of
 $6.3\times 10^6$\Msun\ and a minimum mass for the baryonic volume
-element of $8.0\times 10^7$\Msun. 
+element of $8.0\times 10^7$\Msun for Illustris-1 and a dark matter
+particle mass of $7.6\times 10^6$\Msun.
 The corresponding spatial resolution is $1.4$ kpc for the dark matter
@@
     \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-DM}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-Dark}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
     % \hline
@@
     The first column summarize the results from the 24 pairs in
-    Illustris-1-DM, the second column from the 20 pairs in
+    Illustris-1-Dark, the second column from the 20 pairs in
     Illustris-1 and the third column from the 12 pairs in the

### 2018-01-24 paper/paper.tex
edit

@@
 element of $8.0\times 10^7$\Msun for Illustris-1 and a dark matter
-particle mass of $7.6\times 10^6$\Msun.
-The corresponding spatial resolution is $1.4$ kpc for the dark matter
-gravitational softening and $0.7$ kpc for the typical size of the
-smallest gas cell size.
+particle mass of $7.6\times 10^6$\Msun for Illustris-1-Dark.
+In both simulations the dark matter gravitational softening is $1.4$
+kpc.
 
-We buid a sample of Isolated Pairs that resemble the conditions
-in the LG.
-To construct this sample we select first all galaxies with  an stellar mass in the range $1\times10^{10}\Msun
-<M_{\star}<1.5 \times 10^{11} \Msun$.
-Then we consider the following criteria for all galaxies in that set.
+We buid a sample of pairs that resemble the conditions in the LG.
+To construct this sample we select from Illustris-1 all galaxies with an stellar
+mass in the range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11}
+\Msun$.
+Then we select the pairs with the following conditions.
 
@@
 mass.
-We end up with a total of 20 pairs that fulfill these criteria,
+We end up with a total of 20 pairs in Illustris-1.
+In Illustris-1-DM we use the center of mass position of the 27 pairs
+in Illustris-1 to find the matching halo pairs.
+After discarding the pairs with less than 15 detected subhalos in one
+of the halos we end up with a toal of 24 pairs. 
+This corresponds to a pair number density of $\sim 2 \times10^{-5}$
+pairs Mpc$^{-3}$ 
 Appendix A shows the physical  properties (stellar masses, maximum
-circular velocities, radial velocities and separation) in those pairs. 
-This corresponds to a pair number density of $2 \times10^{-5}$
-pairs Mpc$^{-3}$
+circular velocities, radial velocities and separation) in those
+pairs.
 
@@
 galaxies are barely resolved in stellar mass at magnitudes of
-$M_V=9$. We prefer using the dark matter information as the smallest
-sub-halos are sampled with at least $35$ particles. 
-We chose the satellite samples by ranking the subhalos in decreasing
-order of its maximum circular velocity and select the first $N_p$
-halos in the list. 
+$M_V=-9$, close to the limit of the 11 ``classical'' MW satellites.
+We use instead the dark matter information as the smallest sub-halos
+we care about are sampled with at least $40$ particles.
+
+Both in Illustris-1 and Illustris-1-Dm we chose the satellite samples
+by ranking the subhalos in decreasing order of its current maximum
+circular velocity and select the first $N_p$ halos in the list.  
 The results presented here correspond to $11\leq N_p\leq 15$.
@@
 
-For a detailed description of the ELVIS project and data we refer the
-reader to. 
+We use data from the public release of the Exploring the Local
+Universe In Simulations (ELVIS) project.
+For a detailed description of that project and its data we refer the
+reader to \cite{XX}. 
 Here we summarize the elements relevant to our discussion.
-The data we use from the ELVIS project comes from the resimulation of
-dark matter halo pairs selected in dark matter only cosmological simulations.
+
+ELVIS data comes from resimulations of dark matter halo pairs selected
+in dark matter only cosmological simulations. 
 The parent cosmological boxes have a cosmology consistent with the
 Wilkinson Microwave Anisotropy Probe 7 results.
-They used the results from 50 simulation boxes of side lenght $70.4$
-Mpc to select pairs with kinematic characteristics similar to the LG.
+
+The ELVIS project used the results from $50$ simulation boxes of side
+lenght $70.4$ Mpc to select pairs with kinematic characteristics
+similar to the LG. 
 These selection criteria included the following
@@
 
-This corresponds to a pair number density of $8 \times10^{-6}$ pairs
-Mpc$^{-3}$, this is a factor $2.4$ lower than the pair number density
-we find in Illustris-1.
+This corresponds to a pair number density of $\sim 8 \times10^{-6}$ pairs
+Mpc$^{-3}$, this is a factor $\sim 2.5$ lower than the pair number density
+we find in the Illustris data.
 There were a total of 146 pairs that met those criteria, but only $12$
@@
 tangential velocity less than $75$ \kms. 
-In this paper we only use the results from the $12$ resimulated pairs.
+The dark matter particle resolution in these resimulations is
+$1.9\times 10^5$, a thousand times larger than Illustris-1.
+In this paper we only use the results from these $12$ resimulated pairs.
+
+Appendix A compares the physical properties (stellar masses, maximum
+circular velocities, radial velocities and separation) in those
+pairs against the results from the Illustris-1 simulations.
 

### 2018-01-31 paper/paper.tex
edit

@@
 After building the normalized variables with the simulated data we
-perform  a Kolmogorov-Smirnov test with the null hypothesis of belongig
+perform  a Kolmogorov-Smirnov test with the null hypothesis of belonging
 to a normal distribution with mean and standard deviation computed
 from the mean and standard deviation from the data itself. 
-We find that the distributions for $w$, $c/a$ and $b/a$ cannot reject
-the null hypothesis.
+We find that the distributions for the normalized $w$, $c/a$ and $b/a$
+are consistent with gaussian ditributions.
 
-We then build a multivariate normal distribution for the two halos and
-the three variables consistent with a unidimensional normal
-distribution using the vector of mean values and covariance matrix.
-This means that our final covariance matrix is $6\times 6$ and takes
-into account the correlations internal to a single galaxy and with its
-partner. 
+Based on this result we build a multivariate normal distribution for
+the joint distributions of the normalized $w$, $c/a$ and $b/a$:
+
+\begin{equation}
+p(X; \mu, \Sigma) = \frac{1}{(2\pi)^{3/2}|\Sigma|^{1/2}} \exp\left(-\frac{1}{2}(X-\mu)^{T}\Sigma^{-1}(X-\mu)\right), 
+\end{equation}
+% 
+where $X=[w, c/a, b/a]^{T}$ is a vector variable with the normalized
+quantities, $\mu$ is the vector mean and the $\Sigma$ is the
+covariance matrix.
+
 We compute the preferred covariance matrix and the mean distribution values
@@
 estimate the uncertainty on every reported coefficient.
+This compact description allows us to generate samples of size $N$
+that are consistent by construction with their parent simulation.
 
-This compact description allows us to generate samples of size $N$
-that are consistent by construction with their parent
-simulation. Finally, we use the generated samples to estimate how
-commoon are the deviations from sphericity that we measure in the observational
-data.  We use a single-tail test in this comparison, meaning that we
-always measure the fraction of points with values smaller than the
-treshold value.
+Finally, we use the generated samples to estimate how
+common are the deviations from sphericity that we measure in the
+observational data.  
+We use a double-tailed test in this comparison, meaning that we
+always measure the fraction of points with absolute values larger than the
+treshold absolute observed value.
 

### 2018-01-31 paper/paper.tex
paper

@@
 Table \ref{table:observations} and Table \ref{table:simulations}
-summarize the mean values and uncertainties for the plane width, $c/a$
+summarize the mean values and uncertainties for the plane $w$, $c/a$
 ratio and $b/a$ ratio in the observations and simulations, respectively. 
 The uncertainty in the observations is computed over the results with
-different number of satellites, while in the observations it
+different number of satellites, while in the simulations it
 corresponds to the standard deviation over different halos.
-In the following subsections we describe in detail the results for the
-distributions.
+
+The observed widths are always smaller than its randomized version.
+For M31 there is barely a ratio of $0.92$ between observed and
+randomized, while for the MW this factor goes down to less than half
+$0.48$. 
+The observed $c/a$ ratio follows the same extreme trend for
+the MW compared to a M31 distribution closer to spherical, 
+The $b/a$ ratio is statisically the same between observations and the
+spherical randomization.
+
+In the following subsections we describe in detail the results on the 
+distributions for $w$, $c/a$ and $b/a$
 

### 2018-01-31 paper/paper.tex
edit

@@
 
-Figure \ref{fig:scatter_width} summarizes the results for the plane
-width distributions.
-The panel on the left compares the results for the MW and M31
-observations against its randomized version. 
+Figure \ref{fig:scatter_width} summarizes the results for the width
+measurements.
+The left panel compares the results for the MW and M31
+observations (stars) against its spherically randomized satellites.
 The most interesting outcome is that the MW plane width is smaller
 than $\approx 98\%$ of the planes computed from the randomized distribution,
-while the M31 plane width is consistent with the same distribution.
+while the M31 plane width is only slightly smaller than the average of
+the distribution.
+
+The middle panel in \ref{fig:scatter} compares the observational resul
+against the measurements of all pairs from the Illustris1-Dark
+simulation.
+In this case we have a similar result as before. 
+The observed MW width is smaller than all the results in the
+simulation, there is not a single halo with similar values.
+On the other hand, the results for the M31 are entirely consistend
+with observations. Most of the halos in the simulation show a width
+value similar to M31.
+
+The right panel.
 

### 2018-01-31 paper/paper.tex
edit caption

@@
 \begin{equation}
-p(X; \mu, \Sigma) = \frac{1}{(2\pi)^{3/2}|\Sigma|^{1/2}} \exp\left(-\frac{1}{2}(X-\mu)^{T}\Sigma^{-1}(X-\mu)\right), 
+p(X; \mu, \Sigma) = \frac{1}{(2\pi)^{3/2}|\Sigma|^{1/2}}
+\exp\left(-\frac{1}{2}(X-\mu)^{T}\Sigma^{-1}(X-\mu)\right), 
+\label{eq:multivariate}
 \end{equation}
@@
 \includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
-\caption{Plane width characterization in the Local Group and the
-  Isolated Pairs. In all panels the horizontal axis corresponds to the
-  M31 or the most massive halo in the pair and the vertical axis to
-  the MW or the least massive halo in the pair.
-The panel on the left shows the plane width in physical units
-comparing the results from observations
+\caption{Plane width characterization in observations and
+  simulations (Illustris1-Dark in this case.) In all panels the
+  horizontal/vertical axis corresponds to the  M31/MW or the
+  most/less massive halo in the pair 
+  Left. Plane width in physical units comparing the results from observations
 (stars) against the result of spherically randomizing the satellite
-positions while keeping its radial distance (circles). 
-The panel in the middle compares the average from the observations
-(star) and the average from each one of the Isolated Pairs (circles
-with error bars).
-The panel on the right has the same information as the middle panel,
-only that this time each point has been normalized (median substracted
-and normalized by the standar deviation) to the results of its
-randomization. 
-The main message of this series of plots is that the MW has a
-significantly thiner plane both compared to the result of its own
-satellite spherical randomization (left panel) and the expectation from
-simulations (middle panel). 
+positions (circles). 
+Middle. Average from the observations (star) and the average from each
+pair in the simulation (circles).
+Right. Same as the middle panel only that this time each point has
+been normalized (median substracted and normalized by the standar
+deviation) to the results of its randomization. 
+The main message of these panels that the MW has a significantly
+thiner plane both compared to the result of its own satellite
+spherical randomization (left panel) and the expectation from
+simulations (middle and right panel).  
 This low value is $2\sigma$ away from what is expected in a spherical
 distribution. 
-In the M31 their satellites are in agreement with the expectations
-both from an spherical distribution and the results form the
+In M31 the satellite distribution are in agreement with the
+expectations both from an spherical distribution and the results form the
 simulations. 
-A second conclusion is that the spherically averaged plane width
-MW (seen in the point cloud in the left panel) is smaller than the
-average expectation from simulations, while for M31 the spherical
-average is consistent with simulations. 
 \label{fig:scatter_width}}
 \end{figure*}
-
 \begin{figure*}
@@
 
-The middle panel in \ref{fig:scatter} compares the observational resul
-against the measurements of all pairs from the Illustris1-Dark
-simulation.
+The middle panel in Figure \ref{fig:scatter_width} compares the
+observational result (star) against the measurements of all pairs from the Illustris1-Dark
+simulation (circles).
 In this case we have a similar result as before. 
@@
 
-The right panel.
+The right panel in Figure \ref{fig:scatter_width} shows the result for
+the normalized width.  
+This panel tells the same story as the middle panel. The M31 values
+are typical while the MW is an outlier. 
+The added value of the data in this panel is that it is the normalized
+which is consistent with normal distributions.
+This is the data used to build the mean values vector and covariance
+matrix described in Equation \ref{eq:multivariate}.
 

### 2018-01-31 paper/paper.tex
edit

@@
 \begin{abstract}
-We quantify the asphericity in the spatial distribution of the
-brightest satellites around the Milky Way (MW) and M31, the dominant
-galaxies in the Local Group (LG).
 We use simulations to build an explicit probability distribution for the
-asphericity around galaxies similar to the LG in the Lambda Cold Dark
-Matter (LCDM) paradigm.
+asphericity in the satellite distribution around galaxies similar to the
+Local Group (LG) in the Lambda Cold Dark Matter (LCDM) paradigm.
 This allows us to estimate the atipicallity
@@
 Detailed results differ greatly among the simulations, suggesting a
-strong influence of resolution, modelled physics and criteria to select
+strong influence of resolution, simulated physics and criteria to select
 LG pairs.
@@
 in the LCDM paradigm.
-We summarize our results in terms of mean values and covariance
-matrices. 
-This approach facilitates the comparison between asphericity results
-from different numerical setups and choices to select LG pairs in
-simulations.  
+The approach presented here will facilitate the comparison between
+asphericity results from different numerical setups and choices to
+select halo pairs in simulations, hopefully helping to clarify the
+reasons behin the LG atipicallity in LCDM. 
 \end{abstract}
@@
 This time for the $c/a$ axis ratio. 
-The message holds in this case as for the plane width.
-The MW is has a significantly low $c/a$ value compared to the
-expectation from a spherical distribution and simulations. 
+The same message holds in this case; namely, that 
+the MW is has a significantly lowwe $c/a$ value than the
+expectation from the spherical distribution and the simulations. 
 This low value is also $2\sigma$ away from the expactations for an
 spherical distribution.
-M31 is consistent both with an spherical distribution and the results
-from simulations.
-However, in this case the axis ratio in the spherically averaged case
-is completeley consistent with the expectation from simulations.
+On the other hand, M31 is consistent both with an spherical
+distribution and the results from simulations.
 \label{fig:scatter_ca_ratio}}
@@
 This time for the $b/a$ axis ratio. In this case both the MW and M31
-are consistent with the results of a spherical distribution and the
+are consistent with the results of a spherical distribution and 
 simulations. 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.47\textwidth]{expected_numbers_n_M31.pdf}
-\includegraphics[width=0.47\textwidth]{expected_numbers_n_MW.pdf}
-\caption{Probability distribution for the expected number of M31 and
-  MW halos  showing the same degree of atipicality as the Local Group if drawn
-  from a sample of 10000 isolated pairs. 
-  The distributions correspond to results derived from Illustris-DM, Illustris,
-  and ELVIS data.
-  In the most optimistic case (Illustris-DM), $1\%$ of the pairs have
-  two halos with properties similar to the LG. In the case of
-  Illustris this percentage drops to $0.1\%$ and $0.01\%$ for ELVIS.
-\label{fig:expected_number}}
-\end{figure}
-
 \section{Results}
@@
 In the following subsections we describe in detail the results on the 
-distributions for $w$, $c/a$ and $b/a$
+distributions for $w$, $c/a$ and $b/a$. 
+The plots in the main body of the paper correspond to the
+Illustris1-Dark simulation; the results from the other simulations are
+included in the Appendix.
 
@@
 matrix described in Equation \ref{eq:multivariate}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.47\textwidth]{expected_numbers_n_M31.pdf}
+\includegraphics[width=0.47\textwidth]{expected_numbers_n_MW.pdf}
+\caption{Probability distribution for the expected number of M31 and
+  MW halos  showing the same degree of atipicality as the Local Group if drawn
+  from a sample of 10000 isolated pairs. 
+  The distributions correspond to results derived from Illustris-DM, Illustris,
+  and ELVIS data.
+  In the most optimistic case (Illustris-DM), $1\%$ of the pairs have
+  two halos with properties similar to the LG. In the case of
+  Illustris this percentage drops to $0.1\%$ and $0.01\%$ for ELVIS.
+\label{fig:expected_number}}
+\end{figure*}
 

### 2018-01-31 paper/paper.tex
edit

@@
 \begin{abstract}
-We use simulations to build an explicit probability distribution for the
+We use numerical simulations to build an explicit probability distribution for the
 asphericity in the satellite distribution around galaxies similar to the
@@
 \includegraphics[width=0.45\textwidth]{gaussian_model_illustrisdm_MW.pdf}
-\caption{Correlations between the multivariate gaussian model built on
-  the normalized values for the plane width $w$, $c/a$ ratio and $b/a$ ratio. 
-Left/right panel correspond to M31/MW. 
+\caption{Results from multivariate gaussian model fitted on   the
+  normalized values for the plane width $w$, $c/a$ ratio and $b/a$
+  ratio from the Illustris1-Dark results.  
+  Left/right panel correspond
+  to M31/MW.  
+  The cross indicates the observed values.
   The contour levels in the 2D histograms correspond to the $1\sigma$,
@@
   The results for the gaussian model are built from $10^6$ point
-realizations in the six-dimensional space spaned by the variables of
-interest. 
-The correlation matrix and the mean values are computed from the
-results in the Illustris-1 simulation.
-The cross indicates the LG values.
+  realizations in the three-dimensional space spaned by the variables of
+  interest for each halo. 
   This plot clearly shows how the M31 results are well within the
-expectations from simulations while MW has an unusual low value for
+  expectations from simulations while the MW has an unusual low value for
   the plane width and the $c/a$ axis ratio.
-Equivalent results from the ELVIS data are presented in Figure
-\ref{fig:correlations_elvis}.
-\label{fig:correlations_illustris}}
+\label{fig:correlations_illustrisdm}}
 \end{figure*}
@@
 The left panel compares the results for the MW and M31
-observations (stars) against its spherically randomized satellites.
+observations (stars) against its spherically randomized satellites
+(circles). 
 The most interesting outcome is that the MW plane width is smaller
@@
 \subsection{$c/a$ axis ratio}
+
 Figure \ref{fig:scatter_ca_ratio} shows the results for the minor to
 major axis ratio. 
-Corresponding in the ELVIS data are in the appendix in Figure
-\ref{fig:scatter_elvis}.
+The layout is the same as in Figure \ref{fig:scatter_width}.
+The results for the $c/a$ ratio follow the same trends as for the
+width $w$.
 
-The left panel shows the results for the LG compared against its
-spherically randomized version.
-As expected the $c/a$ ratio in the MW is significantly lower as the
-measured values for spherical distributions. 
+The left panel in Figure \ref{fig:scatter_ca_ratio} shows how the MW
+the $c/a$ ratio is significantly lower as the measured values for
+spherical distributions, it is smaller than $\approx 98\%$ of the
+randomized distributions.   
 On the other hand the ratio for M31 is lower than the mean of the
 spherical values but still well within its variance.
-In contrast to the results for the plane width, this time the
-randomized values have symmetrical expectations between the two
-galaxies.
 
-The middle panel shows the LG compared against the results from
-Illustris. In this case we find a similar trend. The MW is atypical
-and M31 is within the variance from the simulation data.
-This time, however, there is a single MW-like galaxy out of the total
-of 20 that shows an $c/a$ as small as the MW.
-The only assymetry evident between the simulated halos is in the
-dispersion, the $c/a$ distribution for the massive halos seems to be
-wider than it is for the less massive partner.
+The middle panel in the same Figure shows the LG compared against the
+results in the simulations. 
+In this case we find a similar trend as before. 
+The MW is atypical and M31 is within the variance from the simulation data.
+This time, however, there are two MW-like halos out of the total
+of 24 that show an $c/a$ as small as the MW.
 
 The right panel shows the normalized results. 
-This highlights the two results mentioned above.
-First, the MW shows a low $c/a$ ration close to two standard deviations away
-from the mean value of the spherical distribution; this contrasts the
-results for M31 which are close to $1$ standard deviation away.
-Second, the less massive halos in the Illustris simulation present a
-smaller dispersion in their deviations from sphericity than the
-its masssive partner.
-The MW axis ratio smaller than $\approx 98\%$ of the randomized
-satellite distributions.   and its atipicallity is only comparable to
-one halo in the Illustris  simulation (none in the ELVIS simulation).
+The MW shows a low $c/a$ ration close to between two and three
+standard deviations away from the mean value of the spherical
+distribution; this contrasts the results for M31 which are close to
+$1$ standard deviation away.
 
@@
 Figure \ref{fig:scatter_ba_ratio} shows the results for the minor to
-major axis ratio. 
-Corresponding in the ELVIS data are in the appendix in Figure
-\ref{fig:scatter_elvis}.
-In all cases of comparison (against randomized distribution,
-comparasion against simulations and degree of deviation from
-sphericity) the results for both the MW and M31 do not seem atypical
-or deviated from the expectations for an spherical dsitribution.
+major axis ratio with the same layout as Figure \ref{fig_scatter_ca_ratio}
+In all cases of comparison (against randomized distribution
+and simulations  the results for both the MW and M31 are typical.
 

### 2018-01-31 paper/paper.tex
edit

@@
 This is the data used to build the mean values vector and covariance
-matrix described in Equation \ref{eq:multivariate}.
+matrix described in Equation
 
@@
 
-\subsection{Multivariate Distributions}
+\subsection{Fit to a Multivariate Gaussian Distributions}
 
+Figure \ref{fig:correlations_illustrisdm} illustrates the results from
+ compute the covariance matrix and mean vector in
+ Eq.\ref{eq:multivariate} from the normalized quantities in the
+ simulation.   
+The distributions are computed from $10^6$ with the multivariate
+gaussian.
+
+\subsection{Number of Expected LG Systems}
 This is all the information that is needed to compute the fraction of
@@
 performing such a computation.
-
-\section{Discussion}
 

### 2018-01-31 paper/paper.tex
edit

@@
  compute the covariance matrix and mean vector in
- Eq.\ref{eq:multivariate} from the normalized quantities in the
- simulation.   
-The distributions are computed from $10^6$ with the multivariate
+ Eq.\ref{eq:multivariate} from the normalized quantities computed from
+ the Illlustris1-Dark simulation.
+The distributions in the Figure are computed from $10^6$ with the multivariate
 gaussian. 
+Similar plots for Illustris1 and ELVIS are in the Appendix.
+The values for all the covariance matrices and mean vectors for all
+the simulations are listed in the Appendix.
+
+This results nicely summarizes the results we had in the previous
+sections. 
+The left triangular plot shows how M31 falls into the middle of all 2D
+distributions always close to the peak and within the $1-\sigma$
+range. 
+The right plot clearly places the MW observations outside the
+$3\sigma$ range in the joint distributions that involve the width
+$w$.
+
+In both cases the strongest positive correlation is present for the
 

### 2018-01-31 paper/paper.tex
edit

@@
 We fit the parameters of this gaussian to the results from 
-LG samples coming from three different simulations: ELVIS, Illustris1
-and Illustris-DarkMatter.
-We finally compare the observational results against the distributions
+LG samples coming from three different simulations
+to finally compare the observational results against the distributions
 derived from the simulations.
 
-We find that in the best case (Illustris1-DarkMatter) the deviation from aesphericity in the observed LG is only
-expected in $3\pm2$ pairs out of a sample of $10^4$ isolated pairs. 
-This places the LG as a $3\sigma$ outlier. 
+We find that in the best case (Illustris1-DarkMatter) the deviation
+from aesphericity in the observed LG is only  expected in $3\pm2$
+pairs out of a sample of $10^4$ isolated pairs. This places the LG as
+a $3\sigma$ outlier.   
 The weight to explain this atypical result is not distributed equally
-between the MW and M31. While M31 presents a fully typical asphericity
-in the expectations from LCDM, the MW shows aspherical deviations in
-plane width and the major-to-minor axis ratio highly atypical in the
+between the MW and M31. 
+While M31 presents a fully typical asphericity in the expectations
+from LCDM, the MW shows aspherical deviations in plane width and the
+major-to-minor axis ratio highly atypical in the 
 framework of LCDM. 
-We estimate that with the M31 $XX$ out of $2000$ pairs show normalized
-characteristics larget r equal than M31, while this number drops to 
-$XX$ for the MW.
+We estimate that with the M31 between $37\%$ and $58\%$ of the pairs
+pairs show normalized characteristics larger than M31, while
+this fraction drops to less than $1\%$ for the MW.
+These fractions are robust to changes in the numerical simulations and to
+the criteria used to define the pairs.
 
-The method we present to quantify how atypical is the LG is robust to
-the numerical simulations used to define the LCDM expectations. 
-Quantifying the degree of asphericity highlights the atypicality of
-the Milky Way stressing the stark difference with M31 and its more
-typical nature. 
-This atypical distribution also adds up to the presence of two bright
-satellite galaxies, which is also uncommon both in simulations and
-observations.
+The highly aspherical distribution of the brightest MW satellites is
+in stark contrast to the more spherical M31 distribution.
+Furthermore, the atipicallity of the MW distribution in the LCDM
+context adds up to the also atypical presence of two bright satellite
+galaxies.
 
-The extension of the framework we present in this paper to describe
-outliers found as a second order deviation (i.e. fiding a \emph{subset} of
-satellites in M31 that are in a plane or \emph{adding} velocity
-information) could also be possible along the line of work presented
-by, that avoid finding in observations the exact observed distribution
-and instead focuse in defining atypicallity.
+The focus of our approach is building explicit probability
+distributions for the observables of interest, instead of trying to
+find simulated objects that fullfil different observational criteria. 
+This approach is particularly useful in the case of atypical
+observables. 
+Building the probability distribution allows for an atypicallity
+quantification without needing to build explicit samples of objects
+that are already scarce and difficult to find in simulations.
 
-The quantitative study we present allows us to estimate  the volumes 
-that cosmological simulations have to probe in order to study similar
-LG configurations.
-Such atypical satellite distribution should be seen as an opportunity
-to constraint in high detail the initial conditions and environment
-that allowed such pattern to emerge.
+An extension of this framework to outliers in higher order deviations
+(i.e. a \emph{subset} of satellites that are in a plane or
+coherent \emph{velocity} strictures) should also be possible, similar
+to the work presented by XX on the satellite velocity anisotropy.
+
+From the results we derive in this paper we also estimate that a
+cosmological volume of at least $( XX )^3$ is required to find a halo pair
+that shows similar asphericity characteristics as the LG. 
+This atypical satellite distribution should be seen as an opportunity
+to constrain in high detail the initial conditions and environment
+that allowed such a pattern to emerge.
 

### 2018-02-06 paper/paper.tex
abstract

@@
 \begin{abstract}
-We use numerical simulations to build an explicit probability distribution for the
-asphericity in the satellite distribution around galaxies similar to the
-Local Group (LG) in the Lambda Cold Dark Matter (LCDM) paradigm.
+We use numerical simulations to build an explicit probability
+distribution for the asphericity in the satellite distribution around
+galaxies similar to the Local Group (LG) in the Lambda Cold Dark
+Matter (LCDM) paradigm. 
 This allows us to estimate the atipicallity
@@
 LG pairs.
-However, there are three common trends in these simulations. First, at most of
-$1\%$ the pairs are expected to have satellite distributions with the
-same asphericity as the Local Group; second, between
-$38\%$ to $59\%$ of the pairs have a halo with a satellite
+However, there are three common trends in these simulations. 
+First, at most of $1\%$ the pairs are expected to have satellite
+distributions with the same asphericity aas the Local Group; second,
+between $38\%$ to $59\%$ of the pairs have a halo with a satellite
 distribution as aspherical as in M31; and third, at most $2\%$ of the
 pairs have a satellite distribution as planar as in the MW. 
-The brightest satellites in M31 galaxy turn out to have a rather typical distribution 
-in the LCDM context, while the MW is atypical in this respect. 
+The brightest satellites in M31 galaxy turn out to have a rather
+typical distribution in the LCDM context, while the MW is atypical in
+this respect.  
 These results place the LG close to the level of a 3-$\sigma$ outlier
 in the LCDM paradigm. 
-The approach presented here will facilitate the comparison between
+The approach presented here facilitates the comparison between
 asphericity results from different numerical setups and choices to

### 2018-02-06 paper/paper.tex
edit

@@
 In both cases the strongest positive correlation is present for the
+width and the $c/a$ axis ratio. A weaker but still positive
+correlation is present for the width and the $b/a$ axis ratio.
 
 \subsection{Number of Expected LG Systems}
-This is all the information that is needed to compute the fraction of
-pairs that are expected to share the same asphericity as the LG.
-We start the Discussion section by describing the results of
-performing such a computation.
+
+The fits to the multivariate gaussian distributions can be used now to
+compute the expected number of pairs with characteristics similar to
+the LG.
+To do this we generate $10^3$ samples, each sample contains $10^4$
+pairs which are drawn from the multivariate gaussian distributions.
+
+Figure \ref{fig:expected_number} summarizes the results from this
+experiment. 
+The left panel
 

### 2018-02-06 paper/paper.tex
edit

@@
 To do this we generate $10^3$ samples, each sample contains $10^4$
-pairs which are drawn from the multivariate gaussian distributions.
+pairs, where each pair member is drawn from the corresponding
+multivariate gaussian distributions.
 
@@
 experiment. 
-The left panel
+The left panel shows the probability density for the number of M31
+systems in a parent sampe of $10^4$ pairs, the right panel shows the
+results for the MW.
+
+We consider that a sampled system is similar to the M31/MW galaxy if the
+distance of each of its characteristics ($w$, $c/a$, $b/a$) to the
+sample mean is larger than the distance of the observational values to
+the sample mean. 
+That is, we perform a double-tailed test using the observational
+values as a threshold.
+
+Under this conditions
 

### 2018-02-07 paper/paper.tex
sigma outlier
edit

@@
 
-The fits to the multivariate gaussian distributions can be used now to
+We us the fits to the multivariate gaussian distributions to
 compute the expected number of pairs with characteristics similar to
@@
 multivariate gaussian distributions.
+
+We consider that a sampled system is similar to the M31/MW galaxy if the
+distance of each of its characteristics ($w$, $c/a$, $b/a$) to the
+sample mean is equal or larger than the distance of the observational
+values to the sample mean.   
+That is, we perform a double-tailed test using the observational
+values as a threshold.
 
@@
 
-We consider that a sampled system is similar to the M31/MW galaxy if the
-distance of each of its characteristics ($w$, $c/a$, $b/a$) to the
-sample mean is larger than the distance of the observational values to
-the sample mean. 
-That is, we perform a double-tailed test using the observational
-values as a threshold.
-
-Under this conditions
+In a three dimensional gaussian distribution, having a $1\sigma$,
+$2\sigma$ and $3\sigma$ interval corresponds to have respectively $19 \%$, $73 \%$ and
+$97 \%$ of the total of points in the distribution.
+% FUNDAMENTALS OF MULTIVARIATE STATISTICS, for Imaging and optics,
+% Bajorski.
+%In [150]: stats.chi2.cdf(l**2,3)
+%Out[150]: array([ 0.19874804,  0.73853587,  0.97070911])
+With this consideration, the $LG$ has the same degree of atipicality
+as an $3\sigma$ outlier.
 

### 2018-02-07 paper/paper.tex
edit

@@
 results for the MW.
+For M31, between $37\%$ to $58\%$ of the pairs have a satellite
+distribution as aspherical as M31 in observations; this fraction drops
+dramatically for the MW where only $0.03\% to 2\%$ of the satellites
+are expected to have extreme aspherical distributions as the MW.
+Considering the joint distribution of M31 and MW we find that at most
+$1\%$ of the pairs are expected to be similar to the LG.
 

### 2018-02-07 paper/paper.tex
edit

@@
 this respect.  
-These results place the LG close to the level of a 3-$\sigma$ outlier
+These results place the LG at the level of a $3\sigma$ outlier
 in the LCDM paradigm. 
@@
 are expected to have extreme aspherical distributions as the MW.
+
 Considering the joint distribution of M31 and MW we find that at most
 $1\%$ of the pairs are expected to be similar to the LG.
-
 In a three dimensional gaussian distribution, having a $1\sigma$,
@@
 $97 \%$ of the total of points in the distribution.
+With this result in mind the $LG$ has the same degree of atipicality
+as an $3\sigma$ outlier. 
 % FUNDAMENTALS OF MULTIVARIATE STATISTICS, for Imaging and optics,
@@
 %Out[150]: array([ 0.19874804,  0.73853587,  0.97070911])
-With this consideration, the $LG$ has the same degree of atipicality
-as an $3\sigma$ outlier.
+
+Among the three simulations, the results infered from ELVIS data show
+the lowest fraction of M31 and MW systems; for Illustris1-Dark we have
+the highest fraction of M31/MW systems. The results from Illustris1
+are in between these two, actually closer to ELVIS.
 

### 2018-02-07 paper/paper.tex
appendix figures

@@
 \end{figure*}
+
 \begin{figure*}
@@
 
-\section{Results from ELVIS}
 \begin{figure*}
 \centering
-\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
-\caption{ELVIs results for the quantities presented for the Illustris-1
+\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
+\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
+\caption{
+\label{fig:physical}}
+\end{figure*}
+
+\section{Results from ELVIS and Illustris1}
+\begin{figure*}
+\centering
+\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_width.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_width.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
+\caption{ELVIs results for the quantities presented for the Illustris1-Dark
   simulation in Figures  \ref{fig:scatter_width},
@@
 \caption{
-Same layout as Figure \ref{fig:correlations_illustris}, this time
+Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
 computed from the ELVIS data.
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=0.28\textwidth]{scatter_ranked_width.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_ranked_ca_ratio.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_ranked_ba_ratio.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_width.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
+\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
+\caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
+  computed from the Illustris1 data.
+\label{fig:scatter_illustris}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_M31.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
+\caption{
+Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
+computed from the Illustris1 data.
+\label{fig:correlations_illustris}}
+\end{figure*}
+
 \section{Covariance Matrices and Mean value vectors}

### 2018-02-07 paper/paper.tex
new plots physical characteristics
edit

@@
 the highest fraction of M31/MW systems. The results from Illustris1
-are in between these two, actually closer to ELVIS.
+are in between these two, but closer to ELVIS.
+
+The most probable reason for these trends is the different median mass
+for the MW/M31 halos in the pairs from these simulations. 
+For instance for the MW halo the median maximum circular velocity is
+$\sim 160$ \kms, $\sim 150$ \kms and $\sim 120$ \kms in the ELVIS,
+Illustris1 and Illustris1-Dark simulations, respectively.
+For the M31 halo this median velocity is $\sim 200$\kms both for the
+ELVIS and Illustris1 simulations, while for the Illustris1-Dark it is
+$\sim 160$ \kms.
 
@@
 %https://arxiv.org/abs/1407.1078
-\newpage
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
-\caption{
+\begin{figure}
+\centering
+\includegraphics[width=0.34\textwidth]{int_distro_LG_v_rad.pdf}
+\includegraphics[width=0.34\textwidth]{int_distro_LG_d.pdf}
+\includegraphics[width=0.34\textwidth]{int_distro_M31_vmax.pdf}
+\includegraphics[width=0.34\textwidth]{int_distro_MW_vmax.pdf}
+\caption{Physical characteristics of the LG pairs selected in the
+  simulations. All lots show the integrated distributions. The
+  physical properties are the radial comoving velocity between the MW
+  and M31, the radial separation between the MW and M31 and the
+  maximum circular velocity for the M31 and MW dark matter halo.
 \label{fig:physical}}
-\end{figure*}
+\end{figure}
 

### 2018-02-07 paper/paper.tex
matrices
matrix
figsize

@@
 \centering
-\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_width.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_width.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
 \caption{ELVIs results for the quantities presented for the Illustris1-Dark
@@
 \centering
-\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_M31.pdf}
-\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_MW.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_M31.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_MW.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=0.28\textwidth]{scatter_ranked_width.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_ranked_ca_ratio.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_ranked_ba_ratio.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_width.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
-\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_width.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
 \caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
@@
 \centering
-\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_M31.pdf}
-\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_illustris_M31.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_illustris_MW.pdf}
 \caption{
@@
 
+\newpage
+\newpage
 \section{Covariance Matrices and Mean value vectors}
-Illustris M31
-
-Covariance
-\begin{verbatim}
-[[ 0.83+/-0.03  0.78+/-0.04  0.41+/-0.04]
- [ 0.78+/-0.04  1.16+/-0.05 -0.15+/-0.05]
- [ 0.41+/-0.04 -0.15+/-0.05  0.96+/-0.04]]
-\end{verbatim}
-
-Mean
-
-\begin{verbatim}
-[-0.18+/-0.04 -0.41+/-0.05  -0.20+/-0.05]
-\end{verbatim}
-
-Illustris MW
-\begin{verbatim}
-[[ 0.78+/-0.06  0.63+/-0.07  0.40+/-0.03]
- [ 0.63+/-0.07  0.69+/-0.08   0.06+/-0.02]
- [ 0.40+/-0.03  0.06+/-0.02   0.61+/-0.04]]
-\end{verbatim}
-
-Mean
-\begin{verbatim}
-[-0.17+/-0.04 -0.40+/-0.04 -0.23+/-0.04]
-\end{verbatim}
-
-IllustrisDM M31
-
-Covariance
-\begin{verbatim}
-[[ 1.50+/-0.08  1.27+/-0.08  0.64+/-0.04]
- [ 1.27+/-0.08  1.31+/-0.08  0.28+/-0.04]
- [ 0.64+/-0.04  0.28+/-0.04  0.70+/-0.04]]
-\end{verbatim}
-
-Mean
-\begin{verbatim}
-[-0.37+/-0.05 -0.55+/-0.05  -0.13+/-0.03]
-\end{verbatim}
-
-IllustrisDM M31
-
-Covariance
-\begin{verbatim}
-[[ 1.03+/-0.05  0.94+/-0.05  0.36+/-0.03 ]
- [ 0.94+/-0.05  1.24+/-0.07 -0.18+/-0.04]
- [ 0.36+/-0.03  -0.18+/-0.04  0.86+/0.03]]
-\end{verbatim}
-
-Mean
-\begin{verbatim}
-[-0.45+/-0.04 -0.61+/-0.05 -0.31+/-0.04]
-\end{verbatim}
-
-ELVIS M31
-
-Covariance
-\begin{verbatim}
-[[ 1.60+/-0.19  1.22+/-0.14  0.70+/-0.09]
- [ 1.22+/-0.14  1.08+/-0.10  0.35+/-0.05]
- [ 0.70+/-0.09  0.35+/-0.05  0.63+/-0.10]]
-\end{verbatim}
-
-Mean
-\begin{verbatim}
-[-0.18+/-0.08 -0.28+/-0.07 -0.22+/-0.05]
-\end{verbatim}
-
-ELVIS MW
-Covariance
-\begin{verbatim}
-[[ 0.45+/-0.04    0.61+/-0.09 -0.11+/-0.09 ]
- [ 0.61+/-0.09  1.21+/-0.17 -0.63+/-0.09]
- [-0.11+/-0.05  -0.63+/-0.09  0.64+/-0.06]]
-\end{verbatim}
-
-\begin{verbatim}
-[-0.32+/-0.04 -0.74+/-0.07 -0.08+/-0.05]
-\end{verbatim}
+\subsection{Illustris-1}
+
+\subsubsection{M31}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+0.83\pm 0.03  & 0.78\pm 0.04  & 0.41\pm 0.04\\
+0.78\pm 0.04  & 1.16\pm 0.05 & -0.15\pm 0.05\\
+0.41\pm 0.04 & -0.15\pm 0.05 & 0.96\pm 0.04\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.18\pm 0.04 & -0.41\pm 0.05  -0.20\pm 0.05
+\end{bmatrix}
+\]
+
+\subsubsection{MW}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 0.78\pm 0.06 & 0.63 \pm 0.07  & 0.40 \pm 0.03\\
+  0.63\pm 0.07 & 0.69 \pm 0.08 &  0.06 \pm 0.02\\
+  0.40\pm 0.03 & 0.06 \pm 0.02 &  0.61\pm 0.04\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.17\pm 0.04 & -0.40\pm 0.04 -0.23\pm 0.04\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1-Dark}
+
+\subsubsection{M31}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 1.50\pm 0.08 & 1.27\pm 0.08 & 0.64\pm 0.04\\
+  1.27\pm 0.08 &  1.31\pm 0.08&  0.28\pm 0.04\\
+  0.64\pm 0.04 &  0.28\pm 0.04 & 0.70\pm 0.04\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.37\pm 0.05& -0.55\pm 0.05 & -0.13\pm 0.03\\
+\end{bmatrix}
+\]
+
+\subsubsection{MW}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 1.03\pm 0.05 & 0.94\pm 0.05  & 0.36\pm 0.03\\
+  0.94\pm 0.05 & 1.24\pm 0.07 & -0.18\pm 0.04\\
+  0.36\pm 0.03 & -0.18\pm 0.04  & 0.86\pm 0.03\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.45\pm 0.04 & -0.61\pm 0.05 & -0.31\pm 0.04\\
+\end{bmatrix}
+\]
+
+\subsection{ELVIS}
+
+\subsubsection{M31}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 1.60\pm 0.19  & 1.22\pm 0.14 & 0.70 \pm 0.09\\
+  1.22\pm 0.14 &  1.08\pm 0.10 & 0.35 \pm 0.05\\
+  0.70\pm 0.09 & 0.35\pm 0.05  & 0.63 \pm 0.10\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.18\pm 0.08 & -0.28\pm 0.07 &-0.22\pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsubsection{MW}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 0.45\pm 0.04 & 0.61\pm0.09 & -0.11\pm0.09 \\
+  0.61\pm0.09 & 1.21\pm0.17 & -0.63\pm0.09\\
+ -0.11\pm0.05 & -0.63\pm0.09 & 0.64\pm0.06\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.32\pm 0.04 -0.74\pm 0.07 -0.08\pm 0.05\\
+\end{bmatrix}
+\]
 

### 2018-02-07 paper/paper.tex
galaxias

@@
 
-We use three dimentional positions as reported by. 
-The appendix includes the tables with the values we use in our
-computations.
-For each central galaxy we use the 15 brightest satellites within a
-distance of $300$kpc to the central galaxy.
-The satellites for the MW are: 
-THe satellites for M31 are:
+The base for our analysis is the catalog compiled in
+\citep{2014yCat..74351928P} which reports information on all 
+galaxies within 3 Mpc around the Sun to that date. 
+Detailed description of the compiled catalog can be found in
+\citep{2013MNRAS.435.1928P}, here we summarize the relevant features
+for the current study.
+
+The information in the catalog is based on the catalogue compiled by
+\cite{2012AJ....144....4M}.
+The distance estimate are based on resolved stellar populations. 
+We use three dimensional positions in a cartesian Coordinate system
+as computed by \cite{2013MNRAS.435.1928P}.
+In this coordinate system the $z$-axis points toward the Galactic north pole, the
+$x-$-axis points in the direction from the Sun to the Galactic centre,
+and the $y$-axis points in the direction of the Galactic rotation.
+
+For both the M31 and MW we only use the 11 to 15 brightest satellites(using
+$M_V$ magnitudes) within a distance of $300$kpc to its central galaxy.
+The satellites included for the MW analysis are: 
+LMC, SMC, Canis Major, Sagittarius dSph, Fornax, Leo I, Sculptor,
+Leo II, Sextans I, Carina, Ursa Minor, Draco, Canes Venatici (I),
+Hercules and Bootes II.
+The satellites included for the MW analysis are: Triangulum, NGC205,
+M32, IC10, NGC185, NGC147, Andromeda VII, Andromeda II, Andromeda
+XXXII, Andromeda XXXI, Andromeda I, Andromeda VI, Andromeda XXIII, LGS 3, 
+ and Andromeda III.
 

### 2018-02-07 paper/paper.tex
full update

@@
   \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
+  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
     \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
+    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
+    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
+    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
     % \hline
     % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-5}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
+    \cline{2-7}
+    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
     %\hhline{~--}
     \hline
-    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
-    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
-    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
+    Plane width (kpc) & $59\pm 3$  & $21\pm 2$  & $65\pm 12$   &
+    $45\pm 8$    & $-0.48\pm 0.24$ & $-2.48\pm 0.26$\\\hline
+    $c/a$ ratio & $0.45\pm 0.04$ & $0.25\pm 0.05$ & $0.55\pm0.10$ &
+    $0.53\pm 0.10$ & $-1.03\pm 0.37$ & $-2.18\pm 0.42$\\ \hline
+    $b/a$ ratio & $0.82\pm 0.06$ & $0.80\pm 0.04$ & $0.82\pm0.07$ &
+    $0.81\pm 0.08$ & $-0.02\pm 0.82$ & $-0.13\pm 0.47$\\ \hline
   \end{tabular}
@@
     observational data, the second column uses the spherically
-    randomized version of the observational data. \label{table:observations}}
+    randomized version of the observational data, the third column
+    corresponds to the observational data recentered and normalized
+    by the randomized values. \label{table:observations}}
 \end{table*}

### 2018-02-07 paper/paper.tex
new refs

@@
 However, there are three common trends in these simulations. 
-First, at most of $1\%$ the pairs are expected to have satellite
+First, at most of $2\%$ the pairs are expected to have satellite
 distributions with the same asphericity aas the Local Group; second,
-between $38\%$ to $59\%$ of the pairs have a halo with a satellite
-distribution as aspherical as in M31; and third, at most $2\%$ of the
+between $27\%$ to $56\%$ of the pairs have a halo with a satellite
+distribution as aspherical as in M31; and third, at most $3\%$ of the
 pairs have a satellite distribution as planar as in the MW. 
@@
 Finally, to compute the odds of finding the LG satellite distributions 
-in LCDM simulations, we do not make a direct search for the exact
+in LCDM simulations, we do not make a direct search for the 
 observed values into simulations because, as we show in Section, the
-LG is itself rare and we do not have enough simulated systems to
+LG is itself difficult to fina and we do not have enough simulated systems to
 perform such a brute force solution. 
-We also avoid this direct comparison for a second reason. 
-We do not want to implicitly use either LCDM or observations as what
-is considered normal or standard and compute the deviations from that
-point. 
-Our approach is different. 
-We set as a point of reference an spherical satellite
+We also avoid this direct comparison because we do not want to
+implicitly use either LCDM or observations as what is considered
+normal or standard and compute the deviations from that point.
+
+Our approach is different. We set as a point of reference an spherical satellite
 distribution to quantify how both simulations and observations
-deviate from the spherical distribution.
+deviate from the spherical distribution, following recent
+recommendations presented in \citep{2017AN....338..854P}
+
 Simulations help us to construct an explicit probability distribution
 for deviations from sphericity in LCDM.
-Then we compute the odds of finding n satellite distributions that
+Then we compute the odds of finding a satellite distribution that
 deviates from sphericity as much as the LG does.
@@
 results for the MW.
-For M31, between $37\%$ to $58\%$ of the pairs have a satellite
+For M31, between $27\%$ to $56\%$ of the pairs have a satellite
 distribution as aspherical as M31 in observations; this fraction drops
-dramatically for the MW where only $0.03\% to 2\%$ of the satellites
+dramatically for the MW where only $0.02\% to 3\%$ of the satellites
 are expected to have extreme aspherical distributions as the MW.
@@
 Considering the joint distribution of M31 and MW we find that at most
-$1\%$ of the pairs are expected to be similar to the LG.
+$2\%$ of the pairs are expected to be similar to the LG.
 In a three dimensional gaussian distribution, having a $1\sigma$,

### 2018-02-07 paper/paper.tex
typos

@@
 Detailed results differ greatly among the simulations, suggesting a
-strong influence of resolution, simulated physics and criteria to select
-LG pairs.
+strong influence of the typical DM halo mass in the different pair samples.
 However, there are three common trends in these simulations. 
 First, at most of $2\%$ the pairs are expected to have satellite
-distributions with the same asphericity aas the Local Group; second,
+distributions with the same asphericity as the Local Group; second,
 between $27\%$ to $56\%$ of the pairs have a halo with a satellite
@@
 asphericity results from different numerical setups and choices to
-select halo pairs in simulations, hopefully helping to clarify the
-reasons behin the LG atipicallity in LCDM. 
+select halo pairs in simulations, hopefully helping out to clarify the
+reasons behind the LG atipicallity in LCDM. 
 \end{abstract}
@@
 Hercules and Bootes II.
-The satellites included for the MW analysis are: Triangulum, NGC205,
+The satellites included for the M31 analysis are: Triangulum, NGC205,
 M32, IC10, NGC185, NGC147, Andromeda VII, Andromeda II, Andromeda
@@
 asphericity of the satellite distribution in the Local Group.
-We build up on the suggestions made in \cite{XX}.
+We build up on the suggestions made in \cite{2017AN....338..854P}.
 We do not look for planes or coherent kinematical structures in the

### 2018-02-08 paper/paper.tex
references

@@
 Illustris-1,  Illustris-1-Dark and ELVIS. 
-Detailed results differ greatly among the simulations, suggesting a
-strong influence of the typical DM halo mass in the different pair samples.
+Detailed results differ among the simulations suggesting a strong
+influence of the typical DM halo mass in the different pair samples.  
 However, there are three common trends in these simulations. 
 First, at most of $2\%$ the pairs are expected to have satellite
-distributions with the same asphericity as the Local Group; second,
+distributions with the same asphericity as the LG; second,
 between $27\%$ to $56\%$ of the pairs have a halo with a satellite
@@
 The approach presented here facilitates the comparison between
-asphericity results from different numerical setups and choices to
-select halo pairs in simulations, hopefully helping out to clarify the
-reasons behind the LG atipicallity in LCDM. 
+different numerical setups and choices to select halo pairs in simulations.
+Quantifying the probability density for the satellite distribuition
+asphericity as a function of halo mass and large scale environment 
+will be a necessary step to understand the origin of the LG
+atipicallity in the LCDM context as presented here.  
 \end{abstract}
@@
 
-The spatial distribution of satellite galaxies around our Milky Way and the
-M31 galaxy provides a stringent test for structure formation theories
-in a explicit cosmological context. 
+The spatial distribution of satellite galaxies around our Milky Way
+(MW) and the M31 galaxy provides a stringent test for structure
+formation theories in a explicit cosmological context.  
 The presence of a Vast Polar Structure of satellites around the Milky
@@
 In the case of M31,  observational studies have found a planar satellite
-distribution in a subset of $15$ satellites out of an homogeneous
-sample of $27$ satellites. 
+distribution in a subset of $15$ satellites out of the homogeneous
+parent sample of $27$ satellites. 
 However, taking into account the $11$ brightest satellites (as a
-comparison with the MW) there does not seem to be any planar structure.
+comparison with the MW) there isn't evidnce for any planar structure.
 
@@
 in the observable Universe cannot be properly addressed given the
-current limits in observations. 
-So far it has only been possible to contraint that $5\%$ of the
-Milky-Way like galaxies in the Universe have two bright satellite
-galaxies as is the case of the Milky Way and its Large and Small
-Magellanic Clouds.
+current observational limitations.
+Comparisons against observations in large galaxy surveys have only
+been able to constrain that $5\%$ of the Milky-Way like galaxies in
+the Universe have two bright satellite galaxies as is the case of the
+Milky Way and its Large and Small Magellanic Clouds. 
+A planar structure ouside the Local Group (LG) has only been confirmed
+in Centaurus A \citep{muller2018whirling}.
 

### 2018-02-08 paper/paper.tex
edit

@@
 
-However, the tipicallity of satellite distributions can be addressed
-in simulations.
+To date, the tipicallity of satellite distributions can only be
+addressed in simulations.
 Most of the studies have been performed in the currently preferred
@@
 Universe described by General Relativity including a Cosmological
-Constant, the so-called Lambda Cold Dark Matter (LCDM).
+Constant, the so-called Lambda Cold Dark Matter (LCDM) model.
 The broad consensus is that these highly structured satellite distributions
@@
 There are still disagreements on the precise degree of atypicallity
-and the conditions required to simulate satellite distributions closer
+and the conditions required to simulate satellite distributions closer.
+These disagreements seem to be originated on what is considered to be
+a LG analog in the simulation.
 

### 2018-02-08 paper/paper.tex
edit

@@
 
-To date, the tipicallity of satellite distributions can only be
+To date, the atipicallity of satellite distributions can only be
 addressed in simulations.
@@
 The transition from studying individual halos to pairs has been
-motivated by the hypotesis hat the location of the Local Group in
+motivated by studies that show how the LG location in the cosmic web
+plays a role in distingushing the the MW and M31 halos from the
+average $\sim 10^{12}$ \Msun DM halo.
+
 the cosmic web should play a determinant role in building up planar

### 2018-02-08 paper/paper.tex
refs

@@
 the MW and M31.
-The transition from studying individual halos to pairs has been
+The transition from individual halos to pairs has been
 motivated by studies that show how the LG location in the cosmic web
 plays a role in distingushing the the MW and M31 halos from the
-average $\sim 10^{12}$ \Msun DM halo.
-
-the cosmic web should play a determinant role in building up planar
-satellite distributions through preferential alignments and accretions
-histories of galaxies.
-
-Studies of the Local Group in an explicit cosmological context have
-also renewed the interest on performing constrained simulations that
-could reproduce the observed large scale structure of the Universe,
-This has also motivated the study of the two dominant galaxies in the 
-Local Group as a pair in a cosmological context finding that the LG
-itself has relatively uncommon kinematic configuration in the context
-of LCDM and a strong preference to lie along filaments.
+average $\sim 10^{12}$ \Msun\ DM halo \citep{2011MNRAS.417.1434F}
+Studies of the LG as a pair of isolated DM halos have also found that
+the LG itself has relatively atypical kinematicsin the context
+of LCDM and a strong preference to lie along filaments \citep{ForeroRomero2013}.
+Putting together these pieces, the cosmic web should therefore play a
+determinant role in building up planar satellite distributions through
+preferential alignments and accretions histories of galaxies
+\citep{2014MNRAS.443.1090F}.
 

### 2018-02-08 paper/paper.tex
edit

@@
 
-The aim of our work is to put together some of these pieces in a 
-simple framework to quantify how atypical is the satellite
-distribution found in the Local Group.
-Some of the explicit characteristics we want to keep in our treatment
-of the problem are the (i) cosmological context, (ii) the LG as a pair
-of galaxies and (iii) a simple and robust description for the
-satellites.
-
-The first condition constrains the kind of simulations we use. 
-We either results from fully cosmological simulations or resimulations
-of cosmological sub-volumes. 
-The second condition constraints the kind of samples we want to
-use. We build explicit samples of pairs that resemble the kinematic
-structure of the MW and M31. 
-The third condition motivates to only use the inertia tensor as a
-description for the satellites positions, while droping any
-information that might come from 3D velocities (high uncertainties) or
-involved algorithms for plane fitting.
-
-Finally, to compute the odds of finding the LG satellite distributions 
-in LCDM simulations, we do not make a direct search for the 
-observed values into simulations because, as we show in Section, the
-LG is itself difficult to fina and we do not have enough simulated systems to
-perform such a brute force solution. 
-We also avoid this direct comparison because we do not want to
-implicitly use either LCDM or observations as what is considered
-normal or standard and compute the deviations from that point.
-
-Our approach is different. We set as a point of reference an spherical satellite
-distribution to quantify how both simulations and observations
-deviate from the spherical distribution, following recent
-recommendations presented in \citep{2017AN....338..854P}
-
-Simulations help us to construct an explicit probability distribution
-for deviations from sphericity in LCDM.
-Then we compute the odds of finding a satellite distribution that
-deviates from sphericity as much as the LG does.
+The aim of our work is to overcome two difficulties in the study of
+atipicallity in satellite distributions.
+First, atypicallity is usually computed from distributions comming from
+different simulated pair samples, making it inconvenient to compare
+results from different studies. 
+Second, halo pairs with similar to the LG are scarse in cosmological
+volumes, making it hard to make direct comparisons against simulated
+systems that fully resemble the LG.
+
+We surmount the first difficulty by setting as a point of reference an
+spherical satellite distribution and not LCDM simulations. 
+This spherical distribution is built from the data itself
+(observational or simulated) by randomizing its angular position
+around the central galaxy and keeping fixed its radial distance
+\citep{2017AN....338..854P}.
+
+We handle the second difficuly by building an analytic probability
+distribution that is compatible with the simulated data.
+We the use the simulations to estimate the parameters in this
+distribution to later use it as a parent sample to generate any
+desired number of samples that are by construction statistically
+compatible with simulations.
+
+To summarize, simulations help us to construct an explicit probability
+distribution for deviations from sphericity for a given LCDM simulated
+sample.  
+Using this distribution we compute the odds of finding a satellite
+distribution that deviates from sphericity as much as the LG does.
 

### 2018-02-08 paper/paper.tex
edit

@@
 \citep{2017AN....338..854P}. 
-
-We handle the second difficuly by building an analytic probability
-distribution that is compatible with the simulated data.
-We the use the simulations to estimate the parameters in this
+We characterize each satellite distribution with its inertia
+tensor and summarize the results with the scalars describing the width
+of the distribution and their axis ratios.
+
+We handle the second difficuly by building an explicit analytic
+probability distribution that is compatible with the simulated data.
+We then use the simulations to estimate the parameters in this
 distribution to later use it as a parent sample to generate any
@@
 
-To summarize, simulations help us to construct an explicit probability
+To summarize, simulations help us first to construct an explicit probability
 distribution for deviations from sphericity for a given LCDM simulated
-sample.  
-Using this distribution we compute the odds of finding a satellite
+sample and then, using this distribution, we compute the odds of finding a satellite
 distribution that deviates from sphericity as much as the LG does.
@@
 simulated data to be used throughout the paper.
-Next, in Section we describe the methods we use to quantify and
-characterize the satellite distributions.
-In section we present the results. 
-In the discussion section we quantify the correlations between the main
-plane properties as described by the simulations.
-We use this results to quantify the degree of atipicality of the LG
-and estimate the volume that has to probed in simulations in order to
-find a pair with a satellite distribution as atipical as the LG. 
-Finally, we summarize our conclusions in Section .
+In Section we describe the methods we use to build halo pairs and 
+characterize its satellite distributions.
+In Section we present our results to finally present our conclusions
+in Section.
 
@@
 
-For both the M31 and MW we only use the 11 to 15 brightest satellites(using
+For both the M31 and MW we only use the 11 to 15 brightest satellites (using
 $M_V$ magnitudes) within a distance of $300$kpc to its central galaxy.

### 2018-02-15 paper/paper.tex
bib, y otras correcciones

@@
 Detailed results differ among the simulations suggesting a strong
-influence of the typical DM halo mass in the different pair samples.  
+influence of the typical Dark Matter (DM) halo mass in the different pair samples.  
 However, there are three common trends in these simulations. 
@@
 pairs have a satellite distribution as planar as in the MW. 
-The brightest satellites in M31 galaxy turn out to have a rather
-typical distribution in the LCDM context, while the MW is atypical in
+The brightest satellites in the M31 galaxy turn out to have a rather
+typical distribution in the LCDM context, while the MW distribution is atypical in
 this respect.  
@@
 (MW) and the M31 galaxy provides a stringent test for structure
-formation theories in a explicit cosmological context.  
+formation theories in a explicit cosmological context
+\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S, 2016arXiv160601516L}.  
 The presence of a Vast Polar Structure of satellites around the Milky
-Way has been stablished in the last decade.
+Way has been stablished in the last decade \citep{2013MNRAS.435.1928P}.
 This structure is present in the $11$ brightest "classical" dwarf
 galaxies and has been confirmed as fainter satellites have been
-detected. 
+detected \citep{2014MNRAS.441.2124B}. %XXXXXXX  
 In the case of M31, observational studies have found a planar satellite
-distribution in a subset of $15$ satellites out of the homogeneous
-parent sample of $27$ satellites. 
-However, taking into account the $11$ brightest satellites (as a
-comparison with the MW) there isn't evidnce for any planar structure.
+distribution in a subset of $15$ satellites out of the 
+%homogeneous parent sample
+%comentario: yo no describiría la poblacion como homogenea porque la
+%mayoría están entre M31 y la MW la poblción está "loopsided"
+total poulation of $27$ satellites.\citep{2013ApJ...766..120C,
+2013Natur.493...62I} 
+However, taking into account only the $11$ brightest satellites (as a
+comparison with the MW) there is no evidence of any planar structure
+in M31.
 
@@
 in the observable Universe cannot be properly addressed given the
-current observational limitations.
+current observational limitations. %citation?
 Comparisons against observations in large galaxy surveys have only
@@
 the Universe have two bright satellite galaxies as is the case of the
-Milky Way and its Large and Small Magellanic Clouds. 
+Milky Way and its Large and Small Magellanic Clouds.%citation 
 A planar structure ouside the Local Group (LG) has only been confirmed
@@
 The broad consensus is that these highly structured satellite distributions
-are hard to find in simulations.  
+are hard to find in simulations \citep{}.  
 There are still disagreements on the precise degree of atypicallity
@@
 
-Some studies have focused on the study of individual dark matter halos
+Some studies have focused on the individual dark matter halos
 that could host galaxies like the MW or M31, while some other studies
@@
 motivated by studies that show how the LG location in the cosmic web
-plays a role in distingushing the the MW and M31 halos from the
+plays a role in distinguishing the MW and M31 halos from the
 average $\sim 10^{12}$ \Msun\ DM halo \citep{2011MNRAS.417.1434F}
 Studies of the LG as a pair of isolated DM halos have also found that
-the LG itself has relatively atypical kinematicsin the context
+the LG itself has relatively atypical kinematics in the context
 of LCDM and a strong preference to lie along filaments \citep{ForeroRomero2013}.
@@
 results from different studies. 
-Second, halo pairs with similar to the LG are scarse in cosmological
-volumes, making it hard to make direct comparisons against simulated
+Second, halo pairs similar to the LG are scarse in cosmological
+volumes, making it hard to perform direct comparisons against simulated
 systems that fully resemble the LG.
 
-We surmount the first difficulty by setting as a point of reference an
+We surmount the first difficulty by setting as a point of reference a
 spherical satellite distribution and not LCDM simulations.
+%comentario: esta explicación no me parece muy clara
 This spherical distribution is built from the data itself
 (observational or simulated) by randomizing its angular position
-around the central galaxy and keeping fixed its radial distance
+around the central galaxy and keeping its radial distance fixed
 \citep{2017AN....338..854P}. 
@@
 tensor and summarize the results with the scalars describing the width
-of the distribution and their axis ratios.
+of the distribution and its axis ratios.
 
@@
 
-In Section we list the sources of the observational and
+In Section \ref{sec:DataSamples} we list the sources of the observational and
 simulated data to be used throughout the paper.
-In Section we describe the methods we use to build halo pairs and 
+In Section \ref{sec:SpatialMeasurements} we describe the methods we use to build halo pairs and 
 characterize its satellite distributions.
-In Section we present our results to finally present our conclusions
-in Section.
-
-\section{Data samples}
+In Section \ref{sec:results} we present our results to finally
+conclude in Section \ref{sec:conclusions}.
+
+\section{Data samples}\label{sec:DataSamples}
 
@@
 
-The information in the catalog is based on the catalogue compiled by
+The information in the catalogue is based on the catalogue compiled by
 \cite{2012AJ....144....4M}.
-The distance estimate are based on resolved stellar populations. 
-We use three dimensional positions in a cartesian Coordinate system
+The distance estimates are based on resolved stellar populations. 
+We use three dimensional positions in a cartesian coordinate system
 as computed by \cite{2013MNRAS.435.1928P}.
-In this coordinate system the $z$-axis points toward the Galactic north pole, the
-$x-$-axis points in the direction from the Sun to the Galactic centre,
+In this coordinate system the $z$-axis points towards the Galactic north pole, the
+$x$-axis points in the direction from the Sun to the Galactic centre,
 and the $y$-axis points in the direction of the Galactic rotation.
@@
 We buid a sample of pairs that resemble the conditions in the LG.
-To construct this sample we select from Illustris-1 all galaxies with an stellar
+To construct this sample we select from Illustris-1 all galaxies with a stellar
 mass in the range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11}
@@
 After discarding the pairs with less than 15 detected subhalos in one
-of the halos we end up with a toal of 24 pairs. 
+of the halos we end up with a total of 24 pairs. 
 This corresponds to a pair number density of $\sim 2 \times10^{-5}$
@@
 Appendix A shows the physical  properties (stellar masses, maximum
-circular velocities, radial velocities and separation) in those
+circular velocities, radial velocities and separation) of those
 pairs.
@@
 we care about are sampled with at least $40$ particles.  
-
-Both in Illustris-1 and Illustris-1-Dm we chose the satellite samples
+%comentario: este último criterio no me parece que esté claramente
+%descrito
+
+Both in Illustris-1 and Illustris-1-DM we chose the satellite samples
 by ranking the subhalos in decreasing order of its current maximum
@@
 For a detailed description of that project and its data we refer the
-reader to \cite{XX}. 
+reader to \cite{2014MNRAS.438.2578G}. 
 Here we summarize the elements relevant to our discussion.
@@
 Additionally, the selected pairs for resimulation have a relative
-tangential velocity less than $75$ \kms. 
+tangential velocity less than $75 $\kms. 
 The dark matter particle resolution in these resimulations is
@@
 
-We compute the satellite statistics fo 11 up to 15 satellites.
-The lowest bound corresponds to the number of classical Milky Way
+We compute the satellite statistics for 11 up to 15 satellites.
+The lower limit corresponds to the number of classical Milky Way
 satellites.
@@
   \caption{Results from observations. Mean values and standard deviations for the different
-    quantities describing satellite distribution: plane width, $c/a$
+    quantities describing the satellite distributions: plane width, $c/a$
     ratio and $b/a$ ratio. 
@@
   \caption{Results from simulations. Mean values and standard deviations for the different
-    quantities describing satellite distributions: plane width, $c/a$
+    quantities describing the satellite distributions: plane width, $c/a$
     ratio and $b/a$ ratio. 
@@
 We base all our results on the description provided by the inertia
-tensor defined by the satellites's positions.
+tensor defined by the satellites' positions.
 
@@
   (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
+\label{eq:intensor}
 \end{equation}
@@
 We keep fixed the radial position of every satellite
-with respect to the central galaxy and then randomizing its angular
+with respect to the central galaxy and then randomize its angular
 position. 
 We repeat this procedure 1000 times for each satellite distribution
-and proceed to measure the quantities mentioned in the last section:
+and proceed to measure the quantities mentioned in the previous section:
 $w$, $c/a$ and $b/a$.
-For each quantity we compute an average and standard deviation from
+For each quantity we compute the average and standard deviation from
 the 1000 random samples. 
@@
 distribution against its randomized version. 
-The second intermediate comparison we make are observations against
-simulations.
+The second intermediate comparison we make is of the observations against
+the simulations.
 The final comparison is between the normalized quantities, both
@@
 spheriticy. 
-We do not want to directly compare how the results observations
+We do not want to directly compare how the observations
 deviate from simulations but to compare the deviations from
@@
 That is, out of the the $n$ pairs we have, we perfom $n$ different
-covariance and mean value measurement using only $n-1$ pairs. 
+covariance and mean value measurements using only $n-1$ pairs. 
 The reported covariance and mean values correspond to the average of
-all measurements, the corresponding standard deviation also help us to
+all measurements, the corresponding standard deviation also helps us to
 estimate the uncertainty on every reported coefficient.
@@
 \caption{Plane width characterization in observations and
-  simulations (Illustris1-Dark in this case.) In all panels the
+  simulations (Illustris1-Dark in this case). In all panels the
   horizontal/vertical axis corresponds to the  M31/MW or the
@@
 pair in the simulation (circles).
-Right. Same as the middle panel only that this time each point has
-been normalized (median substracted and normalized by the standar
+Right. Same as the middle panel except that this time each point has
+been normalized (median substracted and normalized by the standard
 deviation) to the results of its randomization. 
-The main message of these panels that the MW has a significantly
-thiner plane both compared to the result of its own satellite
+The main message of these panels is that the MW has a significantly
+thinner plane both compared to the result of its own satellite
 spherical randomization (left panel) and the expectation from
@@
 distribution. 
-In M31 the satellite distribution are in agreement with the
+In M31 the satellite distribution is in agreement with the
 expectations both from an spherical distribution and the results form the
@@
 The same message holds in this case; namely, that 
-the MW is has a significantly lowwe $c/a$ value than the
-expectation from the spherical distribution and the simulations. 
-This low value is also $2\sigma$ away from the expactations for an
+the MW has a significantly lower $c/a$ value than the
+expectation from the spherical distribution and from the simulations. 
+This low value is also $2\sigma$ away from the expactations for a
 spherical distribution.
-On the other hand, M31 is consistent both with an spherical
-distribution and the results from simulations.
+On the other hand, M31 is consistent both with a spherical
+distribution and with the results from simulations.
 \label{fig:scatter_ca_ratio}}
@@
 are consistent with the results of a spherical distribution and 
-simulations. 
+the simulations. 
 \label{fig:scatter_ba_ratio}}
@@
 \includegraphics[width=0.45\textwidth]{gaussian_model_illustrisdm_MW.pdf}
-\caption{Results from multivariate gaussian model fitted on   the
+\caption{Results from multivariate gaussian model fitted to the
   normalized values for the plane width $w$, $c/a$ ratio and $b/a$
   ratio from the Illustris1-Dark results.  
-  Left/right panel correspond
-  to M31/MW.  
+  Left/right panel correspond to M31/MW respectively.  
   The cross indicates the observed values.
@@
 $2\sigma$ and $3\sigma$ contours in two dimensions.
-  The dahsed vertical lines in the histograms along the diagonal
+  The dashed vertical lines in the histograms along the diagonal
   correspond to the $1\sigma$ boundaries in one dimension.
@@
 ratio and $b/a$ ratio in the observations and simulations, respectively. 
-The uncertainty in the observations is computed over the results with
+The uncertainty in the observations is computed from the results with
 different number of satellites, while in the simulations it
@@
 simulation, there is not a single halo with similar values.
-On the other hand, the results for the M31 are entirely consistend
+On the other hand, the results for the M31 are entirely consistent
 with observations. Most of the halos in the simulation show a width
@@
 This is the data used to build the mean values vector and covariance
-matrix described in Equation
+matrix described in Equation \ref{}
 
@@
 The left panel in Figure \ref{fig:scatter_ca_ratio} shows how the MW
-the $c/a$ ratio is significantly lower as the measured values for
-spherical distributions, it is smaller than $\approx 98\%$ of the
+$c/a$ ratio is significantly lower than the measured values for
+spherical distributions, and it is smaller than $\approx 98\%$ of the
 randomized distributions.   
@@
 spherical values but still well within its variance.
-
 The middle panel in the same Figure shows the LG compared against the
@@
 This time, however, there are two MW-like halos out of the total
-of 24 that show an $c/a$ as small as the MW.
-
+of 24 that show an $c/a$ as small as that of the MW.
 The right panel shows the normalized results. 
-The MW shows a low $c/a$ ration close to between two and three
+The MW shows a low $c/a$ ratio close to between two and three
 standard deviations away from the mean value of the spherical
-distribution; this contrasts the results for M31 which are close to
+distribution; this contrasts with the results for M31 which are close to
 $1$ standard deviation away.
@@
 In all cases of comparison (against randomized distribution
-and simulations  the results for both the MW and M31 are typical.
+and simulations) the results for both the MW and M31 are typical.
 
@@
 Figure \ref{fig:correlations_illustrisdm} illustrates the results from
- compute the covariance matrix and mean vector in
- Eq.\ref{eq:multivariate} from the normalized quantities computed from
+ computing the covariance matrix and mean vector in
+ Eq.\ref{eq:multivariate} from the normalized quantities obtained from
  the Illlustris1-Dark simulation.
-The distributions in the Figure are computed from $10^6$ with the multivariate
+The distributions in this Figure are computed from $10^6$ with the multivariate
 gaussian. 
 Similar plots for Illustris1 and ELVIS are in the Appendix.
-The values for all the covariance matrices and mean vectors for all
-the simulations are listed in the Appendix.
-
-This results nicely summarizes the results we had in the previous
-sections. 
-The left triangular plot shows how M31 falls into the middle of all 2D
-distributions always close to the peak and within the $1-\sigma$
+The values for all the covariance matrices and mean vectors
+foricorresponding to all the simulations are listed in the Appendix.
+
+This result nicely summarizes the results we had in the previous
+sections. The left triangular plot shows how M31 falls into the middle of all 2D
+distributions and is always close to the peak and within the $1-\sigma$
 range. 
@@
 
-We us the fits to the multivariate gaussian distributions to
+We use the fits to the multivariate gaussian distributions to
 compute the expected number of pairs with characteristics similar to
-the LG.
-To do this we generate $10^3$ samples, each sample contains $10^4$
+those of the LG.
+To do this we generate $10^3$ samples, each sample containing $10^4$
 pairs, where each pair member is drawn from the corresponding
-multivariate gaussian distributions.
+multivariate gaussian distribution.
 
@@
 Figure \ref{fig:expected_number} summarizes the results from this
-experiment. 
-The left panel shows the probability density for the number of M31
+experiment. The left panel shows the probability density for the number of M31
 systems in a parent sampe of $10^4$ pairs, the right panel shows the
 results for the MW.
-For M31, between $27\%$ to $56\%$ of the pairs have a satellite
-distribution as aspherical as M31 in observations; this fraction drops
-dramatically for the MW where only $0.02\% to 3\%$ of the satellites
-are expected to have extreme aspherical distributions as the MW.
+For M31, between $27\%$ and $56\%$ of the pairs have a satellite
+distribution as aspherical as the observed in M31. This fraction drops
+dramatically for the MW where only $0.02\%$ to $3\%$ of the satellites
+are expected to have as extreme aspherical distributions as the MW.
 
@@
 With this result in mind the $LG$ has the same degree of atipicality
-as an $3\sigma$ outlier. 
+as a $3\sigma$ outlier. 
 % FUNDAMENTALS OF MULTIVARIATE STATISTICS, for Imaging and optics,
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusions}
 
@@
 We first measure the width and axis ratios for the satellite
-distribution of interest. 
+distributions of interest. 
 Then, we measure the same quantities for spherically
@@
 We find that in the best case (Illustris1-DarkMatter) the deviation
-from aesphericity in the observed LG is only  expected in $3\pm2$
+from asphericity in the observed LG is only expected in $3\pm2$
 pairs out of a sample of $10^4$ isolated pairs. This places the LG as
@@
 distributions for the observables of interest, instead of trying to
-find simulated objects that fullfil different observational criteria. 
+find simulated objects that fulfill different observational criteria. 
 This approach is particularly useful in the case of atypical
@@
 (i.e. a \emph{subset} of satellites that are in a plane or
-coherent \emph{velocity} strictures) should also be possible, similar
-to the work presented by XX on the satellite velocity anisotropy.
+coherent \emph{velocity} structures) should also be possible, similar
+to the work presented by XX\cite{2013Natur.493...62I} on the satellite velocity anisotropy.
 

### 2018-02-15 paper/paper.tex
edit, remove repeated bibtex entries

@@
 Detailed results differ among the simulations suggesting a strong
-influence of the typical Dark Matter (DM) halo mass in the different pair samples.  
+influence of the typical Dark Matter (DM) halo mass in the different
+pair samples. 
 However, there are three common trends in these simulations. 
@@
 this respect.  
-These results place the LG at the level of a $3\sigma$ outlier
-in the LCDM paradigm. 
-The approach presented here facilitates the comparison between
-different numerical setups and choices to select halo pairs in simulations.
-Quantifying the probability density for the satellite distribuition
-asphericity as a function of halo mass and large scale environment 
-will be a necessary step to understand the origin of the LG
-atipicallity in the LCDM context as presented here.  
+These results place the LG at the level of a $3\sigma$ outlier in the
+LCDM paradigm. 
+Understand this atipicallity will require quantifying the probability
+distribution for the satellite distribuition asphericity as a function
+of halo mass and large scale environment. 
+The approach presented can facilitate this study and other comparisons
+between different numerical setups and choices to select LG pairs in
+simulations.  
 \end{abstract}

### 2018-02-15 paper/paper.tex
edit

@@
 Detailed results differ among the simulations suggesting a strong
-influence of the typical Dark Matter (DM) halo mass in the different
-pair samples. 
-However, there are three common trends in these simulations. 
+influence of the typical Dark Matter (DM) halo mass in the LG samples.
+However, there are three common trends.
 First, at most of $2\%$ the pairs are expected to have satellite
@@
 pairs have a satellite distribution as planar as in the MW. 
-The brightest satellites in the M31 galaxy turn out to have a rather
-typical distribution in the LCDM context, while the MW distribution is atypical in
-this respect.  
+The brightest satellites in the M31 galaxy have a rather typical
+distribution in the LCDM context, while the MW distribution is
+atypical in this respect.  
 These results place the LG at the level of a $3\sigma$ outlier in the
 LCDM paradigm. 
-Understand this atipicallity will require quantifying the probability
+Understand this atipicality will require quantifying the probability
 distribution for the satellite distribuition asphericity as a function
@@
 The approach presented can facilitate this study and other comparisons
-between different numerical setups and choices to select LG pairs in
-simulations.  
+between different numerical setups and choices to study satellites
+around LG pairs in simulations.  
 \end{abstract}

### 2018-02-15 paper/paper.tex
edit

@@
 asphericity of the satellite distribution in the Local Group.
-We build up on the suggestions made in \cite{2017AN....338..854P}.
-We do not look for planes or coherent kinematical structures in the
-interest of keeping the method straightforward and robust.
+We build up on the suggestions made in \cite{2017AN....338..854P}, 
+focusing on asphericity estimates for a fixed number of the brightest
+satellites around each galaxy.
+In the interest of keeping the method straightforward and robust we do
+not look for planes in subsets of satellites or coherent kinematical
+structures.
 
@@
 distributions of interest. 
-Then, we measure the same quantities for spherically
-randomized data. 
-Finally, renormalize the initial results to the mean value and
-standard deviation from the randomized samples.
+Then, we measure the same quantities for the same set of points after
+a process of spherical randomization.
+Finally, we renormalize the initial results to the mean value and
+standard deviation computed from the randomized data.
 

### 2018-02-15 paper/paper.tex
edit

@@
 In this paper we develop and demostrate a method to quantify the
-asphericity of the satellite distribution in the Local Group.
-We build up on the suggestions made in \cite{2017AN....338..854P}, 
-focusing on asphericity estimates for a fixed number of the brightest
-satellites around each galaxy.
+asphericity of the satellite distribution in the around the MW and M31.  
 In the interest of keeping the method straightforward and robust we do
@@
 structures. 
-
-The method uses as a reference point the spherically randomized data
-of the system under study.
-We first measure the width and axis ratios for the satellite
+We focus on the asphericity estimates for a fixed number of the
+brightest satellites around each galaxy.
+
+The method uses as a reference the spherically randomized data
+of the system under study \citep{2017AN....338..854P}.  
+To this end, we first measure the width and axis ratios for the satellite
 distributions of interest. 
@@
 
-The normalized quantities for different systems are well reproduced by
+We find that these normalized quantities are well described by
 a multivariate gaussian distribution. 
-We fit the parameters of this gaussian to the results from 
-LG samples coming from three different simulations
-to finally compare the observational results against the distributions
-derived from the simulations.
+We fit estimate the mean and covariance of this distributions using
+the results of LG pairs coming from three different numerical
+simulations, we inally compare the observational results against the
+distributions derived from the simulations: Illustris-1,
+Illustris-1-Dark and ELVIS.
 

### 2018-02-19 paper/paper.tex
ref
references

@@
 LCDM paradigm. 
-Understand this atipicality will require quantifying the probability
-distribution for the satellite distribuition asphericity as a function
-of halo mass and large scale environment. 
-The approach presented can facilitate this study and other comparisons
+We suggest that to understand this atipicality will require quantifying
+the probability distribution for the satellite distribuition
+asphericity as a function of halo mass and large scale environment. 
+The approach presented here can facilitate that study and other comparisons
 between different numerical setups and choices to study satellites
@@
 formation theories in a explicit cosmological context
-\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S, 2016arXiv160601516L}.  
+\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S}
 The presence of a Vast Polar Structure of satellites around the Milky
-Way has been stablished in the last decade \citep{2013MNRAS.435.1928P}.
+Way, first suggested by \cite{1976RGOB..182..241K} and
+\cite{1976MNRAS.174..695L} as a Magellanic Plane, has been
+stablished in the last decade \citep{2005A&A...431..517K,2013MNRAS.435.1928P}. 
 This structure is present in the $11$ brightest "classical" dwarf
@@
 distribution in a subset of $15$ satellites out of the 
-%homogeneous parent sample
-%comentario: yo no describiría la poblacion como homogenea porque la
-%mayoría están entre M31 y la MW la poblción está "loopsided"
 total poulation of $27$ satellites.\citep{2013ApJ...766..120C,
 2013Natur.493...62I}
-However, taking into account only the $11$ brightest satellites (as a
-comparison with the MW) there is no evidence of any planar structure
-in M31.
 
@@
 
+\section*{Acknowledgements} 
+We acknowledge Universidad de los Andes and COLCIENCIAS (Project -
+XXX) for the computing resources used in this project.
+
 \bibliographystyle{mnras}

### 2018-02-19 paper/paper.tex
referencias

@@
 formation theories in a explicit cosmological context
-\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S}
+\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S}.
 The presence of a Vast Polar Structure of satellites around the Milky
@@
 galaxies and has been confirmed as fainter satellites have been
-detected \citep{2014MNRAS.441.2124B}. %XXXXXXX  
+detected \citep{2014MNRAS.441.2124B}. 
 In the case of M31, observational studies have found a planar satellite
@@
 total poulation of $27$ satellites.\citep{2013ApJ...766..120C,
-2013Natur.493...62I}
+2013Natur.493...62I}, although its $11$ brightest satellites (to make
+a fair comparison against the MW) do not show any special feature.
 
 The question whether this kind of planar configurations are atypical
-in the observable Universe cannot be properly addressed given the
-current observational limitations. %citation?
-Comparisons against observations in large galaxy surveys have only
-been able to constrain that $5\%$ of the Milky-Way like galaxies in
-the Universe have two bright satellite galaxies as is the case of the
-Milky Way and its Large and Small Magellanic Clouds.%citation 
-A planar structure ouside the Local Group (LG) has only been confirmed
-in Centaurus A \citep{muller2018whirling}.
+on cosmological samples has not been properly addressed given the
+current observational limitations. For instance, comparisons in large
+galaxy surveys have only been able to constrain that $5\%$ of the
+Milky-Way like galaxies in the Universe have two bright satellite
+galaxies as is the case of the Milky Way and its Large and Small
+Magellanic Clouds \citep{2011ApJ...733...62L}, or
+that pairs of bright satellites preferentially show anti-correlated
+when they are diametrically oposed \citep{2014Natur.511..563I}.
+A planar structure outside the Local Group (LG) has been confirmed
+in Centaurus A \citep{muller2018whirling} a galaxy that is only $\sim
+4$Mpc away.
 
@@
 addressed in simulations.
+First studies 
 Most of the studies have been performed in the currently preferred

### 2018-02-19 paper/paper.tex
results previous publications

@@
 \centering
+\begin{tabular}{|p{2.5cm}|p{6cm}| p{5cm}| c|}\hline
+Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
+\text{\cite{2005A&A...431..517K}} & Disk height in MW's 11 classical
+satellites & Monte Carlo satellite distributions with a power law
+radial distribution. & $0.5$ \\
+\hline
+\end{tabular}
+\caption{Probability results derived in previous publications.}
+\end{table*}
+
+\begin{table*}
+  \centering
   \renewcommand{\arraystretch}{1.2}

### 2018-02-19 paper/paper.tex
references

--- 2018-02-19 paper/paper.tex
@@
 total poulation of $27$ satellites.\citep{2013ApJ...766..120C,
-2013Natur.493...62I}, although its $11$ brightest satellites (to make
-a fair comparison against the MW) do not show any special feature.
+2013Natur.493...62I}, although its brightest satellites
+do not show any special feature and are consistent with a random
+distribution \citep{2006AJ....131.1405K, 2007MNRAS.374.1125M}.
 
@@
 conclude in Section \ref{sec:conclusions}.
+
+\begin{table*}
+\centering
+\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
+Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
+\text{\cite{2005A&A...431..517K}} & RMS height in MW's 11 classical
+satellites & Monte Carlo from an spherical power law
+radial distribution. & $<0.5$ \\
+\text{\cite{2005MNRAS.363..146L}} & Triaxiality of MW's 11 classical
+satellites & 6 high resolution DM only N-body simulations. & common \\
+\text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in
+MW's 11 classical satellites & 3 high resolution DM only N-body
+simulations. & 2 \\
+\text{\cite{2006AJ....131.1405K}} & RMS height in M31's 15 brightest
+satellites & Monte Carlo satellite distributions with a power law
+radial distribution & $87-99$\\
+\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in MW's
+11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
+simulations & $<0.5$\\
+\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in M31's
+16 brightest satellites & Monte Carlo from an spherical power law radial
+distribution & $17$\\
+\hline
+\end{tabular}
+\caption{Probability results derived in previous publications.}
+\end{table*}
 

### 2018-02-20 paper/paper.tex
references
referencias

@@
 do not show any special feature and are consistent with a random
-distribution \citep{2006AJ....131.1405K, 2007MNRAS.374.1125M}.
+spherically symmetric distribution \citep{2006AJ....131.1405K,
+  2007MNRAS.374.1125M, 2013ApJ...766..120C}.
 
@@
 \text{\cite{2005MNRAS.363..146L}} & Triaxiality of MW's 11 classical
-satellites & 6 high resolution DM only N-body simulations. & common \\
+satellites & 6 high resolution DM only N-body simulations. & High\\
 \text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in
@@
 distribution & $17$\\
+\text{\cite{2009MNRAS.399..550L}}& Triaxiality in MW 11 classical satellites & 436 halos from a
+cosmological N-body simulation ($1.3\times 10^{8}$\Msun particle mass)
+&  High \\
+\text{\cite{2013ApJ...766..120C}}& RMS height in M31's 27 brightest
+satellites & Monte Carlo randomized satellite distribution & High\\
+\text{\cite{2013MNRAS.429..725S}}& $c/a$ ratio in MW's 12 brightest
+satellites & 6 High resolution DM only N-body simulations ($\sim
+10^3$\Msun particle mass resolution) of individual halos & Low \\
 \hline

### 2018-02-21 paper/paper.tex
references

@@
 The broad consensus is that these highly structured satellite distributions
-are hard to find in simulations \citep{}.  
-There are still disagreements on the precise degree of atypicallity
-and the conditions required to simulate satellite distributions closer.
-These disagreements seem to be originated on what is considered to be
-a LG analog in the simulation.
+are hard to find in simulations. 
+There are still disagreements on the precise degree of atypicallity. 
+\cite{2015MNRAS.452.3838C} showed that part of the disagreement is the
+ambiguitiy in defining a planar configuration, finding that actually
+planar structures show a large diversity, hindering the possibility to
+use one or to systems as a cosmological probe.
 

### 2018-02-21 paper/paper.tex
full tables

@@
 Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
+\text{\cite{2006AJ....131.1405K}} & RMS height in M31's 15 brightest
+satellites & Monte Carlo satellite distributions with a power law
+radial distribution & $87-99$\\
+\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in M31's
+16 brightest satellites & Monte Carlo from an spherical power law radial
+distribution & $17$\\
+\text{\cite{2013ApJ...766..120C}}& RMS height in M31's 27 brightest
+satellites & Monte Carlo randomized satellite distribution & High\\
+This Work & Triaxiality and RMS height in M31's 11-15 brightest
+satellites & 24 halos in cosmological N-body Dark Matter only simulation ($\sim
+10^{6}$\Msun particle mass resolution)& 56 \\
+This Work & Triaxiality and RMS height in M31's 11-15 brightest
+satellites & 20 halos in cosmological N-body hydro simulation ($\sim
+10^{6}$\Msun particle mass resolution)& 27 \\
+This Work & Triaxiality and RMS height in M31's 11-15 brightest
+satellites & 12 high resolution DM only N-body simulations ($\sim
+10^{5}$\Msun particle mass resolution) of individual halos & 37 \\
+\hline
+\end{tabular}
+\caption{Probability results derived in previous publications for the
+  triaxiality and/or root mean squared (RMS) height of M31 satellites.
+\label{table:M31}}
+\end{table*}
+
+\begin{table*}
+\centering
+\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
+Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
 \text{\cite{2005A&A...431..517K}} & RMS height in MW's 11 classical
@@
 \text{\cite{2005MNRAS.363..146L}} & Triaxiality of MW's 11 classical
-satellites & 6 high resolution DM only N-body simulations. & High\\
+satellites & 6 high resolution DM only N-body simulations ($\sim10^5$
+\Msun\ particle mass resolution). & High\\ 
 \text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in 
 MW's 11 classical satellites & 3 high resolution DM only N-body
-simulations. & 2 \\
-\text{\cite{2006AJ....131.1405K}} & RMS height in M31's 15 brightest
-satellites & Monte Carlo satellite distributions with a power law
-radial distribution & $87-99$\\
+simulations. ($\sim10^6$ \Msun\ particle mass resolution) & 2 \\
 \text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in MW's
@@
 simulations & $<0.5$\\
-\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in M31's
-16 brightest satellites & Monte Carlo from an spherical power law radial
-distribution & $17$\\
 \text{\cite{2009MNRAS.399..550L}}& Triaxiality in MW 11 classical satellites & 436 halos from a
-cosmological N-body simulation ($1.3\times 10^{8}$\Msun particle mass)
+cosmological N-body simulation ($1.3\times 10^{8}$\Msun\ particle mass)
 &  High \\
-\text{\cite{2013ApJ...766..120C}}& RMS height in M31's 27 brightest
-satellites & Monte Carlo randomized satellite distribution & High\\
 \text{\cite{2013MNRAS.429..725S}}& $c/a$ ratio in MW's 12 brightest
@@
 10^3$\Msun particle mass resolution) of individual halos & Low \\
+This Work & Triaxiality and RMS height in M31's 11-15 brightest
+satellites & 24 halos in cosmological N-body Dark Matter only simulation ($\sim
+10^{6}$\Msun particle mass resolution)& 3\\
+This Work & Triaxiality and RMS height in M31's 11-15 brightest
+satellites & 20 halos in cosmological N-body hydro simulation ($\sim
+10^{6}$\Msun particle mass resolution)& 0.6 \\
+This Work & Triaxiality and RMS height in M31's 11-15 brightest
+satellites & 12 high resolution DM only N-body simulations ($\sim
+10^{5}$\Msun particle mass resolution) of individual halos & 0.2 \\
 \hline
 \end{tabular}
-\caption{Probability results derived in previous publications.}
+\caption{Same as Table \ref{table:M31} for the MW satellites.
+\label{table:MW}}
 \end{table*}

### 2018-02-21 paper/paper.tex
edit
new intro

@@
 The spatial distribution of satellite galaxies around our Milky Way
-(MW) and the M31 galaxy provides a stringent test for structure
-formation theories in a explicit cosmological context
+(MW) and the M31 galaxy is becoming a stringent test for structure
+formation theories in a explicit cosmological context. 
+This started with the suggestion of a Magellanic Plane, a flattened
+structure of satellite galaxies around the MW, first suggested by
+\cite{1976RGOB..182..241K} and \cite{1976MNRAS.174..695L}.
+
+\cite{2005A&A...431..517K} then quantified that the
+highly planar distribution of the 11 classical MW satellites has less
+than a $0.5\%$ chance  to happen by chance if the
+parent distribution is spherically symmetric, interpreting this as a
+challenge to the Lambda Cold Dark Matter (LCDM) paradigm.
+The same year it was recognized, using numerical simulations, that the
+satellites should not be compared with an spherically
+symmetric distribution given that Dark Matter halos in LCDM
+are expected to be triaxial
+\citep{2005MNRAS.363..146L, 2005ApJ...629..219Z}.
+Nevertheless, estimates of the chances to find simulated satellites as
+planar as in the MW were inconclusive. 
+\cite{2005MNRAS.363..146L} reported that
+satellite planes should be expected in every DM while
+\cite{2005ApJ...629..219Z} gave an estimate of a $2\%$ probability to
+have an arrangement as extreme as in observations.
+
+Later, \cite{2007MNRAS.374.1125M} used simulations to confirm the low chances
+found in \cite{2005A&A...431..517K}.
+This result was challenged by \cite{2009MNRAS.399..550L} who continue
+to report a high chances to find a planar configuration;
+the most recent numerical experiment with high resolution simulations
+by \cite{2013MNRAS.429..725S} reports low chances to find the
+observational result, but precise figures are not quoted in either of
+these two reports. 
 \citep{2015ApJ...815...19P, 2016MNRAS.457.1931S}.
 The presence of a Vast Polar Structure of satellites around the Milky
-Way, first suggested by \cite{1976RGOB..182..241K} and
-\cite{1976MNRAS.174..695L} as a Magellanic Plane, has been
-stablished in the last decade \citep{2005A&A...431..517K,2013MNRAS.435.1928P}. 
+Way,
+stablished in the last decade
+\citep{2013MNRAS.435.1928P}. 
 This structure is present in the $11$ brightest "classical" dwarf
@@
 use one or to systems as a cosmological probe.
-
-Some studies have focused on the individual dark matter halos
-that could host galaxies like the MW or M31, while some other studies
-have tried to simulate the formation of galaxy pairs resembling both
-the MW and M31.
-The transition from individual halos to pairs has been
-motivated by studies that show how the LG location in the cosmic web
-plays a role in distinguishing the MW and M31 halos from the
-average $\sim 10^{12}$ \Msun\ DM halo \citep{2011MNRAS.417.1434F}
-Studies of the LG as a pair of isolated DM halos have also found that
-the LG itself has relatively atypical kinematics in the context
-of LCDM and a strong preference to lie along filaments \citep{ForeroRomero2013}.
-Putting together these pieces, the cosmic web should therefore play a
-determinant role in building up planar satellite distributions through
-preferential alignments and accretions histories of galaxies
-\citep{2014MNRAS.443.1090F}.
-
-The aim of our work is to overcome two difficulties in the study of
-atipicallity in satellite distributions.
-First, atypicallity is usually computed from distributions comming from
-different simulated pair samples, making it inconvenient to compare
-results from different studies. 
-Second, halo pairs similar to the LG are scarse in cosmological
-volumes, making it hard to perform direct comparisons against simulated
-systems that fully resemble the LG.
-
-We surmount the first difficulty by setting as a point of reference a
-spherical satellite distribution and not LCDM simulations.
-%comentario: esta explicación no me parece muy clara
-This spherical distribution is built from the data itself
-(observational or simulated) by randomizing its angular position
-around the central galaxy and keeping its radial distance fixed
-\citep{2017AN....338..854P}. 
-We characterize each satellite distribution with its inertia
-tensor and summarize the results with the scalars describing the width
-of the distribution and its axis ratios.
-
-We handle the second difficuly by building an explicit analytic
-probability distribution that is compatible with the simulated data.
-We then use the simulations to estimate the parameters in this
-distribution to later use it as a parent sample to generate any
-desired number of samples that are by construction statistically
-compatible with simulations.
-
-To summarize, simulations help us first to construct an explicit probability
-distribution for deviations from sphericity for a given LCDM simulated
-sample and then, using this distribution, we compute the odds of finding a satellite
-distribution that deviates from sphericity as much as the LG does.
-
-In Section \ref{sec:DataSamples} we list the sources of the observational and
-simulated data to be used throughout the paper.
-In Section \ref{sec:SpatialMeasurements} we describe the methods we use to build halo pairs and 
-characterize its satellite distributions.
-In Section \ref{sec:results} we present our results to finally
-conclude in Section \ref{sec:conclusions}.
 
@@
 
+Some studies have focused on the individual dark matter halos
+that could host galaxies like the MW or M31, while some other studies
+have tried to simulate the formation of galaxy pairs resembling both
+the MW and M31.
+The transition from individual halos to pairs has been
+motivated by studies that show how the LG location in the cosmic web
+plays a role in distinguishing the MW and M31 halos from the
+average $\sim 10^{12}$ \Msun\ DM halo \citep{2011MNRAS.417.1434F}
+Studies of the LG as a pair of isolated DM halos have also found that
+the LG itself has relatively atypical kinematics in the context
+of LCDM and a strong preference to lie along filaments \citep{ForeroRomero2013}.
+Putting together these pieces, the cosmic web should therefore play a
+determinant role in building up planar satellite distributions through
+preferential alignments and accretions histories of galaxies
+\citep{2014MNRAS.443.1090F}.
+
+The aim of our work is to overcome two difficulties in the study of
+atipicallity in satellite distributions.
+First, atypicallity is usually computed from distributions comming from
+different simulated pair samples, making it inconvenient to compare
+results from different studies. 
+Second, halo pairs similar to the LG are scarse in cosmological
+volumes, making it hard to perform direct comparisons against simulated
+systems that fully resemble the LG.
+
+We surmount the first difficulty by setting as a point of reference a
+spherical satellite distribution and not LCDM simulations.
+%comentario: esta explicación no me parece muy clara
+This spherical distribution is built from the data itself
+(observational or simulated) by randomizing its angular position
+around the central galaxy and keeping its radial distance fixed
+\citep{2017AN....338..854P}. 
+We characterize each satellite distribution with its inertia
+tensor and summarize the results with the scalars describing the width
+of the distribution and its axis ratios.
+
+We handle the second difficuly by building an explicit analytic
+probability distribution that is compatible with the simulated data.
+We then use the simulations to estimate the parameters in this
+distribution to later use it as a parent sample to generate any
+desired number of samples that are by construction statistically
+compatible with simulations.
+
+To summarize, simulations help us first to construct an explicit probability
+distribution for deviations from sphericity for a given LCDM simulated
+sample and then, using this distribution, we compute the odds of finding a satellite
+distribution that deviates from sphericity as much as the LG does.
+
+In Section \ref{sec:DataSamples} we list the sources of the observational and
+simulated data to be used throughout the paper.
+In Section \ref{sec:SpatialMeasurements} we describe the methods we use to build halo pairs and 
+characterize its satellite distributions.
+In Section \ref{sec:results} we present our results to finally
+conclude in Section \ref{sec:conclusions}.
+
 \section{Data samples}\label{sec:DataSamples}

### 2018-02-21 paper/paper.tex
table

@@
 This Work & Triaxiality and RMS height in M31's 11-15 brightest
-satellites & 24 halos in cosmological N-body Dark Matter only simulation ($\sim
+satellites & 24 halos from selected pairs in a cosmological N-body Dark Matter only simulation ($\sim
 10^{6}$\Msun particle mass resolution)& 56 \\
 This Work & Triaxiality and RMS height in M31's 11-15 brightest
-satellites & 20 halos in cosmological N-body hydro simulation ($\sim
+satellites & 20 halos from selected pairs in a cosmological N-body hydro simulation ($\sim
 10^{6}$\Msun particle mass resolution)& 27 \\
@@
 satellites & 12 high resolution DM only N-body simulations ($\sim
-10^{5}$\Msun particle mass resolution) of individual halos & 37 \\
+10^{5}$\Msun particle mass resolution) of halo pairs & 37 \\
 \hline
@@
 10^3$\Msun particle mass resolution) of individual halos & Low \\
+\text{\cite{2016MNRAS.457.1931S}}& $c/a$ ratio in MW's 11 classical satellites & 12
+high resolution Hydro simulation of halo pairs ($\sim 10^{4}$\Msun particle
+mass resolution) & High\\
 This Work & Triaxiality and RMS height in M31's 11-15 brightest
-satellites & 24 halos in cosmological N-body Dark Matter only simulation ($\sim
-10^{6}$\Msun particle mass resolution)& 3\\
+satellites & 24 halos from selected pairs in a cosmological N-body
+Dark Matter only simulation ($\sim 10^{6}$\Msun particle mass resolution)& 3\\
 This Work & Triaxiality and RMS height in M31's 11-15 brightest
-satellites & 20 halos in cosmological N-body hydro simulation ($\sim
-10^{6}$\Msun particle mass resolution)& 0.6 \\
+satellites & 20 halos from selected pairs in acosmological N-body
+hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& 0.6 \\
 This Work & Triaxiality and RMS height in M31's 11-15 brightest
 satellites & 12 high resolution DM only N-body simulations ($\sim
-10^{5}$\Msun particle mass resolution) of individual halos & 0.2 \\
+10^{5}$\Msun particle mass resolution) of halo pairs & 0.2 \\
 \hline

### 2018-02-21 paper/paper.tex
referencias

@@
 atypical in this respect.  
-These results place the LG at the level of a $3\sigma$ outlier in the
-LCDM paradigm. 
+These quantitative results place the LG at the level of a $3\sigma$
+outlier in the LCDM paradigm. 
 We suggest that to understand this atipicality will require quantifying
@@
 
-Later, \cite{2007MNRAS.374.1125M} used simulations to confirm the low chances
-found in \cite{2005A&A...431..517K}.
+Later, \cite{2007MNRAS.374.1125M} used simulations to confirm the low
+chances ($<0.5\%$) found in \cite{2005A&A...431..517K}.
 This result was challenged by \cite{2009MNRAS.399..550L} who continue
-to report a high chances to find a planar configuration;
-the most recent numerical experiment with high resolution simulations
-by \cite{2013MNRAS.429..725S} reports low chances to find the
-observational result, but precise figures are not quoted in either of
-these two reports. 
-\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S}.
+to report high chances to find a planar configuration;
+two more recent numerical experiment with high resolution simulations
+(\cite{2013MNRAS.429..725S} and \cite{2016MNRAS.457.1931S}) report
+contradicting results (low and high chances to find the observational
+result, respectively) but precise figures are not quoted in either of
+these three reports. \citep{2015ApJ...815...19P,2016MNRAS.457.1931S}.
+%\citep{2015ApJ...815...19P,2016MNRAS.457.1931S}.
 The presence of a Vast Polar Structure of satellites around the Milky
-Way,
-stablished in the last decade
-\citep{2013MNRAS.435.1928P}. 
+Way, stablished in the last decade \citep{2013MNRAS.435.1928P}.
 This structure is present in the $11$ brightest "classical" dwarf
@@
 \centering
-\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
+\begin{tabular}{|p{4.0cm}|p{5.5cm}| p{4.0cm}| c|}\hline
 Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
@@
 10^3$\Msun particle mass resolution) of individual halos & Low \\
+\text{\cite{2014ApJ...789L..24P}}& $c/a$ and $b/a$ ratio in MW's 11
+classical satellites & 48 high resoltion DM only N-body simulations
+($\sim 10^{5}$\Msun particle mass resolution) of both halo pairs and
+isolated halos & 0.77\\
 \text{\cite{2016MNRAS.457.1931S}}& $c/a$ ratio in MW's 11 classical satellites & 12

### 2018-02-21 paper/paper.tex
references + intro

@@
 these three reports. \citep{2015ApJ...815...19P,2016MNRAS.457.1931S}.
-%\citep{2015ApJ...815...19P,2016MNRAS.457.1931S}.
-The presence of a Vast Polar Structure of satellites around the Milky
-Way, stablished in the last decade \citep{2013MNRAS.435.1928P}.
-This structure is present in the $11$ brightest "classical" dwarf
-galaxies and has been confirmed as fainter satellites have been
-detected \citep{2014MNRAS.441.2124B}. 
+Meanwhile, \cite{2013MNRAS.429.1502W, 2014ApJ...789L..24P} reported
+on new tests using high resolution simulations and cosmological
+volumes arriving at a chance of $6\%$ and $0.77\%$, respectively to
+have a satellite distribution as triaxial as the observations.
+
 In the case of M31, observational studies have found a planar satellite
 distribution in a subset of $15$ satellites out of the 
-total poulation of $27$ satellites.\citep{2013ApJ...766..120C,
+total poulation of $27$ satellites \citep{2013ApJ...766..120C,
 2013Natur.493...62I}, although its brightest satellites
-do not show any special feature and are consistent with a random
-spherically symmetric distribution \citep{2006AJ....131.1405K,
+do not show any special feature.
+All the studies agree on the point that the satellite distribution of
+the 15 to 27 brightest satellites are consistent with 
+spherically symmetric distribution and easy to reproduce in LCDM
+simulations \citep{2006AJ....131.1405K,
   2007MNRAS.374.1125M, 2013ApJ...766..120C}.
-
-The question whether this kind of planar configurations are atypical
-on cosmological samples has not been properly addressed given the
-current observational limitations. For instance, comparisons in large
-galaxy surveys have only been able to constrain that $5\%$ of the
-Milky-Way like galaxies in the Universe have two bright satellite
-galaxies as is the case of the Milky Way and its Large and Small
-Magellanic Clouds \citep{2011ApJ...733...62L}, or
-that pairs of bright satellites preferentially show anti-correlated
-when they are diametrically oposed \citep{2014Natur.511..563I}.
-A planar structure outside the Local Group (LG) has been confirmed
-in Centaurus A \citep{muller2018whirling} a galaxy that is only $\sim
-4$Mpc away.
-
-To date, the atipicallity of satellite distributions can only be
-addressed in simulations.
-First studies 
-Most of the studies have been performed in the currently preferred
-paradigm, which is based on a Cold Dark Matter cosmology in a expanding
-Universe described by General Relativity including a Cosmological
-Constant, the so-called Lambda Cold Dark Matter (LCDM) model.
-The broad consensus is that these highly structured satellite distributions
-are hard to find in simulations. 
-There are still disagreements on the precise degree of atypicallity. 
-\cite{2015MNRAS.452.3838C} showed that part of the disagreement is the
-ambiguitiy in defining a planar configuration, finding that actually
-planar structures show a large diversity, hindering the possibility to
-use one or to systems as a cosmological probe.
 
@@
 \centering
-\begin{tabular}{|p{4.0cm}|p{5.5cm}| p{4.0cm}| c|}\hline
+\begin{tabular}{|p{4.0cm}|p{4.5cm}| p{5.5cm}| c|}\hline
 Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
-\text{\cite{2005A&A...431..517K}} & RMS height in MW's 11 classical
+\text{\cite{2005A&A...431..517K}} & RMS height in 11 classical
 satellites & Monte Carlo from an spherical power law
 radial distribution. & $<0.5$ \\
-\text{\cite{2005MNRAS.363..146L}} & Triaxiality of MW's 11 classical
+\text{\cite{2005MNRAS.363..146L}} & Triaxiality of 11 classical
 satellites & 6 high resolution DM only N-body simulations ($\sim10^5$
@@
 \text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in 
-MW's 11 classical satellites & 3 high resolution DM only N-body
+11 classical satellites & 3 high resolution DM only N-body
 simulations. ($\sim10^6$ \Msun\ particle mass resolution) & 2 \\
-\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in MW's
-11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
+\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in 11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
 simulations & $<0.5$\\
-\text{\cite{2009MNRAS.399..550L}}& Triaxiality in MW 11 classical satellites & 436 halos from a
+\text{\cite{2009MNRAS.399..550L}}& Triaxiality in 11 classical satellites & 436 halos from a
 cosmological N-body simulation ($1.3\times 10^{8}$\Msun\ particle mass)
 &  High \\
-\text{\cite{2013MNRAS.429..725S}}& $c/a$ ratio in MW's 12 brightest
+\text{\cite{2013MNRAS.429..725S}}& $c/a$ ratio in 12 brightest
 satellites & 6 High resolution DM only N-body simulations ($\sim
 10^3$\Msun particle mass resolution) of individual halos & Low \\
-\text{\cite{2014ApJ...789L..24P}}& $c/a$ and $b/a$ ratio in MW's 11
+\text{\cite{2013MNRAS.429.1502W}}& $c/a$ ratio or RMS height in 11 brightest
+satellites & 1686 halos from a cosmological DM only N-body simulation
+($\sim 10^6$\Msun particle mass resolution) & 6 or 13 \\
+\text{\cite{2014ApJ...789L..24P}}& $c/a$ and $b/a$ ratio in 11
 classical satellites & 48 high resoltion DM only N-body simulations
@@
 isolated halos & 0.77\\
-\text{\cite{2016MNRAS.457.1931S}}& $c/a$ ratio in MW's 11 classical satellites & 12
+\text{\cite{2016MNRAS.457.1931S}}& $c/a$ ratio in 11 classical satellites & 12
 high resolution Hydro simulation of halo pairs ($\sim 10^{4}$\Msun particle
 mass resolution) & High\\
-This Work & Triaxiality and RMS height in M31's 11-15 brightest
+This Work & Triaxiality and RMS height in 11-15 brightest
 satellites & 24 halos from selected pairs in a cosmological N-body
 Dark Matter only simulation ($\sim 10^{6}$\Msun particle mass resolution)& 3\\
-This Work & Triaxiality and RMS height in M31's 11-15 brightest
+This Work & Triaxiality and RMS height in 11-15 brightest
 satellites & 20 halos from selected pairs in acosmological N-body
 hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& 0.6 \\
-This Work & Triaxiality and RMS height in M31's 11-15 brightest
+This Work & Triaxiality and RMS height in 11-15 brightest
 satellites & 12 high resolution DM only N-body simulations ($\sim
@@
 \end{table*}
-
-Some studies have focused on the individual dark matter halos
-that could host galaxies like the MW or M31, while some other studies
-have tried to simulate the formation of galaxy pairs resembling both
-the MW and M31.
-The transition from individual halos to pairs has been
-motivated by studies that show how the LG location in the cosmic web
-plays a role in distinguishing the MW and M31 halos from the
-average $\sim 10^{12}$ \Msun\ DM halo \citep{2011MNRAS.417.1434F}
-Studies of the LG as a pair of isolated DM halos have also found that
-the LG itself has relatively atypical kinematics in the context
-of LCDM and a strong preference to lie along filaments \citep{ForeroRomero2013}.
-Putting together these pieces, the cosmic web should therefore play a
-determinant role in building up planar satellite distributions through
-preferential alignments and accretions histories of galaxies
-\citep{2014MNRAS.443.1090F}.
 

### 2018-02-21 paper/paper.tex
edit

@@
 these three reports. \citep{2015ApJ...815...19P,2016MNRAS.457.1931S}.
-Meanwhile, \cite{2013MNRAS.429.1502W, 2014ApJ...789L..24P} reported
+Meanwhile, \cite{2013MNRAS.429.1502W} and \cite{2014ApJ...789L..24P} reported
 on new tests using high resolution simulations and cosmological
-volumes arriving at a chance of $6\%$ and $0.77\%$, respectively to
+volumes arriving at a chance of $6\%$ and $0.77\%$, respectively, to
 have a satellite distribution as triaxial as the observations.
@@
 do not show any special feature.
-All the studies agree on the point that the satellite distribution of
+All published studies agree on the point that the global satellite distribution of
 the 15 to 27 brightest satellites are consistent with 
@@
   2007MNRAS.374.1125M, 2013ApJ...766..120C}.    
+Table \ref{table:M31} and Table \ref{table:MW} summarize the story we
+have just told, including the results from this paper using the
+methodolgy we describe in the upcoming sections.
 
@@
 Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
-\text{\cite{2006AJ....131.1405K}} & RMS height in M31's 15 brightest
+\text{\cite{2006AJ....131.1405K}} & RMS height in 15 brightest
 satellites & Monte Carlo satellite distributions with a power law
 radial distribution & $87-99$\\
-\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in M31's
-16 brightest satellites & Monte Carlo from an spherical power law radial
+\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in 16 brightest satellites & Monte Carlo from an spherical power law radial
 distribution & $17$\\
-\text{\cite{2013ApJ...766..120C}}& RMS height in M31's 27 brightest
+\text{\cite{2013ApJ...766..120C}}& RMS height in M31's brightest
 satellites & Monte Carlo randomized satellite distribution & High\\
-This Work & Triaxiality and RMS height in M31's 11-15 brightest
+This Work & Triaxiality and RMS height in 11-15 brightest
 satellites & 24 halos from selected pairs in a cosmological N-body Dark Matter only simulation ($\sim
 10^{6}$\Msun particle mass resolution)& 56 \\
-This Work & Triaxiality and RMS height in M31's 11-15 brightest
+This Work & Triaxiality and RMS height in 11-15 brightest
 satellites & 20 halos from selected pairs in a cosmological N-body hydro simulation ($\sim
 10^{6}$\Msun particle mass resolution)& 27 \\
-This Work & Triaxiality and RMS height in M31's 11-15 brightest
+This Work & Triaxiality and RMS height in 11-15 brightest
 satellites & 12 high resolution DM only N-body simulations ($\sim
@@
 
-The aim of our work is to overcome two difficulties in the study of
-atipicallity in satellite distributions.
-First, atypicallity is usually computed from distributions comming from
-different simulated pair samples, making it inconvenient to compare
-results from different studies. 
-Second, halo pairs similar to the LG are scarse in cosmological
-volumes, making it hard to perform direct comparisons against simulated
-systems that fully resemble the LG.
-
-We surmount the first difficulty by setting as a point of reference a
+Trying to reconcile and understand the seemly conflicting or inconclusive
+results on the MW has its origin on the frequentist fashion generally used to
+compute probabilities.
+Usually, the process starts by building a high level parent sample in the
+simulation and then counting how many elements has a subset
+meeting some criteria. 
+The first inconvenient with this approach is that the probability
+estimate is made against whatever turns out to be typical in each
+simulation. 
+Comparing results across simulations would require first
+characterizing the simulations at the high level parent samples.
+The second inconvenient is that it is hard to find systems that fully resemble
+the LG, this means that the high level parent sample has a small size
+making it hard to find elements that fit some criteria.
+
+In this paper, we surmount the first difficulty by setting as a point of reference a
 spherical satellite distribution and not LCDM simulations.
-%comentario: esta explicación no me parece muy clara
+
 This spherical distribution is built from the data itself

### 2018-02-21 paper/paper.tex
edit

@@
   2007MNRAS.374.1125M, 2013ApJ...766..120C}.    
-Table \ref{table:M31} and Table \ref{table:MW} summarize the story we
-have just told, including the results from this paper using the
+Table \ref{table:M31} and Table \ref{table:MW} summarize some more
+details on the results we have just mentioned.
+Those tables also include the results from this paper using the
 methodolgy we describe in the upcoming sections.
@@
 \centering
-\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
-Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
+\begin{tabular}{|p{4.0cm}|p{4.5cm}| p{5.5cm}| c|}\hline
+Reference & Target Measurement & Parent Simulation & Probability ($\%$)\\\hline
 \text{\cite{2006AJ....131.1405K}} & RMS height in 15 brightest
@@
 distribution & $17$\\
-\text{\cite{2013ApJ...766..120C}}& RMS height in M31's brightest
+\text{\cite{2013ApJ...766..120C}}& RMS height in the 27 brightest
 satellites & Monte Carlo randomized satellite distribution & High\\
@@
 \begin{tabular}{|p{4.0cm}|p{4.5cm}| p{5.5cm}| c|}\hline
-Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
+Reference & Target Measurement & Parent Simulation & Probability ($\%$)\\\hline
 \text{\cite{2005A&A...431..517K}} & RMS height in 11 classical
@@
 
-In this paper, we surmount the first difficulty by setting as a point of reference a
-spherical satellite distribution and not LCDM simulations.
-
-This spherical distribution is built from the data itself
+In this paper we surmount the first difficulty by setting as direct 
+point of reference an spherical satellite distribution and not the
+simulations themselves.
+The spherical distribution is built from the data itself
 (observational or simulated) by randomizing its angular position
@@
 \citep{2017AN....338..854P}. 
-We characterize each satellite distribution with its inertia
-tensor and summarize the results with the scalars describing the width
-of the distribution and its axis ratios.
-
-We handle the second difficuly by building an explicit analytic
-probability distribution that is compatible with the simulated data.
-We then use the simulations to estimate the parameters in this
+We then characterize each satellite distribution in terms of the
+scalars describing its deviation from the spherical distribution.
+We handle the second difficulty by building an explicit analytic
+probability distribution of the deviations from asphericity; this
+solves the problem of having a common reference point to compare
+simulations. 
+We then use different simulations to estimate the parameters in this
 distribution to later use it as a parent sample to generate any
 desired number of samples that are by construction statistically
-compatible with simulations.
-
-To summarize, simulations help us first to construct an explicit probability
-distribution for deviations from sphericity for a given LCDM simulated
-sample and then, using this distribution, we compute the odds of finding a satellite
-distribution that deviates from sphericity as much as the LG does.
+compatible with simulations, overcoming the problem of having a small
+number of systems in the parent simulations.
+
+To summarize, we start by using asphericity to characterize in the
+same way simulations and observations. 
+Then, we build an explicit probability distribution for the asphericity and
+use simulations to estimate the parameters in this
+distribution. 
+Finally, we use these distributions to generate large number of
+samples and directly estimate the number of systems meeting a desired
+set of criteria.
 

### 2018-02-21 paper/paper.tex
edit

@@
 formation theories in a explicit cosmological context.
+
 This started with the suggestion of a Magellanic Plane, a flattened
@@
 \cite{1976RGOB..182..241K} and \cite{1976MNRAS.174..695L}.  
-
 \cite{2005A&A...431..517K} then quantified that the
@@
 challenge to the Lambda Cold Dark Matter (LCDM) paradigm.
-The same year it was recognized, using numerical simulations, that the
-satellites should not be compared with an spherically
-symmetric distribution given that Dark Matter halos in LCDM
-are expected to be triaxial
-\citep{2005MNRAS.363..146L, 2005ApJ...629..219Z}.
-Nevertheless, estimates of the chances to find simulated satellites as
-planar as in the MW were inconclusive. 
-\cite{2005MNRAS.363..146L} reported that
-satellite planes should be expected in every DM while
-\cite{2005ApJ...629..219Z} gave an estimate of a $2\%$ probability to
-have an arrangement as extreme as in observations.
+The same year it was recognized, using numerical simulations, that
+this comparison was unfair given given that Dark Matter halos in LCDM
+are expected to be triaxial and not spherical
+Nevertheless, some estimates of the chances to find simulated satellites as
+planar as in the MW 
+were as low as $2\%$ \citep{2005ApJ...629..219Z} while others expected
+planar satellite configurations in every DM halo
+\citep{2005MNRAS.363..146L}.
 
@@
 result, respectively) but precise figures are not quoted in either of
-these three reports. \citep{2015ApJ...815...19P,2016MNRAS.457.1931S}.
+these three reports. 
 Meanwhile, \cite{2013MNRAS.429.1502W} and \cite{2014ApJ...789L..24P} reported
@@
 In the case of M31, observational studies have found a planar satellite
-distribution in a subset of $15$ satellites out of the 
+distribution in a special subset of $15$ satellites out of the 
 total poulation of $27$ satellites \citep{2013ApJ...766..120C,
@@
 do not show any special feature.
-All published studies agree on the point that the global satellite distribution of
+All published studies agree on the point that the spatial distribution of
 the 15 to 27 brightest satellites are consistent with 
@@
 Table \ref{table:M31} and Table \ref{table:MW} summarize some more
-details on the results we have just mentioned.
+details on the results we have just mentioned \footnote{
 Those tables also include the results from this paper using the
-methodolgy we describe in the upcoming sections.
+methodolgy we describe in the upcoming sections.}.
 
@@
 Comparing results across simulations would require first
-characterizing the simulations at the high level parent samples.
+characterizing all the simulations at the high level parent samples,
+something that is difficult to do in practice.
 The second inconvenient is that it is hard to find systems that fully resemble
@@
 
-In this paper we surmount the first difficulty by setting as direct 
+In this paper we control the first effect by setting as direct 
 point of reference an spherical satellite distribution and not the
 simulations themselves.
-The spherical distribution is built from the data itself
+The spherical satellite distribution is built from the data itself
 (observational or simulated) by randomizing its angular position
@@
 \citep{2017AN....338..854P}. 
-We then characterize each satellite distribution in terms of the
+We characterize each satellite distribution in terms of the
 scalars describing its deviation from the spherical distribution.
-We handle the second difficulty by building an explicit analytic
+We then build an explicit analytic
 probability distribution of the deviations from asphericity; this

### 2018-02-21 paper/paper.tex
pdf

@@
 This started with the suggestion of a Magellanic Plane, a flattened
-structure of satellite galaxies around the MW, first suggested by
-\cite{1976RGOB..182..241K} and \cite{1976MNRAS.174..695L}.  
+structure of satellite galaxies and globular clusters around the MW,
+first suggested by \cite{1976RGOB..182..241K} and \cite{1976MNRAS.174..695L}.  
 \cite{2005A&A...431..517K} then quantified that the
@@
 The same year it was recognized, using numerical simulations, that
-this comparison was unfair given given that Dark Matter halos in LCDM
+this comparison was unfair given that Dark Matter halos in LCDM
 are expected to be triaxial and not spherical
@@
 
-Trying to reconcile and understand the seemly conflicting or inconclusive
-results on the MW has its origin on the frequentist fashion generally used to
-compute probabilities.
-Usually, the process starts by building a high level parent sample in the
+Some of the difficulty in trying to reconcile and understand the
+seemly conflicting or inconclusive results on the MW has its origin on
+the frequentist fashion generally used to compute probabilities.
+Usually, this process starts by building a high level parent sample in the
 simulation and then counting how many elements has a subset
-meeting some criteria. 
-The first inconvenient with this approach is that the probability
-estimate is made against whatever turns out to be typical in each
-simulation. 
-Comparing results across simulations would require first
+meeting some criteria. This has two incovenients.
+The first is that the probability estimate is made against whatever
+turns out to be typical in each simulation. 
+A fair comparison across simulations would require first
 characterizing all the simulations at the high level parent samples,
@@
 The second inconvenient is that it is hard to find systems that fully resemble
-the LG, this means that the high level parent sample has a small size
-making it hard to find elements that fit some criteria.
-
-In this paper we control the first effect by setting as direct 
+the LG while having enough resolution to say something about the
+satellites, this means that the high level parent sample has a small
+size, making it hard to derive robust probabilities by counting.
+
+In this paper we control the first effect by setting as a direct 
 point of reference an spherical satellite distribution and not the
@@
 The spherical satellite distribution is built from the data itself
-(observational or simulated) by randomizing its angular position
-around the central galaxy and keeping its radial distance fixed
-\citep{2017AN....338..854P}. 
-We characterize each satellite distribution in terms of the
-scalars describing its deviation from the spherical distribution.
+(observational or simulated) by randomizing the angular position
+of each satellite around the central galaxy and keeping its radial
+distance fixed \citep{2017AN....338..854P}. 
+We characterize the satellites in terms of the scalars describing its
+deviation from the spherical distribution. 
 We then build an explicit analytic
-probability distribution of the deviations from asphericity; this
+probability distribution for the deviations from asphericity; this
 solves the problem of having a common reference point to compare
@@
 desired number of samples that are by construction statistically
-compatible with simulations, overcoming the problem of having a small
+compatible with simulations; thus overcoming the problem of having a small
 number of systems in the parent simulations.
@@
 
+The rest of the paper is structured as follows. 
 In Section \ref{sec:DataSamples} we list the sources of the observational and

### 2018-02-21 paper/paper.tex
edit

@@
 chances ($<0.5\%$) found in \cite{2005A&A...431..517K}.
-This result was challenged by \cite{2009MNRAS.399..550L} who continue
+This result was challenged by \cite{2009MNRAS.399..550L} who continued
 to report high chances to find a planar configuration;
 two more recent numerical experiment with high resolution simulations
-(\cite{2013MNRAS.429..725S} and \cite{2016MNRAS.457.1931S}) report
+(\cite{2013MNRAS.429..725S} and \cite{2016MNRAS.457.1931S}) reported
 contradicting results (low and high chances to find the observational
@@
 these three reports. 
-Meanwhile, \cite{2013MNRAS.429.1502W} and \cite{2014ApJ...789L..24P} reported
-on new tests using high resolution simulations and cosmological
+Meanwhile, \cite{2013MNRAS.429.1502W} and \cite{2014ApJ...789L..24P} published
+the results new tests using high resolution simulations and cosmological
 volumes arriving at a chance of $6\%$ and $0.77\%$, respectively, to
@@
 total poulation of $27$ satellites \citep{2013ApJ...766..120C,
-2013Natur.493...62I}, although its brightest satellites
-do not show any special feature.
+2013Natur.493...62I}, although considering the satellites ranked by
+luminosity does not show any special feature.
 All published studies agree on the point that the spatial distribution of
-the 15 to 27 brightest satellites are consistent with 
-spherically symmetric distribution and easy to reproduce in LCDM
-simulations \citep{2006AJ....131.1405K,
-  2007MNRAS.374.1125M, 2013ApJ...766..120C}.    
+the 15 to 27 brightest satellites are consistent with  spherically
+symmetric distribution and easy to reproduce in LCDM simulations
+\citep{2006AJ....131.1405K,2007MNRAS.374.1125M, 2013ApJ...766..120C}.    
 Table \ref{table:M31} and Table \ref{table:MW} summarize some more
@@
 something that is difficult to do in practice. 
-The second inconvenient is that it is hard to find systems that fully resemble
-the LG while having enough resolution to say something about the
-satellites, this means that the high level parent sample has a small
-size, making it hard to derive robust probabilities by counting.
+The second inconvenient is that the systems that fully resemble
+the LG (i.e. its stellar mass content, morphology or kinematics) have
+a low cosmological number density, this means that for the current
+cosmological volumes in simulations the high level parent sample has a
+small size, making it hard to derive robust probabilities by counting.
 
@@
 
-The rest of the paper is structured as follows. 
+The rest of the paper describes in detail our implementation and
+results. It is structured as follows. 
 In Section \ref{sec:DataSamples} we list the sources of the observational and

### 2018-02-23 paper/paper.tex
edit

@@
 \end{tabular}
-\caption{Probability results derived in previous publications for the
-  triaxiality and/or root mean squared (RMS) height of M31 satellites.
+\caption{Probability to find  the triaxiality and/or root mean squared
+  (RMS) height of M31 satellites in LCDM simulations. 
 \label{table:M31}}
@@
 
-To summarize, we start by using asphericity to characterize in the
-same way simulations and observations. 
+To summarize, we use asphericity to characterize in the
+on equal footing simulations and observations. 
 Then, we build an explicit probability distribution for the asphericity and
-use simulations to estimate the parameters in this
-distribution. 
+use simulations to estimate the parameters in this distribution. 
 Finally, we use these distributions to generate large number of
@@
 simulated data to be used throughout the paper.
-In Section \ref{sec:SpatialMeasurements} we describe the methods we use to build halo pairs and 
+In Section \ref{sec:SpatialMeasurements} we describe the methods we
+use to build halo pairs and  
 characterize its satellite distributions.
@@
 \subsection{Describing Samples with the Inertia Tensor}
-We base all our results on the description provided by the inertia
+We base describe the satellites with the inertia
 tensor defined by the satellites' positions.
@@
 planar satellite distribution. 
-We also define the width, $w$, of the planar satellite distribution,
-as the standard deviation of all satellite distances to the plane
-defined by the vector $\hat{n}$.
+We also define the Root Mean Squared (RMS) width $w$, of the planar
+satellite distribution, as the standard deviation of the satellite
+distances to the plane defined by the vector $\hat{n}$.
 
@@
 \begin{itemize}
-\item Plane width, $w$.
+\item RMS plane width, $w$.
 \item $c/a$ axis ratio.
@@
 
-We compare every satellite distribution against its own spherically
+We compare each satellite distribution against its own spherically
 randomized distribution.
@@
 \begin{bmatrix}
--0.18\pm 0.04 & -0.41\pm 0.05  -0.20\pm 0.05
+-0.18\pm 0.04 & -0.41\pm 0.05 & -0.20\pm 0.05\\
 \end{bmatrix}
@@
 \begin{bmatrix}
--0.17\pm 0.04 & -0.40\pm 0.04 -0.23\pm 0.04\\
+-0.17\pm 0.04 & -0.40\pm 0.04 & -0.23\pm 0.04\\
 \end{bmatrix}
@@
 \begin{bmatrix}
--0.32\pm 0.04 -0.74\pm 0.07 -0.08\pm 0.05\\
+-0.32\pm 0.04 & -0.74\pm 0.07 &-0.08\pm 0.05\\
 \end{bmatrix}

### 2018-02-27 paper/paper.tex
edit abstract

@@
 outlier in the LCDM paradigm. 
-We suggest that to understand this atipicality will require quantifying
-the probability distribution for the satellite distribuition
-asphericity as a function of halo mass and large scale environment. 
-The approach presented here can facilitate that study and other comparisons
-between different numerical setups and choices to study satellites
-around LG pairs in simulations.  
+We suggest that understanding the reasons for this atipicality
+will require quantifying the asphericity probability distribution as a
+function of halo mass and large scale environment.
+The approach presented here can facilitate that kind study and other
+comparisons between different numerical setups and choices to study
+satellites around LG pairs in simulations.  
 \end{abstract}

### 2018-02-27 paper/paper.tex
edit intro

@@
 formation theories in a explicit cosmological context. 
-
-This started with the suggestion of a Magellanic Plane, a flattened
+This started with the suggested existence of a Magellanic Plane, a flattened
 structure of satellite galaxies and globular clusters around the MW,
-first suggested by \cite{1976RGOB..182..241K} and \cite{1976MNRAS.174..695L}.  
-\cite{2005A&A...431..517K} then quantified that the
+by \cite{1976RGOB..182..241K} and \cite{1976MNRAS.174..695L}.  
+Fourty years later \cite{2005A&A...431..517K} quantified that the
 highly planar distribution of the 11 classical MW satellites has less
@@
 this comparison was unfair given that Dark Matter halos in LCDM
-are expected to be triaxial and not spherical
+are expected to be triaxial and not spherical.
 Nevertheless, some estimates of the chances to find simulated satellites as
@@
 contradicting results (low and high chances to find the observational
-result, respectively) but precise figures are not quoted in either of
-these three reports. 
+result, respectively) but precise figures were not quoted in these three reports. 
 Meanwhile, \cite{2013MNRAS.429.1502W} and \cite{2014ApJ...789L..24P} published
-the results new tests using high resolution simulations and cosmological
+the results of new tests using high resolution simulations and cosmological
 volumes arriving at a chance of $6\%$ and $0.77\%$, respectively, to
@@
 Usually, this process starts by building a high level parent sample in the
-simulation and then counting how many elements has a subset
-meeting some criteria. This has two incovenients.
+simulation and then counting how many elements has the subset
+meeting some criteria. 
+This has two incovenients.
 The first is that the probability estimate is made against whatever
@@
 We then build an explicit analytic
-probability distribution for the deviations from asphericity; this
-solves the problem of having a common reference point to compare
-simulations. 
-We then use different simulations to estimate the parameters in this
+probability distribution for the asphericity; this solves the problem
+of having a common reference point to compare simulations. 
+We then use a simulation to estimate the parameters in this
 distribution to later use it as a parent sample to generate any
 desired number of samples that are by construction statistically
-compatible with simulations; thus overcoming the problem of having a small
-number of systems in the parent simulations.
+compatible with the simulation; thus overcoming the problem of having
+a small number of systems in the parent simulations.
 

### 2018-02-27 paper/paper.tex
edit intro

@@
 small size, making it hard to derive robust probabilities by counting.   
-
-In this paper we control the first effect by setting as a direct 
-point of reference an spherical satellite distribution and not the
-simulations themselves.
+In this paper we present and demostrate a method to overcome these two
+limitations.
+
+We control the first effect by setting as a direct point of reference
+an spherical satellite distribution and not the simulations themselves.
 The spherical satellite distribution is built from the data itself
@@
 deviation from the spherical distribution. 
-We then build an explicit analytic
-probability distribution for the asphericity; this solves the problem
-of having a common reference point to compare simulations. 
-We then use a simulation to estimate the parameters in this
-distribution to later use it as a parent sample to generate any
-desired number of samples that are by construction statistically
-compatible with the simulation; thus overcoming the problem of having
-a small number of systems in the parent simulations.
-
-To summarize, we use asphericity to characterize in the
-on equal footing simulations and observations. 
+We then build an explicit analytic probability distribution for the
+asphericity; this solves the problem of having a common reference
+point to compare simulations.  
+We use a simulation to estimate the parameters in this distribution to
+later use it as a parent sample to generate any desired number of
+samples that are by construction statistically compatible with the
+simulation; thus overcoming the problem of having a small number of
+systems in the parent simulations.
+
+To summarize, we use asphericity to characterize on equal footing
+simulations and observations.  
 Then, we build an explicit probability distribution for the asphericity and
-use simulations to estimate the parameters in this distribution. 
-Finally, we use these distributions to generate large number of
+use simulations to estimate its free parameters.
+Finally, we use these distributions to generate large numbers of
 samples and directly estimate the number of systems meeting a desired

### 2018-02-27 paper/paper.tex
edit conclusions

@@
 
-In this paper we develop and demostrate a method to quantify the
-asphericity of the satellite distribution in the around the MW and M31.  
-In the interest of keeping the method straightforward and robust we do
-not look for planes in subsets of satellites or coherent kinematical
-structures. 
-We focus on the asphericity estimates for a fixed number of the
-brightest satellites around each galaxy.
+In this paper we developed and demostrated a method to quantify the
+asphericity of the satellite distribution around the MW and M31.  
+In the interest of keeping the method straightforward and robust we
+focus on the asphericity estimates for a fixed number of the brightest
+satellites around each galaxy.
 
@@
 Then, we measure the same quantities for the same set of points after
-a process of spherical randomization.
+the spherical randomziation process.
 Finally, we renormalize the initial results to the mean value and
@@
 
-We find that these normalized quantities are well described by
-a multivariate gaussian distribution. 
-We fit estimate the mean and covariance of this distributions using
+We found that these normalized quantities are well described by
+a multivariate gaussian distribution in spite of the original
+quantities being bound.
+We estimated the mean and covariance of this distributions using
 the results of LG pairs coming from three different numerical
-simulations, we inally compare the observational results against the
-distributions derived from the simulations: Illustris-1,
-Illustris-1-Dark and ELVIS.
-
-We find that in the best case (Illustris1-DarkMatter) the deviation
-from asphericity in the observed LG is only expected in $3\pm2$
-pairs out of a sample of $10^4$ isolated pairs. This places the LG as
-a $3\sigma$ outlier.   
+simulations (Illustris-1, Illustris-1-Dark and ELVIS). 
+Finally, we compared the observational results against the
+distributions derived from the simulations
+
+We found that in the best case (Illustris1-Dark) the degree of
+asphericity in the observed LG is only expected in $3\pm2$  pairs out
+of a sample of $10^4$ isolated pairs. 
+This places the LG as a $3\sigma$ outlier.   
 The weight to explain this atypical result is not distributed equally
@@
 from LCDM, the MW shows aspherical deviations in plane width and the
-major-to-minor axis ratio highly atypical in the 
-framework of LCDM. 
-We estimate that with the M31 between $37\%$ and $58\%$ of the pairs
-pairs show normalized characteristics larger than M31, while
+major-to-minor axis ratio highly atypical in the  framework of LCDM,
+confirming the original hint by \cite{2005A&A...431..517K} and more
+recent results by \cite{2015ApJ...815...19P}. 
+We estimated that with the M31 between $37\%$ and $58\%$ of the pairs
+pairs show aspherical characteristics larger than M31, while
 this fraction drops to less than $1\%$ for the MW. 
-These fractions are robust to changes in the numerical simulations and to
-the criteria used to define the pairs.
-
-The highly aspherical distribution of the brightest MW satellites is
-in stark contrast to the more spherical M31 distribution.
-Furthermore, the atipicallity of the MW distribution in the LCDM
-context adds up to the also atypical presence of two bright satellite
-galaxies.
-
-The focus of our approach is building explicit probability
+These fractions are robust to changes in the numerical simulations
+and, the criteria used to define the pairs and the methods used to
+estimate the parameters of the multivariate normal distribution.
+
+The focus of our approach was building an explicit probability
 distributions for the observables of interest, instead of trying to
@@
 This approach is particularly useful in the case of atypical
-observables. 
-Building the probability distribution allows for an atypicallity
+observables as its the case of interest, as it allows for an atypicallity
 quantification without needing to build explicit samples of objects
 that are already scarce and difficult to find in simulations.
-
 An extension of this framework to outliers in higher order deviations
-(i.e. a \emph{subset} of satellites that are in a plane or
-coherent \emph{velocity} structures) should also be possible, similar
-to the work presented by XX\cite{2013Natur.493...62I} on the satellite velocity anisotropy.
-
-From the results we derive in this paper we also estimate that a
-cosmological volume of at least $( XX )^3$ is required to find a halo pair
-that shows similar asphericity characteristics as the LG. 
-This atypical satellite distribution should be seen as an opportunity
-to constrain in high detail the initial conditions and environment
-that allowed such a pattern to emerge.
+(i.e. coherent \emph{velocity} structures) should also be possible, 
+provided that an explicit probability distribution for the scalars of
+interest can be built.
+
+The highly aspherical satellite distribution in the MW is another piece of
+information that points at an atypical configuration in LCDM.
+We also have the number of satellites as bright as the Mageallanic
+Clouds, only expected in $5\%$ of galaxies \citep{2011ApJ...743..117B}
+and the atypical kinematics of M31 with a very low tangential velocity,
+only expected in less than $1\%$ of the pairs with similar
+environmental characteristics \citep{ForeroRomero2013}. 
+In other words, if we were in a typical LG pair in LCDM, the MW should
+have zero satellites like the Magellanic Clouds, it's satellite
+distribution should be similar to M31's and M31 should have a larger
+tangential velocity.
+
+The LG atypicality should be seen as an opportunity to constrain in
+high detail the environment that allowed such a pattern to emerge. 
+Although local correlations between LG assembly, pair kinematics, halo shapes and
+satellite distributions are expected in LCDM
+\citep{2011MNRAS.417.1434F,2014MNRAS.443.1090F,2015ApJ...799...45F,2015MNRAS.452.1052L},
+we claim that detailed studies of the satellite asphericity as a function
+of halo mass and cosmic web environment are still missing to
+understand what fearures in the initial conditions of our Local Group
+are responsible for the assembly extreme features observed in its satellite
+distribution.
 

### 2018-02-27 paper/paper.tex
agradecimientos

@@
 this fraction drops to less than $1\%$ for the MW. 
-These fractions are robust to changes in the numerical simulations
-and, the criteria used to define the pairs and the methods used to
+These fractions are robust to changes in the numerical simulations, 
+the criteria used to define the pairs and the methods used to
 estimate the parameters of the multivariate normal distribution.
@@
 high detail the environment that allowed such a pattern to emerge. 
-Although local correlations between LG assembly, pair kinematics, halo shapes and
+Although broad correlations between LG assembly, pair kinematics, halo shapes and
 satellite distributions are expected in LCDM
@@
 of halo mass and cosmic web environment are still missing to
-understand what fearures in the initial conditions of our Local Group
-are responsible for the assembly extreme features observed in its satellite
+understand what fearures in the initial conditions of our LG
+are responsible for the extreme features observed in its satellite
 distribution.
@@
 \section*{Acknowledgements} 
-We acknowledge Universidad de los Andes and COLCIENCIAS (Project -
-XXX) for the computing resources used in this project.
+We acknowledge financial support from: Universidad de Los Andes
+(Colombia); COLCIENCIAS (c\'odigo 120471250459, contrato FP44842-287-
+2016); the European Union’s Horizon 2020 Research and Innovation
+Programme under the Marie Sk\l{}odowska-Curie grant agreement No 73437
+(LACEGAL).
 

### 2018-02-27 paper/paper.tex
edit

@@
 
-The base for our analysis is the catalog compiled in
-\citep{2014yCat..74351928P} which reports information on all 
+The base for our analysis is the catalog compiled by
+\cite{2014yCat..74351928P} which reports information on all 
 galaxies within 3 Mpc around the Sun to that date. 
 Detailed description of the compiled catalog can be found in
-\citep{2013MNRAS.435.1928P}, here we summarize the relevant features
+\cite{2013MNRAS.435.1928P}, here we summarize the relevant features
 for the current study.
-
 The information in the catalogue is based on the catalogue compiled by
@@
 We end up with a total of 20 pairs in Illustris-1.
-In Illustris-1-DM we use the center of mass position of the 27 pairs
+
+In Illustris-1-Dark we use the center of mass position of the 27 pairs
 in Illustris-1 to find the matching halo pairs.
 After discarding the pairs with less than 15 detected subhalos in one
-of the halos we end up with a total of 24 pairs. 
+of the halos we end up with a total of 24 pairs in Illustris-1-Dark. 
 This corresponds to a pair number density of $\sim 2 \times10^{-5}$
@@
 Although Illustris-1 has stellar particles, we do not use their
-properties to select the satelite population because the smallest
-galaxies are barely resolved in stellar mass at magnitudes of
-$M_V=-9$, close to the limit of the 11 ``classical'' MW satellites.
-We use instead the dark matter information as the smallest sub-halos
-we care about are sampled with at least $40$ particles.  
-%comentario: este último criterio no me parece que esté claramente
-%descrito
-
-Both in Illustris-1 and Illustris-1-DM we chose the satellite samples
+properties to select the satelite population.
+The smallest galaxies are barely resolved in stellar mass at
+magnitudes of $M_V=-9$, close to the limit of the 11 ``classical'' MW
+satellites, we use instead the dark matter information. 
+Both in Illustris-1 and Illustris-1-Dark we chose the satellite samples
 by ranking the subhalos in decreasing order of its current maximum
 circular velocity and select the first $N_p$ halos in the list.  
+Under these conditions the smallest sub-halos are sampled with at least $40$ particles.  
 The results presented here correspond to $11\leq N_p\leq 15$.
@@
 Mpc$^{-3}$, this is a factor $\sim 2.5$ lower than the pair number density
-we find in the Illustris data.
+we find in the Illustris-1 data.
 There were a total of 146 pairs that met those criteria, but only $12$
@@
 The dark matter particle resolution in these resimulations is
-$1.9\times 10^5$, a thousand times larger than Illustris-1.
+$1.9\times 10^5$, a thousand times better than Illustris-1.
 In this paper we only use the results from these $12$ resimulated pairs.
@@
 We compare the joint satellite distributions in the MW and M31 at fixed
-satellite number, $N_s$.
+satellite number, $N_p$.
 This means that the magnitude cut corresponding to the faintest
 satellite included in the sample is different in each case.
-We make this choice for two reasons. 
-First, to be sure that there is a non-zero number of satellites in the
-simulations to make the computations.  
-Second, to rule out the influence of satellite numbers in the
-statistics.
+We make this choice to to rule out the influence of satellite numbers
+in the statistics.
 
 We compute the satellite statistics for 11 up to 15 satellites.
-The lower limit corresponds to the number of classical Milky Way
-satellites.
-The upper limit corresponds to the maximum number of satellites that
-can be resolved in both halos for most of the isolated pairs in Illustris-1.
-In simulations we rank the subhalos by their maximum
-circular velocity, in observations we rank the satellites by its $M_V$
+The lower limit corresponds to the number of classical MW satellites,
+while the upper limit corresponds to the minimum number of M31
+satellites included in the analysis.
+In simulations we rank the subhalos by their maximum circular
+velocity, in observations we rank the satellites by its $M_V$
 magnitude.

### 2018-02-27 paper/paper.tex
edit

@@
 
-We also use two kinds of satellite distributions. 
-The first keeps the positions for the satellites fixed as provided in
-the observations/simulations; the second randomizes the angular positions of
-the satellites around the central galaxy while keeping its radial
-distance fixed. The randomization process is done 1000 times for each
-galaxy.
-
 \begin{table*}
@@
 \subsection{Describing Samples with the Inertia Tensor}
-We base describe the satellites with the inertia
+
+We describe the satellites with the inertia
 tensor defined by the satellites' positions.
@@
 \begin{equation}
-{\bf{\bar{I}}} = \sum_{k=1}^{N_s}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
+{\bf{\bar{I}}} = \sum_{k=1}^{N_p}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
   (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
@@
 planar satellite distribution. 
-We also define the Root Mean Squared (RMS) width $w$, of the planar
-satellite distribution, as the standard deviation of the satellite
-distances to the plane defined by the vector $\hat{n}$.
-
-To summarize we characterize the satellite distribution by for
+We also define the Root Mean Squared (RMS) plane width $w$ as the
+standard deviation of the satellite distances to the plane defined by
+the vector $\hat{n}$.
+
+To summarize we characterize the satellite distribution with the following
 quantities obtained from the inertia tensor: 
@@
 
-\subsection{Comparing Satellite Samples}
+\subsection{Characterizing Asphericity}
 
@@
 deviation of the randomized samples.
-
-This allows us to make a first comparison. 
-The observed/simulated
-distribution against its randomized version. 
-The second intermediate comparison we make is of the observations against
-the simulations.
-The final comparison is between the normalized quantities, both
-observed and simulated.
-
-The comparison between the normalized quantities is the one that
-carries the important information about the deviations from
-spheriticy. 
-We do not want to directly compare how the observations
-deviate from simulations but to compare the deviations from
-asphericity in observations and simulations.
-
-\subsection{Describing joint satellite distributions}
+These normalized quantities are used to build the explicit probability
+distributions for the scalars describing aesphericity.
+
+\subsection{Building an explicit asphericity probability distribution}
 
@@
 to a normal distribution with mean and standard deviation computed
-from the mean and standard deviation from the data itself. 
-We find that the distributions for the normalized $w$, $c/a$ and $b/a$
-are consistent with gaussian ditributions.
+from the mean and standard deviation estimated from the data.
+Although the physical quantities of interests are bound, unlike the
+random variables from a normal distribution, we find that the
+distributions for the normalized $w$, $c/a$ and $b/a$ are indeed
+consistent with gaussian ditributions.
 
@@
 with a jackknife technique. 
-That is, out of the the $n$ pairs we have, we perfom $n$ different
-covariance and mean value measurements using only $n-1$ pairs. 
+That is, out of the the $n$ pairs in each simulation, we perfom $n$
+different covariance and mean value measurements using only $n-1$ pairs. 
 The reported covariance and mean values correspond to the average of

### 2018-02-27 paper/paper.tex
edit

@@
 The uncertainty in the observations is computed from the results with
-different number of satellites, while in the simulations it
-corresponds to the standard deviation over different halos.
-
-The observed widths are always smaller than its randomized version.
+different number of satellites; in the simulations it  corresponds to
+the standard deviation over different halos.
+
+The observed widths $w$ are always smaller than its randomized version.
 For M31 there is barely a ratio of $0.92$ between observed and
@@
 spherical randomization. 
+This confirms the extreme planar distribution for the MW and the more
+spherical distribution for the M31.
 
@@
 The plots in the main body of the paper correspond to the
-Illustris1-Dark simulation; the results from the other simulations are
-included in the Appendix.
+Illustris-1-Dark simulation; the results from the other simulations
+are included in the Appendix \ref{appendix:plots}.
 
@@
 
-%% Alignments between galaxies, satellite systems and haloes
-%% https://arxiv.org/pdf/1605.01728.pdf
-
-%M31 mass
-%% https://arxiv.org/abs/1410.0017
-
-%MW mass
-%https://arxiv.org/abs/1407.1078
-
 \appendix
@@
 \section{Physical Characteristics of the Isolated Pairs samples}
+\label{appendix:physical}
 
@@
 \centering
-\includegraphics[width=0.34\textwidth]{int_distro_LG_v_rad.pdf}
-\includegraphics[width=0.34\textwidth]{int_distro_LG_d.pdf}
-\includegraphics[width=0.34\textwidth]{int_distro_M31_vmax.pdf}
-\includegraphics[width=0.34\textwidth]{int_distro_MW_vmax.pdf}
+\includegraphics[width=0.30\textwidth]{int_distro_LG_v_rad.pdf}
+\includegraphics[width=0.30\textwidth]{int_distro_LG_d.pdf}
+\includegraphics[width=0.30\textwidth]{int_distro_M31_vmax.pdf}
+\includegraphics[width=0.30\textwidth]{int_distro_MW_vmax.pdf}
 \caption{Physical characteristics of the LG pairs selected in the
@@
 
+\section{Covariance Matrices and Mean value vectors}
+\label{appendix:covariance}
+\subsection{Illustris-1}
+
+\subsubsection{M31}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+0.83\pm 0.03  & 0.78\pm 0.04  & 0.41\pm 0.04\\
+0.78\pm 0.04  & 1.16\pm 0.05 & -0.15\pm 0.05\\
+0.41\pm 0.04 & -0.15\pm 0.05 & 0.96\pm 0.04\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.18\pm 0.04 & -0.41\pm 0.05 & -0.20\pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsubsection{MW}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 0.78\pm 0.06 & 0.63 \pm 0.07  & 0.40 \pm 0.03\\
+  0.63\pm 0.07 & 0.69 \pm 0.08 &  0.06 \pm 0.02\\
+  0.40\pm 0.03 & 0.06 \pm 0.02 &  0.61\pm 0.04\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.17\pm 0.04 & -0.40\pm 0.04 & -0.23\pm 0.04\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1-Dark}
+
+\subsubsection{M31}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 1.50\pm 0.08 & 1.27\pm 0.08 & 0.64\pm 0.04\\
+  1.27\pm 0.08 &  1.31\pm 0.08&  0.28\pm 0.04\\
+  0.64\pm 0.04 &  0.28\pm 0.04 & 0.70\pm 0.04\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.37\pm 0.05& -0.55\pm 0.05 & -0.13\pm 0.03\\
+\end{bmatrix}
+\]
+
+\subsubsection{MW}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 1.03\pm 0.05 & 0.94\pm 0.05  & 0.36\pm 0.03\\
+  0.94\pm 0.05 & 1.24\pm 0.07 & -0.18\pm 0.04\\
+  0.36\pm 0.03 & -0.18\pm 0.04  & 0.86\pm 0.03\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.45\pm 0.04 & -0.61\pm 0.05 & -0.31\pm 0.04\\
+\end{bmatrix}
+\]
+
+\subsection{ELVIS}
+
+\subsubsection{M31}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 1.60\pm 0.19  & 1.22\pm 0.14 & 0.70 \pm 0.09\\
+  1.22\pm 0.14 &  1.08\pm 0.10 & 0.35 \pm 0.05\\
+  0.70\pm 0.09 & 0.35\pm 0.05  & 0.63 \pm 0.10\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.18\pm 0.08 & -0.28\pm 0.07 &-0.22\pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsubsection{MW}
+
+\[
+\Sigma= 
+\begin{bmatrix}
+ 0.45\pm 0.04 & 0.61\pm0.09 & -0.11\pm0.09 \\
+  0.61\pm0.09 & 1.21\pm0.17 & -0.63\pm0.09\\
+ -0.11\pm0.05 & -0.63\pm0.09 & 0.64\pm0.06\\
+\end{bmatrix}
+\]
+
+\[
+\mu= 
+\begin{bmatrix}
+-0.32\pm 0.04 & -0.74\pm 0.07 &-0.08\pm 0.05\\
+\end{bmatrix}
+\]
+
 \section{Results from ELVIS and Illustris1}
+\label{appendix:plots}
 \begin{figure*}
@@
 
-\newpage
-\newpage
-\section{Covariance Matrices and Mean value vectors}
-\subsection{Illustris-1}
-
-\subsubsection{M31}
-
-\[
-\Sigma= 
-\begin{bmatrix}
-0.83\pm 0.03  & 0.78\pm 0.04  & 0.41\pm 0.04\\
-0.78\pm 0.04  & 1.16\pm 0.05 & -0.15\pm 0.05\\
-0.41\pm 0.04 & -0.15\pm 0.05 & 0.96\pm 0.04\\
-\end{bmatrix}
-\]
-
-\[
-\mu= 
-\begin{bmatrix}
--0.18\pm 0.04 & -0.41\pm 0.05 & -0.20\pm 0.05\\
-\end{bmatrix}
-\]
-
-\subsubsection{MW}
-
-\[
-\Sigma= 
-\begin{bmatrix}
- 0.78\pm 0.06 & 0.63 \pm 0.07  & 0.40 \pm 0.03\\
-  0.63\pm 0.07 & 0.69 \pm 0.08 &  0.06 \pm 0.02\\
-  0.40\pm 0.03 & 0.06 \pm 0.02 &  0.61\pm 0.04\\
-\end{bmatrix}
-\]
-
-\[
-\mu= 
-\begin{bmatrix}
--0.17\pm 0.04 & -0.40\pm 0.04 & -0.23\pm 0.04\\
-\end{bmatrix}
-\]
-
-\subsection{Illustris-1-Dark}
-
-\subsubsection{M31}
-
-\[
-\Sigma= 
-\begin{bmatrix}
- 1.50\pm 0.08 & 1.27\pm 0.08 & 0.64\pm 0.04\\
-  1.27\pm 0.08 &  1.31\pm 0.08&  0.28\pm 0.04\\
-  0.64\pm 0.04 &  0.28\pm 0.04 & 0.70\pm 0.04\\
-\end{bmatrix}
-\]
-
-\[
-\mu= 
-\begin{bmatrix}
--0.37\pm 0.05& -0.55\pm 0.05 & -0.13\pm 0.03\\
-\end{bmatrix}
-\]
-
-\subsubsection{MW}
-
-\[
-\Sigma= 
-\begin{bmatrix}
- 1.03\pm 0.05 & 0.94\pm 0.05  & 0.36\pm 0.03\\
-  0.94\pm 0.05 & 1.24\pm 0.07 & -0.18\pm 0.04\\
-  0.36\pm 0.03 & -0.18\pm 0.04  & 0.86\pm 0.03\\
-\end{bmatrix}
-\]
-
-\[
-\mu= 
-\begin{bmatrix}
--0.45\pm 0.04 & -0.61\pm 0.05 & -0.31\pm 0.04\\
-\end{bmatrix}
-\]
-
-\subsection{ELVIS}
-
-\subsubsection{M31}
-
-\[
-\Sigma= 
-\begin{bmatrix}
- 1.60\pm 0.19  & 1.22\pm 0.14 & 0.70 \pm 0.09\\
-  1.22\pm 0.14 &  1.08\pm 0.10 & 0.35 \pm 0.05\\
-  0.70\pm 0.09 & 0.35\pm 0.05  & 0.63 \pm 0.10\\
-\end{bmatrix}
-\]
-
-\[
-\mu= 
-\begin{bmatrix}
--0.18\pm 0.08 & -0.28\pm 0.07 &-0.22\pm 0.05\\
-\end{bmatrix}
-\]
-
-\subsubsection{MW}
-
-\[
-\Sigma= 
-\begin{bmatrix}
- 0.45\pm 0.04 & 0.61\pm0.09 & -0.11\pm0.09 \\
-  0.61\pm0.09 & 1.21\pm0.17 & -0.63\pm0.09\\
- -0.11\pm0.05 & -0.63\pm0.09 & 0.64\pm0.06\\
-\end{bmatrix}
-\]
-
-\[
-\mu= 
-\begin{bmatrix}
--0.32\pm 0.04 & -0.74\pm 0.07 &-0.08\pm 0.05\\
-\end{bmatrix}
-\]
-
 \end{document}

### 2018-02-27 paper/paper.tex
edit

@@
 \caption{Plane width characterization in observations and
-  simulations (Illustris1-Dark in this case). In all panels the
+  simulations (Illustris-1-Dark in this case). In all panels the
   horizontal/vertical axis corresponds to the  M31/MW or the
@@
   normalized values for the plane width $w$, $c/a$ ratio and $b/a$
-  ratio from the Illustris1-Dark results.  
+  ratio from the Illustris-1-Dark results.  
   Left/right panel correspond to M31/MW respectively.  
@@
 the normalized width.  
-This panel tells the same story as the middle panel. The M31 values
-are typical while the MW is an outlier. 
+This panel tells the same story as the middle panel. 
+The M31 values are typical while the MW is an outlier. 
 The added value of the data in this panel is that it is the normalized
@@
 This is the data used to build the mean values vector and covariance
-matrix described in Equation \ref{}
+matrix described in Equation \ref{eq:multivariate}.
 
@@
   MW halos showing the same degree of atipicality as the Local Group if drawn
-  from a sample of 10000 isolated pairs. 
-  The distributions correspond to results derived from Illustris-DM, Illustris,
+  from a sample of $10^4$ isolated pairs. 
+  The distributions correspond to results derived from Illustris-1-Dark, Illustris,
   and ELVIS data.
-  In the most optimistic case (Illustris-DM), $1\%$ of the pairs have
-  two halos with properties similar to the LG. In the case of
-  Illustris this percentage drops to $0.1\%$ and $0.01\%$ for ELVIS.
+  In the most optimistic case (Illustris-1-Dark), $1\%$ of the pairs have
+  two halos with properties similar to the LG. 
+  In the case of Illustris-1 this percentage drops to $0.1\%$ and
+  $0.01\%$ for ELVIS. 
 \label{fig:expected_number}}
@@
 Figure \ref{fig:scatter_ba_ratio} shows the results for the minor to
-major axis ratio with the same layout as Figure \ref{fig_scatter_ca_ratio}
+major axis ratio with the same layout as Figure \ref{fig:scatter_ca_ratio}
 In all cases of comparison (against randomized distribution
@@
  Eq.\ref{eq:multivariate} from the normalized quantities obtained from
- the Illlustris1-Dark simulation.
-The distributions in this Figure are computed from $10^6$ with the multivariate
-gaussian. 
-Similar plots for Illustris1 and ELVIS are in the Appendix.
+ the Illustris-1-Dark simulation.
+The distributions in this Figure are computed from $10^6$ points
+generated with the multivariate gaussian. 
+Similar plots for Illustris-1 and ELVIS are in the Appendix \ref{appendix:plots}.
 The values for all the covariance matrices and mean vectors
-foricorresponding to all the simulations are listed in the Appendix.
+foricorresponding to all the simulations are listed in the Appendix \ref{appendix:covariance}.
 
 This result nicely summarizes the results we had in the previous
-sections. The left triangular plot shows how M31 falls into the middle of all 2D
-distributions and is always close to the peak and within the $1-\sigma$
+sections. The left hand triangular plot shows how M31 falls into the middle of all 2D
+distributions and is always close to the peak and within the $1\sigma$
 range. 
-The right plot clearly places the MW observations outside the
+The right hand plot clearly places the MW observations outside the
 $3\sigma$ range in the joint distributions that involve the width
@@
 In both cases the strongest positive correlation is present for the
-width and the $c/a$ axis ratio. A weaker but still positive
-correlation is present for the width and the $b/a$ axis ratio.
+width and the $c/a$ axis ratio. A weaker  correlation is present for
+the width and the $b/a$ axis ratio.
 
@@
 Among the three simulations, the results infered from ELVIS data show
-the lowest fraction of M31 and MW systems; for Illustris1-Dark we have
-the highest fraction of M31/MW systems. The results from Illustris1
+the lowest fraction of M31 and MW systems; for Illustris-1-Dark we have
+the highest fraction of M31/MW systems. The results from Illustris-1
 are in between these two, but closer to ELVIS.
@@
 $\sim 160$ \kms, $\sim 150$ \kms and $\sim 120$ \kms in the ELVIS,
-Illustris1 and Illustris1-Dark simulations, respectively.
+Illustris-1 and Illustris-1-Dark simulations, respectively.
 For the M31 halo this median velocity is $\sim 200$\kms both for the
-ELVIS and Illustris1 simulations, while for the Illustris1-Dark it is
+ELVIS and Illustris1 simulations, while for the Illustris-1-Dark it is
 $\sim 160$ \kms.
@@
 \caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
-  computed from the Illustris1 data.
+  computed from the Illustris-1 data.
 \label{fig:scatter_illustris}}
@@
 Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
-computed from the Illustris1 data.
+computed from the Illustris-1 data.
 \label{fig:correlations_illustris}}

### 2018-03-01 paper/paper.tex
edit

@@
 Detailed results differ among the simulations suggesting a strong
-influence of the typical Dark Matter (DM) halo mass in the LG samples.
+influence of the typical Dark Matter (DM) halo mass in the LG samples
+and simulated baryonic effects.
 However, there are three common trends.
@@
 function of halo mass and large scale environment.
-The approach presented here can facilitate that kind study and other
+The approach presented here can facilitate that kind of study and other
 comparisons between different numerical setups and choices to study
@@
 \citep{2006AJ....131.1405K,2007MNRAS.374.1125M, 2013ApJ...766..120C}.
+%comentario: no estoy segura de que el paper de Conn esté bien citado acá.
+el dice "It is clear that while the satellites of M31 when taken as a whole are no more planar than one can expect from a random distribution, a subset consisting of roughly half the sample is remarkably planar".
+Y en esta citación "15 to 27 brightest satellites" me parece que puede sonar contradictorio con lo que dice Conn.
 Table \ref{table:M31} and Table \ref{table:MW} summarize some more
@@
 Reference & Target Measurement & Parent Simulation & Probability ($\%$)\\\hline
-\text{\cite{2006AJ....131.1405K}} & RMS height in 15 brightest
+\text{\cite{2006AJ....131.1405K}} & RMS width in 15 brightest
 satellites & Monte Carlo satellite distributions with a power law
 radial distribution & $87-99$\\
-\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in 16 brightest satellites & Monte Carlo from an spherical power law radial
+\text{\cite{2007MNRAS.374.1125M}} & $c/a$ ratio and RMS width in 16 brightest satellites & Monte Carlo from a spherical power law radial
 distribution & $17$\\
-\text{\cite{2013ApJ...766..120C}}& RMS height in the 27 brightest
+\text{\cite{2013ApJ...766..120C}}& RMS width in the 27 brightest
 satellites & Monte Carlo randomized satellite distribution & High\\
-This Work & Triaxiality and RMS height in 11-15 brightest
+This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 24 halos from selected pairs in a cosmological N-body Dark Matter only simulation ($\sim
 10^{6}$\Msun particle mass resolution)& 56 \\
-This Work & Triaxiality and RMS height in 11-15 brightest
+This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 20 halos from selected pairs in a cosmological N-body hydro simulation ($\sim
 10^{6}$\Msun particle mass resolution)& 27 \\
-This Work & Triaxiality and RMS height in 11-15 brightest
+This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 12 high resolution DM only N-body simulations ($\sim
@@
 Reference & Target Measurement & Parent Simulation & Probability ($\%$)\\\hline
-\text{\cite{2005A&A...431..517K}} & RMS height in 11 classical
-satellites & Monte Carlo from an spherical power law
+\text{\cite{2005A&A...431..517K}} & RMS width in 11 classical
+satellites & Monte Carlo from a spherical power law
 radial distribution. & $<0.5$ \\
-\text{\cite{2005MNRAS.363..146L}} & Triaxiality of 11 classical
+\text{\cite{2005MNRAS.363..146L}} & $c/a$ ratio of 11 classical
 satellites & 6 high resolution DM only N-body simulations ($\sim10^5$
 \Msun\ particle mass resolution). & High\\ 
-\text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in 
+\text{\cite{2005ApJ...629..219Z}} & $c/a$ ratio and disk height in 
 11 classical satellites & 3 high resolution DM only N-body
 simulations. ($\sim10^6$ \Msun\ particle mass resolution) & 2 \\
-\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in 11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
+\text{\cite{2007MNRAS.374.1125M}} & $c/a$ ratio and RMS width in 11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
 simulations & $<0.5$\\
-\text{\cite{2009MNRAS.399..550L}}& Triaxiality in 11 classical satellites & 436 halos from a
+\text{\cite{2009MNRAS.399..550L}}& $c/a$ ratio in 11 classical satellites & 436 halos from a
 cosmological N-body simulation ($1.3\times 10^{8}$\Msun\ particle mass)
@@
 10^3$\Msun particle mass resolution) of individual halos & Low \\
-\text{\cite{2013MNRAS.429.1502W}}& $c/a$ ratio or RMS height in 11 brightest
+\text{\cite{2013MNRAS.429.1502W}}& $c/a$ ratio or RMS width in 11 brightest
 satellites & 1686 halos from a cosmological DM only N-body simulation
@@
 mass resolution) & High\\
-This Work & Triaxiality and RMS height in 11-15 brightest
+This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 24 halos from selected pairs in a cosmological N-body
 Dark Matter only simulation ($\sim 10^{6}$\Msun particle mass resolution)& 3\\
-This Work & Triaxiality and RMS height in 11-15 brightest
+This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 20 halos from selected pairs in acosmological N-body
 hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& 0.6 \\
-This Work & Triaxiality and RMS height in 11-15 brightest
+This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 12 high resolution DM only N-body simulations ($\sim
@@
 We control the first effect by setting as a direct point of reference
-an spherical satellite distribution and not the simulations themselves.
+a spherical satellite distribution and not the simulations themselves.
 The spherical satellite distribution is built from the data itself
@@
 use to build halo pairs and  
-characterize its satellite distributions.
+characterize their satellite distributions.
 In Section \ref{sec:results} we present our results to finally
@@
 In this coordinate system the $z$-axis points towards the Galactic north pole, the
-$x$-axis points in the direction from the Sun to the Galactic centre,
+$x$-axis points in the direction from the Sun to the Galactic center,
 and the $y$-axis points in the direction of the Galactic rotation.
@@
 For both the M31 and MW we only use the 11 to 15 brightest satellites (using
-$M_V$ magnitudes) within a distance of $300$kpc to its central galaxy.
+$M_V$ magnitudes) within a distance of $300$kpc from its central galaxy.
 The satellites included for the MW analysis are: 
@@
 hole and super massive black hole feedback. 
-The simulation volume is a cubic box of $75$ \Mpch\ on a side.
+The simulation volume is a cubic box with a $75$ \Mpch\ side.
 The cosmological parameters correspond to a $\Lambda$CDM cosmology
@@
 We buid a sample of pairs that resemble the conditions in the LG.
-To construct this sample we select from Illustris-1 all galaxies with a stellar
+To construct this sample we select from Illustris-1 all the galaxies with a stellar
 mass in the range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11}
@@
 This corresponds to a pair number density of $\sim 2 \times10^{-5}$
-pairs Mpc$^{-3}$ 
+pairs Mpc$^{-3}$. 
 Appendix A shows the physical  properties (stellar masses, maximum
@@
 while the upper limit corresponds to the minimum number of M31
-satellites included in the analysis.
+satellites usually included M31 studies.
 In simulations we rank the subhalos by their maximum circular
@@
     ratio and $b/a$ ratio. 
-    The first colum refers to the results from
+    The first column refers to the results from
     observational data, the second column uses the spherically
@@
     ratio and $b/a$ ratio. 
-    The first column summarize the results from the 24 pairs in
+    The first column summarizes the results from the 24 pairs in
     Illustris-1-Dark, the second column from the 20 pairs in
@@
 These normalized quantities are used to build the explicit probability
-distributions for the scalars describing aesphericity.
+distributions for the scalars describing asphericity.
 
@@
 from the mean and standard deviation estimated from the data.
-Although the physical quantities of interests are bound, unlike the
+Although the physical quantities of interest are bound, unlike the
 random variables from a normal distribution, we find that the
@@
 In M31 the satellite distribution is in agreement with the
-expectations both from an spherical distribution and the results form the
+expectations both from a spherical distribution and the results from the
 simulations. 
@@
 The values for all the covariance matrices and mean vectors
-foricorresponding to all the simulations are listed in the Appendix \ref{appendix:covariance}.
+corresponding to all the simulations are listed in the Appendix \ref{appendix:covariance}.
 
@@
 We consider that a sampled system is similar to the M31/MW galaxy if the
-distance of each of its characteristics ($w$, $c/a$, $b/a$) to the
+distance of each of its normalized characteristics ($w$, $c/a$, $b/a$) to the
 sample mean is equal or larger than the distance of the observational
@@
 In a three dimensional gaussian distribution, having a $1\sigma$,
-$2\sigma$ and $3\sigma$ interval corresponds to have respectively $19 \%$, $73 \%$ and
+$2\sigma$ and $3\sigma$ interval corresponds to having respectively $19 \%$, $73 \%$ and
 $97 \%$ of the total of points in the distribution.
@@
 $\sim 160$ \kms.
+
+Another element that influences this trend is the simulated physics.
+This is evident in the comparison between Illustris-1 and Illustris-1-Dark.
+These two simulations share the same characteristics except for the
+inclusion of baryonic physics in Illustris-1.
+We find that extreme MW systems are easier to find in the DM only
+simulation. 
+The results listed in Appendix \ref{appendix:covariance} show that
+halos are closer to spherical once baryonic effects are included. 
+For instance the mean value for the normalized width goes closer to
+zero, from $-0.45\pm 0.04$  to $-0.17\pm0.04$, and the same is true
+for the $c/a$ ratio that changes from $-0.61\pm0.04$ in the DM only
+simulation to $-0.40\pm 0.04$ in Illustris-1.  
+We postpone a detailed quantification of this effect for a future
+study.
 
@@
 recent results by \cite{2015ApJ...815...19P}. 
-We estimated that with the M31 between $37\%$ and $58\%$ of the pairs
-pairs show aspherical characteristics larger than M31, while
+We estimated that with the M31 between $37\%$ and $58\%$ of the pairs show aspherical characteristics larger than M31, while
 this fraction drops to less than $1\%$ for the MW. 
 These fractions are robust to changes in the numerical simulations, 
-the criteria used to define the pairs and the methods used to
+the criteria used to define the pairs and to the methods used to
 estimate the parameters of the multivariate normal distribution.
@@
 that are already scarce and difficult to find in simulations.
+
 An extension of this framework to outliers in higher order deviations
@@
 interest can be built.  
+The approach presented here is also useful to gauge the influence of 
+influence of different physical elements incluedes the simulation. 
+For instance, in our case the data hints towards rounder satellite
+distributions in simulations that include baryonic effects.
 
@@
 We also have the number of satellites as bright as the Mageallanic
-Clouds, only expected in $5\%$ of galaxies \citep{2011ApJ...743..117B}
-and the atypical kinematics of M31 with a very low tangential velocity,
-only expected in less than $1\%$ of the pairs with similar
-environmental characteristics \citep{ForeroRomero2013}. 
-In other words, if we were in a typical LG pair in LCDM, the MW should
-have zero satellites like the Magellanic Clouds, it's satellite
-distribution should be similar to M31's and M31 should have a larger
-tangential velocity.
-
-The LG atypicality should be seen as an opportunity to constrain in
-high detail the environment that allowed such a pattern to emerge. 
-Although broad correlations between LG assembly, pair kinematics, halo shapes and
-satellite distributions are expected in LCDM
+Clouds, only expected in $5\%$ of galaxies
+\citep{2011ApJ...743..117B} and 
+the satellite velocities around the MW with a radial/tangential
+anisotropy only expected in $3\%$ of systems in LCDM
+\citep{2017MNRAS.468L..41C}. 
+One could also add the atypical kinematics of M31 with a very low
+tangential velocity, which is only expected in less than $1\%$ of the pairs
+with similar environmental characteristics \citep{ForeroRomero2013}.
+
+This atypicality should be seen as an opportunity to constrain in
+great detail the environment that allowed such a pattern to emerge. 
+Although broad correlations between LG assembly, pair kinematics, halo
+shapes and satellite distributions are expected in LCDM
 \citep{2011MNRAS.417.1434F,2014MNRAS.443.1090F,2015ApJ...799...45F,2015MNRAS.452.1052L},
@@
 of halo mass and cosmic web environment are still missing to
-understand what fearures in the initial conditions of our LG
+understand what features in the initial conditions of our LG
 are responsible for the extreme features observed in its satellite

### 2018-03-01 paper/paper.tex
abstract

@@
 \begin{abstract}
-We use numerical simulations to build an explicit probability
-distribution for the asphericity in the satellite distribution around
-galaxies similar to the Local Group (LG) in the Lambda Cold Dark
-Matter (LCDM) paradigm. 
-This allows us to estimate the atipicallity
+We use simulations to build an explicit probability distribution for
+the asphericity in the satellite distribution around galaxies similar
+to the Local Group (LG) in the Lambda Cold Dark Matter (LCDM) paradigm. 
+We use this distribution to to estimate the  atipicallity
 of the satellite distributions in the LG even when the underlying
-simulations do not have enough systems that fully resemble the LG.
+simulations do not have enough systems fully resembling the LG.
 We demonstrate the method using three different simulations:
@@
 Detailed results differ among the simulations suggesting a strong
-influence of the typical Dark Matter (DM) halo mass in the LG samples
-and simulated baryonic effects.
+influence of the typical DM halo mass in the LG samples and simulated
+baryonic effects. 
 However, there are three common trends.
@@
 pairs have a satellite distribution as planar as in the MW. 
-The brightest satellites in the M31 galaxy have a rather typical
-distribution in the LCDM context, while the MW distribution is
-atypical in this respect.  
 These quantitative results place the LG at the level of a $3\sigma$
 outlier in the LCDM paradigm. 
-We suggest that understanding the reasons for this atipicality
+We suggest that understanding the reasons for this atypicality
 will require quantifying the asphericity probability distribution as a
@@
 
-\begin{keywords}Galaxies: halos --- Galaxies: statistics --- Dark
-  Matter --- Methods: numerical  
+\begin{keywords}Cosmology: Dark Matter --- Galaxies:Local Group ---
+  Methods: numerical  
 \end{keywords}
@@
 \caption{Probability distribution for the expected number of M31 and
-  MW halos showing the same degree of atipicality as the Local Group if drawn
+  MW halos showing the same degree of atypicality as the Local Group if drawn
   from a sample of $10^4$ isolated pairs. 
@@
 $97 \%$ of the total of points in the distribution.
-With this result in mind the $LG$ has the same degree of atipicality
+With this result in mind the $LG$ has the same degree of atypicality
 as a $3\sigma$ outlier. 

### 2018-03-01 paper/paper.tex
refs

@@
 (Colombia); COLCIENCIAS (c\'odigo 120471250459, contrato FP44842-287-
-2016); the European Union’s Horizon 2020 Research and Innovation
+2016); the European Union's Horizon 2020 Research and Innovation
 Programme under the Marie Sk\l{}odowska-Curie grant agreement No 73437

### 2018-04-10 paper/paper.tex
faltan solo 3 comentarios del reviewer

@@
 to the Local Group (LG) in the Lambda Cold Dark Matter (LCDM) paradigm. 
-We use this distribution to to estimate the  atipicallity
+We use this distribution to estimate the  atypicality
 of the satellite distributions in the LG even when the underlying
@@
 However, there are three common trends.
-First, at most of $2\%$ the pairs are expected to have satellite
+First, at most $2\%$ of the pairs are expected to have satellite
 distributions with the same asphericity as the LG; second,
@@
 (MW) and the M31 galaxy is becoming a stringent test for structure
-formation theories in a explicit cosmological context. 
+formation theories in an explicit cosmological context. 
 This started with the suggested existence of a Magellanic Plane, a flattened
@@
 to report high chances to find a planar configuration;
-two more recent numerical experiment with high resolution simulations
+two more recent numerical experiments with high resolution simulations
 (\cite{2013MNRAS.429..725S} and \cite{2016MNRAS.457.1931S}) reported
@@
 the 15 to 27 brightest satellites are consistent with spherically
-symmetric distribution and easy to reproduce in LCDM simulations
+symmetric distributions and easy to reproduce in LCDM simulations
 \citep{2006AJ....131.1405K,2007MNRAS.374.1125M, 2013ApJ...766..120C}.
@@
 Some of the difficulty in trying to reconcile and understand the
-seemly conflicting or inconclusive results on the MW has its origin on
+seemingly conflicting or inconclusive results on the MW has its origin on
 the frequentist fashion generally used to compute probabilities.
@@
 meeting some criteria. 
-This has two incovenients.
+This has two inconveniences.
 The first is that the probability estimate is made against whatever
@@
 $6.3\times 10^6$\Msun\ and a minimum mass for the baryonic volume
-element of $8.0\times 10^7$\Msun for Illustris-1 and a dark matter
+element of $1.2\times 10^6$\Msun for Illustris-1 and a dark matter
 particle mass of $7.6\times 10^6$\Msun for Illustris-1-Dark.
@@
 satellite included in the sample is different in each case.
-We make this choice to to rule out the influence of satellite numbers
+We make this choice to rule out the influence of satellite numbers
 in the statistics.
@@
 while the upper limit corresponds to the minimum number of M31
-satellites usually included M31 studies.
+satellites usually included in M31 studies.
 In simulations we rank the subhalos by their maximum circular
@@
 \begin{equation}
-{\bf{\bar{I}}} = \sum_{k=1}^{N_p}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
+{\bf{\bar{I}}} = \sum_{i=1}^{N_p}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
   (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
@@
 This allows us to build a normalized version of all quantities of
-interest by substracting the mean and dividing between the standard
+interest by substracting the mean and dividing by the standard
 deviation of the randomized samples.
@@
 with a jackknife technique. 
-That is, out of the the $n$ pairs in each simulation, we perfom $n$
+That is, out of the $n$ pairs in each simulation, we perfom $n$
 different covariance and mean value measurements using only $n-1$ pairs. 
@@
   horizontal/vertical axis corresponds to the  M31/MW or the
-  most/less massive halo in the pair 
+  most/less massive halo in the pair. 
   Left. Plane width in physical units comparing the results from observations
@@
   The results for the gaussian model are built from $10^6$ point
-  realizations in the three-dimensional space spaned by the variables of
+  realizations in the three-dimensional space spanned by the variables of
   interest for each halo. 
@@
 The M31 values are typical while the MW is an outlier.
-The added value of the data in this panel is that it is the normalized
-which is consistent with normal distributions.
-This is the data used to build the mean values vector and covariance
+
+The added value of using the normalized data is that this data is 
+consistent with normal distributions.
+Additionally, this is the data used to build the mean values vector and covariance
 matrix described in Equation \ref{eq:multivariate}. 
+%The added value of the data in this panel is that it is the normalized
+%which is consistent with normal distributions.
+%This is the data used to build the mean values vector and covariance
+%matrix described in Equation \ref{eq:multivariate}.
 
@@
 The right panel shows the normalized results. 
-The MW shows a low $c/a$ ratio close to between two and three
+The MW shows a low $c/a$ ratio between two and three
 standard deviations away from the mean value of the spherical
@@
 
-This result nicely summarizes the results we had in the previous
+This nicely summarizes the results we had in the previous
 sections. The left hand triangular plot shows how M31 falls into the middle of all 2D
@@
 experiment. The left panel shows the probability density for the number of M31
-systems in a parent sampe of $10^4$ pairs, the right panel shows the
+systems in a parent sample of $10^4$ pairs, the right panel shows the
 results for the MW.
 For M31, between $27\%$ and $56\%$ of the pairs have a satellite
-distribution as aspherical as the observed in M31. This fraction drops
+distribution as aspherical as the one observed in M31. This fraction drops
 dramatically for the MW where only $0.02\%$ to $3\%$ of the satellites
@@
 quantities being bound.
-We estimated the mean and covariance of this distributions using
+We estimated the mean and covariance of {\color{red}these} distributions using
 the results of LG pairs coming from three different numerical
@@
 The focus of our approach was building an explicit probability
-distributions for the observables of interest, instead of trying to
+distribution for the observables of interest, instead of trying to
 find simulated objects that fulfill different observational criteria. 
 This approach is particularly useful in the case of atypical
-observables as its the case of interest, as it allows for an atypicallity
-quantification without needing to build explicit samples of objects
+observables, as it allows for an atypicallity
+quantification without the need to build explicit samples of objects
 that are already scarce and difficult to find in simulations.
@@
 The approach presented here is also useful to gauge the influence of 
-influence of different physical elements incluedes the simulation. 
+influence of different physical elements includes the simulation. 
 For instance, in our case the data hints towards rounder satellite
@@
 \caption{Physical characteristics of the LG pairs selected in the
-  simulations. All lots show the integrated distributions. The
+  simulations. All plots show the integrated distributions. The
   physical properties are the radial comoving velocity between the MW

### 2018-04-11 paper/paper.tex
reply

@@
 pairs Mpc$^{-3}$. 
-Appendix A shows the physical  properties (stellar masses, maximum
-circular velocities, radial velocities and separation) of those
-pairs.
+Appendix A shows the maximum, circular velocities, radial velocities and separation of those pairs.
 
@@
 
-Appendix A compares the physical properties (stellar masses, maximum
-circular velocities, radial velocities and separation) in those
-pairs against the results from the Illustris-1 simulations.
+Appendix A compares the physical properties (maximum circular
+velocities, radial velocities and separation) in those pairs against
+the results from the Illustris-1 simulations.
 

### 2018-04-17 code/full_stats_and_plots.py
python script

@@ -1,0 +1,65 @@
+def load_summary(filename):
+    dtype=[('minr', 'f8'),
+           ('maxr', 'f8'), 
+           ('ca_ratio', 'f8'),
+           ('ba_ratio', 'f8'),
+           ('a', 'f8'),
+           ('center', 'f8'),
+           ('width', 'f8'),
+           ('mu', 'f8')]
+    summary = np.loadtxt(filename, dtype=dtype)    
+    return summary
+
+def load_obs(obs_name):
+    dtype=[('name','|S20'),
+           ('x', 'f8'),
+           ('y', 'f8'), 
+           ('z', 'f8'),
+           ('delta_plus', 'f8'),
+           ('delta_minus', 'f8'),
+           ('vmag', 'f8'),
+           ('delta_vmag', 'f8')]
+    obs_data = np.loadtxt(obs_name, dtype=dtype)    
+    return obs_data
+
+def main_halos(snap_data, sort_column='mstar', single_reverse=False):
+    id_sorted = np.argsort(snap_data[sort_column])
+    if single_reverse:
+        id_halo_A = id_sorted[0]
+        main_halos_data = snap_data[id_halo_A]
+    else:
+        id_halo_A = id_sorted[-1]
+        id_halo_B = id_sorted[-2]
+        main_halos_data = snap_data[[id_halo_A, id_halo_B]]
+    return main_halos_data
+
+def satellite_halos(halo_data, halo_center, radius=300, 
+                    max_points=-1, max_initial_points=-1,sort_column='vmag', reverse=False, randomize=False):
+        
+    jj = np.argsort(halo_data[sort_column])
+    if reverse:
+        jj = jj[::-1]
+        
+    tmp_halo = halo_data[jj]
+
+    for col in list(['x','y','z']):
+        tmp_halo[col] = tmp_halo[col] - halo_center[col]
+    
+    r = np.sqrt(tmp_halo['x']**2 + tmp_halo['y']**2 + tmp_halo['z']**2)
+    ii = (r < radius) & (r>1E-6)
+    
+    tmp_halo = tmp_halo[ii]
+    r = np.sqrt(tmp_halo['x']**2 + tmp_halo['y']**2 + tmp_halo['z']**2)
+    
+    if max_initial_points>0 :
+        tmp_halo = tmp_halo[:max_initial_points]
+        r = np.sqrt(tmp_halo['x']**2 + tmp_halo['y']**2 + tmp_halo['z']**2)
+
+    if max_points > 0:
[…]

### 2018-04-17 code/full_stats_and_plots.py
python script

@@ -34,7 +34,8 @@ def main_halos(snap_data, sort_column='mstar', single_reverse=False):
     return main_halos_data
 
 def satellite_halos(halo_data, halo_center, radius=300, 
-                    max_points=-1, max_initial_points=-1,sort_column='vmag', reverse=False, randomize=False):
+                    max_points=-1, max_initial_points=-1,
+                    sort_column='vmag', reverse=False, randomize=False):
         
     jj = np.argsort(halo_data[sort_column])
     if reverse:
@@ -63,3 +64,95 @@ def satellite_halos(halo_data, halo_center, radius=300,
             return tmp_halo[:max_points], np.min(r[:max_points]), np.max(r[:max_points])
     else:
         return tmp_halo, np.min(r), np.max(r)
+
+def gen_random_sphere(n_points):
+    """
+    Sets of points in the 3D sphere
+    """
+    r = np.random.random(n_points)**(1.0/3.0)
+    phi = np.random.random(n_points) * 2.0 * np.pi
+    costheta = 2.0*(np.random.random(n_points) -0.5)
+    theta = np.arccos(costheta)
+    x = r * np.sin(theta) * np.cos(phi)
+    y = r * np.sin(theta) * np.sin(phi)
+    z = r * np.cos(th
+    
+def compile_randomized(group_id=0, iter_id=0, n_sat=11, n_random=1000, 
+                         elvis = False,
+                         obs_data=False,
+                         reverse=False,
+                         sort_column='vmax',
+                         randomize=False,
+                         data_path = "../data/mstar_selected/", 
+                         obs_data_path = "../data/obs/",
+                         output_path = "../data/mstar_selected_summary/"):
+    
+    if obs_data:
+        MW_data = load_obs(os.path.join(obs_data_path, "MW_satellites.txt"))
+        M31_data = load_obs(os.path.join(obs_data_path, "M31_satellites.txt"))
+    
+        M31 = main_halos(M31_data, sort_column='vmag', single_reverse=True)
+        MW = main_halos(MW_data, sort_column='vmag', single_reverse=True)
+    else:
+        if elvis:
+            base_name = 'elvis'
+        else:
+            base_name = 'Illustris_group'
+        M31_data = load_snapshot(os.path.join(data_path, "{}_{}.dat".format(base_name, group_id)), elvis=elvis)
[…]

### 2018-04-17 code/full_stats_and_plots.py
python stats script

@@ -1,3 +1,23 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import matplotlib.cm as cm
+from scipy.optimize import curve_fit
+import matplotlib as mpl
+import struct
+import glob
+import os 
+import struct
+from sklearn import linear_model
+import scipy.linalg
+from scipy import stats
+from scipy import integrate
+from scipy.stats import powerlaw
+hubble = 0.73
+vmax_MW = 220.0
+vmax_M31 = 270.0
+m_star_M31 = 10.3
+m_star_MW = 6.08
+
 def load_summary(filename):
     dtype=[('minr', 'f8'),
            ('maxr', 'f8'), 
@@ -9,6 +29,43 @@ def load_summary(filename):
            ('mu', 'f8')]
     summary = np.loadtxt(filename, dtype=dtype)    
     return summary
+
+def load_snapshot(snap_name, boxsize=75000.0, elvis=False):
+    if elvis:
+        dtype=[('haloid','i8'),
+            ('x', 'f8'),('y', 'f8'), ('z', 'f8'),
+            ('vx', 'f8'),('vy', 'f8'),('vz', 'f8'),
+            ('vmax', 'f8'),('vmaxpeak', 'f8'),
+            ('virmass', 'f8'),('virmasspeak', 'f8'),  
+            ('virradius', 'f8'),('peakradius', 'f8'),
+            ('aexppeak', 'f8'),
+            ('mstar', 'f8'),('mstarbehrooze', 'f8'),
+            ('npart', 'i8'),
+           ('parentid','i8'),('upid', 'i8')]
+    else:
+        dtype=[('subid','i8'),
+           ('parentid','i8'),
+           ('x', 'f8'),
+           ('y', 'f8'), 
+           ('z', 'f8'),
+           ('vx', 'f8'),
+           ('vy', 'f8'),
+           ('vz', 'f8'),
+           ('vmax', 'f8'),
+           ('bmag', 'f8'),
+           ('vmag', 'f8'),
+           ('mstar', 'f8')]
+    snap_data = np.loadtxt(snap_name, dtype=dtype) 
+    print('reading {}'.format(snap_name))
+    if not elvis:
+        # this takes into account periodic boudary conditions from Illustris
+        for col in list(['x','y','z']):
+            if((snap_data[col].max() - snap_data[col].min()) > 0.5 * boxsize):
+                snap_data[col] = (snap_data[col] - 0.5 * boxsize) % boxsize
[…]

### 2018-04-17 code/asphericity_stats.py
asphericity basic stats from observations

@@ -1,0 +1,109 @@
+import numpy as np
+import glob
+import os
+def load_summary(filename):
+    dtype=[('minr', 'f8'),
+           ('maxr', 'f8'), 
+           ('ca_ratio', 'f8'),
+           ('ba_ratio', 'f8'),
+           ('a', 'f8'),
+           ('center', 'f8'),
+           ('width', 'f8'),
+           ('mu', 'f8')]
+    summary = np.loadtxt(filename, dtype=dtype)    
+    return summary
+
+def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_sat=11, full_data=False):
+    files = glob.glob(input_path+"M31_group_*_nsat_{}.dat".format(n_sat))
+    group_id = []
+    for f in files:
+        i = int(f.split("_")[-3])
+        if i not in group_id:
+            group_id.append(i)
+    #print(group_id, len(group_id))
+
+    n_groups = len(group_id)
+    
+    fields = ['width','mu', 'a', 'ba_ratio', 'ca_ratio']
+    M31_all = {}
+    MW_all = {}
+    if full_data:
+        for field in fields:
+            M31_all[field] = np.empty((0))
+            MW_all[field] = np.empty((0))
+            M31_all[field+'_random'] = np.empty((0))
+            MW_all[field+'_random'] = np.empty((0))
+    else:
+        for field in fields:
+            M31_all[field] = np.ones(n_groups)
+            MW_all[field] = np.ones(n_groups)
+            M31_all[field+'_sigma'] = np.ones(n_groups)
+            MW_all[field+'_sigma'] = np.ones(n_groups)
+        
+            M31_all[field+'_random'] = np.ones(n_groups)
+            MW_all[field+'_random'] = np.ones(n_groups)
+            M31_all[field+'_random_sigma'] = np.ones(n_groups)
+            MW_all[field+'_random_sigma'] = np.ones(n_groups)
+
+    for g in range(n_groups):
+        MW_summary = {}
+        M31_summary = {}
+    
+        filename_MW = os.path.join(input_path,"MW_group_{}_nsat_{}.dat".format(group_id[g],n_sat))
+        filename_M31 = os.path.join(input_path,"M31_group_{}_nsat_{}.dat".format(group_id[g],n_sat))
+
+        MW_summary[g] = load_summary(filename_MW)
+        M31_summary[g] = load_summary(filename_M31)
+    
+    
+    for field in fields:
[…]

### 2018-04-17 paper/paper.tex
obs table updated

@@
     \hline
-    Plane width (kpc) & $59\pm 3$  & $21\pm 2$  & $65\pm 12$   &
-    $45\pm 8$    & $-0.48\pm 0.24$ & $-2.48\pm 0.26$\\\hline
-    $c/a$ ratio & $0.45\pm 0.04$ & $0.25\pm 0.05$ & $0.55\pm0.10$ &
-    $0.53\pm 0.10$ & $-1.03\pm 0.37$ & $-2.18\pm 0.42$\\ \hline
-    $b/a$ ratio & $0.82\pm 0.06$ & $0.80\pm 0.04$ & $0.82\pm0.07$ &
-    $0.81\pm 0.08$ & $-0.02\pm 0.82$ & $-0.13\pm 0.47$\\ \hline
+Plane width (kpc) & $63.64$ & $19.34$ & $55.78$ & $38.60$ & $0.74$ & $-4.45$\\\hline
+$c/a$ ratio & $0.42$ & $0.18$ & $0.51$ & $0.45$ & $-0.87$ & $-2.75$\\\hline
+$b/a$ ratio & $0.96$ & $0.87$ & $0.82$ & $0.83$ & $1.74$ & $0.67$\\\hline
   \end{tabular}
-  \caption{Results from observations. Mean values and standard deviations for the different
+  \caption{Results from observations with $N_s=11$. 
+    for the different
     quantities describing the satellite distributions: plane width, $c/a$
@@
     corresponds to the observational data recentered and normalized
-    by the randomized values. \label{table:observations}}
+    by the standard deviation of the randomized data. \label{table:observations}}
 \end{table*}

### 2018-04-17 code/asphericity_stats.py
print observatinal stats

@@ -90,20 +90,21 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
     return M31_all, MW_all
 
 
+fields = ['width','ca_ratio', 'ba_ratio']
+names = {'width':'Plane width (kpc)', 'ca_ratio':'$c/a$ ratio', 'ba_ratio':'$b/a$ ratio'}
+
 for n_sat in range(11, 16):
     print("OBSERVATIONS - NSAT = {}".format(n_sat))
     in_path = "../data/obs_summary/"
     M31_obs_stats, MW_obs_stats = load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
 
-    fields = ['width','ba_ratio', 'ca_ratio']
     print("M31 values\nField & Physical & Random & Normalized")
     for field in fields:
-        print(field, M31_obs_stats[field], M31_obs_stats[field+'_random'], 
-          (M31_obs_stats[field]-M31_obs_stats[field+'_random'])/M31_obs_stats[field+'_random_sigma'])
+        print("{} & ${:.2f}$ & ${:.2f}$ & ${:.2f}$ & ${:.2f}$ & ${:.2f}$ & ${:.2f}$\\\\\\hline".format(
+            names[field], 
+            M31_obs_stats[field][0], MW_obs_stats[field][0],
+              M31_obs_stats[field+'_random'][0], MW_obs_stats[field+'_random'][0],
+              (M31_obs_stats[field][0]-M31_obs_stats[field+'_random'][0])/M31_obs_stats[field+'_random_sigma'][0],
+            (MW_obs_stats[field][0]-M31_obs_stats[field+'_random'][0])/MW_obs_stats[field+'_random_sigma'][0]))
     print()
-    print("MW values\nField & Physical & Random & Normalized")
-    for field in fields:
-        print(field, MW_obs_stats[field], MW_obs_stats[field+'_random'], 
-          (MW_obs_stats[field]-M31_obs_stats[field+'_random'])/MW_obs_stats[field+'_random_sigma'])
-    print()
-    print()
+    

### 2018-04-17 code/asphericity_stats.py
updated script

@@ -20,7 +20,7 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
         i = int(f.split("_")[-3])
         if i not in group_id:
             group_id.append(i)
-    #print(group_id, len(group_id))
+    print(group_id, len(group_id))
 
     n_groups = len(group_id)
     
@@ -45,10 +45,9 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
             M31_all[field+'_random_sigma'] = np.ones(n_groups)
             MW_all[field+'_random_sigma'] = np.ones(n_groups)
 
+    MW_summary = {}
+    M31_summary = {}
     for g in range(n_groups):
-        MW_summary = {}
-        M31_summary = {}
-    
         filename_MW = os.path.join(input_path,"MW_group_{}_nsat_{}.dat".format(group_id[g],n_sat))
         filename_M31 = os.path.join(input_path,"M31_group_{}_nsat_{}.dat".format(group_id[g],n_sat))
 
@@ -63,13 +62,13 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
         b_random = np.empty((0))
         
         for g in range(n_groups):
-            data = M31_summary[i]
-            a = np.append(a, data[field][0])
-            a_random = np.append(a_random, data[field][1:101])
+            data = M31_summary[g]
+            a = data[field][0]
+            a_random = data[field][1:101]
         
-            data = MW_summary[i]
-            b = np.append(b, data[field][0])
-            b_random = np.append(b_random, data[field][1:101])
+            data = MW_summary[g]
+            b = data[field][0]
+            b_random = data[field][1:101]
                 #print('a_random {} iter: {} {}'.format(field, i, a_random))
            
             if full_data:
@@ -77,6 +76,7 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
                 MW_all[field] = np.append(MW_all[field], b)
                 M31_all[field+'_random'] = np.append(M31_all[field+'_random'], a_random)
                 MW_all[field+'_random'] = np.append(MW_all[field+'_random'], b_random)
+        
[…]

### 2018-04-17 paper/paper.tex
updated table
tabla actualizada

@@
     \hline
-Plane width (kpc) & $63.64$ & $19.34$ & $55.78$ & $38.60$ & $0.74$ & $-4.45$\\\hline
-$c/a$ ratio & $0.42$ & $0.18$ & $0.51$ & $0.45$ & $-0.87$ & $-2.75$\\\hline
-$b/a$ ratio & $0.96$ & $0.87$ & $0.82$ & $0.83$ & $1.74$ & $0.67$\\\hline
+Plane width (kpc) & $63.64$ & $19.34$ & $55.78\pm10.65$ & $38.60\pm8.19$ & $0.74$ & $-4.45$\\\hline
+$c/a$ ratio & $0.42$ & $0.18$ & $0.51\pm0.11$ & $0.45\pm0.12$ & $-0.87$ & $-2.75$\\\hline
+$b/a$ ratio & $0.96$ & $0.87$ & $0.82\pm0.08$ & $0.83\pm0.08$ & $1.74$ & $0.67$\\\hline
   \end{tabular}
@@
     \hline
-    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
-    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
-    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
+Plane width (kpc) & $56.28\pm 18.30$ & $58.30 \pm 13.51$  & $66.66\pm 15.75$ & $64.81\pm 15.34$ & $68.74\pm 16.82$ & $63.70\pm 13.62$\\\hline
+$c/a$ ratio & $0.48\pm 0.15$ & $0.47 \pm 0.11$  & $0.52\pm 0.13$ & $0.50\pm 0.10$ & $0.54\pm 0.15$ & $0.47\pm 0.13$\\\hline
+$b/a$ ratio & $0.80\pm 0.10$ & $0.80 \pm 0.08$  & $0.82\pm 0.09$ & $0.82\pm 0.07$ & $0.81\pm 0.07$ & $0.80\pm 0.09$\\\hline
   \end{tabular}
-  \caption{Results from simulations. Mean values and standard deviations for the different
+  \caption{Results from simulations for $N_s=11$. Mean values and standard deviations for the different
     quantities describing the satellite distributions: plane width, $c/a$
     ratio and $b/a$ ratio. 
-    The first column summarizes the results from the 24 pairs in
-    Illustris-1-Dark, the second column from the 20 pairs in
+    The first column summarizes the results from the 27 pairs in
+    Illustris-1-Dark, the second column from the 23 pairs in
     Illustris-1 and the third column from the 12 pairs in the

### 2018-04-17 code/asphericity_stats.py
script imprime tablas de simulaciones

@@ -110,20 +110,23 @@ for n_sat in range(11,16):
     print()
     
 for n_sat in range(11,16):
-    print("Illustris - NSAT = {}".format(n_sat))
-    
+    print("IllustrisDark / Illustris / Elvis - NSAT = {}".format(n_sat))
     in_path = "../data/illustris1_mstar_selected_summary/"
     M31_illu_stats, MW_illu_stats = load_experiment(input_path=in_path, n_sat=n_sat)
     in_path = "../data/illustris1dark_mstar_selected_summary/"
     M31_illudark_stats, MW_illudark_stats = load_experiment(input_path=in_path, n_sat=n_sat)
     in_path = "../data/elvis_mstar_selected_summary/"
     M31_elvis_stats, MW_elvis_stats = load_experiment(input_path=in_path, n_sat=n_sat)
-    
-    print("M31(phys) - MW(phys) | M31(rand) | MW (rand) | M31(norm) | MW (norm)|")
+
+    print("M31(phys) - MW(phys)|")
     for field in fields:
-        print("{} & {:.2f} {:.2f} & {:.2f} {:.2f} ".format(
+        print("{} & ${:.2f}\pm {:.2f}$ & ${:.2f} \pm {:.2f}$  & ${:.2f}\pm {:.2f}$ & ${:.2f}\pm {:.2f}$ & ${:.2f}\pm {:.2f}$ & ${:.2f}\pm {:.2f}$\\\\\\hline".format(
             names[field],
+            np.mean(M31_illudark_stats[field]), np.std(M31_illudark_stats[field]),
+            np.mean(MW_illudark_stats[field]), np.std(MW_illudark_stats[field]), 
             np.mean(M31_illu_stats[field]), np.std(M31_illu_stats[field]),
-            np.mean(MW_illu_stats[field]), np.mean(MW_illu_stats[field])))
+            np.mean(MW_illu_stats[field]), np.std(MW_illu_stats[field]), 
+            np.mean(M31_elvis_stats[field]), np.std(M31_elvis_stats[field]),
+            np.mean(MW_elvis_stats[field]), np.std(MW_elvis_stats[field])))
     print()
              

### 2018-04-18 paper/paper.tex
new plots for the covariances

@@
 \centering
-\includegraphics[width=0.45\textwidth]{gaussian_model_illustrisdm_M31.pdf}
-\includegraphics[width=0.45\textwidth]{gaussian_model_illustrisdm_MW.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustris1dark_M31_n_11.pdf}
+\includegraphics[width=0.45\textwidth]{gaussian_model_illustris1dark_MW_n_11.pdf}
 \caption{Results from multivariate gaussian model fitted to the
@@
 \centering
-\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_M31.pdf}
-\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_MW.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_M31_n_11.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=0.48\textwidth]{gaussian_model_illustris_M31.pdf}
-\includegraphics[width=0.48\textwidth]{gaussian_model_illustris_MW.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_illustris1_M31_n_11.pdf}
+\includegraphics[width=0.48\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
 \caption{

### 2018-04-18 code/asphericity_stats.py
plot covariance matrices

@@ -1,6 +1,9 @@
 import numpy as np
 import glob
 import os
+import matplotlib.pyplot as plt
+import corner
+
 def load_summary(filename):
     dtype=[('minr', 'f8'),
            ('maxr', 'f8'), 
@@ -89,44 +92,199 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
                 
     return M31_all, MW_all
 
+def points_in_experiment(experiment):
+    keys = list(experiment.keys())
+    n_points = len(experiment[keys[0]])
+    return n_points
 
-fields = ['width','ca_ratio', 'ba_ratio']
-names = {'width':'Plane width (kpc)', 'ca_ratio':'$c/a$ ratio', 'ba_ratio':'$b/a$ ratio'}
+def copy_experiment(experiment, id_to_remove=None):
+    copy = {}
+    n_points = points_in_experiment(experiment)
+    for k in experiment.keys():
+        if id_to_remove is None:
+            copy[k] = experiment[k].copy()
+        else:
+            ii = np.arange(n_points)
+            copy[k] = experiment[k][ii!=id_to_remove]
+    return copy
 
-for n_sat in range(11,16):
-    print("OBSERVATIONS - NSAT = {}".format(n_sat))
+def get_data_obs(obs_data):
+    fields = {0:'width', 1:'ca_ratio', 2:'ba_ratio'}
+    n_fields = len(fields)
+    data_obs = np.zeros((n_fields, len(obs_data['width'])))
+
+    for i in range(n_fields):
+        field = fields[i]
+        x_obs = (obs_data[field] - obs_data[field+'_random'])/obs_data[field+'_random_sigma']
+        data_obs[i,:] = x_obs[:]
+    
+    return {'data_obs': data_obs, 'fields':fields}
+
+
+def covariance_and_mean(experiment):
+    fields = {0:'width', 1:'ca_ratio', 2:'ba_ratio'}
+    n_fields = len(fields)
+    n_points = points_in_experiment(experiment)
+    data_sim = np.zeros((n_fields, n_points))
+    for i in range(n_fields):
+        field = fields[i]
+        x_sim = (experiment[field] - experiment[field+'_random'])/experiment[field+'_random_sigma']
+        data_sim[i,:] = x_sim[:]
+    
+    data_cov = np.cov(data_sim)
[…]

### 2018-04-18 code/asphericity_stats.py
asphericity as a function of n_points

@@ -185,7 +185,7 @@ def print_obs_shape():
                 M31_obs_stats[field+'_random'][0], M31_obs_stats[field+'_random_sigma'][0],
                 MW_obs_stats[field+'_random'][0],MW_obs_stats[field+'_random_sigma'][0],
                 (M31_obs_stats[field][0]-M31_obs_stats[field+'_random'][0])/M31_obs_stats[field+'_random_sigma'][0],
-                (MW_obs_stats[field][0]-M31_obs_stats[field+'_random'][0])/MW_obs_stats[field+'_random_sigma'][0]))
+                (MW_obs_stats[field][0]-MW_obs_stats[field+'_random'][0])/MW_obs_stats[field+'_random_sigma'][0]))
         print()
 
 
@@ -211,6 +211,9 @@ def print_sim_shape():
                 np.mean(MW_elvis_stats[field]), np.std(MW_elvis_stats[field])))
         print()
              
+
+
+
             
 def plot_covariance(simulation, n_sat):
     print('simulation {}'.format(simulation))
@@ -284,7 +287,25 @@ def plot_covariance(simulation, n_sat):
     plt.close('all')
 
 
-for n_sat in range(11,16):
-    plot_covariance('illustris1', n_sat)
-    plot_covariance('illustris1dark', n_sat)
-    plot_covariance('elvis', n_sat)
+def plot_asphericity_obs(field):
+    plt.figure(figsize=(8,5))
+    plt.rc('text', usetex=True,)
+    plt.rc('font', family='serif', size=25)
+    for n_sat in range(11,16):
+        in_path = "../data/obs_summary/"
+        M31_obs_stats, MW_obs_stats = load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
+        M31_obs = get_data_obs(M31_obs_stats)
+        MW_obs = get_data_obs(MW_obs_stats)
+        print(n_sat, M31_obs['fields'][field], MW_obs['fields'][field],M31_obs['data_obs'][field], MW_obs['data_obs'][field])
+        plt.scatter(n_sat, M31_obs['data_obs'][field], marker='*', s=300, color='black', alpha=0.9, label='M31')
+        plt.scatter(n_sat, MW_obs['data_obs'][field], marker='o', s=300, color='black', alpha=0.9, label='M31')
+        
+    filename = "../paper/normalized_{}_n_dependence.pdf".format(M31_obs['fields'][field])
[…]

### 2018-04-18 code/asphericity_stats.py
asphericity as a function of n_points

@@ -291,7 +291,7 @@ def plot_asphericity_obs(field):
     plt.figure(figsize=(8,5))
     plt.rc('text', usetex=True,)
     plt.rc('font', family='serif', size=25)
-    for n_sat in range(11,16):
+    for n_sat in range(11,15):
         in_path = "../data/obs_summary/"
         M31_obs_stats, MW_obs_stats = load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
         M31_obs = get_data_obs(M31_obs_stats)
@@ -299,7 +299,7 @@ def plot_asphericity_obs(field):
         print(n_sat, M31_obs['fields'][field], MW_obs['fields'][field],M31_obs['data_obs'][field], MW_obs['data_obs'][field])
         plt.scatter(n_sat, M31_obs['data_obs'][field], marker='*', s=300, color='black', alpha=0.9, label='M31')
         plt.scatter(n_sat, MW_obs['data_obs'][field], marker='o', s=300, color='black', alpha=0.9, label='M31')
-        
+    plt.legend()
     filename = "../paper/normalized_{}_n_dependence.pdf".format(M31_obs['fields'][field])
     print('saving figure to {}'.format(filename))
     plt.savefig(filename, bbox_inches='tight')

### 2018-04-18 code/asphericity_stats.py
asphericity as a function of n_points

@@ -288,18 +288,27 @@ def plot_covariance(simulation, n_sat):
 
 
 def plot_asphericity_obs(field):
-    plt.figure(figsize=(8,5))
+    plt.figure(figsize=(7,7))
     plt.rc('text', usetex=True,)
     plt.rc('font', family='serif', size=25)
-    for n_sat in range(11,15):
+    for n_sat in range(11,16):
         in_path = "../data/obs_summary/"
         M31_obs_stats, MW_obs_stats = load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
         M31_obs = get_data_obs(M31_obs_stats)
         MW_obs = get_data_obs(MW_obs_stats)
         print(n_sat, M31_obs['fields'][field], MW_obs['fields'][field],M31_obs['data_obs'][field], MW_obs['data_obs'][field])
-        plt.scatter(n_sat, M31_obs['data_obs'][field], marker='*', s=300, color='black', alpha=0.9, label='M31')
-        plt.scatter(n_sat, MW_obs['data_obs'][field], marker='o', s=300, color='black', alpha=0.9, label='M31')
+        if n_sat==11:
+            plt.scatter(n_sat, M31_obs['data_obs'][field], marker='*', s=300, color='black', alpha=0.9, label='M31')
+            plt.scatter(n_sat, MW_obs['data_obs'][field], marker='o', s=300, color='black', alpha=0.9, label='MW')
+        else:
+            plt.scatter(n_sat, M31_obs['data_obs'][field], marker='*', s=300, color='black', alpha=0.9)
+            plt.scatter(n_sat, MW_obs['data_obs'][field], marker='o', s=300, color='black', alpha=0.9)
+            
+    ylabel = {'width': 'Normalized Plane Width', 'ca_ratio':'Normalized $c/a$ ratio', 'ba_ratio':'Normalized $b/a$ ratio'}
     plt.legend()
+    plt.xlabel("$N_s$")
+    plt.ylabel(ylabel[M31_obs['fields'][field]])
+    plt.grid()
     filename = "../paper/normalized_{}_n_dependence.pdf".format(M31_obs['fields'][field])
     print('saving figure to {}'.format(filename))
     plt.savefig(filename, bbox_inches='tight')

### 2018-04-18 code/asphericity_stats.py
numbers

@@ -314,7 +314,52 @@ def plot_asphericity_obs(field):
     plt.savefig(filename, bbox_inches='tight')
     plt.clf()
     
-plot_asphericity_obs(0)
-plot_asphericity_obs(1)
-plot_asphericity_obs(2)
+def number_LG(sim_cov_M31, sim_mean_M31, sim_cov_MW, sim_mean_MW, obs_M31, obs_MW, n_sample=20):
+    n_try = 1000
+    n_out = np.ones(n_try)
+    n_MW = np.ones(n_try)
+    n_M31 = np.ones(n_try)
 
+    for i in range(n_try):
+        sim_M31 = np.random.multivariate_normal(sim_mean_M31, sim_cov_M31, size=n_sample)
+        sim_MW = np.random.multivariate_normal(sim_mean_MW, sim_cov_MW, size=n_sample)
+        
+        like_M31_from_M31 = sim_M31[:,0]<1E6
+        like_MW_from_MW = sim_MW[:,0]<1E6
+        for j in range(3):
+            like_M31_from_M31 &= (np.abs(sim_M31[:,j]-sim_mean_M31[j]) > np.abs(obs_M31[j]-sim_mean_M31[j]))
+            like_MW_from_MW &= (np.abs(sim_MW[:,j]-sim_mean_MW[j]) > np.abs(obs_MW[j]-sim_mean_MW[j]))
+        #print(sim_M31[like_M31_from_M31,:])
+        
+        n_out[i] = np.count_nonzero(like_M31_from_M31 & like_MW_from_MW)
+        n_MW[i] = np.count_nonzero(like_MW_from_MW)
+        n_M31[i] = np.count_nonzero(like_M31_from_M31)
+        #print(n_M31[i])
+    return {'n_LG': n_out, 'n_MW':n_MW, 'n_M31':n_M31}
+
+
+def get_numbers(simulation, n_sat):
+    print('simulation {}'.format(simulation))
+    in_path = "../data/{}_mstar_selected_summary/".format(simulation)
+    M31_sim_stats, MW_sim_stats = load_experiment(input_path=in_path, n_sat=n_sat)
+
+    in_path = "../data/obs_summary/"
+    M31_obs_stats, MW_obs_stats = load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
+    M31_obs = get_data_obs(M31_obs_stats)
+    MW_obs = get_data_obs(MW_obs_stats)
+    
[…]

### 2018-04-18 code/asphericity_stats.py
updated script

@@ -354,12 +354,94 @@ def get_numbers(simulation, n_sat):
     n_out_list_sim = number_LG(cov_sim_M31['covariance'], cov_sim_M31['mean'],
              cov_sim_MW['covariance'], cov_sim_MW['mean'],
              M31_obs['data_obs'], MW_obs['data_obs'], n_sample=10000)
-    print(np.mean(n_out_list_sim['n_M31']), np.std(n_out_list_sim['n_M31']))
-    print(np.mean(n_out_list_sim['n_MW']), np.std(n_out_list_sim['n_MW']))
-    print(np.mean(n_out_list_sim['n_LG']), np.std(n_out_list_sim['n_LG']))
+    return {'mean_n_M31':np.mean(n_out_list_sim['n_M31']), 'std_n_M31':np.std(n_out_list_sim['n_M31']),
+           'mean_n_MW':np.mean(n_out_list_sim['n_MW']), 'std_n_MW':np.std(n_out_list_sim['n_MW']),
+           'mean_n_LG':np.mean(n_out_list_sim['n_LG']), 'std_n_LG':np.std(n_out_list_sim['n_LG'])}
     print()
     
-for i in range(11,16):
-    get_numbers('illustris1dark', i)
-    get_numbers('illustris1', i)
-    get_numbers('elvis', i)
+def print_numbers():
+    LG_out = open('../data/numbers/LG_numbers.txt', 'w')
+    M31_out = open('../data/numbers/M31_numbers.txt', 'w')
+    MW_out = open('../data/numbers/MW_numbers.txt', 'w')
+
+    for i in range(11,16):
+        a = get_numbers('illustris1dark', i)
+        b = get_numbers('illustris1', i)
+        c = get_numbers('elvis', i)
+        LG_out.write("{} {} {} {} {} {} {}\n".format(i, 
+                                                  a['mean_n_LG'], a['std_n_LG'],
+                                                  b['mean_n_LG'], b['std_n_LG'],
+                                                  c['mean_n_LG'], c['std_n_LG']))
+        M31_out.write("{} {} {} {} {} {} {}\n".format(i, 
+                                                  a['mean_n_M31'], a['std_n_M31'],
+                                                  b['mean_n_M31'], b['std_n_M31'],
+                                                  c['mean_n_M31'], c['std_n_M31']))
[…]

### 2018-04-19 code/general_plots.py
general plot

@@ -1,0 +1,101 @@
+import numpy as np
+import glob
+import os
+import matplotlib.pyplot as plt
+import corner
+import asphericity_stats as asp
+
+def plot_randoms_and_sims(simulation, n_sat):
+    print('simulation {}'.format(simulation))
+    in_path = "../data/{}_mstar_selected_summary/".format(simulation)
+    M31_sim_stats, MW_sim_stats = asp.load_experiment(input_path=in_path, n_sat=n_sat, full_data=True)
+
+    in_path = "../data/obs_summary/"
+    M31_obs_stats, MW_obs_stats = asp.load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
+    M31_obs = asp.get_data_obs(M31_obs_stats, normed=False)
+    MW_obs = asp.get_data_obs(MW_obs_stats, normed=False)
+
+    M31_obs_stats, MW_obs_stats = asp.load_experiment(input_path=in_path, n_sat=n_sat, full_data=True)
+    
+        
+    data_random_obs_M31 = np.array([M31_obs_stats['width_random'],
+                                    M31_obs_stats['ca_ratio_random'], 
+                                    M31_obs_stats['ba_ratio_random']]).T
+    data_random_obs_MW = np.array([MW_obs_stats['width_random'],
+                                    MW_obs_stats['ca_ratio_random'], 
+                                    MW_obs_stats['ba_ratio_random']]).T
+    
+    print(np.shape(data_random_obs_MW))
+    print(MW_obs)
+        
+    plt.figure(figsize=(8,5))
+    plt.rc('text', usetex=True,)
+    plt.rc('font', family='serif', size=25)
+    figure = corner.corner(data_random_obs_M31, 
+                      quantiles=[0.16, 0.5, 0.84],
+                      labels=[r"$w$ M31", r"$c/a$ M31", r"$b/a$ M31"],
+                      show_titles=True, title_kwargs={"fontsize": 12}, 
+                      truths=M31_obs['data_obs'])
+        
+        
+    min_w = 10; max_w = 90; min_ac = 0.0; max_ac = 1.0 ; min_ab = 0.6; max_ab = 1.0
+    ndim = 3
+    axes = np.array(figure.axes).reshape(ndim,ndim)
[…]

### 2018-04-19 code/data_tables_and_plots.py
data tables and plots

@@ -1,0 +1,53 @@
+import compile_randomized_data as crd
+
+obs = False
+illustris1 = False
+illustris1dark = False
+elvis = False
+
+if obs:        
+    print('Compiling stats for the observations')
+    output_path = "../data/obs_summary/"
+    for j in range(11,16):
+        print('\t Nsat = {}'.format(j))
+        crd.compile_stats(group_id=0, n_sat = j, n_random=10000, 
+                        output_path=output_path, sort_column='vmag', randomize=False, reverse=False, obs_data=True)
+    
+if illustris1:
+    print('Compiling stats for illustris1')
+    input_path = "../data/illustris1_mstar_selected/"
+    output_path = "../data/illustris1_mstar_selected_summary/"
+    for j in range(11,16):
+        print('\t Nsat = {}'.format(j))
+        for i in range(27):
+            crd.compile_stats(group_id=i, n_sat=j, n_random=10000, data_path=input_path,
+                            output_path=output_path, sort_column='vmax', reverse=True, randomize=False)
+
+if illustris1dark:
+    print('Compiling stats for illustris1dark')
+    input_path = "../data/illustris1dark_mstar_selected/"
+    output_path = "../data/illustris1dark_mstar_selected_summary/"
+    for j in range(11,16):
+        print('\t Nsat = {}'.format(j))
+        for i in range(27):
+            crd.compile_stats(group_id=i, n_sat=j, n_random=10000, data_path=input_path,
+                            output_path=output_path, sort_column='vmax', reverse=True, randomize=False)
+if elvis:
+    print('Compiling stats for ELVIS')
+    input_path = "../data/elvis_mstar_selected/"
+    output_path = "../data/elvis_mstar_selected_summary/"
+    for j in range(11,16):
+        print('\t Nsat = {}'.format(j))
+        for i in range(12):
+            crd.compile_stats(group_id=i, n_sat=j, n_random=10000, data_path=input_path,
+                            output_path=output_path, sort_column='vmax', reverse=True, randomize=False, elvis=True)
+            
+import asphericity_stats as asp
+
+ObsTable = False
+SimTable = True
+if ObsTable:
+    asp.print_table_obs_shape()
+    
+if SimTable:
+    asp.print_table_sim_shape()

### 2018-04-19 code/asphericity_stats.py
updated scripts

@@ -67,11 +67,11 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
         for g in range(n_groups):
             data = M31_summary[g]
             a = data[field][0]
-            a_random = data[field][1:101]
+            a_random = data[field][1:]
         
             data = MW_summary[g]
             b = data[field][0]
-            b_random = data[field][1:101]
+            b_random = data[field][1:]
                 #print('a_random {} iter: {} {}'.format(field, i, a_random))
            
             if full_data:
@@ -108,14 +108,17 @@ def copy_experiment(experiment, id_to_remove=None):
             copy[k] = experiment[k][ii!=id_to_remove]
     return copy
 
-def get_data_obs(obs_data):
+def get_data_obs(obs_data, normed=True):
     fields = {0:'width', 1:'ca_ratio', 2:'ba_ratio'}
     n_fields = len(fields)
     data_obs = np.zeros((n_fields, len(obs_data['width'])))
 
     for i in range(n_fields):
         field = fields[i]
-        x_obs = (obs_data[field] - obs_data[field+'_random'])/obs_data[field+'_random_sigma']
+        if normed:
+            x_obs = (obs_data[field] - obs_data[field+'_random'])/obs_data[field+'_random_sigma']
+        else:
+            x_obs = obs_data[field]
         data_obs[i,:] = x_obs[:]
     
     return {'data_obs': data_obs, 'fields':fields}
@@ -168,7 +171,7 @@ def jacknife_covariance(experiment):
     return {'covariance': covariance_avg, 'covariance_error': covariance_std, 'mean': mean_avg, 'mean_error': mean_std}
 
 
-def print_obs_shape():
+def print_table_obs_shape():
     fields = ['width','ca_ratio', 'ba_ratio']
     names = {'width':'Plane width (kpc)', 'ca_ratio':'$c/a$ ratio', 'ba_ratio':'$b/a$ ratio'}
 
@@ -188,8 +191,9 @@ def print_obs_shape():
                 (MW_obs_stats[field][0]-MW_obs_stats[field+'_random'][0])/MW_obs_stats[field+'_random_sigma'][0]))
         print()
 
-
-def print_sim_shape():
[…]

### 2018-04-19 code/compile_randomized_data.py

@@ -295,45 +295,3 @@ def compile_stats(group_id=0, n_sat=11, n_random=1000,
     output_A.close()
     output_B.close()
                    
-
-obs = False
-illustris1 = False
-illustris1dark = False
-elvis = False
-
-if (obs):        
-    print('Compiling stats for the observations')
-    output_path = "../data/obs_summary/"
-    for j in range(11,16):
-        print('\t Nsat = {}'.format(j))
-        compile_stats(group_id=0, n_sat = j, n_random=1000, 
-                        output_path=output_path, sort_column='vmag', randomize=False, reverse=False, obs_data=True)
-    
-if illustris1:
-    print('Compiling stats for illustris1')
-    input_path = "../data/illustris1_mstar_selected/"
-    output_path = "../data/illustris1_mstar_selected_summary/"
-    for j in range(11,16):
-        print('\t Nsat = {}'.format(j))
-        for i in range(27):
-            compile_stats(group_id=i, n_sat=j, n_random=1000, data_path=input_path,
-                            output_path=output_path, sort_column='vmax', reverse=True, randomize=False)
-
-if illustris1dark:
-    print('Compiling stats for illustris1dark')
-    input_path = "../data/illustris1dark_mstar_selected/"
-    output_path = "../data/illustris1dark_mstar_selected_summary/"
-    for j in range(11,16):
-        print('\t Nsat = {}'.format(j))
-        for i in range(27):
-            compile_stats(group_id=i, n_sat=j, n_random=1000, data_path=input_path,
-                            output_path=output_path, sort_column='vmax', reverse=True, randomize=False)
-if elvis:
-    print('Compiling stats for ELVIS')
-    input_path = "../data/elvis_mstar_selected/"
-    output_path = "../data/elvis_mstar_selected_summary/"
-    for j in range(11,16):
-        print('\t Nsat = {}'.format(j))
-        for i in range(12):
-            compile_stats(group_id=i, n_sat=j, n_random=1000, data_path=input_path,
-                            output_path=output_path, sort_column='vmax', reverse=True, randomize=False, elvis=True)

### 2018-04-19 code/data_tables_and_plots.py

@@ -45,9 +45,34 @@ if elvis:
 import asphericity_stats as asp
 
 ObsTable = False
-SimTable = True
+SimTable = False
+CovPlots = False
+ObsAsphPlots = False
+PrintModelNumbers = False
+PlotModelNumbers = False
+PlotShapeRandomObs = True
+
 if ObsTable:
     asp.print_table_obs_shape()
     
 if SimTable:
     asp.print_table_sim_shape()
+    
+if CovPlots:
+    asp.plot_covariance('illustris1dark', 11)
+    asp.plot_covariance('illustris1', 11)
+    asp.plot_covariance('elvis', 11)
+    
+if ObsAsphPlots:
+    asp.plot_asphericity_obs(0)
+    asp.plot_asphericity_obs(1)
+    asp.plot_asphericity_obs(2)
+    
+if PrintModelNumbers:
+    asp.print_numbers()
+
+if PlotModelNumbers:
+    asp.plot_numbers()
+
+if PlotShapeRandomObs:
+    asp.plot_shape_obs_randoms(11)

### 2018-04-19 code/general_plots.py

@@ -98,4 +98,6 @@ def plot_randoms_and_sims(simulation, n_sat):
     plt.close('all')
 
 
-plot_randoms_and_sims('illustris1', 11)
+#plot_randoms_and_sims('illustris1', 11)
+
+

### 2018-04-19 code/general_plots.py
unused script

@@ -1,103 +1,0 @@
-import numpy as np
-import glob
-import os
-import matplotlib.pyplot as plt
-import corner
-import asphericity_stats as asp
-
-def plot_randoms_and_sims(simulation, n_sat):
-    print('simulation {}'.format(simulation))
-    in_path = "../data/{}_mstar_selected_summary/".format(simulation)
-    M31_sim_stats, MW_sim_stats = asp.load_experiment(input_path=in_path, n_sat=n_sat, full_data=True)
-
-    in_path = "../data/obs_summary/"
-    M31_obs_stats, MW_obs_stats = asp.load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
-    M31_obs = asp.get_data_obs(M31_obs_stats, normed=False)
-    MW_obs = asp.get_data_obs(MW_obs_stats, normed=False)
-
-    M31_obs_stats, MW_obs_stats = asp.load_experiment(input_path=in_path, n_sat=n_sat, full_data=True)
-    
-        
-    data_random_obs_M31 = np.array([M31_obs_stats['width_random'],
-                                    M31_obs_stats['ca_ratio_random'], 
-                                    M31_obs_stats['ba_ratio_random']]).T
-    data_random_obs_MW = np.array([MW_obs_stats['width_random'],
-                                    MW_obs_stats['ca_ratio_random'], 
-                                    MW_obs_stats['ba_ratio_random']]).T
-    
-    print(np.shape(data_random_obs_MW))
-    print(MW_obs)
-        
-    plt.figure(figsize=(8,5))
-    plt.rc('text', usetex=True,)
-    plt.rc('font', family='serif', size=25)
-    figure = corner.corner(data_random_obs_M31, 
-                      quantiles=[0.16, 0.5, 0.84],
-                      labels=[r"$w$ M31", r"$c/a$ M31", r"$b/a$ M31"],
-                      show_titles=True, title_kwargs={"fontsize": 12}, 
-                      truths=M31_obs['data_obs'])
-        
-        
-    min_w = 10; max_w = 90; min_ac = 0.0; max_ac = 1.0 ; min_ab = 0.6; max_ab = 1.0
-    ndim = 3
-    axes = np.array(figure.axes).reshape(ndim,ndim)
[…]

### 2018-04-19 code/asphericity_stats.py
latest version

@@ -487,7 +487,7 @@ def plot_shape_obs_randoms(n_sat):
     ax = axes[2,0];ax.set_xlim(min_w, max_w);ax.set_ylim(min_ab, max_ab)
 
 
-    filename = "../paper/input_{}_M31_n_{}.pdf".format(simulation, n_sat)
+    filename = "../paper/input_obs_M31_n_{}.pdf".format(n_sat)
     print('saving figure to {}'.format(filename))
     plt.savefig(filename, bbox_inches='tight')
     plt.clf()
@@ -510,7 +510,7 @@ def plot_shape_obs_randoms(n_sat):
     ax = axes[1,0];ax.set_xlim(min_w, max_w);ax.set_ylim(min_ac, max_ac)
     ax = axes[2,0];ax.set_xlim(min_w, max_w);ax.set_ylim(min_ab, max_ab)
 
-    filename = "../paper/input_{}_MW_n_{}.pdf".format(simulation, n_sat)
+    filename = "../paper/input_obs_MW_n_{}.pdf".format(n_sat)
     print('saving figure to {}'.format(filename))
     plt.savefig(filename, bbox_inches='tight')
     plt.clf()

### 2018-04-19 code/data_tables_and_plots.py

@@ -76,3 +76,4 @@ if PlotModelNumbers:
 
 if PlotShapeRandomObs:
     asp.plot_shape_obs_randoms(11)
+    asp.plot_shape_obs_randoms(12)

### 2018-04-20 code/asphericity_stats.py
normed plots

@@ -47,6 +47,8 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
             MW_all[field+'_random'] = np.ones(n_groups)
             M31_all[field+'_random_sigma'] = np.ones(n_groups)
             MW_all[field+'_random_sigma'] = np.ones(n_groups)
+            M31_all[field+'_normed'] = np.ones(n_groups)
+            MW_all[field+'_normed'] = np.ones(n_groups)
 
     MW_summary = {}
     M31_summary = {}
@@ -89,6 +91,8 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
                 MW_all[field+'_random'][g] = np.average(b_random)
                 M31_all[field+'_random_sigma'][g] = np.std(a_random)
                 MW_all[field+'_random_sigma'][g] = np.std(b_random)
+                M31_all[field+'_normed'][g] = (M31_all[field][g] - M31_all[field+'_random'][g])/M31_all[field+'_random_sigma'][g]
+                MW_all[field+'_normed'][g] = (MW_all[field][g] - MW_all[field+'_random'][g])/MW_all[field+'_random_sigma'][g]
                 
     return M31_all, MW_all
 
@@ -511,6 +515,181 @@ def plot_shape_obs_randoms(n_sat):
     ax = axes[2,0];ax.set_xlim(min_w, max_w);ax.set_ylim(min_ab, max_ab)
 
     filename = "../paper/input_obs_MW_n_{}.pdf".format(n_sat)
+    print('saving figure to {}'.format(filename))
+    plt.savefig(filename, bbox_inches='tight')
+    plt.clf()
+    
+    plt.close('all')
+
+    
+def plot_shape_obs_sims(simulation, n_sat):
+    print('simulation {}'.format(simulation))
+    simulation_name = {'illustris1':'Illustris1', 'illustris1dark':'Illustris1Dark', 'elvis':'ELVIS'}
+    in_path = "../data/{}_mstar_selected_summary/".format(simulation)
+    M31_sim_stats, MW_sim_stats = load_experiment(input_path=in_path, n_sat=n_sat, full_data=True)
+    
+    in_path = "../data/obs_summary/"
[…]

### 2018-04-20 code/data_tables_plots.py

@@ -50,7 +50,9 @@ CovPlots = False
 ObsAsphPlots = False
 PrintModelNumbers = False
 PlotModelNumbers = False
-PlotShapeRandomObs = True
+PlotShapeRandomObs = False
+PlotShapeObsSim = False
+PlotShapeObsSimNormed = True
 
 if ObsTable:
     asp.print_table_obs_shape()
@@ -77,3 +79,11 @@ if PlotModelNumbers:
 if PlotShapeRandomObs:
     asp.plot_shape_obs_randoms(11)
     asp.plot_shape_obs_randoms(12)
+    
+if PlotShapeObsSim:
+    asp.plot_shape_obs_sims('illustris1dark', 11)
+    asp.plot_shape_obs_sims('illustris1', 11)
+    asp.plot_shape_obs_sims('elvis', 11)
+
+if PlotShapeObsSimNormed:
+    asp.plot_shape_obs_sims_normed('illustris1dark', 11)

### 2018-04-20 code/data_tables_plots.py
normed plots

@@ -87,3 +87,5 @@ if PlotShapeObsSim:
 
 if PlotShapeObsSimNormed:
     asp.plot_shape_obs_sims_normed('illustris1dark', 11)
+    asp.plot_shape_obs_sims_normed('illustris1', 11)
+    asp.plot_shape_obs_sims_normed('elvis', 11)

### 2018-04-20 code/asphericity_stats.py
updated script

@@ -394,9 +394,9 @@ def plot_numbers():
     LG_data = np.loadtxt('../data/numbers/LG_numbers.txt')
     M31_data = np.loadtxt('../data/numbers/M31_numbers.txt')
     MW_data = np.loadtxt('../data/numbers/MW_numbers.txt')
-    LG_data = LG_data/1E2
-    M31_data = M31_data/1E2
-    MW_data = MW_data/1E2
+    LG_data[:,1:] = LG_data[:,1:]/1E2
+    M31_data[:,1:] = M31_data[:,1:]/1E2
+    MW_data[:,1:] = MW_data[:,1:]/1E2
     plt.figure(figsize=(7,7))
     plt.rc('text', usetex=True,)
     plt.rc('font', family='serif', size=25)
@@ -409,7 +409,7 @@ def plot_numbers():
                 fmt='>', markersize=20, color='black', alpha=0.5, label='ELVIS')
     plt.legend()
     plt.xlabel("$N_s$")
-    plt.ylabel("$N_{LG} (\%)$")
+    plt.ylabel("Local Group Systems $(\%)$")
     plt.grid()
     filename = "../paper/LG_numbers.pdf"
     print('saving figure to {}'.format(filename))
@@ -427,7 +427,7 @@ def plot_numbers():
     plt.errorbar(MW_data[:,0], MW_data[:,5], yerr=MW_data[:,6],
                 fmt='>', markersize=20, color='black', alpha=0.5, label='ELVIS')
     plt.xlabel("$N_s$")
-    plt.ylabel("$N_{MW} (\%)$")
+    plt.ylabel("MW Galaxies $(\%)$")
     plt.grid()
     filename = "../paper/MW_numbers.pdf"
     print('saving figure to {}'.format(filename))
@@ -445,7 +445,7 @@ def plot_numbers():
     plt.errorbar(M31_data[:,0], M31_data[:,5], yerr=M31_data[:,6],
                 fmt='>', markersize=20, color='black', alpha=0.5, label='ELVIS')
     plt.xlabel("$N_s$")
-    plt.ylabel("$N_{M31} (\%)$")
+    plt.ylabel("M31 Galaxies $(\%)$")
     plt.grid()
     filename = "../paper/M31_numbers.pdf"
     print('saving figure to {}'.format(filename))
@@ -643,7 +643,7 @@ def plot_shape_obs_sims_normed(simulation, n_sat):
[…]

### 2018-04-20 code/data_tables_plots.py

@@ -49,10 +49,10 @@ SimTable = False
 CovPlots = False
 ObsAsphPlots = False
 PrintModelNumbers = False
-PlotModelNumbers = False
+PlotModelNumbers = True
 PlotShapeRandomObs = False
 PlotShapeObsSim = False
-PlotShapeObsSimNormed = True
+PlotShapeObsSimNormed = False
 
 if ObsTable:
     asp.print_table_obs_shape()

### 2018-04-20 paper/paper.tex
updated table
updated tables
new plots in paper
updated figures

@@
     \hline
-Plane width (kpc) & $63.64$ & $19.34$ & $55.78\pm10.65$ & $38.60\pm8.19$ & $0.74$ & $-4.45$\\\hline
-$c/a$ ratio & $0.42$ & $0.18$ & $0.51\pm0.11$ & $0.45\pm0.12$ & $-0.87$ & $-2.75$\\\hline
-$b/a$ ratio & $0.96$ & $0.87$ & $0.82\pm0.08$ & $0.83\pm0.08$ & $1.74$ & $0.67$\\\hline
+lane width (kpc) & $63.64$ & $19.34$ & $56.74\pm10.96$ & $37.56\pm7.90$ & $0.63$ & $-2.31$\\\hline
+$c/a$ ratio & $0.42$ & $0.18$ & $0.53\pm0.11$ & $0.46\pm0.11$ & $-1.00$ & $-2.46$\\\hline
+$b/a$ ratio & $0.96$ & $0.87$ & $0.81\pm0.08$ & $0.80\pm0.09$ & $1.69$ & $0.80$\\\hline
   \end{tabular}
@@
 \centering
-\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
+\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11.pdf}
+\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
 \caption{Plane width characterization in observations and
@@
 Middle. Average from the observations (star) and the average from each
-pair in the simulation (circles).
-Right. Same as the middle panel except that this time each point has
+pair in the simulation (circles).}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11_normed.pdf}
+\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11_normed.pdf}
+\caption{Right. Same as the middle panel except that this time each point has
 been normalized (median substracted and normalized by the standard
@@
 expectations both from a spherical distribution and the results from the
-simulations. 
-\label{fig:scatter_width}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ca_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ca_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ca_ratio.pdf}
-\caption{Same layout as in Figure \ref{fig:scatter_width}. 
-This time for the $c/a$ axis ratio. 
-The same message holds in this case; namely, that 
-the MW has a significantly lower $c/a$ value than the
-expectation from the spherical distribution and from the simulations. 
-This low value is also $2\sigma$ away from the expactations for a
-spherical distribution.
-On the other hand, M31 is consistent both with a spherical
-distribution and with the results from simulations.
-\label{fig:scatter_ca_ratio}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ba_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ba_ratio.pdf}
-\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ba_ratio.pdf}
-\caption{Same layout as in Figure \ref{fig:scatter_width}. 
-This time for the $b/a$ axis ratio. In this case both the MW and M31
-are consistent with the results of a spherical distribution and 
-the simulations. 
-\label{fig:scatter_ba_ratio}}
+simulations. }
 \end{figure*}
@@
 \centering
-\includegraphics[width=0.47\textwidth]{expected_numbers_n_M31.pdf}
-\includegraphics[width=0.47\textwidth]{expected_numbers_n_MW.pdf}
+\includegraphics[width=0.32\textwidth]{LG_numbers.pdf}
+\includegraphics[width=0.32\textwidth]{M31_numbers.pdf}
+\includegraphics[width=0.32\textwidth]{MW_numbers.pdf}
 \caption{Probability distribution for the expected number of M31 and

### 2018-04-20 code/asphericity_stats.py
updated gaussian model script

@@ -221,17 +221,19 @@ def print_table_sim_shape():
              
             
 def plot_covariance(simulation, n_sat):
+    simulation_name = {'illustris1':'Illustris1', 'illustris1dark':'Illustris1Dark', 'elvis':'ELVIS'}
     print('simulation {}'.format(simulation))
     in_path = "../data/{}_mstar_selected_summary/".format(simulation)
-    M31_illu_stats, MW_illu_stats = load_experiment(input_path=in_path, n_sat=n_sat)
+    M31_sim_stats, MW_sim_stats = load_experiment(input_path=in_path, n_sat=n_sat)
 
+    
     in_path = "../data/obs_summary/"
     M31_obs_stats, MW_obs_stats = load_experiment(input_path=in_path, n_sat=n_sat, full_data=False)
     M31_obs = get_data_obs(M31_obs_stats)
     MW_obs = get_data_obs(MW_obs_stats)
     
-    cov_illustris_M31 = jacknife_covariance(M31_illu_stats)
-    cov_illustris_MW = jacknife_covariance(MW_illu_stats)
+    cov_illustris_M31 = jacknife_covariance(M31_sim_stats)
+    cov_illustris_MW = jacknife_covariance(MW_sim_stats)
         
     data_random_illustris_M31 = np.random.multivariate_normal(
             cov_illustris_M31['mean'], cov_illustris_M31['covariance'], size=100000)
@@ -249,17 +251,21 @@ def plot_covariance(simulation, n_sat):
                       truths=M31_obs['data_obs'])
         
         
+    min_w = -4; max_w = 4; min_ac = -4; max_ac = 4 ; min_ab = -4; max_ab = 4
     ndim = 3
     axes = np.array(figure.axes).reshape(ndim,ndim)
-    for i in range(ndim):
-        ax = axes[i, i]
-        ax.set_xlim(-5,5)
-            
-    for yi in range(ndim):
-        for xi in range(yi):
-            ax = axes[yi, xi]
-            ax.set_xlim(-5,5)
-            ax.set_ylim(-5,5)
+    ax = axes[1,1];ax.set_xlim(min_ac, max_ac)
+    ax = axes[2,1];ax.set_xlim(min_ac, max_ac);ax.set_ylim(min_ab, max_ab);
[…]

### 2018-04-20 code/data_tables_plots.py

@@ -46,10 +46,10 @@ import asphericity_stats as asp
 
 ObsTable = False
 SimTable = False
-CovPlots = False
+CovPlots = True
 ObsAsphPlots = False
 PrintModelNumbers = False
-PlotModelNumbers = True
+PlotModelNumbers = False
 PlotShapeRandomObs = False
 PlotShapeObsSim = False
 PlotShapeObsSimNormed = False

### 2018-04-20 paper/paper.tex
new plots in the appendix

@@
 \centering
-\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_width.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_width.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
+\includegraphics[width=0.40\textwidth]{input_illustris1_obs_M31_n_11.pdf}
+\includegraphics[width=0.40\textwidth]{input_illustris1_obs_MW_n_11.pdf}
+\includegraphics[width=0.40\textwidth]{input_illustris1_obs_M31_n_11_normed.pdf}
+\includegraphics[width=0.40\textwidth]{input_illustris1_obs_MW_n_11_normed.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_M31_n_11.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
 \caption{ELVIs results for the quantities presented for the Illustris1-Dark
@@
 \centering
-\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_M31_n_11.pdf}
-\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
-\caption{
-Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
-computed from the ELVIS data.
-\label{fig:correlations_elvis}}
+\includegraphics[width=0.40\textwidth]{input_elvis_obs_M31_n_11.pdf}
+\includegraphics[width=0.40\textwidth]{input_elvis_obs_MW_n_11.pdf}
+\includegraphics[width=0.40\textwidth]{input_elvis_obs_M31_n_11_normed.pdf}
+\includegraphics[width=0.40\textwidth]{input_elvis_obs_MW_n_11_normed.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_M31_n_11.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
+\caption{ELVIs results for the quantities presented for the Illustris1-Dark
+  simulation in Figures  \ref{fig:scatter_width},
+  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
+Upper row corresponds to the raw values from observations and
+simulated pairs, while the second row normalizes the same values to
+the mean and standard deviation on its spherically randomized
+counterparts. 
+\label{fig:scatter_elvis}}
 \end{figure*}
@@
 \centering
-\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_width.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
-\caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
-  computed from the Illustris-1 data.
-\label{fig:scatter_illustris}}
+\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1dark_M31_n_12.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1dark_MW_n_12.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_M31_n_12.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_MW_n_12.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_M31_n_12.pdf}
+\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_MW_n_12.pdf}
+\caption{ELVIs results for the quantities presented for the Illustris1-Dark
+  simulation in Figures  \ref{fig:scatter_width},
+  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
+Upper row corresponds to the raw values from observations and
+simulated pairs, while the second row normalizes the same values to
+the mean and standard deviation on its spherically randomized
+counterparts. 
+\label{fig:scatter_elvis}}
 \end{figure*}
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.48\textwidth]{gaussian_model_illustris1_M31_n_11.pdf}
-\includegraphics[width=0.48\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
-\caption{
-Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
-computed from the Illustris-1 data.
-\label{fig:correlations_illustris}}
-\end{figure*}
-
 \end{document}

### 2018-04-20 code/data_tables_plots.py
updated script for plots

@@ -46,7 +46,7 @@ import asphericity_stats as asp
 
 ObsTable = False
 SimTable = False
-CovPlots = True
+CovPlots = False
 ObsAsphPlots = False
 PrintModelNumbers = False
 PlotModelNumbers = False
@@ -61,9 +61,10 @@ if SimTable:
     asp.print_table_sim_shape()
     
 if CovPlots:
-    asp.plot_covariance('illustris1dark', 11)
-    asp.plot_covariance('illustris1', 11)
-    asp.plot_covariance('elvis', 11)
+    for nsat in range(11,16):
+        asp.plot_covariance('illustris1dark', nsat)
+        asp.plot_covariance('illustris1', nsat)
+        asp.plot_covariance('elvis', nsat)
     
 if ObsAsphPlots:
     asp.plot_asphericity_obs(0)
@@ -77,15 +78,17 @@ if PlotModelNumbers:
     asp.plot_numbers()
 
 if PlotShapeRandomObs:
-    asp.plot_shape_obs_randoms(11)
-    asp.plot_shape_obs_randoms(12)
+    for nsat in range(11,16):
+        asp.plot_shape_obs_randoms(nsat)
     
 if PlotShapeObsSim:
-    asp.plot_shape_obs_sims('illustris1dark', 11)
-    asp.plot_shape_obs_sims('illustris1', 11)
-    asp.plot_shape_obs_sims('elvis', 11)
+    for nsat in range(11,16):
+        asp.plot_shape_obs_sims('illustris1dark', nsat)
+        asp.plot_shape_obs_sims('illustris1', nsat)
+        asp.plot_shape_obs_sims('elvis', nsat)
 
 if PlotShapeObsSimNormed:
-    asp.plot_shape_obs_sims_normed('illustris1dark', 11)
-    asp.plot_shape_obs_sims_normed('illustris1', 11)
-    asp.plot_shape_obs_sims_normed('elvis', 11)
+    for nsat in range(11,16):
+        asp.plot_shape_obs_sims_normed('illustris1dark', nsat)
+        asp.plot_shape_obs_sims_normed('illustris1', nsat)
+        asp.plot_shape_obs_sims_normed('elvis', nsat)

### 2018-04-23 paper/paper.tex
updated abstract and new figures

@@
 We use simulations to build an explicit probability distribution for
-the asphericity in the satellite distribution around galaxies similar
-to the Local Group (LG) in the Lambda Cold Dark Matter (LCDM) paradigm. 
+the asphericity in the satellite distribution around Local Group (LG)
+type galaxies in the Lambda Cold Dark Matter (LCDM) paradigm. 
 We use this distribution to estimate the  atypicality
@@
 simulations do not have enough systems fully resembling the LG.
-We demonstrate the method using three different simulations:
-Illustris-1,  Illustris-1-Dark and ELVIS. 
-Detailed results differ among the simulations suggesting a strong
-influence of the typical DM halo mass in the LG samples and simulated
-baryonic effects. 
+We demonstrate the method using three different simulations
+(Illustris-1,  Illustris-1-Dark and ELVIS) and a number of satellites
+ranging from 11 to 15.
+Detailed results differ greatly among the simulations suggesting a
+strong influence of the typical DM halo mass, the methodology to
+select the satellites and the simulated baryonic effects. 
 However, there are three common trends.
@@
 distributions with the same asphericity as the LG; second,
-between $27\%$ to $56\%$ of the pairs have a halo with a satellite
-distribution as aspherical as in M31; and third, at most $3\%$ of the
-pairs have a satellite distribution as planar as in the MW. 
+at most $80\%$ of the pairs have a halo with a satellite
+distribution as aspherical as in M31; and third, at most $4\%$ of the
+pairs have a halo with satellite distribution as planar as in the MW. 
 These quantitative results place the LG at the level of a $3\sigma$
@@
 \centering
+\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
+\caption{Results}
+\end{figure*}
+
+\begin{figure*}
+\centering
 \includegraphics[width=0.45\textwidth]{gaussian_model_illustris1dark_M31_n_11.pdf}

### 2018-04-23 paper/paper.tex
updated caption

@@
 \includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
-\caption{Plane width characterization in observations and
-  simulations (Illustris-1-Dark in this case). In all panels the
-  horizontal/vertical axis corresponds to the  M31/MW or the
-  most/less massive halo in the pair. 
-  Left. Plane width in physical units comparing the results from observations
-(stars) against the result of spherically randomizing the satellite
-positions (circles). 
-Middle. Average from the observations (star) and the average from each
-pair in the simulation (circles).}
+\caption{Scalars describing satellite shape around the LG galaxies for
+  a fixed number of satellites $N_s$=11:
+  plane width $w$ in physical units, $c/a$ ratio and $b/a$ ratio.
+  Left: M31, rigth: MW. The square at the center are observations; the
+2D histograms are the contour levels after randomizing $10^4$ the
+satellite positions while keeping the radial distribution fixed; the
+blue circles are the results from Illustris-1-Dark. For the M31 these
+three results (observations, randomized observations and simulations)
+seem to be in broad agreement, while for the MW the three results
+clearly differ. The corresponding plots for Illustris-1 and ELVIS can
+be found in Figures \ref{fig:all_plots_illustris1} and
+\ref{fig:all_plots_elvis},
+respectively. \label{fig:physical_illustris1dark}}    
 \end{figure*}
@@
 \includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11_normed.pdf}
-\caption{Right. Same as the middle panel except that this time each point has
-been normalized (median substracted and normalized by the standard
-deviation) to the results of its randomization. 
-The main message of these panels is that the MW has a significantly
-thinner plane both compared to the result of its own satellite
-spherical randomization (left panel) and the expectation from
-simulations (middle and right panel).  
-This low value is $2\sigma$ away from what is expected in a spherical
-distribution. 
-In M31 the satellite distribution is in agreement with the
-expectations both from a spherical distribution and the results from the
-simulations. }
+\caption{Same layout as Figure \ref{fig:physical}. 
+  Each scalar
+  quantity is recentered and normalized by the mean value and standard
+  deviation from the $10^4$ randomizations. 
+  The distribution from the randomization now has by definition a mean
+of zero and standard deviation of one. 
+The results for the width and $c/a$ ratio of MW satellites are more
+than two standard deviations away from the mean. } 
 \end{figure*}
@@
   maximum circular velocity for the M31 and MW dark matter halo.
-\label{fig:physical}}
+\label{fig:phyical}}
 \end{figure}
@@
 \includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
-\caption{ELVIs results for the quantities presented for the Illustris1-Dark
+\caption{Illustris-1 results for the quantities presented for the Illustris1-Dark
   simulation in Figures  \ref{fig:scatter_width},
@@
 counterparts. 
-\label{fig:scatter_elvis}}
+\label{fig:all_plots_illustris1}}
 \end{figure*}
@@
 counterparts. 
-\label{fig:scatter_elvis}}
+\label{fig:all_plots_elvis}}
 \end{figure*}

### 2018-04-23 paper/paper.tex
caption

@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
+\caption{Normalized asphericity scalars from observations as a function
+  of satellite number, $N_s$. Left: plane width; center: $c/a$ ratio;
+  right: $b/a$ ratio. 
+  The plane width and $c/a$ ratio for the MW is
+  consistently consistently found beyond two standard
+  deviations; M31 shows the opposite trend and is always found
+  \emph{within} two standard deviations \label{fig:normalized_n}.} 
+\end{figure*}
+
 \subsection{Characterizing Asphericity}
@@
 seem to be in broad agreement, while for the MW the three results
-clearly differ. The corresponding plots for Illustris-1 and ELVIS can
-be found in Figures \ref{fig:all_plots_illustris1} and
+clearly differ. 
+The corresponding plots for Illustris-1 and ELVIS are
+in Figures \ref{fig:all_plots_illustris1} and
 \ref{fig:all_plots_elvis},
@@
 \includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11_normed.pdf}
-\caption{Same layout as Figure \ref{fig:physical}. 
+\caption{Same layout as Figure \ref{fig:physical_illustris1dark}. 
   Each scalar
@@
   deviation from the $10^4$ randomizations. 
-  The distribution from the randomization now has by definition a mean
-of zero and standard deviation of one. 
+  The distribution from the randomizations (plots over the diagonal)
+  now has by definition a mean of zero and standard deviation of one. 
 The results for the width and $c/a$ ratio of MW satellites are more
-than two standard deviations away from the mean. } 
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
-\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
-\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
-\caption{Results}
+than two standard deviations away from the mean. 
+The corresponding plots for Illustris-1 and ELVIS are
+in Figures \ref{fig:all_plots_illustris1} and
+\ref{fig:all_plots_elvis},
+respectively. \label{fig:normalized_illustris1dark}}     
 \end{figure*}

### 2018-04-25 paper/paper.tex
caption

@@
   \end{tabular}
-  \caption{Results from observations with $N_s=11$. 
-    for the different
-    quantities describing the satellite distributions: plane width, $c/a$
+  \caption{Results from observations with $N_s=11$ for the plane width, $c/a$
     ratio and $b/a$ ratio. 
-    The first column refers to the results from
-    observational data, the second column uses the spherically
-    randomized version of the observational data, the third column
-    corresponds to the observational data recentered and normalized
-    by the standard deviation of the randomized data. \label{table:observations}}
+    The first column refers to the results in physical units, the
+    second column uses the spherically  randomized version of the 
+    observational data and the third column corresponds to the
+    observational data recentered and normalized using the mean and standard
+    deviation from the randomized data. Figure \ref{fig:normalized_n}
+    shows all the normalized data results for $11\leq N_s\leq
+    15$\label{table:observations}.}  
 \end{table*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
+\caption{Normalized asphericity scalars from observations as a function
+  of satellite number, $N_s$. Left: plane width; center: $c/a$ ratio;
+  right: $b/a$ ratio. 
+  The plane width and $c/a$ ratio for the MW is
+  consistently consistently found beyond two standard
+  deviations; M31 shows the opposite trend and is always found
+  \emph{within} two standard deviations \label{fig:normalized_n}.} 
+\end{figure*}
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
-\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
-\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
-\caption{Normalized asphericity scalars from observations as a function
-  of satellite number, $N_s$. Left: plane width; center: $c/a$ ratio;
-  right: $b/a$ ratio. 
-  The plane width and $c/a$ ratio for the MW is
-  consistently consistently found beyond two standard
-  deviations; M31 shows the opposite trend and is always found
-  \emph{within} two standard deviations \label{fig:normalized_n}.} 
-\end{figure*}
-
 \subsection{Characterizing Asphericity}

### 2018-04-25 paper/paper.tex
new references

@@
 
-\subsection{Data from the Illustris project}
+\subsection{Simulated Data}
+
+We use data from three different simulations Illustris-1,
+Illustris-1-Dark and ELVIS. 
+In what follows we describe the relevant detailed of those
+simulations, how the halo pairs resembling the LG are selected and how
+the satellite samples for each halo is built.
+Figure \ref{fig:physical_pairs} summarizes the physical properties (maximum
+circular velocities, radial velocities and separation) of the halo
+pairs to be used.
+
+\subsubsection{Illustris-1 and Illustris-1-Dark}
 \label{sec:illustris}
@@
 \citep{2014MNRAS.444.1518V}. 
-This suite of cosmological simulations, performed using the quasi-Lagrangian
-code AREPO \citep{2010MNRAS.401..791S}, followed the coupled evolution of dark 
-matter and gas and includes parametrizations to account for the effects of
+This suite of cosmological simulations were performed using the quasi-Lagrangian
+code AREPO \citep{2010MNRAS.401..791S}.
+They followed the coupled evolution of dark  matter and gas and
+includes parametrizations to account for the effects of 
 gas cooling, photoionization, star formation, stellar feedback, black
@@
 We extract halo and galaxy information from the Illustris-1 and
-Illustris-1-Dark simulations, the former simulation includes
-hydrodynamics and star formation prescriptions while the latter only
+Illustris-1-Dark simulations. 
+The former includes hydrodynamics and star formation prescriptions while the latter only
 includes dark matter physics. 
@@
 $6.3\times 10^6$\Msun\ and a minimum mass for the baryonic volume
-element of $1.2\times 10^6$\Msun for Illustris-1 and a dark matter
-particle mass of $7.6\times 10^6$\Msun for Illustris-1-Dark.
+element of $1.2\times 10^6$\Msun\ for Illustris-1 and a dark matter
+particle mass of $7.6\times 10^6$\Msun\ for Illustris-1-Dark.
 In both simulations the dark matter gravitational softening is $1.4$
@@
 by ranking the subhalos in decreasing order of its current maximum
-circular velocity and select the first $N_p$ halos in the list.  
-Under these conditions the smallest sub-halos are sampled with at least $40$ particles.  
+circular velocity and select the first $N_s$ halos in the list.  
 The results presented here correspond to $11\leq N_p\leq 15$.
+
+These selection criteria are convenient because it allows us to direct
+our attention at baryonic physics as the driver behing the differences
+in the results between the two simulations. 
+Under these conditions the smallest sub-halos are sampled with at
+least $40$ particles. This approximation works well for the $~10$ most
+massive subhalos in MW type galaxies. 
+To a good approximation these are the systems with the highest
+circular velocity at infall \citep{2011MNRAS.415L..40B}, which is the
+physical quantity expected to best correlate with luminosity
+\citep{2004ApJ...609...35K,2006ApJ...647..201C,2010MNRAS.404.1111G}.
 
@@
 In this paper we only use the results from these $12$ resimulated pairs.
-
-Appendix A compares the physical properties (maximum circular
-velocities, radial velocities and separation) in those pairs against
-the results from the Illustris-1 simulations.
+To be consistent with the satellite selection in Illustris-1 we also
+select satellites by ranking them by maximum circular velocity,
 
@@
   deviations; M31 shows the opposite trend and is always found
-  \emph{within} two standard deviations \label{fig:normalized_n}.} 
+  \emph{within} two standard deviations. \label{fig:normalized_n}} 
 \end{figure*}
@@
   maximum circular velocity for the M31 and MW dark matter halo.
-\label{fig:phyical}}
+\label{fig:physical_pairs}}
 \end{figure}

### 2018-04-25 paper/paper.tex
latest update

@@
 
-We buid a sample of pairs that resemble the conditions in the LG.
-To construct this sample we select from Illustris-1 all the galaxies with a stellar
-mass in the range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11}
-\Msun$.
+We buid a sample of pairs that resemble the conditions in the LG as follows.
+First, we select from Illustris-1 all the galaxies with a stellar mass
+in the range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
 Then we select the pairs with the following conditions.
@@
 \item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
-the closest to halo $B$, the two are considered as a pair. 
+the closest to $B$, the two are considered as a pair. 
 \item With $d_{AB}$ the distance between the two galaxies and
@@
 We find 27 pairs with these conditions. 
-We then select the pairs where in both halos there are at least 15
-detected subhalos, thus discarding pairs with halos with the lowest
-mass.
-We end up with a total of 20 pairs in Illustris-1.
-
 In Illustris-1-Dark we use the center of mass position of the 27 pairs
@@
 pairs Mpc$^{-3}$. 
-Appendix A shows the maximum, circular velocities, radial velocities and separation of those pairs.
+Figure \ref{fig:physical_pairs} summarizes the physical properties (maximum
+circular velocities, radial velocities and separation) of the halo
+pairs to be used.
 
 Although Illustris-1 has stellar particles, we do not use their
-properties to select the satelite population.
+properties to select the satelite population for the results reported
+here. 
 The smallest galaxies are barely resolved in stellar mass at
@@
 satellites, we use instead the dark matter information. 
-Both in Illustris-1 and Illustris-1-Dark we chose the satellite samples
-by ranking the subhalos in decreasing order of its current maximum
-circular velocity and select the first $N_s$ halos in the list.  
-The results presented here correspond to $11\leq N_p\leq 15$.
-
-These selection criteria are convenient because it allows us to direct
-our attention at baryonic physics as the driver behing the differences
-in the results between the two simulations. 
+However, we tested using $M_V$ in Illustris-1 as a selection criteria
+and the results we report here are not strongly influenced by that
+choice.
+
+We decide to use both in Illustris-1 and Illustris-1-Dark the same
+satellite selection rules.
+Namely, selecting the satellites by ranking the subhalos in decreasing
+order of its current maximum circular velocity and select the first
+$N_s$ halos in the list. 
+These selection criteria are also convenient.
+They allow us to direct our attention at baryonic physics as the driver
+behind the differences in the results between the two simulations. 
 Under these conditions the smallest sub-halos are sampled with at
-least $40$ particles. This approximation works well for the $~10$ most
-massive subhalos in MW type galaxies. 
-To a good approximation these are the systems with the highest
-circular velocity at infall \citep{2011MNRAS.415L..40B}, which is the
-physical quantity expected to best correlate with luminosity
+least $40$ particles. This approximation works well for the $\approx 10$ most
+massive subhalos in MW type galaxies; to a good approximation these
+are the systems with the highest circular velocity at infall
+\citep{2011MNRAS.415L..40B}, which is the physical quantity expected
+to best correlate with luminosity
 \citep{2004ApJ...609...35K,2006ApJ...647..201C,2010MNRAS.404.1111G}.
@@
 
-This corresponds to a pair number density of $\sim 8 \times10^{-6}$ pairs
-Mpc$^{-3}$, this is a factor $\sim 2.5$ lower than the pair number density
-we find in the Illustris-1 data.
+This corresponds to a number density of $\sim 8 \times10^{-6}$
+pairs/Mpc$^{3}$, which is a factor $\sim 2.5$ lower than the pair
+number density we find in the Illustris-1 data.
 There were a total of 146 pairs that met those criteria, but only $12$
@@
 The dark matter particle resolution in these resimulations is
-$1.9\times 10^5$, a thousand times better than Illustris-1.
+$1.9\times 10^5$, an order of magnitude times better than Illustris-1.
 In this paper we only use the results from these $12$ resimulated pairs.
-To be consistent with the satellite selection in Illustris-1 we also
-select satellites by ranking them by maximum circular velocity,
+To be consistent with the satellite selection in Illustris-1 and
+Illustris-1-Dark we also select satellites by ranking them by their
+maximum circular velocity.
 
@@
     The first column summarizes the results from the 27 pairs in
-    Illustris-1-Dark, the second column from the 23 pairs in
+    Illustris-1-Dark, the second column from the 24 pairs in
     Illustris-1 and the third column from the 12 pairs in the

### 2018-04-28 paper/paper.tex
caption

@@
 \caption{Normalized asphericity scalars from observations as a function
-  of satellite number, $N_s$. Left: plane width; center: $c/a$ ratio;
+  of satellite number. Left: plane width; center: $c/a$ ratio;
   right: $b/a$ ratio. 
   The plane width and $c/a$ ratio for the MW is
-  consistently consistently found beyond two standard
-  deviations; M31 shows the opposite trend and is always found
+  consistently found beyond two standard
+  deviations.
+  M31 shows the opposite trend and is always found
   \emph{within} two standard deviations. \label{fig:normalized_n}} 
@@
 \includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11_normed.pdf}
-\caption{Same layout as Figure \ref{fig:physical_illustris1dark}. 
+\caption{
+Same layout as Figure \ref{fig:physical_illustris1dark}. 
   Each scalar
@@
 \includegraphics[width=0.45\textwidth]{gaussian_model_illustris1dark_MW_n_11.pdf}
-\caption{Results from multivariate gaussian model fitted to the
-  normalized values for the plane width $w$, $c/a$ ratio and $b/a$
-  ratio from the Illustris-1-Dark results.  
-  Left/right panel correspond to M31/MW respectively.  
-  The cross indicates the observed values.
-  The contour levels in the 2D histograms correspond to the $1\sigma$,
-$2\sigma$ and $3\sigma$ contours in two dimensions.
-  The dashed vertical lines in the histograms along the diagonal
-  correspond to the $1\sigma$ boundaries in one dimension.
-  The results for the gaussian model are built from $10^6$ point
-  realizations in the three-dimensional space spanned by the variables of
-  interest for each halo. 
-  This plot clearly shows how the M31 results are well within the
-  expectations from simulations while the MW has an unusual low value for
-  the plane width and the $c/a$ axis ratio.
-\label{fig:correlations_illustrisdm}}
+\caption{
+Same layout as Figure \ref{fig:normalized_illustris1dark}. 
+This time the distribution comes from the multivariate gaussian model 
+with its parameters estimated from the Illustris-1-Dark results.
+The corresponding plots for Illustris-1 and ELVIS are
+in Figures \ref{fig:all_plots_illustris1} and \ref{fig:all_plots_elvis},
+respectively. \label{fig:gaussian_illustris1dark}}     
 \end{figure*}
@@
 \includegraphics[width=0.32\textwidth]{MW_numbers.pdf}
-\caption{Probability distribution for the expected number of M31 and
-  MW halos showing the same degree of atypicality as the Local Group if drawn
-  from a sample of $10^4$ isolated pairs. 
-  The distributions correspond to results derived from Illustris-1-Dark, Illustris,
-  and ELVIS data.
-  In the most optimistic case (Illustris-1-Dark), $1\%$ of the pairs have
-  two halos with properties similar to the LG. 
-  In the case of Illustris-1 this percentage drops to $0.1\%$ and
-  $0.01\%$ for ELVIS. 
+\caption{
+Percentage of systems that have asphericity scalars as extreme as the
+LG (left), M31 (middle) and MW (right).  
+This percentage is computed as a function of satellite number for all
+the three simulations (Illustris-1-Dark, Illustris-1 and ELVIS).
+The common trend is that at most of $2\%$ of LG-like pairs are expected to
+be as extreme as observations, with most of the weight of this
+atypicallity falls onto the MW; at most $4\%$ of similar systems have
+such an aspherical satellite distribution. 
 \label{fig:expected_number}}
@@
 quantities being bound.
-We estimated the mean and covariance of {\color{red}these} distributions using
+We estimated the mean and covariance of these distributions using
 the results of LG pairs coming from three different numerical

### 2018-04-30 paper/paper.tex
covariance matrix illustris1dark
cov matrices in paper
referee report, paper corrections and bib file

@@
 by \cite{1976RGOB..182..241K} and \cite{1976MNRAS.174..695L}.  
-Fourty years later \cite{2005A&A...431..517K} quantified that the
+Forty years later \cite{2005A&A...431..517K} quantified that the
 highly planar distribution of the 11 classical MW satellites has less
@@
 distribution in a special subset of $15$ satellites out of the 
-total poulation of $27$ satellites \citep{2013ApJ...766..120C,
+total population of $27$ satellites \citep{2013ApJ...766..120C,
 2013Natur.493...62I}, although considering the satellites ranked by
 luminosity does not show any special feature.
+Additionally \cite{2015ApJ...799L..13C} studied the observed
+properties of several M31 satellites and concluded that there were no differences between
+the on- and off-plane dwarf galaxies. This suggests that it is
+unlikely that the on- and off-plane satellite galaxies have different
+formation histories and that therefore the plane of satellites could
+not be explained as being the result of a special formation
+mechanism.
 All published studies agree on the point that the spatial distribution of
@@
 Those tables also include the results from this paper using the
-methodolgy we describe in the upcoming sections.}.
+methodology we describe in the upcoming sections.}.
 
@@
 \text{\cite{2014ApJ...789L..24P}}& $c/a$ and $b/a$ ratio in 11
-classical satellites & 48 high resoltion DM only N-body simulations
+classical satellites & 48 high resolution DM only N-body simulations
 ($\sim 10^{5}$\Msun particle mass resolution) of both halo pairs and
@@
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
-satellites & 20 halos from selected pairs in acosmological N-body
+satellites & 20 halos from selected pairs in a cosmological N-body
 hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& 0.6 \\
@@
 small size, making it hard to derive robust probabilities by counting.   
-In this paper we present and demostrate a method to overcome these two
+In this paper we present and demonstrate a method to overcome these two
 limitations.
@@
 Illustris-1 has $1820^3$ dark matter particles and $1820^3$ initial gas
-volumen elements, while Illustris-1-Dark has $1820^3$ dark matter particles.
+volume elements, while Illustris-1-Dark has $1820^3$ dark matter particles.
 This corresponds to a dark matter particle mass of
@@
 
-We buid a sample of pairs that resemble the conditions in the LG as follows.
+We build a sample of pairs that resemble the conditions in the LG as follows.
 First, we select from Illustris-1 all the galaxies with a stellar mass
@@
 Although Illustris-1 has stellar particles, we do not use their
-properties to select the satelite population for the results reported
+properties to select the satellite population for the results reported
 here. 
@@
 The ELVIS project used the results from $50$ simulation boxes of side
-lenght $70.4$ Mpc to select pairs with kinematic characteristics
+length $70.4$ Mpc to select pairs with kinematic characteristics
 similar to the LG. 
@@
 This allows us to build a normalized version of all quantities of
-interest by substracting the mean and dividing by the standard
+interest by subtracting the mean and dividing by the standard
 deviation of the randomized samples.
@@
 distributions for the normalized $w$, $c/a$ and $b/a$ are indeed
-consistent with gaussian ditributions.
+consistent with gaussian distributions.
 
@@
 with a jackknife technique. 
-That is, out of the $n$ pairs in each simulation, we perfom $n$
+That is, out of the $n$ pairs in each simulation, we perform $n$
 different covariance and mean value measurements using only $n-1$ pairs. 
@@
 always measure the fraction of points with absolute values larger than the
-treshold absolute observed value.
+threshold absolute observed value.
 
@@
   plane width $w$ in physical units, $c/a$ ratio and $b/a$ ratio.
-  Left: M31, rigth: MW. The square at the center are observations; the
+  Left: M31, right: MW. The square at the center are observations; the
 2D histograms are the contour levels after randomizing $10^4$ the
@@
 the MW compared to a M31 distribution closer to spherical, 
-The $b/a$ ratio is statisically the same between observations and the
+The $b/a$ ratio is statistically the same between observations and the
 spherical randomization. 
@@
 be as extreme as observations, with most of the weight of this
-atypicallity falls onto the MW; at most $4\%$ of similar systems have
+atypicality falls onto the MW; at most $4\%$ of similar systems have
 such an aspherical satellite distribution. 
@@
 
-Among the three simulations, the results infered from ELVIS data show
+Among the three simulations, the results inferred from ELVIS data show
 the lowest fraction of M31 and MW systems; for Illustris-1-Dark we have
@@
 
-In this paper we developed and demostrated a method to quantify the
+In this paper we developed and demonstrated a method to quantify the
 asphericity of the satellite distribution around the MW and M31.  
@@
 Then, we measure the same quantities for the same set of points after
-the spherical randomziation process.
+the spherical randomization process.
 Finally, we renormalize the initial results to the mean value and
@@
 This approach is particularly useful in the case of atypical
-observables, as it allows for an atypicallity
+observables, as it allows for an atypicality
 quantification without the need to build explicit samples of objects
@@
 information that points at an atypical configuration in LCDM.
-We also have the number of satellites as bright as the Mageallanic
+We also have the number of satellites as bright as the Magellanic
 Clouds, only expected in $5\%$ of galaxies

### 2018-04-30 paper/paper.tex
edit

--- 2018-04-28 paper/paper.tex
@@
 Detailed results differ greatly among the simulations suggesting a
-strong influence of the typical DM halo mass, the methodology to
-select the satellites and the simulated baryonic effects. 
+strong influence of the typical DM halo mass, the number of satellites
+and the simulated baryonic effects.   
 However, there are three common trends.
@@
 We suggest that understanding the reasons for this atypicality
-will require quantifying the asphericity probability distribution as a
+requires quantifying the asphericity probability distribution as a
 function of halo mass and large scale environment.
@@
 \citep{2006AJ....131.1405K,2007MNRAS.374.1125M, 2013ApJ...766..120C}.
-%comentario: no estoy segura de que el paper de Conn esté bien citado acá.
-el dice "It is clear that while the satellites of M31 when taken as a whole are no more planar than one can expect from a random distribution, a subset consisting of roughly half the sample is remarkably planar".
-Y en esta citación "15 to 27 brightest satellites" me parece que puede sonar contradictorio con lo que dice Conn.
+
 Table \ref{table:M31} and Table \ref{table:MW} summarize some more
@@
     observational data and the third column corresponds to the
-    observational data recentered and normalized using the mean and standard
+    observational data re-centered and normalized using the mean and standard
     deviation from the randomized data. Figure \ref{fig:normalized_n}
@@
   Each scalar
-  quantity is recentered and normalized by the mean value and standard
+  quantity is re-centered and normalized by the mean value and standard
   deviation from the $10^4$ randomizations. 
@@
 \label{appendix:covariance}
-\subsection{Illustris-1}
+\subsection{Illustris-1-Dark}
 
 \subsubsection{M31}
-
 \[
@@
 \begin{bmatrix}
-0.83\pm 0.03  & 0.78\pm 0.04  & 0.41\pm 0.04\\
-0.78\pm 0.04  & 1.16\pm 0.05 & -0.15\pm 0.05\\
-0.41\pm 0.04 & -0.15\pm 0.05 & 0.96\pm 0.04\\
+2.02 \pm 0.09 & 1.46 \pm 0.09 & 0.97 \pm 0.07\\
+1.46 \pm 0.09 & 1.69 \pm 0.10 & -0.01 \pm 0.05\\
+0.97 \pm 0.07 & -0.01 \pm 0.05 & 1.42 \pm 0.08\\
 \end{bmatrix}
@@
 \begin{bmatrix}
--0.18\pm 0.04 & -0.41\pm 0.05 & -0.20\pm 0.05\\
+-0.43 \pm 0.06 & -0.56 \pm 0.06 & -0.17 \pm 0.05\\
 \end{bmatrix}
@@
 \begin{bmatrix}
- 0.78\pm 0.06 & 0.63 \pm 0.07  & 0.40 \pm 0.03\\
-  0.63\pm 0.07 & 0.69 \pm 0.08 &  0.06 \pm 0.02\\
-  0.40\pm 0.03 & 0.06 \pm 0.02 &  0.61\pm 0.04\\
+0.94 \pm 0.04 & 0.71 \pm 0.04 & 0.36 \pm 0.03\\
+0.71 \pm 0.04 & 0.93 \pm 0.05 & -0.27 \pm 0.03\\
+0.36 \pm 0.03 & -0.27 \pm 0.03 & 0.94 \pm 0.04\\
 \end{bmatrix}
@@
 \begin{bmatrix}
--0.17\pm 0.04 & -0.40\pm 0.04 & -0.23\pm 0.04\\
+-0.40 \pm 0.04 & -0.69 \pm 0.04 & -0.19 \pm 0.04\\
 \end{bmatrix}
@@
 
-\subsection{Illustris-1-Dark}
-
+\subsection{Illustris-1}
 \subsubsection{M31}
-
 \[
@@
 \begin{bmatrix}
- 1.50\pm 0.08 & 1.27\pm 0.08 & 0.64\pm 0.04\\
-  1.27\pm 0.08 &  1.31\pm 0.08&  0.28\pm 0.04\\
-  0.64\pm 0.04 &  0.28\pm 0.04 & 0.70\pm 0.04\\
+1.59 \pm 0.08 & 1.23 \pm 0.07 & 0.80 \pm 0.06\\
+1.23 \pm 0.07 & 1.44 \pm 0.08 & 0.01 \pm 0.06\\
+0.80 \pm 0.06 & 0.01 \pm 0.06 & 1.26 \pm 0.08\\
 \end{bmatrix}
 \]
-
 \[
@@
 \begin{bmatrix}
--0.37\pm 0.05& -0.55\pm 0.05 & -0.13\pm 0.03\\
+0.03 \pm 0.06 & -0.24 \pm 0.06 & -0.01 \pm 0.05\\
 \end{bmatrix}
 \]
-
 \subsubsection{MW}
-
 \[
@@
 \begin{bmatrix}
- 1.03\pm 0.05 & 0.94\pm 0.05  & 0.36\pm 0.03\\
-  0.94\pm 0.05 & 1.24\pm 0.07 & -0.18\pm 0.04\\
-  0.36\pm 0.03 & -0.18\pm 0.04  & 0.86\pm 0.03\\
+1.01 \pm 0.05 & 0.72 \pm 0.05 & 0.62 \pm 0.04\\
+0.72 \pm 0.05 & 0.78 \pm 0.05 & 0.12 \pm 0.03\\
+0.62 \pm 0.04 & 0.12 \pm 0.03 & 0.80 \pm 0.04\\
 \end{bmatrix}
 \]
-
 \[
@@
 \begin{bmatrix}
--0.45\pm 0.04 & -0.61\pm 0.05 & -0.31\pm 0.04\\
+-0.07 \pm 0.05 & -0.45 \pm 0.04 & 0.02 \pm 0.04\\
 \end{bmatrix}
@@
 \subsubsection{M31}
-
 \[
@@
 \begin{bmatrix}
- 1.60\pm 0.19  & 1.22\pm 0.14 & 0.70 \pm 0.09\\
-  1.22\pm 0.14 &  1.08\pm 0.10 & 0.35 \pm 0.05\\
-  0.70\pm 0.09 & 0.35\pm 0.05  & 0.63 \pm 0.10\\
+1.77 \pm 0.23 & 1.44 \pm 0.18 & 0.65 \pm 0.09\\
+1.44 \pm 0.18 & 1.54 \pm 0.15 & 0.15 \pm 0.06\\
+0.65 \pm 0.09 & 0.15 \pm 0.06 & 0.77 \pm 0.11\\
 \end{bmatrix}
 \]
-
 \[
@@
 \begin{bmatrix}
--0.18\pm 0.08 & -0.28\pm 0.07 &-0.22\pm 0.05\\
+0.07 \pm 0.09 & -0.06 \pm 0.08 & -0.08 \pm 0.06\\
 \end{bmatrix}
 \]
-
 \subsubsection{MW}
-
 \[
@@
 \begin{bmatrix}
- 0.45\pm 0.04 & 0.61\pm0.09 & -0.11\pm0.09 \\
-  0.61\pm0.09 & 1.21\pm0.17 & -0.63\pm0.09\\
- -0.11\pm0.05 & -0.63\pm0.09 & 0.64\pm0.06\\
+0.59 \pm 0.06 & 0.61 \pm 0.11 & 0.11 \pm 0.08\\
+0.61 \pm 0.11 & 1.25 \pm 0.19 & -0.71 \pm 0.12\\
+0.11 \pm 0.08 & -0.71 \pm 0.12 & 1.13 \pm 0.11\\
 \end{bmatrix}
 \]
-
 \[
@@
 \begin{bmatrix}
--0.32\pm 0.04 & -0.74\pm 0.07 &-0.08\pm 0.05\\
+-0.25 \pm 0.05 & -0.59 \pm 0.08 & -0.16 \pm 0.07\\
 \end{bmatrix}

### 2018-04-30 paper/paper.tex
edit

@@
 
-In the case of M31, observational studies have found a planar satellite
-distribution in a special subset of $15$ satellites out of the 
-total poulation of $27$ satellites \citep{2013ApJ...766..120C,
-2013Natur.493...62I}, although considering the satellites ranked by
-luminosity does not show any special feature.
-All published studies agree on the point that the spatial distribution of
-the 15 to 27 brightest satellites are consistent with spherically
-symmetric distributions and easy to reproduce in LCDM simulations
+In the case of M31, all studies agree on the point that the spatial
+distribution of the 15 to 27 brightest satellites  are consistent with
+spherically symmetric distributions and easy to reproduce in LCDM simulations
 \citep{2006AJ....131.1405K,2007MNRAS.374.1125M, 2013ApJ...766..120C}.
+In a very different observational statement, there is  subset of $15$
+satellites out of the  total poulation of $27$ satellites
+\citep{2013ApJ...766..120C, 2013Natur.493...62I} that shows a very
+planar distribution. 
+However, in this paper we do not address these \emph{plane finding}
+algorithms and focus instead on the characterization of the satellite
+distribution ranked by decreasing luminosity, maximum circular
+velocity or stellar mass.
 
@@
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
-satellites & 24 halos from selected pairs in a cosmological N-body Dark Matter only simulation ($\sim
-10^{6}$\Msun particle mass resolution)& 56 \\
+satellites & 27 halos from selected pairs in a cosmological N-body Dark Matter only simulation ($\sim
+10^{6}$\Msun particle mass resolution)& $<80$ \\
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
-satellites & 20 halos from selected pairs in a cosmological N-body hydro simulation ($\sim
-10^{6}$\Msun particle mass resolution)& 27 \\
+satellites & 24 halos from selected pairs in a cosmological N-body hydro simulation ($\sim
+10^{6}$\Msun particle mass resolution)& $<71$ \\
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 12 high resolution DM only N-body simulations ($\sim
-10^{5}$\Msun particle mass resolution) of halo pairs & 37 \\
+10^{5}$\Msun particle mass resolution) of halo pairs & $<57$ \\
 \hline
@@
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
-satellites & 24 halos from selected pairs in a cosmological N-body
-Dark Matter only simulation ($\sim 10^{6}$\Msun particle mass resolution)& 3\\
+satellites & 27 halos from selected pairs in a cosmological N-body
+Dark Matter only simulation ($\sim 10^{6}$\Msun particle mass
+resolution)& $<4$\\
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
-satellites & 20 halos from selected pairs in acosmological N-body
-hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& 0.6 \\
+satellites & 24 halos from selected pairs in acosmological N-body
+hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& $<1.5$ \\
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
 satellites & 12 high resolution DM only N-body simulations ($\sim
-10^{5}$\Msun particle mass resolution) of halo pairs & 0.2 \\
+10^{5}$\Msun particle mass resolution) of halo pairs & $<1.6$\\
 \hline

### 2018-04-30 paper/paper.tex
edit

@@
 velocity or stellar mass.  
-
 Table \ref{table:M31} and Table \ref{table:MW} summarize some more
@@
 \caption{Probability to find  the triaxiality and/or root mean squared
-  (RMS) height of M31 satellites in LCDM simulations. 
+  (RMS) width of M31 satellites in LCDM simulations. 
 \label{table:M31}}
@@
 \Msun\ particle mass resolution). & High\\ 
-\text{\cite{2005ApJ...629..219Z}} & $c/a$ ratio and disk height in 
+\text{\cite{2005ApJ...629..219Z}} & $c/a$ ratio and disk width in 
 11 classical satellites & 3 high resolution DM only N-body

### 2018-04-30 paper/paper.tex
refs

@@
 halos are closer to spherical once baryonic effects are included. 
-For instance the mean value for the normalized width goes closer to
-zero, from $-0.45\pm 0.04$  to $-0.17\pm0.04$, and the same is true
-for the $c/a$ ratio that changes from $-0.61\pm0.04$ in the DM only
-simulation to $-0.40\pm 0.04$ in Illustris-1.  
+For instance for $N_p=11$ the mean value for the normalized width goes
+closer to zero, from $-0.43\pm 0.04$  to $-0.03\pm0.06$, and the same
+is true for the $c/a$ ratio that changes from $-0.56\pm0.06$ in the DM
+only simulation to $-0.24\pm 0.06$ in Illustris-1.  
+This trend has been reported before for the DM distribution in the
+whole halo \cite{2013MNRAS.429.3316B}.
+Our results suggest that it also hold for the satellite distribution.
 We postpone a detailed quantification of this effect for a future

### 2018-04-30 paper/paper.tex
discussion

@@
 asphericity of the satellite distribution around the MW and M31.  
-In the interest of keeping the method straightforward and robust we
+In the interest of keeping the demonstration straightforward and robust we
 focus on the asphericity estimates for a fixed number of the brightest
@@
 We found that these normalized quantities are well described by
-a multivariate gaussian distribution in spite of the original
-quantities being bound.
+a multivariate gaussian distribution 
 We estimated the mean and covariance of these distributions using
@@
 
-We found that in the best case (Illustris1-Dark) the degree of
-asphericity in the observed LG is only expected in $3\pm2$ pairs out
-of a sample of $10^4$ isolated pairs. 
+We found that in the best case (Illustris-1-Dark) the degree of
+asphericity in the observed LG is only expected in $2\%$ of the
+pairs. 
 This places the LG as a $3\sigma$ outlier.   
@@
 recent results by \cite{2015ApJ...815...19P}. 
-We estimated that with the M31 between $37\%$ and $58\%$ of the pairs show aspherical characteristics larger than M31, while
-this fraction drops to less than $1\%$ for the MW. 
+We estimated that with the M31 between $5\%$ and $80\%$ of the pairs
+show aspherical characteristics larger than M31, while this fraction
+drops to less than $4\%$ for the MW.  
 These fractions are robust to changes in the numerical simulations,
-the criteria used to define the pairs and to the methods used to
-estimate the parameters of the multivariate normal distribution.
+the criteria used to define the pairs, the way to select the
+satellites and to the methods used to estimate the parameters of the
+multivariate normal distribution.
 
@@
 This approach is particularly useful in the case of atypical
-observables, as it allows for an atypicallity
-quantification without the need to build explicit samples of objects
-that are already scarce and difficult to find in simulations.
+observables, as it allows for an atypicallity quantification without
+building explicit samples of objects that are already scarce and
+difficult to find in simulations.
 
@@
 with similar environmental characteristics \citep{ForeroRomero2013}.  
+Quantifying whether these four characteristics are correlated one would
+need a simulation with
+
+Assuming that these properties are independent one would need at
+least $10^6$ pairs in order to find a single pair that meets all four
+characteristics (aspherical satellite distribution, bright Magellanic
+Clouds, satellite velocity anisotropy and atypical pair kinematics).
+Using the number density for pairs in Illustris-1 ($2\times 10^{-5}$
+pairs/Mpc$^{3}$) this would imply a cubic simulation volume of $5$ Gpc on a
+side, something unfeasible under current technology.
+However, studying two characteristics at a time to find possible
+correlations, and at least one pair resembling observations, reduces
+the box size to $500$ Mpc, something that is close to current
+simulations such as Illustris-TNG \citep{2018MNRAS.473.4077P}.
 
@@
 \citep{2011MNRAS.417.1434F,2014MNRAS.443.1090F,2015ApJ...799...45F,2015MNRAS.452.1052L},
-we claim that detailed studies of the satellite asphericity as a function
-of halo mass and cosmic web environment are still missing to
-understand what features in the initial conditions of our LG
-are responsible for the extreme features observed in its satellite
+we claim that detailed studies of the satellite asphericity as a
+function of halo mass and cosmic web environment are still missing to
+understand what features in the initial conditions of our LG are
+responsible for the extreme features observed in its satellite
 distribution.

### 2018-04-30 paper/paper.tex
new refs

@@
 In the case of M31, all studies agree on the point that the spatial
-distribution of the 15 to 27 brightest satellites  are consistent with
+distribution of the $15$ to $27$ brightest satellites  are consistent with
 spherically symmetric distributions and easy to reproduce in LCDM simulations
 \citep{2006AJ....131.1405K,2007MNRAS.374.1125M, 2013ApJ...766..120C}.
-In a very different observational statement, there is  subset of $15$
-satellites out of the  total poulation of $27$ satellites
-\citep{2013ApJ...766..120C, 2013Natur.493...62I} that shows a very
-planar distribution. 
+In a very different observational statement, there is a subset of $15$
+satellites out of the total population of $27$ satellites that show a
+highly planar distribution
+\citep{2013ApJ...766..120C,2013Natur.493...62I,2015ApJ...799L..13C}.
+This so-called satellite plane is deemed to be difficult to produce in
+LCDM simulations and is thought to be transient structure
+\citep{2015MNRAS.452.3838C,2015ApJ...809...49B,2015ApJ...800...34G,2016MNRAS.460.4348B,2017MNRAS.466.3119A,2017MNRAS.465..641F}.  
 However, in this paper we do not address these \emph{plane finding}
 algorithms and focus instead on the characterization of the satellite
-distribution ranked by decreasing luminosity, maximum circular
+distribution ranked either by decreasing luminosity, maximum circular
 velocity or stellar mass.  
@@
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
-satellites & 24 halos from selected pairs in acosmological N-body
+satellites & 24 halos from selected pairs in ac osmological N-body
 hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& $<1.5$ \\
@@
 This approach is particularly useful in the case of atypical
-observables, as it allows for an atypicallity quantification without
+observables, as it allows for an atypicality quantification without
 building explicit samples of objects that are already scarce and

### 2018-05-01 paper/paper.tex
edit

@@
 However, in this paper we do not address these \emph{plane finding}
-algorithms and focus instead on the characterization of the satellite
-distribution ranked either by decreasing luminosity, maximum circular
-velocity or stellar mass.  
+algorithms and focus instead on the characterization of the global
+satellite distribution ranked either by decreasing luminosity, maximum
+circular velocity or stellar mass. 
 Table \ref{table:M31} and Table \ref{table:MW} summarize some more
@@
 This Work & $c/a$ ratio, $b/a$ ratio and RMS width in 11-15 brightest
-satellites & 24 halos from selected pairs in ac osmological N-body
+satellites & 24 halos from selected pairs in a cosmological N-body
 hydro simulation ($\sim 10^{6}$\Msun particle mass resolution)& $<1.5$ \\
@@
 the LG (i.e. its stellar mass content, morphology or kinematics) have
-a low cosmological number density, this means that for the current
-cosmological volumes in simulations the high level parent sample has a
-small size, making it hard to derive robust probabilities by counting.   
+a low cosmological number density \citep{ForeroRomero2013}, this means
+that for the current cosmological volumes in simulations the high
+level parent sample has a small size, making it hard to derive robust
+probabilities by counting.    
 In this paper we present and demonstrate a method to overcome these two
@@
 
-We use data from three different simulations Illustris-1,
+We use data from three different simulations: Illustris-1,
 Illustris-1-Dark and ELVIS. 
@@
 satellites, we use instead the dark matter information.
-However, we tested using $M_V$ in Illustris-1 as a selection criteria
-and the results we report here are not strongly influenced by that
-choice.
-
-We decide to use both in Illustris-1 and Illustris-1-Dark the same
-satellite selection rules.
+
+We decide to use the same satellite selection rules both in
+Illustris-1 and Illustris-1-Dark. 
 Namely, selecting the satellites by ranking the subhalos in decreasing
@@
 $N_s$ halos in the list. 
-These selection criteria are also convenient.
-They allow us to direct our attention at baryonic physics as the driver
-behind the differences in the results between the two simulations. 
+These selection criteria also  allow us to direct our attention at
+baryonic physics as the driver behind the differences in the results
+between the two simulations.  
 Under these conditions the smallest sub-halos are sampled with at
-least $40$ particles. This approximation works well for the $\approx 10$ most
-massive subhalos in MW type galaxies; to a good approximation these
+least $40$ particles. 
+To a good approximation these
 are the systems with the highest circular velocity at infall
@@
 Wilkinson Microwave Anisotropy Probe 7 results.
-
 The ELVIS project used the results from $50$ simulation boxes of side
@@
 To be consistent with the satellite selection in Illustris-1 and
-Illustris-1-Dark we also select satellites by ranking them by their
+Illustris-1-Dark we select satellites by ranking them by their
 maximum circular velocity.
@@
 We compare the joint satellite distributions in the MW and M31 at fixed
-satellite number, $N_p$.
-This means that the magnitude cut corresponding to the faintest
-satellite included in the sample is different in each case.
-We make this choice to rule out the influence of satellite numbers
-in the statistics.
-
-We compute the satellite statistics for 11 up to 15 satellites.
+satellite number, $N_s$.
+This means that the maximum circular velocity cut corresponding to the
+smallest satellite included in the sample is different in each case.
+We make this choice to explicitly model the influence of satellite numbers
+on the statistics.
+
+We compute the satellite statistics for $11\leq N_s\leq 15$.
 The lower limit corresponds to the number of classical MW satellites,
@@
 magnitude.
+
+We also tested using $M_V$ and stellar mass in Illustris-1, and the
+stellar mass in ELVIS (provided through abundance matching) as a
+selection criterion. Our main conclusions remain unchanged by that
+choice.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
+\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
+\caption{Normalized asphericity scalars from observations as a function
+  of satellite number. Left: plane width; center: $c/a$ ratio;
+  right: $b/a$ ratio. 
+  The plane width and $c/a$ ratio for the MW is
+  consistently found beyond two standard
+  deviations.
+  M31 shows the opposite trend and is always found
+  \emph{within} two standard deviations. \label{fig:normalized_n}} 
+\end{figure*}
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
-\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
-\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
-\caption{Normalized asphericity scalars from observations as a function
-  of satellite number. Left: plane width; center: $c/a$ ratio;
-  right: $b/a$ ratio. 
-  The plane width and $c/a$ ratio for the MW is
-  consistently found beyond two standard
-  deviations.
-  M31 shows the opposite trend and is always found
-  \emph{within} two standard deviations. \label{fig:normalized_n}} 
-\end{figure*}
-
 \begin{table*}
@@
 position. 
-We repeat this procedure 1000 times for each satellite distribution
+We repeat this procedure $10^4$ times for each satellite distribution
 and proceed to measure the quantities mentioned in the previous section:
 $w$, $c/a$ and $b/a$.
-For each quantity we compute the average and standard deviation from
-the 1000 random samples. 
 This allows us to build a normalized version of all quantities of
 interest by subtracting the mean and dividing by the standard
-deviation of the randomized samples.
-These normalized quantities are used to build the explicit probability
+deviation of the values from randomized samples.
+We use the normalized quantities to build the explicit probability
 distributions for the scalars describing asphericity.
@@
 observational data.  
-We use a double-tailed test in this comparison, meaning that we
+We use a double-tailed test around the mean in this comparison, meaning that we
 always measure the fraction of points with absolute values larger than the
-threshold absolute observed value.
+absolute observed value with the mean substracted.
 
@@
 
-Table \ref{table:observations} and Table \ref{table:simulations}
-summarize the mean values and uncertainties for the plane $w$, $c/a$
-ratio and $b/a$ ratio in the observations and simulations, respectively. 
-The uncertainty in the observations is computed from the results with
-different number of satellites; in the simulations it corresponds to
-the standard deviation over different halos.
-
-The observed widths $w$ are always smaller than its randomized version.
-For M31 there is barely a ratio of $0.92$ between observed and
-randomized, while for the MW this factor goes down to less than half
-$0.48$. 
-The observed $c/a$ ratio follows the same extreme trend for
-the MW compared to a M31 distribution closer to spherical, 
-The $b/a$ ratio is statistically the same between observations and the
-spherical randomization. 
+Figure \ref{fig:normalized_n} shows, as a function of the number of
+satellites, the normalized plane width $w$, $c/a$ ratio and
+$b/a$ ratio from observations. 
+The most oustanding feature of this plot is that for $w$ and $c/a$
+ratio the MW is always two standard deviations away from the mean,
+while M31 is always within 2 standard deviations.
+The results for the $b/a$ ratio are always 2 standard deviations both
+for the MW and M31. 
 This confirms the extreme planar distribution for the MW and the more
@@
 In the following subsections we describe in detail the results on the 
-distributions for $w$, $c/a$ and $b/a$. 
+distributions for $w$, $c/a$ and $b/a$ and its comparison against
+observations. 
 The plots in the main body of the paper correspond to the
-Illustris-1-Dark simulation; the results from the other simulations
-are included in the Appendix \ref{appendix:plots}.
+Illustris-1-Dark simulation and $N_s=11$; the results from the other
+two simulations are included in the Appendix \ref{appendix:plots}.
 

### 2018-05-01 paper/paper.tex
remove tables

@@
 
-\begin{table*}
-  \centering
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
-    \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
-    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
-    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-7}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
-    %\hhline{~--}
-    \hline
-lane width (kpc) & $63.64$ & $19.34$ & $56.74\pm10.96$ & $37.56\pm7.90$ & $0.63$ & $-2.31$\\\hline
-$c/a$ ratio & $0.42$ & $0.18$ & $0.53\pm0.11$ & $0.46\pm0.11$ & $-1.00$ & $-2.46$\\\hline
-$b/a$ ratio & $0.96$ & $0.87$ & $0.81\pm0.08$ & $0.80\pm0.09$ & $1.69$ & $0.80$\\\hline
-  \end{tabular}
-  \caption{Results from observations with $N_s=11$ for the plane width, $c/a$
-    ratio and $b/a$ ratio. 
-    The first column refers to the results in physical units, the
-    second column uses the spherically  randomized version of the 
-    observational data and the third column corresponds to the
-    observational data re-centered and normalized using the mean and standard
-    deviation from the randomized data. Figure \ref{fig:normalized_n}
-    shows all the normalized data results for $11\leq N_s\leq
-    15$\label{table:observations}.}  
-\end{table*}
-
-\begin{table*}
-  \centering
-  \renewcommand{\arraystretch}{1.2}
-  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
-    \hline
-    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-Dark}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-7}
-    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
-    %\hhline{~--}
-    \hline
-Plane width (kpc) & $56.28\pm 18.30$ & $58.30 \pm 13.51$  & $66.66\pm 15.75$ & $64.81\pm 15.34$ & $68.74\pm 16.82$ & $63.70\pm 13.62$\\\hline
-$c/a$ ratio & $0.48\pm 0.15$ & $0.47 \pm 0.11$  & $0.52\pm 0.13$ & $0.50\pm 0.10$ & $0.54\pm 0.15$ & $0.47\pm 0.13$\\\hline
-$b/a$ ratio & $0.80\pm 0.10$ & $0.80 \pm 0.08$  & $0.82\pm 0.09$ & $0.82\pm 0.07$ & $0.81\pm 0.07$ & $0.80\pm 0.09$\\\hline
-  \end{tabular}
-  \caption{Results from simulations for $N_s=11$. Mean values and standard deviations for the different
-    quantities describing the satellite distributions: plane width, $c/a$
-    ratio and $b/a$ ratio. 
-    The first column summarizes the results from the 27 pairs in
-    Illustris-1-Dark, the second column from the 24 pairs in
-    Illustris-1 and the third column from the 12 pairs in the
-    ELVIS project.\label{table:simulations}}
-\end{table*}
-
 \subsection{Describing Samples with the Inertia Tensor}

### 2018-05-01 paper/paper.tex
results

@@
 
-In the following subsections we describe in detail the results on the 
-distributions for $w$, $c/a$ and $b/a$ and its comparison against
-observations. 
-The plots in the main body of the paper correspond to the
-Illustris-1-Dark simulation and $N_s=11$; the results from the other
-two simulations are included in the Appendix \ref{appendix:plots}.
-
-\subsection{Plane Width}
-
+In the following subsections we describe in detail the results from
+Illustris-1-Dark for $w$, $c/a$ and $b/a$ for a fixed number of
+satellites $N_s=11$.
+The results from the other two simulations are included in the
+Appendix \ref{appendix:plots}. 
+The full covariance matrices are in the Appendix
+\ref{appendix:matrices}.
+
+\subsection{Physical Units}
+%subsection{Plane Width}
+
+Figure \ref{fig:physical_illustris1dark} summarizes the results in
+physical units.
+It compares three different groups: observations, simulations and the
+observations randomized.
+The left panel shows the results for M31 and the panel on the left for
+the MW.
+
+The most interesting outcome is that the MW plane width is smaller
+than $\approx 98\%$ of the planes computed from the randomized distribution;
+its  $c/a$ ratio is also significantly lower than the measured values for
+the randomized distributions.   
+On the other hand the results for $M31$ for the same quantities are
+within $1-\sigma$ of the randomized results.
+
+The comparison against observations also provides an extreme picture
+for the MW. 
+In this case the mean witdh from simulation is almost twice as the
+mean width from the randomization. 
+A possible criticism to this result is that the typical halo mass in
+the simulation is larger than the it is for the MW. 
+For this reason we renormalize all quantities ($w$, $c/a$ and $b/a$)
+to the mean value and standard deviation provided by its spherical
+randomization. 
+In this way the physical scale of the halo becomes a second order
+effect and only the deviations from asphericity are protagonist.
+
+\subsection{Normalized Units}
+
+Figure \ref{normalized_illustris1dark} summarizes  the results of
+renormalizing to the randomized results.
+The layout is the same as Figure \ref{physical_illustris1dark}.
 Figure \ref{fig:scatter_width} summarizes the results for the width
@@
 (circles).
-The most interesting outcome is that the MW plane width is smaller
-than $\approx 98\%$ of the planes computed from the randomized distribution,
-while the M31 plane width is only slightly smaller than the average of
-the distribution.
 
@@
 
-The left panel in Figure \ref{fig:scatter_ca_ratio} shows how the MW
-$c/a$ ratio is significantly lower than the measured values for
-spherical distributions, and it is smaller than $\approx 98\%$ of the
-randomized distributions.   
 On the other hand the ratio for M31 is lower than the mean of the
@@
 
-\subsection{Fit to a Multivariate Gaussian Distributions}
+\subsection{Multivariate Gaussian model}
 

### 2018-05-01 paper/paper.tex
edit

@@
 On the other hand the results for $M31$ for the same quantities are
-within $1-\sigma$ of the randomized results.
+within $1\sigma$ of the randomized results.
 
@@
 
-Figure \ref{normalized_illustris1dark} summarizes  the results of
+Figure \ref{fig:normalized_illustris1dark} summarizes  the results of
 renormalizing to the randomized results.
-The layout is the same as Figure \ref{physical_illustris1dark}.
-Figure \ref{fig:scatter_width} summarizes the results for the width
-measurements.
-The left panel compares the results for the MW and M31
-observations (stars) against its spherically randomized satellites
-(circles).
-
-The middle panel in Figure \ref{fig:scatter_width} compares the
-observational result (star) against the measurements of all pairs from the Illustris1-Dark
-simulation (circles).
-In this case we have a similar result as before. 
-The observed MW width is smaller than all the results in the
-simulation, there is not a single halo with similar values.
-On the other hand, the results for the M31 are entirely consistent
-with observations. Most of the halos in the simulation show a width
-value similar to M31.
-
-The right panel in Figure \ref{fig:scatter_width} shows the result for
-the normalized width.  
-This panel tells the same story as the middle panel. 
-The M31 values are typical while the MW is an outlier.
-
-The added value of using the normalized data is that this data is 
-consistent with normal distributions.
-Additionally, this is the data used to build the mean values vector and covariance
-matrix described in Equation \ref{eq:multivariate}. 
-%The added value of the data in this panel is that it is the normalized
-%which is consistent with normal distributions.
-%This is the data used to build the mean values vector and covariance
-%matrix described in Equation \ref{eq:multivariate}.
+The layout is the same as Figure \ref{fig:physical_illustris1dark}.
+By construction, the relative position of the observations and the
+randomized results keeps constant; The MW continues to be atypical
+with respect to its own randomized distribution.
+
+The most notorious difference comes from the changes in the
+simulations. 
+The previous large difference betwen the width distribution from
+MW observations and simulations is reduced. 
+The reason is that normalized quantities are not dependent on the
+physical scale anymore; only the deviations from asphericity are
+important.
+
+The distributions for the normalized quantities from simulations are
+well described by gaussians. 
+The parameters of the gaussian model (covariance matrix and mean)
+are different depending on the simulation and number of particles, but
+all of them are well described by the multivariate gaussian.
+
+\subsection{Multivariate Gaussian model}
+
+Figure \ref{fig:gaussian_illustris1dark} summarized the results from
+ computing the covariance matrix and mean vector in
+ Eq.\ref{eq:multivariate} from the normalized quantities obtained from
+ the Illustris-1-Dark simulation.
+The distributions in this Figure are computed from $10^6$ points
+generated with the multivariate gaussian.
+
+This nicely summarizes the results we had in the previous
+sections. 
+The left hand triangular plot shows how M31 falls within the $2\sigma$
+contours in the 2D scatter plots;
+while the right hand plot clearly places the MW observations at the
+border of the $3\sigma$ range in the joint distributions that involve
+the width $w$.
+
+In both cases the strongest positive correlation is present for the
+width and the $c/a$ axis ratio. 
+A weaker correlation is present for the width and the $b/a$ axis
+ratio.  
+The weakest correlation, positive or negative depending on the
+simulation, is present for the $c/a$ ratio and $b/a$ ratio.
+
+The mean values also hold valuable information. 
+For the three quantities the mean in negative, a confirmation of the
+well known fact that the satellite distribution from LCDM simulations
+is not consistent with an spherical distribution.
+We also computed the correlation between the M31 and MW results,
+finding that it is very weak and can be safely discarded.
+
+The explicity formulation for this probability distribution allows us
+to generate large samples with asphericity properties consistent with
+the parent simulation. 
+From this samples we can explicitly compute the fraction of systems
+that, for instance, show the extreme MW values.
+
+\subsection{Number of Expected LG Systems}
 
@@
 
-\subsection{$c/a$ axis ratio}
-
-Figure \ref{fig:scatter_ca_ratio} shows the results for the minor to
-major axis ratio. 
-The layout is the same as in Figure \ref{fig:scatter_width}.
-The results for the $c/a$ ratio follow the same trends as for the
-width $w$.
-
-On the other hand the ratio for M31 is lower than the mean of the
-spherical values but still well within its variance.
-The middle panel in the same Figure shows the LG compared against the
-results in the simulations. 
-In this case we find a similar trend as before. 
-The MW is atypical and M31 is within the variance from the simulation data.
-This time, however, there are two MW-like halos out of the total
-of 24 that show an $c/a$ as small as that of the MW.
-The right panel shows the normalized results. 
-The MW shows a low $c/a$ ratio between two and three
-standard deviations away from the mean value of the spherical
-distribution; this contrasts with the results for M31 which are close to
-$1$ standard deviation away.
-
-\subsection{$b/a$ axis ratio}
-
-Figure \ref{fig:scatter_ba_ratio} shows the results for the minor to
-major axis ratio with the same layout as Figure \ref{fig:scatter_ca_ratio}
-In all cases of comparison (against randomized distribution
-and simulations) the results for both the MW and M31 are typical.
-
-\subsection{Multivariate Gaussian model}
-
-Figure \ref{fig:correlations_illustrisdm} illustrates the results from
- computing the covariance matrix and mean vector in
- Eq.\ref{eq:multivariate} from the normalized quantities obtained from
- the Illustris-1-Dark simulation.
-The distributions in this Figure are computed from $10^6$ points
-generated with the multivariate gaussian. 
-Similar plots for Illustris-1 and ELVIS are in the Appendix \ref{appendix:plots}.
-The values for all the covariance matrices and mean vectors
-corresponding to all the simulations are listed in the Appendix \ref{appendix:covariance}.
-
-This nicely summarizes the results we had in the previous
-sections. The left hand triangular plot shows how M31 falls into the middle of all 2D
-distributions and is always close to the peak and within the $1\sigma$
-range. 
-The right hand plot clearly places the MW observations outside the
-$3\sigma$ range in the joint distributions that involve the width
-$w$.
-
-In both cases the strongest positive correlation is present for the
-width and the $c/a$ axis ratio. A weaker correlation is present for
-the width and the $b/a$ axis ratio.
-
-\subsection{Number of Expected LG Systems}
-
-We use the fits to the multivariate gaussian distributions to
-compute the expected number of pairs with characteristics similar to
-those of the LG.
-To do this we generate $10^3$ samples, each sample containing $10^4$
-pairs, where each pair member is drawn from the corresponding
-multivariate gaussian distribution.
+Using the multivariate gaussian model we generate $10^3$ samples, each
+sample containing $10^4$ pairs, where each pair member is drawn from
+the corresponding multivariate gaussian distribution.
 
 We consider that a sampled system is similar to the M31/MW galaxy if the
-distance of each of its normalized characteristics ($w$, $c/a$, $b/a$) to the
-sample mean is equal or larger than the distance of the observational
+absolute distance of each of its normalized characteristics ($w$, $c/a$, $b/a$) to the
+sample mean is equal or larger than the absolute distance of the observational
 values to the sample mean.   
-That is, we perform a double-tailed test using the observational
-values as a threshold.
+That is, we perform a double-tailed test around the mean using the
+observational values as a threshold.
 
 Figure \ref{fig:expected_number} summarizes the results from this
-experiment. The left panel shows the probability density for the number of M31
-systems in a parent sample of $10^4$ pairs, the right panel shows the
-results for the MW.
-For M31, between $27\%$ and $56\%$ of the pairs have a satellite
-distribution as aspherical as the one observed in M31. This fraction drops
-dramatically for the MW where only $0.02\%$ to $3\%$ of the satellites
-are expected to have as extreme aspherical distributions as the MW.
+experiment as a function of satellite number for all three simulations:
+Illustris-1-Dark, Illustris-1 and ELVIS.
 
@@
 
+For M31, between $5\%$ and $80\%$ of the pairs have a satellite
+distribution as aspherical as the one observed in M31. This fraction drops
+dramatically for the MW where only $0.02\%$ to $4\%$ of the satellites
+are expected to have as extreme aspherical distributions as the MW.
+
 Among the three simulations, the results inferred from ELVIS data show
 the lowest fraction of M31 and MW systems; for Illustris-1-Dark we have
-the highest fraction of M31/MW systems. The results from Illustris-1
-are in between these two, but closer to ELVIS.
-
-The most probable reason for these trends is the different median mass
+the highest fraction of M31/MW systems. 
+The results from Illustris-1 are in between these two simulations, but
+closer to ELVIS.
+
+A probable reason for these trends is the different median mass
 for the MW/M31 halos in the pairs from these simulations. 
@@
 study.
+
+\subsection{How to understand an atypical MW}
+
+The highly aspherical satellite distribution in the MW is another piece of
+information that points at an atypical configuration in LCDM.
+We also have the number of satellites as bright as the Magellanic
+Clouds, only expected in $5\%$ of galaxies
+\citep{2011ApJ...743..117B} and 
+the satellite velocities around the MW with a radial/tangential
+anisotropy only expected in $3\%$ of systems in LCDM
+\citep{2017MNRAS.468L..41C}. 
+One could also add the atypical kinematics of M31 with a very low
+tangential velocity, which is only expected in less than $1\%$ of the pairs
+with similar environmental characteristics \citep{ForeroRomero2013}.
+
+Assuming that these properties are independent one would need at
+least $10^6$ pairs in order to find a single pair that meets all four
+characteristics (aspherical satellite distribution, bright Magellanic
+Clouds, satellite velocity anisotropy and atypical pair kinematics).
+Using the number density for pairs in Illustris-1 ($2\times 10^{-5}$
+pairs/Mpc$^{3}$) this would imply a cubic simulation volume of $5$ Gpc on a
+side, something unfeasible under current technology.
+However, studying two characteristics at a time to find possible
+correlations, and at least one pair resembling observations, reduces
+the box size to $500$ Mpc, something that is close to current
+simulations such as Illustris-TNG \citep{2018MNRAS.473.4077P}.
 
@@
 distributions in simulations that include baryonic effects.
-
-The highly aspherical satellite distribution in the MW is another piece of
-information that points at an atypical configuration in LCDM.
-We also have the number of satellites as bright as the Magellanic
-Clouds, only expected in $5\%$ of galaxies
-\citep{2011ApJ...743..117B} and 
-the satellite velocities around the MW with a radial/tangential
-anisotropy only expected in $3\%$ of systems in LCDM
-\citep{2017MNRAS.468L..41C}. 
-One could also add the atypical kinematics of M31 with a very low
-tangential velocity, which is only expected in less than $1\%$ of the pairs
-with similar environmental characteristics \citep{ForeroRomero2013}.  
-Quantifying whether these four characteristics are correlated one would
-need a simulation with
-
-Assuming that these properties are independent one would need at
-least $10^6$ pairs in order to find a single pair that meets all four
-characteristics (aspherical satellite distribution, bright Magellanic
-Clouds, satellite velocity anisotropy and atypical pair kinematics).
-Using the number density for pairs in Illustris-1 ($2\times 10^{-5}$
-pairs/Mpc$^{3}$) this would imply a cubic simulation volume of $5$ Gpc on a
-side, something unfeasible under current technology.
-However, studying two characteristics at a time to find possible
-correlations, and at least one pair resembling observations, reduces
-the box size to $500$ Mpc, something that is close to current
-simulations such as Illustris-TNG \citep{2018MNRAS.473.4077P}.
 

### 2018-05-01 paper/paper.tex
tables

@@
 
-Although Illustris-1 has stellar particles, we do not use their
-properties to select the satellite population for the results reported
-here. 
-The smallest galaxies are barely resolved in stellar mass at
-magnitudes of $M_V=-9$, close to the limit of the 11 ``classical'' MW
-satellites, we use instead the dark matter information.
-
-We decide to use the same satellite selection rules both in
-Illustris-1 and Illustris-1-Dark. 
-Namely, selecting the satellites by ranking the subhalos in decreasing
-order of its current maximum circular velocity and select the first
-$N_s$ halos in the list. 
-These selection criteria also  allow us to direct our attention at
-baryonic physics as the driver behind the differences in the results
-between the two simulations.  
-Under these conditions the smallest sub-halos are sampled with at
-least $40$ particles. 
-To a good approximation these
-are the systems with the highest circular velocity at infall
-\citep{2011MNRAS.415L..40B}, which is the physical quantity expected
-to best correlate with luminosity
-\citep{2004ApJ...609...35K,2006ApJ...647..201C,2010MNRAS.404.1111G}.
-
 \subsection{Data from the ELVIS project}
@@
 In this paper we only use the results from these $12$ resimulated pairs.
-To be consistent with the satellite selection in Illustris-1 and
-Illustris-1-Dark we select satellites by ranking them by their
-maximum circular velocity.
 
@@
 satellite number, $N_s$.
-This means that the maximum circular velocity cut corresponding to the
-smallest satellite included in the sample is different in each case.
 We make this choice to explicitly model the influence of satellite numbers
@@
 
+Although Illustris-1 has stellar particles, we do not use their
+properties to select the satellite population for the results reported
+here. 
+The smallest galaxies are barely resolved in stellar mass at
+magnitudes of $M_V=-9$, close to the limit of the 11 ``classical'' MW
+satellites, we use instead the dark matter information.
+
+We decide instead to use the same satellite selection rules in
+Illustris-1, Illustris-1-Dark and ELVIS.
+Namely, selecting the satellites by ranking the subhalos in decreasing
+order of its current maximum circular velocity and select the first
+$N_s$ halos in the list.
+
+These selection criteria also  allow us to perform a fair comparison
+across simulations. 
+In the case of Illustris-1 versus Illustris-1-Dark, it let us direct
+our attention at baryonic physics as the driver behind the differences
+in the results between these two simulations.  
+To a good approximation these satellites are the systems with the
+highest circular velocity at infall \citep{2011MNRAS.415L..40B}, which
+is the physical quantity expected to best correlate with luminosity
+\citep{2004ApJ...609...35K,2006ApJ...647..201C,2010MNRAS.404.1111G}.  
+With this choice the maximum circular velocity cut corresponding to the
+smallest satellite included in the sample is different for each case;
+in terms of resolution the subhalos are resolved with at least
+$\approx 40 (400)$ particles for the Illustris (ELVIS) simulation.
+
 We compute the satellite statistics for $11\leq N_s\leq 15$.
 The lower limit corresponds to the number of classical MW satellites,
-while the upper limit corresponds to the minimum number of M31
+while the upper limit corresponds to the minimum number of
 satellites usually included in M31 studies.
-In simulations we rank the subhalos by their maximum circular
-velocity, in observations we rank the satellites by its $M_V$
+
+In observations we rank the satellites by its $M_V$
 magnitude.  
-
 We also tested using $M_V$ and stellar mass in Illustris-1, and the
 stellar mass in ELVIS (provided through abundance matching) as a
-selection criterion. Our main conclusions remain unchanged by that
-choice.
+selection criterion. 
+Our main conclusions remain unchanged by those choices.
 
@@
 The mean values also hold valuable information. 
-For the three quantities the mean in negative, a confirmation of the
-well known fact that the satellite distribution from LCDM simulations
-is not consistent with an spherical distribution.
+For the three quantities the mean is negative, a quantification trend
+that the satellite distribution from LCDM simulations tend to be aspherical.
+This trend has a very few exceptions. 
+Nmely the ELVIS results for M31 with $N_s=11,12$ and the Illustris-1
+results for the $MW$ with $N_s=11$, which are consistent with an
+spherical distribution. 
 We also computed the correlation between the M31 and MW results,
@@
 For M31, between $5\%$ and $80\%$ of the pairs have a satellite
-distribution as aspherical as the one observed in M31. This fraction drops
+distribution as aspherical as the one observed in M31.
+This fraction drops
 dramatically for the MW where only $0.02\%$ to $4\%$ of the satellites
 are expected to have as extreme aspherical distributions as the MW.
+A consistent finding is that the M31 fraction is always larger than
+the MW fraction at fixed $N_s$ and simulation.
 
@@
 simulation. 
-The results listed in Appendix \ref{appendix:covariance} show that
+The results listed in Appendix \ref{appendix:matrices} show that
 halos are closer to spherical once baryonic effects are included. 
@@
 
-We found that in the best case (Illustris-1-Dark) the degree of
+We quantified that in the best case (Illustris-1-Dark) the degree of
 asphericity in the observed LG is only expected in $2\%$ of the
@@
 \section*{Acknowledgements} 
-We acknowledge financial support from: Universidad de Los Andes
-(Colombia); COLCIENCIAS (c\'odigo 120471250459, contrato FP44842-287-
-2016); the European Union's Horizon 2020 Research and Innovation
+JEFR acknowledges support from COLCIENCIAS Contract No. 287-2016,
+Project 1204-712-50459 and the European Union's Horizon 2020 Research and Innovation
 Programme under the Marie Sk\l{}odowska-Curie grant agreement No 73437
@@
 \section{Covariance Matrices and Mean value vectors}
-\label{appendix:covariance}
-\subsection{Illustris-1-Dark}
-
-\subsubsection{M31}
+\label{appendix:matrices}
+
+\subsection{Illustris-1-Dark, M31, $N_s=11$}
 \[
@@
 \]
-
 \[
@@
 \]
-
-\subsubsection{MW}
-
+\subsection{Illustris-1-Dark, MW, $N_s=11$}
 \[
@@
 
-\subsection{Illustris-1}
-\subsubsection{M31}
+\subsection{Illustris-1, M31, $N_s=11$}
 \[
@@
 \]
-\subsubsection{MW}
+\subsection{Illustris-1, MW, $N_s=11$}
 \[
@@
 
-\subsection{ELVIS}
-
-\subsubsection{M31}
+\subsection{ELVIS, M31, $N_s=11$}
 \[
@@
 \]
-\subsubsection{MW}
+\subsection{ELVIS, MW, $N_s=11$}
 \[
@@
 
+\subsection{Illustris-1-Dark, M31, $N_s=12$}
+\[
+\Sigma=
+\begin{bmatrix}
+2.34 \pm 0.11 & 1.72 \pm 0.11 & 1.10 \pm 0.06\\
+1.72 \pm 0.11 & 1.72 \pm 0.11 & 0.35 \pm 0.05\\
+1.10 \pm 0.06 & 0.35 \pm 0.05 & 1.21 \pm 0.07\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.58 \pm 0.07 & -0.49 \pm 0.06 & -0.41 \pm 0.05\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1-Dark, MW, $N_s=12$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.25 \pm 0.06 & 0.97 \pm 0.06 & 0.62 \pm 0.04\\
+0.97 \pm 0.06 & 1.19 \pm 0.06 & -0.11 \pm 0.05\\
+0.62 \pm 0.04 & -0.11 \pm 0.05 & 1.19 \pm 0.04\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.38 \pm 0.05 & -0.55 \pm 0.05 & -0.28 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1, M31, $N_s=12$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.01 \pm 0.06 & 0.74 \pm 0.04 & 0.59 \pm 0.06\\
+0.74 \pm 0.04 & 1.03 \pm 0.05 & -0.16 \pm 0.04\\
+0.59 \pm 0.06 & -0.16 \pm 0.04 & 1.12 \pm 0.06\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.09 \pm 0.05 & -0.23 \pm 0.05 & -0.33 \pm 0.05\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1, MW, $N_s=12$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.00 \pm 0.05 & 0.69 \pm 0.05 & 0.64 \pm 0.05\\
+0.69 \pm 0.05 & 0.87 \pm 0.06 & -0.06 \pm 0.04\\
+0.64 \pm 0.05 & -0.06 \pm 0.04 & 1.06 \pm 0.06\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.16 \pm 0.05 & -0.46 \pm 0.04 & -0.12 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{ELVIS, M31, $N_s=12$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.97 \pm 0.28 & 1.64 \pm 0.21 & 0.57 \pm 0.11\\
+1.64 \pm 0.21 & 1.69 \pm 0.17 & 0.11 \pm 0.07\\
+0.57 \pm 0.11 & 0.11 \pm 0.07 & 0.70 \pm 0.12\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.06 \pm 0.09 & -0.18 \pm 0.09 & -0.13 \pm 0.06\\
+\end{bmatrix}
+\]
+\subsection{ELVIS, MW, $N_s=12$}
+\[
+\Sigma=
+\begin{bmatrix}
+0.58 \pm 0.05 & 0.47 \pm 0.10 & 0.23 \pm 0.09\\
+0.47 \pm 0.10 & 1.04 \pm 0.16 & -0.68 \pm 0.09\\
+0.23 \pm 0.09 & -0.68 \pm 0.09 & 1.23 \pm 0.11\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.42 \pm 0.05 & -0.78 \pm 0.07 & -0.16 \pm 0.07\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1-Dark, M31, $N_s=13$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.79 \pm 0.09 & 1.19 \pm 0.08 & 0.90 \pm 0.06\\
+1.19 \pm 0.08 & 1.12 \pm 0.07 & 0.17 \pm 0.03\\
+0.90 \pm 0.06 & 0.17 \pm 0.03 & 1.12 \pm 0.07\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.61 \pm 0.06 & -0.67 \pm 0.05 & -0.37 \pm 0.05\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1-Dark, MW, $N_s=13$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.30 \pm 0.07 & 1.09 \pm 0.06 & 0.52 \pm 0.05\\
+1.09 \pm 0.06 & 1.42 \pm 0.08 & -0.18 \pm 0.06\\
+0.52 \pm 0.05 & -0.18 \pm 0.06 & 1.09 \pm 0.04\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.38 \pm 0.05 & -0.54 \pm 0.05 & -0.30 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1, M31, $N_s=13$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.36 \pm 0.09 & 0.89 \pm 0.05 & 0.97 \pm 0.06\\
+0.89 \pm 0.05 & 0.92 \pm 0.05 & 0.22 \pm 0.05\\
+0.97 \pm 0.06 & 0.22 \pm 0.05 & 1.28 \pm 0.06\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.07 \pm 0.06 & -0.17 \pm 0.05 & -0.30 \pm 0.06\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1, MW, $N_s=13$}
+\[
+\Sigma=
+\begin{bmatrix}
+0.95 \pm 0.08 & 0.90 \pm 0.09 & 0.33 \pm 0.05\\
+0.90 \pm 0.09 & 1.29 \pm 0.10 & -0.24 \pm 0.05\\
+0.33 \pm 0.05 & -0.24 \pm 0.05 & 0.89 \pm 0.08\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.13 \pm 0.05 & -0.47 \pm 0.06 & -0.09 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{ELVIS, M31, $N_s=13$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.99 \pm 0.22 & 1.49 \pm 0.19 & 0.98 \pm 0.11\\
+1.49 \pm 0.19 & 1.45 \pm 0.15 & 0.38 \pm 0.10\\
+0.98 \pm 0.11 & 0.38 \pm 0.10 & 1.06 \pm 0.17\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.18 \pm 0.10 & -0.37 \pm 0.08 & -0.07 \pm 0.07\\
+\end{bmatrix}
+\]
+\subsection{ELVIS, MW, $N_s=13$}
+\[
+\Sigma=
+\begin{bmatrix}
+0.43 \pm 0.05 & 0.54 \pm 0.09 & -0.12 \pm 0.07\\
+0.54 \pm 0.09 & 1.20 \pm 0.17 & -0.85 \pm 0.12\\
+-0.12 \pm 0.07 & -0.85 \pm 0.12 & 0.94 \pm 0.10\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.44 \pm 0.04 & -0.73 \pm 0.07 & -0.30 \pm 0.07\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1-Dark, M31, $N_s=14$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.60 \pm 0.11 & 1.34 \pm 0.09 & 0.68 \pm 0.05\\
+1.34 \pm 0.09 & 1.32 \pm 0.08 & 0.28 \pm 0.04\\
+0.68 \pm 0.05 & 0.28 \pm 0.04 & 0.85 \pm 0.05\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.33 \pm 0.06 & -0.53 \pm 0.05 & -0.15 \pm 0.04\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1-Dark, MW, $N_s=14$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.27 \pm 0.06 & 1.12 \pm 0.06 & 0.40 \pm 0.04\\
+1.12 \pm 0.06 & 1.55 \pm 0.08 & -0.32 \pm 0.05\\
+0.40 \pm 0.04 & -0.32 \pm 0.05 & 1.02 \pm 0.04\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.52 \pm 0.05 & -0.64 \pm 0.06 & -0.40 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1, M31, $N_s=14$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.11 \pm 0.05 & 0.88 \pm 0.05 & 0.83 \pm 0.05\\
+0.88 \pm 0.05 & 1.14 \pm 0.06 & 0.08 \pm 0.05\\
+0.83 \pm 0.05 & 0.08 \pm 0.05 & 1.39 \pm 0.07\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.06 \pm 0.05 & -0.24 \pm 0.05 & -0.23 \pm 0.06\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1, MW, $N_s=14$}
+\[
+\Sigma=
+\begin{bmatrix}
+0.99 \pm 0.07 & 0.88 \pm 0.08 & 0.38 \pm 0.06\\
+0.88 \pm 0.08 & 1.24 \pm 0.10 & -0.26 \pm 0.07\\
+0.38 \pm 0.06 & -0.26 \pm 0.07 & 0.97 \pm 0.09\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.39 \pm 0.05 & -0.62 \pm 0.06 & -0.28 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{ELVIS, M31, $N_s=14$}
+\[
+\Sigma=
+\begin{bmatrix}
+2.04 \pm 0.24 & 1.21 \pm 0.14 & 1.27 \pm 0.17\\
+1.21 \pm 0.14 & 0.97 \pm 0.09 & 0.45 \pm 0.09\\
+1.27 \pm 0.17 & 0.45 \pm 0.09 & 1.31 \pm 0.19\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.37 \pm 0.10 & -0.38 \pm 0.07 & -0.40 \pm 0.08\\
+\end{bmatrix}
+\]
+\subsection{ELVIS, MW, $N_s=14$}
+\[
+\Sigma=
+\begin{bmatrix}
+0.82 \pm 0.08 & 1.06 \pm 0.14 & -0.11 \pm 0.06\\
+1.06 \pm 0.14 & 1.75 \pm 0.20 & -0.62 \pm 0.09\\
+-0.11 \pm 0.06 & -0.62 \pm 0.09 & 0.64 \pm 0.07\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.38 \pm 0.06 & -0.74 \pm 0.09 & -0.13 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1-Dark, M31, $N_s=15$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.65 \pm 0.10 & 1.35 \pm 0.09 & 0.81 \pm 0.06\\
+1.35 \pm 0.09 & 1.34 \pm 0.09 & 0.36 \pm 0.05\\
+0.81 \pm 0.06 & 0.36 \pm 0.05 & 0.97 \pm 0.05\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.31 \pm 0.06 & -0.51 \pm 0.05 & -0.16 \pm 0.05\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1-Dark, MW, $N_s=15$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.52 \pm 0.07 & 1.25 \pm 0.06 & 0.64 \pm 0.05\\
+1.25 \pm 0.06 & 1.58 \pm 0.08 & -0.15 \pm 0.06\\
+0.64 \pm 0.05 & -0.15 \pm 0.06 & 1.18 \pm 0.05\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.50 \pm 0.06 & -0.63 \pm 0.06 & -0.33 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{Illustris-1, M31, $N_s=15$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.18 \pm 0.04 & 0.91 \pm 0.05 & 0.84 \pm 0.05\\
+0.91 \pm 0.05 & 1.11 \pm 0.07 & 0.15 \pm 0.04\\
+0.84 \pm 0.05 & 0.15 \pm 0.04 & 1.23 \pm 0.06\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.25 \pm 0.06 & -0.41 \pm 0.05 & -0.32 \pm 0.06\\
+\end{bmatrix}
+\]
+\subsection{Illustris-1, MW, $N_s=15$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.06 \pm 0.07 & 0.88 \pm 0.07 & 0.44 \pm 0.06\\
+0.88 \pm 0.07 & 1.11 \pm 0.08 & -0.11 \pm 0.05\\
+0.44 \pm 0.06 & -0.11 \pm 0.05 & 0.84 \pm 0.08\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.45 \pm 0.05 & -0.67 \pm 0.05 & -0.32 \pm 0.05\\
+\end{bmatrix}
+\]
+
+\subsection{ELVIS, M31, $N_s=15$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.51 \pm 0.13 & 1.16 \pm 0.11 & 0.74 \pm 0.11\\
+1.16 \pm 0.11 & 1.06 \pm 0.11 & 0.32 \pm 0.06\\
+0.74 \pm 0.11 & 0.32 \pm 0.06 & 0.75 \pm 0.10\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.41 \pm 0.08 & -0.47 \pm 0.07 & -0.48 \pm 0.06\\
+\end{bmatrix}
+\]
+\subsection{ELVIS, MW, $N_s=15$}
+\[
+\Sigma=
+\begin{bmatrix}
+1.13 \pm 0.15 & 1.42 \pm 0.20 & -0.06 \pm 0.08\\
+1.42 \pm 0.20 & 2.16 \pm 0.25 & -0.58 \pm 0.09\\
+-0.06 \pm 0.08 & -0.58 \pm 0.09 & 0.74 \pm 0.09\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.47 \pm 0.07 & -0.72 \pm 0.10 & -0.26 \pm 0.06\\
+\end{bmatrix}
+\]
+
 \section{Results from ELVIS and Illustris1}
 \label{appendix:plots}
+
 \begin{figure*}
 \centering
-\includegraphics[width=0.40\textwidth]{input_illustris1_obs_M31_n_11.pdf}
-\includegraphics[width=0.40\textwidth]{input_illustris1_obs_MW_n_11.pdf}
-\includegraphics[width=0.40\textwidth]{input_illustris1_obs_M31_n_11_normed.pdf}
-\includegraphics[width=0.40\textwidth]{input_illustris1_obs_MW_n_11_normed.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_M31_n_11.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{input_illustris1_obs_M31_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{input_illustris1_obs_MW_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{input_illustris1_obs_M31_n_11_normed.pdf}
+\includegraphics[width=0.37\textwidth]{input_illustris1_obs_MW_n_11_normed.pdf}
+\includegraphics[width=0.37\textwidth]{gaussian_model_illustris1_M31_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
 \caption{Illustris-1 results for the quantities presented for the Illustris1-Dark
-  simulation in Figures  \ref{fig:scatter_width},
-  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
+  simulation in Figures  
+\ref{fig:physical_illustris1dark}, \ref{fig:normalized_illustris1dark}
+and \ref{fig:gaussian_illustris1dark}.
 Upper row corresponds to the raw values from observations and
@@
 \centering
-\includegraphics[width=0.40\textwidth]{input_elvis_obs_M31_n_11.pdf}
-\includegraphics[width=0.40\textwidth]{input_elvis_obs_MW_n_11.pdf}
-\includegraphics[width=0.40\textwidth]{input_elvis_obs_M31_n_11_normed.pdf}
-\includegraphics[width=0.40\textwidth]{input_elvis_obs_MW_n_11_normed.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_M31_n_11.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{input_elvis_obs_M31_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{input_elvis_obs_MW_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{input_elvis_obs_M31_n_11_normed.pdf}
+\includegraphics[width=0.37\textwidth]{input_elvis_obs_MW_n_11_normed.pdf}
+\includegraphics[width=0.37\textwidth]{gaussian_model_elvis_M31_n_11.pdf}
+\includegraphics[width=0.37\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
 \caption{ELVIs results for the quantities presented for the Illustris1-Dark
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1dark_M31_n_12.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1dark_MW_n_12.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_M31_n_12.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_MW_n_12.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_M31_n_12.pdf}
-\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_MW_n_12.pdf}
-\caption{ELVIs results for the quantities presented for the Illustris1-Dark
-  simulation in Figures  \ref{fig:scatter_width},
-  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
-Upper row corresponds to the raw values from observations and
-simulated pairs, while the second row normalizes the same values to
-the mean and standard deviation on its spherically randomized
-counterparts. 
-\label{fig:scatter_elvis}}
-\end{figure*}
-
 \end{document}

### 2018-05-01 paper/paper.tex
referee

@@
 of the satellite distributions in the LG even when the underlying
-simulations do not have enough systems fully resembling the LG.
+simulations do not have enough systems fully resembling the LG in
+terms of its typical masses, separation and kinematics.
 We demonstrate the method using three different simulations
@@
 simulations and observations.  
-Then, we build an explicit probability distribution for the asphericity and
-use simulations to estimate its free parameters.
+Then, we build an analytical probability distribution  for the
+asphericity and use simulations to estimate its free parameters.  
 Finally, we use these distributions to generate large numbers of
@@
 in Illustris-1 to find the matching halo pairs.
-After discarding the pairs with less than 15 detected subhalos in one
+After discarding the pairs with less than 11 detected subhalos in one
 of the halos we end up with a total of 24 pairs in Illustris-1-Dark. 
@@
 satellites usually included in M31 studies.
+This boundary in the satellite number is also present due to the
+limits in the resolution of Illustris.
 
@@
 with similar environmental characteristics \citep{ForeroRomero2013}.  
-
-Assuming that these properties are independent one would need at
+With the small numbers that we have in the simulations we used we
+cannot study properly those correlations. 
+We cannot even find a clear trend linking asphericity to halo mass or
+another pair property.
+
+Assuming that these atypical properties are independent one would need at
 least $10^6$ pairs in order to find a single pair that meets all four

### 2018-05-01 code/asphericity_stats.py
updated plots

@@ -23,7 +23,7 @@ def load_experiment(input_path="../data/mstar_selected_summary/vmax_sorted/", n_
         i = int(f.split("_")[-3])
         if i not in group_id:
             group_id.append(i)
-    print(group_id, len(group_id))
+    #print(group_id, len(group_id))
 
     n_groups = len(group_id)
     
@@ -711,15 +711,15 @@ def plot_shape_obs_sims_normed(simulation, n_sat):
 def print_covariance(simulation, n_sat):
     def print_ab(a, b, c, d, e, f):
         print("{:.2f} \\pm {:.2f} & {:.2f} \\pm {:.2f} & {:.2f} \\pm {:.2f}\\\\".format(a,b,c,d,e,f))
-            
-    print('simulation {}'.format(simulation))
+    simulation_name = {'illustris1':'Illustris-1', 'illustris1dark':'Illustris-1-Dark', 'elvis':'ELVIS'}
+    print()
     in_path = "../data/{}_mstar_selected_summary/".format(simulation)
     M31_sim_stats, MW_sim_stats = load_experiment(input_path=in_path, n_sat=n_sat)
 
     cov_sim_M31 = jacknife_covariance(M31_sim_stats)
     cov_sim_MW = jacknife_covariance(MW_sim_stats)
-
-    print('\\subsubsection{M31}')
+    
+    print('\\subsection{'+'{}'.format(simulation_name[simulation])+', M31, ' + '$N_s={}$'.format(n_sat) + '}')
     print('\\[')
     print('\\Sigma=')
     print('\\begin{bmatrix}')
@@ -739,7 +739,7 @@ def print_covariance(simulation, n_sat):
     print('\\end{bmatrix}')
     print('\\]')
     
-    print('\\subsubsection{MW}')
+    print('\\subsection{'+'{}'.format(simulation_name[simulation])+', MW, ' + '$N_s={}$'.format(n_sat) + '}')
     print('\\[')
     print('\\Sigma=')
     print('\\begin{bmatrix}')

### 2018-05-01 code/data_tables_plots.py

@@ -95,7 +95,7 @@ if PlotShapeObsSimNormed:
         asp.plot_shape_obs_sims_normed('elvis', nsat)
         
 if PrintCovarianceTables:
-    for nsat in range(11,12):
+    for nsat in range(11,16):
         asp.print_covariance('illustris1dark', nsat)
         asp.print_covariance('illustris1', nsat)
         asp.print_covariance('elvis', nsat)

### 2018-05-01 paper/paper.tex
typo

@@
 \begin{abstract}
-We use simulations to build an explicit probability distribution for
+We use simulations to build an analytic probability distribution for
 the asphericity in the satellite distribution around Local Group (LG)
@@
 deviation from the spherical distribution. 
-We then build an explicit analytic probability distribution for the
+We then build an analytic probability distribution for the
 asphericity; this solves the problem of having a common reference
@@
 deviation of the values from randomized samples.
-We use the normalized quantities to build the explicit probability
+We use the normalized quantities to build the analytic probability
 distributions for the scalars describing asphericity.
 
-\subsection{Building an explicit asphericity probability distribution}
+\subsection{Building an analytic asphericity probability distribution}
 
@@
 
-The focus of our approach was building an explicit probability
+The focus of our approach was building an analytic probability
 distribution for the observables of interest, instead of trying to
@@
 (i.e. coherent \emph{velocity} structures) should also be possible, 
-provided that an explicit probability distribution for the scalars of
+provided that an analytic probability distribution for the scalars of
 interest can be built.  
@@
 
-\section*{Acknowledgements} 
+\section*{Acknowledgments} 
 JEFR acknowledges support from COLCIENCIAS Contract No. 287-2016,

### 2018-05-08 paper/paper.tex
edit

@@
 \includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
-\caption{Normalized asphericity scalars from observations as a function
-  of satellite number. Left: plane width; center: $c/a$ ratio;
+\caption{Asphericity scalars from observations as a function
+  of satellite number. 
+  Left: plane width; center: $c/a$ ratio;
   right: $b/a$ ratio. 
+  These quantities can take positive or negative values because they
+  were recentered to the mean and normalized to the standard deviation 
+  of the spherically randomized satellites as explained in Section
+  \ref{sec:normalization}. 
   The plane width and $c/a$ ratio for the MW is
-  consistently found beyond two standard
-  deviations.
+  consistently found \emph{beyond} two standard
+  deviations of the expected result for an statistically spherical
+  distribution. 
   M31 shows the opposite trend and is always found
@@
 
-\subsection{Characterizing Asphericity}
-
+\subsection{Characterizing asphericity with normalized scalars}
+\label{sec:normalization}
 We compare each satellite distribution against its own spherically
@@
 
-After building the normalized variables with the simulated data we
-perform a Kolmogorov-Smirnov test with the null hypothesis of belonging
-to a normal distribution with mean and standard deviation computed
-from the mean and standard deviation estimated from the data.
-Although the physical quantities of interest are bound, unlike the
-random variables from a normal distribution, we find that the
+After building the normalized variables for the simulated data we perform a
+Kolmogorov-Smirnov test with the null hypothesis of belonging to a
+normal distribution with mean and standard deviation computed from the
+mean and standard deviation estimated from the data. 
+Although the physical quantities of interest are bound, we find that the
 distributions for the normalized $w$, $c/a$ and $b/a$ are indeed
@@
 observational data.  
-We use a double-tailed test around the mean in this comparison, meaning that we
-always measure the fraction of points with absolute values larger than the
-absolute observed value with the mean substracted.
+We use a double-tailed test around the mean in this comparison,
+meaning that we count the fraction of generated points points with
+absolute values larger than the absolute observed value with the mean
+substracted.
 
@@
 \includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
-\caption{Scalars describing satellite shape around the LG galaxies for
+\caption{Scalars in physical units describing satellite shape around the LG galaxies for
   a fixed number of satellites $N_s$=11: 
-  plane width $w$ in physical units, $c/a$ ratio and $b/a$ ratio.
-  Left: M31, right: MW. The square at the center are observations; the
-2D histograms are the contour levels after randomizing $10^4$ the
-satellite positions while keeping the radial distribution fixed; the
-blue circles are the results from Illustris-1-Dark. For the M31 these
-three results (observations, randomized observations and simulations)
-seem to be in broad agreement, while for the MW the three results
-clearly differ. 
+  plane width $w$, $c/a$ ratio and $b/a$ ratio.
+  Left: M31, right: MW. 
+  The histograms along the diagonal show the distribution for the
+  $10^4$ values after spherical randomization; the vertical dashed
+  lines show the 16, 50 and 84 percentiles of this distribution; the vertical solid line correspond to
+  observations. 
+  Outside the diagonal there are 2D histograms showing the $1$, $2$, $3$
+  and $4\sigma$ contours for the randomized data.  
+  The square at the center of the cross are observations.
+  The blue circles are the results from Illustris-1-Dark. 
+  For the M31 these three results
+  (observations, randomized observations and simulations) seem to be
+  in broad agreement, while for the MW they clearly differ. 
   The corresponding plots for Illustris-1 and ELVIS are
   in Figures \ref{fig:all_plots_illustris1} and
-\ref{fig:all_plots_elvis},
-respectively. \label{fig:physical_illustris1dark}}     
+\ref{fig:all_plots_elvis}, respectively. \label{fig:physical_illustris1dark}}
 \end{figure*}
@@
 observations randomized.
-The left panel shows the results for M31 and the panel on the left for
+The left panel shows the results for M31 and the panel on the right for
 the MW.
@@
 
-This atypicality should be seen as an opportunity to constrain in
+The LG atypicality should be seen as an opportunity to constrain in
 great detail the environment that allowed such a pattern to emerge. 
@@
 \includegraphics[width=0.37\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
-\caption{Illustris-1 results for the quantities presented for the Illustris1-Dark
+\caption{Illustris-1 results for the same quantities presented for the Illustris-1-Dark
   simulation in Figures  
@@
 \includegraphics[width=0.37\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
-\caption{ELVIs results for the quantities presented for the Illustris1-Dark
-  simulation in Figures  \ref{fig:scatter_width},
-  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
+\caption{ELVIS results for the same quantities presented for the Illustris1-Dark
+  simulation in Figures  
+\ref{fig:physical_illustris1dark}, \ref{fig:normalized_illustris1dark}
+and \ref{fig:gaussian_illustris1dark}.
 Upper row corresponds to the raw values from observations and

### 2018-05-08 code/asphericity_stats.py
update label

@@ -239,13 +239,14 @@ def plot_covariance(simulation, n_sat):
             cov_illustris_M31['mean'], cov_illustris_M31['covariance'], size=100000)
     data_random_illustris_MW = np.random.multivariate_normal(
             cov_illustris_MW['mean'], cov_illustris_MW['covariance'], size=100000)
-
+    s = np.array([1.0,2.0,3.0])
+    levels = 1-np.exp(-(s**2)/2.0)
         
     plt.figure(figsize=(8,5))
     plt.rc('text', usetex=True,)
     plt.rc('font', family='serif', size=25)
     figure = corner.corner( data_random_illustris_M31, 
-                      quantiles=[0.16, 0.5, 0.84],
+                      quantiles=[0.16, 0.5, 0.84],levels=levels,
                       labels=[r"$w$ M31", r"$c/a$ M31", r"$b/a$ M31"],
                       show_titles=True, title_kwargs={"fontsize": 12}, 
                       truths=M31_obs['data_obs'])
@@ -264,7 +265,7 @@ def plot_covariance(simulation, n_sat):
     ax = axes[2,0];ax.set_xlim(min_w, max_w);ax.set_ylim(min_ab, max_ab)
     ax.scatter(M31_sim_stats['width_normed'], M31_sim_stats['ba_ratio_normed'])
     children = ax.get_children()
-    ax.legend([children[6], children[8], children[5]], [simulation_name[simulation], 'Observations', 'Gaussian Model'], 
+    ax.legend([children[5], children[7], children[4]], [simulation_name[simulation], 'Observations', 'Gaussian Model'], 
               loc='upper right', bbox_to_anchor=(3.0, 3.0), fontsize=20, markerscale=2)
 
     filename = "../paper/gaussian_model_{}_M31_n_{}.pdf".format(simulation, n_sat)
@@ -276,7 +277,7 @@ def plot_covariance(simulation, n_sat):
     plt.rc('text', usetex=True,)
     plt.rc('font', family='serif', size=25)
     figure = corner.corner(data_random_illustris_MW, 
-                      quantiles=[0.16, 0.5, 0.84],
+                      quantiles=[0.16, 0.5, 0.84],levels=levels,
                       labels=[r"$w$ MW", r"$c/a$ MW", r"$b/a$ MW"],
                       show_titles=True, title_kwargs={"fontsize": 12}, 
[…]

### 2018-05-08 paper/paper.tex
update

@@
   \ref{sec:normalization}. 
-  The plane width and $c/a$ ratio for the MW is
+  The plane width and $c/a$ ratio for the MW are
   consistently found \emph{beyond} two standard
@@
   distribution. 
-  M31 shows the opposite trend and is always found
+  M31 shows the opposite trend and are always found
   \emph{within} two standard deviations. \label{fig:normalized_n}} 
@@
   $10^4$ values after spherical randomization; the vertical dashed
-  lines show the 16, 50 and 84 percentiles of this distribution; the vertical solid line correspond to
-  observations. 
-  Outside the diagonal there are 2D histograms showing the $1$, $2$, $3$
-  and $4\sigma$ contours for the randomized data.  
+  lines show the $16^{\rm th}$, $50^{\rm th}$ and $84^{\rm th}$
+  percentiles of this distribution; the vertical solid line correspond
+  to observations. 
+  Outside the diagonal there are 2D histograms showing the ($1$, $2$,
+  $3$) $\sigma$ contours for the randomized data.  
   The square at the center of the cross are observations.

### 2018-05-08 code/data_tables_plots.py
updated script

@@ -46,14 +46,14 @@ import asphericity_stats as asp
 
 ObsTable = False
 SimTable = False
-CovPlots = False
+CovPlots = True
 ObsAsphPlots = False
 PrintModelNumbers = False
 PlotModelNumbers = False
 PlotShapeRandomObs = False
-PlotShapeObsSim = False
-PlotShapeObsSimNormed = False
-PrintCovarianceTables = True
+PlotShapeObsSim = True
+PlotShapeObsSimNormed = True 
+PrintCovarianceTables = False
 
 if ObsTable:
     asp.print_table_obs_shape()
@@ -62,7 +62,7 @@ if SimTable:
     asp.print_table_sim_shape()
     
 if CovPlots:
-    for nsat in range(11,16):
+    for nsat in range(11,12):
         asp.plot_covariance('illustris1dark', nsat)
         asp.plot_covariance('illustris1', nsat)
         asp.plot_covariance('elvis', nsat)
@@ -83,19 +83,19 @@ if PlotShapeRandomObs:
         asp.plot_shape_obs_randoms(nsat)
     
 if PlotShapeObsSim:
-    for nsat in range(11,16):
+    for nsat in range(11,12):
         asp.plot_shape_obs_sims('illustris1dark', nsat)
-        asp.plot_shape_obs_sims('illustris1', nsat)
-        asp.plot_shape_obs_sims('elvis', nsat)
+        #asp.plot_shape_obs_sims('illustris1', nsat)
+        #asp.plot_shape_obs_sims('elvis', nsat)
 
 if PlotShapeObsSimNormed:
-    for nsat in range(11,16):
+    for nsat in range(11,12):
         asp.plot_shape_obs_sims_normed('illustris1dark', nsat)
         asp.plot_shape_obs_sims_normed('illustris1', nsat)
         asp.plot_shape_obs_sims_normed('elvis', nsat)
         
 if PrintCovarianceTables:
-    for nsat in range(11,16):
+    for nsat in range(11,12):
         asp.print_covariance('illustris1dark', nsat)
         asp.print_covariance('illustris1', nsat)
         asp.print_covariance('elvis', nsat)

### 2018-05-08 paper/paper.tex
updated paper

@@
 The results for the width and $c/a$ ratio of MW satellites are more
-than two standard deviations away from the mean. 
+than two standard deviations away from the mean of the randomized
+data, both in the 1D distributions (diagonal plots) and the 2D
+distributions (off-diagonal plots). 
 The corresponding plots for Illustris-1 and ELVIS are

### 2018-05-08 paper/paper.tex
updated tex

@@
 \bibliographystyle{mnras}
-\bibliography{Dwarfs}
+%\bibliography{Dwarfs}
+
+\begin{thebibliography}{}
+\makeatletter
+\relax
+\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
+\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
+  {\mn@doi@[]}}
+\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
+  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
+  \endgroup}
+\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
+\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
+\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
+  {dblp:#1}}
+\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
+  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
+  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
+  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
+  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}
+
+\bibitem[\protect\citeauthoryear{{Ahmed}, {Brooks}  \& {Christensen}}{{Ahmed}
+  et~al.}{2017}]{2017MNRAS.466.3119A}
+{Ahmed} S.~H.,  {Brooks} A.~M.,   {Christensen} C.~R.,  2017, \mn@doi [\mnras]
+  {10.1093/mnras/stw3271}, \href
+  {http://adsabs.harvard.edu/abs/2017MNRAS.466.3119A} {466, 3119}
+
+\bibitem[\protect\citeauthoryear{{Boylan-Kolchin}, {Bullock}  \&
+  {Kaplinghat}}{{Boylan-Kolchin} et~al.}{2011}]{2011MNRAS.415L..40B}
+{Boylan-Kolchin} M.,  {Bullock} J.~S.,   {Kaplinghat} M.,  2011, \mn@doi
+  [\mnras] {10.1111/j.1745-3933.2011.01074.x}, \href
+  {http://adsabs.harvard.edu/abs/2011MNRAS.415L..40B} {415, L40}
+
+\bibitem[\protect\citeauthoryear{{Bryan}, {Kay}, {Duffy}, {Schaye}, {Dalla
+  Vecchia}  \& {Booth}}{{Bryan} et~al.}{2013}]{2013MNRAS.429.3316B}
+{Bryan} S.~E.,  {Kay} S.~T.,  {Duffy} A.~R.,  {Schaye} J.,  {Dalla Vecchia} C.,
+    {Booth} C.~M.,  2013, \mn@doi [\mnras] {10.1093/mnras/sts587}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.429.3316B} {429, 3316}
+
+\bibitem[\protect\citeauthoryear{{Buck}, {Macci{\`o}}  \& {Dutton}}{{Buck}
+  et~al.}{2015}]{2015ApJ...809...49B}
+{Buck} T.,  {Macci{\`o}} A.~V.,   {Dutton} A.~A.,  2015, \mn@doi [\apj]
+  {10.1088/0004-637X/809/1/49}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...809...49B} {809, 49}
+
+\bibitem[\protect\citeauthoryear{{Buck}, {Dutton}  \& {Macci{\`o}}}{{Buck}
+  et~al.}{2016}]{2016MNRAS.460.4348B}
+{Buck} T.,  {Dutton} A.~A.,   {Macci{\`o}} A.~V.,  2016, \mn@doi [\mnras]
+  {10.1093/mnras/stw1232}, \href
+  {http://adsabs.harvard.edu/abs/2016MNRAS.460.4348B} {460, 4348}
+
+\bibitem[\protect\citeauthoryear{{Busha}, {Wechsler}, {Behroozi}, {Gerke},
+  {Klypin}  \& {Primack}}{{Busha} et~al.}{2011}]{2011ApJ...743..117B}
+{Busha} M.~T.,  {Wechsler} R.~H.,  {Behroozi} P.~S.,  {Gerke} B.~F.,  {Klypin}
+  A.~A.,   {Primack} J.~R.,  2011, \mn@doi [\apj]
+  {10.1088/0004-637X/743/2/117}, \href
+  {http://adsabs.harvard.edu/abs/2011ApJ...743..117B} {743, 117}
+
+\bibitem[\protect\citeauthoryear{{Cautun} \& {Frenk}}{{Cautun} \&
+  {Frenk}}{2017}]{2017MNRAS.468L..41C}
+{Cautun} M.,  {Frenk} C.~S.,  2017, \mn@doi [\mnras] {10.1093/mnrasl/slx025},
+  \href {http://adsabs.harvard.edu/abs/2017MNRAS.468L..41C} {468, L41}
+
+\bibitem[\protect\citeauthoryear{{Cautun}, {Bose}, {Frenk}, {Guo}, {Han},
+  {Hellwing}, {Sawala}  \& {Wang}}{{Cautun} et~al.}{2015}]{2015MNRAS.452.3838C}
+{Cautun} M.,  {Bose} S.,  {Frenk} C.~S.,  {Guo} Q.,  {Han} J.,  {Hellwing}
+  W.~A.,  {Sawala} T.,   {Wang} W.,  2015, \mn@doi [\mnras]
+  {10.1093/mnras/stv1557}, \href
+  {http://adsabs.harvard.edu/abs/2015MNRAS.452.3838C} {452, 3838}
+
+\bibitem[\protect\citeauthoryear{{Collins} et~al.,}{{Collins}
+  et~al.}{2015}]{2015ApJ...799L..13C}
+{Collins} M.~L.~M.,  et~al., 2015, \mn@doi [\apjl]
+  {10.1088/2041-8205/799/1/L13}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...799L..13C} {799, L13}
+
+\bibitem[\protect\citeauthoryear{{Conn} et~al.,}{{Conn}
+  et~al.}{2013}]{2013ApJ...766..120C}
+{Conn} A.~R.,  et~al., 2013, \mn@doi [\apj] {10.1088/0004-637X/766/2/120},
+  \href {http://adsabs.harvard.edu/abs/2013ApJ...766..120C} {766, 120}
+
+\bibitem[\protect\citeauthoryear{{Conroy}, {Wechsler}  \& {Kravtsov}}{{Conroy}
+  et~al.}{2006}]{2006ApJ...647..201C}
+{Conroy} C.,  {Wechsler} R.~H.,   {Kravtsov} A.~V.,  2006, \mn@doi [\apj]
+  {10.1086/503602}, \href {http://adsabs.harvard.edu/abs/2006ApJ...647..201C}
+  {647, 201}
+
+\bibitem[\protect\citeauthoryear{{Fernando}, {Arias}, {Guglielmo}, {Lewis},
+  {Ibata}  \& {Power}}{{Fernando} et~al.}{2017}]{2017MNRAS.465..641F}
+{Fernando} N.,  {Arias} V.,  {Guglielmo} M.,  {Lewis} G.~F.,  {Ibata} R.~A.,
+  {Power} C.,  2017, \mn@doi [\mnras] {10.1093/mnras/stw2694}, \href
+  {http://adsabs.harvard.edu/abs/2017MNRAS.465..641F} {465, 641}
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero} \&
+  {Gonz{\'a}lez}}{{Forero-Romero} \&
+  {Gonz{\'a}lez}}{2015}]{2015ApJ...799...45F}
+{Forero-Romero} J.~E.,  {Gonz{\'a}lez} R.,  2015, \mn@doi [\apj]
+  {10.1088/0004-637X/799/1/45}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...799...45F} {799, 45}
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Yepes},
+  {Gottl{\"o}ber}, {Piontek}, {Klypin}  \& {Steinmetz}}{{Forero-Romero}
+  et~al.}{2011}]{2011MNRAS.417.1434F}
+{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Yepes} G.,  {Gottl{\"o}ber} S.,
+  {Piontek} R.,  {Klypin} A.,   {Steinmetz} M.,  2011, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2011.19358.x}, \href
+  {http://adsabs.harvard.edu/abs/2011MNRAS.417.1434F} {417, 1434}
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Bustamante},
+  {Gottl{\"o}ber}  \& {Yepes}}{{Forero-Romero} et~al.}{2013}]{ForeroRomero2013}
+{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Bustamante} S.,  {Gottl{\"o}ber} S.,
+  {Yepes} G.,  2013, \mn@doi [\apjl] {10.1088/2041-8205/767/1/L5}, \href
+  {http://adsabs.harvard.edu/abs/2013ApJ...767L...5F} {767, L5}
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Contreras}  \&
+  {Padilla}}{{Forero-Romero} et~al.}{2014}]{2014MNRAS.443.1090F}
+{Forero-Romero} J.~E.,  {Contreras} S.,   {Padilla} N.,  2014, \mn@doi [\mnras]
+  {10.1093/mnras/stu1150}, \href
+  {http://adsabs.harvard.edu/abs/2014MNRAS.443.1090F} {443, 1090}
+
+\bibitem[\protect\citeauthoryear{{Garrison-Kimmel}, {Boylan-Kolchin}, {Bullock}
+   \& {Lee}}{{Garrison-Kimmel} et~al.}{2014}]{2014MNRAS.438.2578G}
+{Garrison-Kimmel} S.,  {Boylan-Kolchin} M.,  {Bullock} J.~S.,   {Lee} K.,
+  2014, \mn@doi [\mnras] {10.1093/mnras/stt2377}, \href
+  {http://adsabs.harvard.edu/abs/2014MNRAS.438.2578G} {438, 2578}
+
+\bibitem[\protect\citeauthoryear{{Gillet}, {Ocvirk}, {Aubert}, {Knebe},
+  {Libeskind}, {Yepes}, {Gottl{\"o}ber}  \& {Hoffman}}{{Gillet}
+  et~al.}{2015}]{2015ApJ...800...34G}
+{Gillet} N.,  {Ocvirk} P.,  {Aubert} D.,  {Knebe} A.,  {Libeskind} N.,  {Yepes}
+  G.,  {Gottl{\"o}ber} S.,   {Hoffman} Y.,  2015, \mn@doi [\apj]
+  {10.1088/0004-637X/800/1/34}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...800...34G} {800, 34}
+
+\bibitem[\protect\citeauthoryear{{Guo}, {White}, {Li}  \&
+  {Boylan-Kolchin}}{{Guo} et~al.}{2010}]{2010MNRAS.404.1111G}
+{Guo} Q.,  {White} S.,  {Li} C.,   {Boylan-Kolchin} M.,  2010, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2010.16341.x}, \href
+  {http://adsabs.harvard.edu/abs/2010MNRAS.404.1111G} {404, 1111}
+
+\bibitem[\protect\citeauthoryear{{Hinshaw} et~al.,}{{Hinshaw}
+  et~al.}{2013}]{2013ApJS..208...19H}
+{Hinshaw} G.,  et~al., 2013, \mn@doi [\apjs] {10.1088/0067-0049/208/2/19},
+  \href {http://adsabs.harvard.edu/abs/2013ApJS..208...19H} {208, 19}
+
+\bibitem[\protect\citeauthoryear{{Ibata} et~al.,}{{Ibata}
+  et~al.}{2013}]{2013Natur.493...62I}
+{Ibata} R.~A.,  et~al., 2013, \mn@doi [\nat] {10.1038/nature11717}, \href
+  {http://adsabs.harvard.edu/abs/2013Natur.493...62I} {493, 62}
+
+\bibitem[\protect\citeauthoryear{{Koch} \& {Grebel}}{{Koch} \&
+  {Grebel}}{2006}]{2006AJ....131.1405K}
+{Koch} A.,  {Grebel} E.~K.,  2006, \mn@doi [\aj] {10.1086/499534}, \href
+  {http://adsabs.harvard.edu/abs/2006AJ....131.1405K} {131, 1405}
+
+\bibitem[\protect\citeauthoryear{{Kravtsov}, {Berlind}, {Wechsler}, {Klypin},
+  {Gottl{\"o}ber}, {Allgood}  \& {Primack}}{{Kravtsov}
+  et~al.}{2004}]{2004ApJ...609...35K}
+{Kravtsov} A.~V.,  {Berlind} A.~A.,  {Wechsler} R.~H.,  {Klypin} A.~A.,
+  {Gottl{\"o}ber} S.,  {Allgood} B.,   {Primack} J.~R.,  2004, \mn@doi [\apj]
+  {10.1086/420959}, \href {http://adsabs.harvard.edu/abs/2004ApJ...609...35K}
+  {609, 35}
+
+\bibitem[\protect\citeauthoryear{{Kroupa}, {Theis}  \& {Boily}}{{Kroupa}
+  et~al.}{2005}]{2005A&A...431..517K}
+{Kroupa} P.,  {Theis} C.,   {Boily} C.~M.,  2005, \mn@doi [\aap]
+  {10.1051/0004-6361:20041122}, \href
+  {http://adsabs.harvard.edu/abs/2005A%26A...431..517K} {431, 517}
+
+\bibitem[\protect\citeauthoryear{{Kunkel} \& {Demers}}{{Kunkel} \&
+  {Demers}}{1976}]{1976RGOB..182..241K}
+{Kunkel} W.~E.,  {Demers} S.,  1976, in {Dickens} R.~J.,  {Perry} J.~E.,
+  {Smith} F.~G.,   {King} I.~R.,  eds,  Royal Greenwich Observatory Bulletins
+  Vol. 182, The Galaxy and the Local Group. p.~241
+
+\bibitem[\protect\citeauthoryear{{Libeskind}, {Frenk}, {Cole}, {Helly},
+  {Jenkins}, {Navarro}  \& {Power}}{{Libeskind}
+  et~al.}{2005}]{2005MNRAS.363..146L}
+{Libeskind} N.~I.,  {Frenk} C.~S.,  {Cole} S.,  {Helly} J.~C.,  {Jenkins} A.,
+  {Navarro} J.~F.,   {Power} C.,  2005, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2005.09425.x}, \href
+  {http://adsabs.harvard.edu/abs/2005MNRAS.363..146L} {363, 146}
+
+\bibitem[\protect\citeauthoryear{{Libeskind}, {Frenk}, {Cole}, {Jenkins}  \&
+  {Helly}}{{Libeskind} et~al.}{2009}]{2009MNRAS.399..550L}
+{Libeskind} N.~I.,  {Frenk} C.~S.,  {Cole} S.,  {Jenkins} A.,   {Helly} J.~C.,
+  2009, \mn@doi [\mnras] {10.1111/j.1365-2966.2009.15315.x}, \href
+  {http://adsabs.harvard.edu/abs/2009MNRAS.399..550L} {399, 550}
+
+\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Tully}, {Courtois},
+  {Pomar{\`e}de}, {Gottl{\"o}ber}  \& {Steinmetz}}{{Libeskind}
+  et~al.}{2015}]{2015MNRAS.452.1052L}
+{Libeskind} N.~I.,  {Hoffman} Y.,  {Tully} R.~B.,  {Courtois} H.~M.,
+  {Pomar{\`e}de} D.,  {Gottl{\"o}ber} S.,   {Steinmetz} M.,  2015, \mn@doi
+  [\mnras] {10.1093/mnras/stv1302}, \href
+  {http://adsabs.harvard.edu/abs/2015MNRAS.452.1052L} {452, 1052}
+
+\bibitem[\protect\citeauthoryear{{Lynden-Bell}}{{Lynden-Bell}}{1976}]{1976MNRAS.174..695L}
+{Lynden-Bell} D.,  1976, \mn@doi [\mnras] {10.1093/mnras/174.3.695}, \href
+  {http://adsabs.harvard.edu/abs/1976MNRAS.174..695L} {174, 695}
+
+\bibitem[\protect\citeauthoryear{{McConnachie}}{{McConnachie}}{2012}]{2012AJ....144....4M}
+{McConnachie} A.~W.,  2012, \mn@doi [\aj] {10.1088/0004-6256/144/1/4}, \href
+  {http://adsabs.harvard.edu/abs/2012AJ....144....4M} {144, 4}
+
+\bibitem[\protect\citeauthoryear{{Metz}, {Kroupa}  \& {Jerjen}}{{Metz}
+  et~al.}{2007}]{2007MNRAS.374.1125M}
+{Metz} M.,  {Kroupa} P.,   {Jerjen} H.,  2007, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2006.11228.x}, \href
+  {http://adsabs.harvard.edu/abs/2007MNRAS.374.1125M} {374, 1125}
+
+\bibitem[\protect\citeauthoryear{{Pawlowski} \& {McGaugh}}{{Pawlowski} \&
+  {McGaugh}}{2014}]{2014ApJ...789L..24P}
+{Pawlowski} M.~S.,  {McGaugh} S.~S.,  2014, \mn@doi [\apjl]
+  {10.1088/2041-8205/789/1/L24}, \href
+  {http://adsabs.harvard.edu/abs/2014ApJ...789L..24P} {789, L24}
+
+\bibitem[\protect\citeauthoryear{{Pawlowski}, {Kroupa}  \&
+  {Jerjen}}{{Pawlowski} et~al.}{2013}]{2013MNRAS.435.1928P}
+{Pawlowski} M.~S.,  {Kroupa} P.,   {Jerjen} H.,  2013, \mn@doi [\mnras]
+  {10.1093/mnras/stt1384}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P} {435, 1928}
+
+\bibitem[\protect\citeauthoryear{{Pawlowski}, {Kroupa}  \&
+  {Jerjen}}{{Pawlowski} et~al.}{2014}]{2014yCat..74351928P}
+{Pawlowski} M.~S.,  {Kroupa} P.,   {Jerjen} H.,  2014, VizieR Online Data
+  Catalog, \href {http://adsabs.harvard.edu/abs/2014yCat..74351928P} {743}
+
+\bibitem[\protect\citeauthoryear{{Pawlowski}, {Famaey}, {Merritt}  \&
+  {Kroupa}}{{Pawlowski} et~al.}{2015}]{2015ApJ...815...19P}
+{Pawlowski} M.~S.,  {Famaey} B.,  {Merritt} D.,   {Kroupa} P.,  2015, \mn@doi
+  [\apj] {10.1088/0004-637X/815/1/19}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...815...19P} {815, 19}
+
+\bibitem[\protect\citeauthoryear{{Pawlowski} et~al.,}{{Pawlowski}
+  et~al.}{2017}]{2017AN....338..854P}
+{Pawlowski} M.~S.,  et~al., 2017, \mn@doi [Astronomische Nachrichten]
+  {10.1002/asna.201713366}, \href
+  {http://adsabs.harvard.edu/abs/2017AN....338..854P} {338, 854}
+
+\bibitem[\protect\citeauthoryear{{Pillepich} et~al.,}{{Pillepich}
+  et~al.}{2018}]{2018MNRAS.473.4077P}
+{Pillepich} A.,  et~al., 2018, \mn@doi [\mnras] {10.1093/mnras/stx2656}, \href
+  {http://adsabs.harvard.edu/abs/2018MNRAS.473.4077P} {473, 4077}
+
+\bibitem[\protect\citeauthoryear{{Sawala} et~al.,}{{Sawala}
+  et~al.}{2016}]{2016MNRAS.457.1931S}
+{Sawala} T.,  et~al., 2016, \mn@doi [\mnras] {10.1093/mnras/stw145}, \href
+  {http://adsabs.harvard.edu/abs/2016MNRAS.457.1931S} {457, 1931}
+
+\bibitem[\protect\citeauthoryear{{Springel}}{{Springel}}{2010}]{2010MNRAS.401..791S}
+{Springel} V.,  2010, \mn@doi [\mnras] {10.1111/j.1365-2966.2009.15715.x},
+  \href {http://adsabs.harvard.edu/abs/2010MNRAS.401..791S} {401, 791}
+
+\bibitem[\protect\citeauthoryear{{Starkenburg} et~al.,}{{Starkenburg}
+  et~al.}{2013}]{2013MNRAS.429..725S}
+{Starkenburg} E.,  et~al., 2013, \mn@doi [\mnras] {10.1093/mnras/sts367}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.429..725S} {429, 725}
+
+\bibitem[\protect\citeauthoryear{{Vogelsberger} et~al.,}{{Vogelsberger}
+  et~al.}{2014}]{2014MNRAS.444.1518V}
+{Vogelsberger} M.,  et~al., 2014, \mn@doi [\mnras] {10.1093/mnras/stu1536},
+  \href {http://adsabs.harvard.edu/abs/2014MNRAS.444.1518V} {444, 1518}
+
+\bibitem[\protect\citeauthoryear{{Wang}, {Frenk}  \& {Cooper}}{{Wang}
+  et~al.}{2013}]{2013MNRAS.429.1502W}
+{Wang} J.,  {Frenk} C.~S.,   {Cooper} A.~P.,  2013, \mn@doi [\mnras]
+  {10.1093/mnras/sts442}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.429.1502W} {429, 1502}
+
+\bibitem[\protect\citeauthoryear{{Zentner}, {Kravtsov}, {Gnedin}  \&
+  {Klypin}}{{Zentner} et~al.}{2005}]{2005ApJ...629..219Z}
+{Zentner} A.~R.,  {Kravtsov} A.~V.,  {Gnedin} O.~Y.,   {Klypin} A.~A.,  2005,
+  \mn@doi [\apj] {10.1086/431355}, \href
+  {http://adsabs.harvard.edu/abs/2005ApJ...629..219Z} {629, 219}
+
+\makeatother
+\end{thebibliography}
 

### 2018-05-08 code/data_tables_plots.py
updated default plots

@@ -46,13 +46,13 @@ import asphericity_stats as asp
 
 ObsTable = False
 SimTable = False
-CovPlots = True
+CovPlots = False
 ObsAsphPlots = False
 PrintModelNumbers = False
 PlotModelNumbers = False
 PlotShapeRandomObs = False
 PlotShapeObsSim = True
-PlotShapeObsSimNormed = True 
+PlotShapeObsSimNormed = False
 PrintCovarianceTables = False
 
 if ObsTable:
@@ -85,8 +85,8 @@ if PlotShapeRandomObs:
 if PlotShapeObsSim:
     for nsat in range(11,12):
         asp.plot_shape_obs_sims('illustris1dark', nsat)
-        #asp.plot_shape_obs_sims('illustris1', nsat)
-        #asp.plot_shape_obs_sims('elvis', nsat)
+        asp.plot_shape_obs_sims('illustris1', nsat)
+        asp.plot_shape_obs_sims('elvis', nsat)
 
 if PlotShapeObsSimNormed:
     for nsat in range(11,12):

### 2018-05-14 paper/paper.tex
new pdf

--- 2018-05-08 paper/paper.tex
@@
 planar as in the MW 
-were as low as $2\%$ \citep{2005ApJ...629..219Z} while others expected
+were as low as $2\%$ \citep{2005ApJ...629..219Z,2005A&A...437..383K} while others expected
 planar satellite configurations in every DM halo
@@
 confirming the original hint by \cite{2005A&A...431..517K} and more
-recent results by \cite{2015ApJ...815...19P}. 
+recent results \citep{2012MNRAS.423.1109P,2015ApJ...815...19P}. 
 We estimated that with the M31 between $5\%$ and $80\%$ of the pairs

### 2018-05-15 code/compile_randomized_data.py
fixed bug with ELVIS distances

@@ -64,7 +64,7 @@ def load_snapshot(snap_name, boxsize=75000.0, elvis=False):
                 snap_data[col] = (snap_data[col] - 0.5 * boxsize) % boxsize
     if elvis: #change units
         for col in list(['x','y','z']):
-            snap_data[col] = snap_data[col] * 1000/hubble
+            snap_data[col] = snap_data[col] * 1000
     return snap_data
 
 def load_obs(obs_name):

### 2018-05-15 code/data_tables_plots.py

@@ -3,7 +3,7 @@ import compile_randomized_data as crd
 obs = False
 illustris1 = False
 illustris1dark = False
-elvis = False
+elvis = True
 
 if obs:        
     print('Compiling stats for the observations')
@@ -46,7 +46,7 @@ import asphericity_stats as asp
 
 ObsTable = False
 SimTable = False
-CovPlots = False
+CovPlots = True
 ObsAsphPlots = False
 PrintModelNumbers = False
 PlotModelNumbers = False

### 2018-05-15 code/data_tables_plots.py
table code

@@ -3,7 +3,7 @@ import compile_randomized_data as crd
 obs = False
 illustris1 = False
 illustris1dark = False
-elvis = True
+elvis = False
 
 if obs:        
     print('Compiling stats for the observations')
@@ -46,14 +46,14 @@ import asphericity_stats as asp
 
 ObsTable = False
 SimTable = False
-CovPlots = True
+CovPlots = False
 ObsAsphPlots = False
 PrintModelNumbers = False
 PlotModelNumbers = False
 PlotShapeRandomObs = False
-PlotShapeObsSim = True
+PlotShapeObsSim = False
 PlotShapeObsSimNormed = False
-PrintCovarianceTables = False
+PrintCovarianceTables = True
 
 if ObsTable:
     asp.print_table_obs_shape()
@@ -95,7 +95,7 @@ if PlotShapeObsSimNormed:
         asp.plot_shape_obs_sims_normed('elvis', nsat)
         
 if PrintCovarianceTables:
-    for nsat in range(11,12):
+    for nsat in range(11,16):
         asp.print_covariance('illustris1dark', nsat)
         asp.print_covariance('illustris1', nsat)
         asp.print_covariance('elvis', nsat)

### 2018-05-16 code/data_tables_plots.py
updated numbers

@@ -48,12 +48,12 @@ ObsTable = False
 SimTable = False
 CovPlots = False
 ObsAsphPlots = False
-PrintModelNumbers = False
-PlotModelNumbers = False
+PrintModelNumbers = True
+PlotModelNumbers = True
 PlotShapeRandomObs = False
 PlotShapeObsSim = False
 PlotShapeObsSimNormed = False
-PrintCovarianceTables = True
+PrintCovarianceTables = False
 
 if ObsTable:
     asp.print_table_obs_shape()

### 2018-05-16 paper/paper.tex
updated version

--- 2018-05-08 paper/paper.tex
@@
 (LACEGAL).   
+We thank the referee, Pavel Kroupa and Marcel Pawlowski for useful
+comments that improved the clarity of the paper.
 
@@
 %\bibliography{Dwarfs}
-
 \begin{thebibliography}{}
@@
 
+\bibitem[\protect\citeauthoryear{{Kang}, {Mao}, {Gao}  \& {Jing}}{{Kang}
+  et~al.}{2005}]{2005A&A...437..383K}
+{Kang} X.,  {Mao} S.,  {Gao} L.,   {Jing} Y.~P.,  2005, \mn@doi [\aap]
+  {10.1051/0004-6361:20052675}, \href
+  {http://adsabs.harvard.edu/abs/2005A%26A...437..383K} {437, 383}
+
 \bibitem[\protect\citeauthoryear{{Koch} \& {Grebel}}{{Koch} \&
@@
   {http://adsabs.harvard.edu/abs/2014ApJ...789L..24P} {789, L24}
+
+\bibitem[\protect\citeauthoryear{{Pawlowski}, {Pflamm-Altenburg}  \&
+  {Kroupa}}{{Pawlowski} et~al.}{2012}]{2012MNRAS.423.1109P}
+{Pawlowski} M.~S.,  {Pflamm-Altenburg} J.,   {Kroupa} P.,  2012, \mn@doi
+  [\mnras] {10.1111/j.1365-2966.2012.20937.x}, \href
+  {http://adsabs.harvard.edu/abs/2012MNRAS.423.1109P} {423, 1109}
 
@@
 \begin{bmatrix}
-1.77 \pm 0.23 & 1.44 \pm 0.18 & 0.65 \pm 0.09\\
-1.44 \pm 0.18 & 1.54 \pm 0.15 & 0.15 \pm 0.06\\
-0.65 \pm 0.09 & 0.15 \pm 0.06 & 0.77 \pm 0.11\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
-0.07 \pm 0.09 & -0.06 \pm 0.08 & -0.08 \pm 0.06\\
+1.36 \pm 0.22 & 1.59 \pm 0.26 & 0.24 \pm 0.07\\
+1.59 \pm 0.26 & 2.00 \pm 0.31 & 0.06 \pm 0.08\\
+0.24 \pm 0.07 & 0.06 \pm 0.08 & 0.52 \pm 0.03\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+0.45 \pm 0.08 & 0.22 \pm 0.10 & 0.07 \pm 0.05\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-0.59 \pm 0.06 & 0.61 \pm 0.11 & 0.11 \pm 0.08\\
-0.61 \pm 0.11 & 1.25 \pm 0.19 & -0.71 \pm 0.12\\
-0.11 \pm 0.08 & -0.71 \pm 0.12 & 1.13 \pm 0.11\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.25 \pm 0.05 & -0.59 \pm 0.08 & -0.16 \pm 0.07\\
+1.53 \pm 0.16 & 0.91 \pm 0.17 & 0.98 \pm 0.09\\
+0.91 \pm 0.17 & 0.89 \pm 0.16 & 0.18 \pm 0.06\\
+0.98 \pm 0.09 & 0.18 \pm 0.06 & 1.19 \pm 0.13\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.46 \pm 0.08 & -0.28 \pm 0.06 & -0.77 \pm 0.07\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-1.97 \pm 0.28 & 1.64 \pm 0.21 & 0.57 \pm 0.11\\
-1.64 \pm 0.21 & 1.69 \pm 0.17 & 0.11 \pm 0.07\\
-0.57 \pm 0.11 & 0.11 \pm 0.07 & 0.70 \pm 0.12\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.06 \pm 0.09 & -0.18 \pm 0.09 & -0.13 \pm 0.06\\
+1.17 \pm 0.09 & 1.60 \pm 0.14 & 0.26 \pm 0.05\\
+1.60 \pm 0.14 & 2.37 \pm 0.21 & 0.11 \pm 0.08\\
+0.26 \pm 0.05 & 0.11 \pm 0.08 & 0.44 \pm 0.04\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+0.66 \pm 0.07 & 0.49 \pm 0.10 & 0.18 \pm 0.04\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-0.58 \pm 0.05 & 0.47 \pm 0.10 & 0.23 \pm 0.09\\
-0.47 \pm 0.10 & 1.04 \pm 0.16 & -0.68 \pm 0.09\\
-0.23 \pm 0.09 & -0.68 \pm 0.09 & 1.23 \pm 0.11\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.42 \pm 0.05 & -0.78 \pm 0.07 & -0.16 \pm 0.07\\
+2.00 \pm 0.18 & 1.14 \pm 0.17 & 1.31 \pm 0.11\\
+1.14 \pm 0.17 & 0.98 \pm 0.17 & 0.39 \pm 0.05\\
+1.31 \pm 0.11 & 0.39 \pm 0.05 & 1.34 \pm 0.16\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.50 \pm 0.10 & -0.34 \pm 0.07 & -0.67 \pm 0.08\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-1.99 \pm 0.22 & 1.49 \pm 0.19 & 0.98 \pm 0.11\\
-1.49 \pm 0.19 & 1.45 \pm 0.15 & 0.38 \pm 0.10\\
-0.98 \pm 0.11 & 0.38 \pm 0.10 & 1.06 \pm 0.17\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.18 \pm 0.10 & -0.37 \pm 0.08 & -0.07 \pm 0.07\\
+1.20 \pm 0.11 & 1.47 \pm 0.16 & 0.48 \pm 0.09\\
+1.47 \pm 0.16 & 2.02 \pm 0.24 & 0.35 \pm 0.08\\
+0.48 \pm 0.09 & 0.35 \pm 0.08 & 0.56 \pm 0.10\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+0.77 \pm 0.07 & 0.61 \pm 0.10 & 0.27 \pm 0.05\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-0.43 \pm 0.05 & 0.54 \pm 0.09 & -0.12 \pm 0.07\\
-0.54 \pm 0.09 & 1.20 \pm 0.17 & -0.85 \pm 0.12\\
--0.12 \pm 0.07 & -0.85 \pm 0.12 & 0.94 \pm 0.10\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.44 \pm 0.04 & -0.73 \pm 0.07 & -0.30 \pm 0.07\\
+1.82 \pm 0.19 & 0.99 \pm 0.15 & 1.43 \pm 0.19\\
+0.99 \pm 0.15 & 0.92 \pm 0.14 & 0.39 \pm 0.08\\
+1.43 \pm 0.19 & 0.39 \pm 0.08 & 1.56 \pm 0.23\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.26 \pm 0.09 & -0.32 \pm 0.06 & -0.37 \pm 0.08\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-2.04 \pm 0.24 & 1.21 \pm 0.14 & 1.27 \pm 0.17\\
-1.21 \pm 0.14 & 0.97 \pm 0.09 & 0.45 \pm 0.09\\
-1.27 \pm 0.17 & 0.45 \pm 0.09 & 1.31 \pm 0.19\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.37 \pm 0.10 & -0.38 \pm 0.07 & -0.40 \pm 0.08\\
+1.22 \pm 0.12 & 1.37 \pm 0.16 & 0.60 \pm 0.09\\
+1.37 \pm 0.16 & 1.78 \pm 0.22 & 0.38 \pm 0.09\\
+0.60 \pm 0.09 & 0.38 \pm 0.09 & 0.79 \pm 0.09\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+0.66 \pm 0.07 & 0.47 \pm 0.09 & 0.25 \pm 0.06\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-0.82 \pm 0.08 & 1.06 \pm 0.14 & -0.11 \pm 0.06\\
-1.06 \pm 0.14 & 1.75 \pm 0.20 & -0.62 \pm 0.09\\
--0.11 \pm 0.06 & -0.62 \pm 0.09 & 0.64 \pm 0.07\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.38 \pm 0.06 & -0.74 \pm 0.09 & -0.13 \pm 0.05\\
+1.83 \pm 0.19 & 1.01 \pm 0.15 & 1.42 \pm 0.16\\
+1.01 \pm 0.15 & 0.92 \pm 0.13 & 0.38 \pm 0.10\\
+1.42 \pm 0.16 & 0.38 \pm 0.10 & 1.64 \pm 0.20\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.24 \pm 0.09 & -0.25 \pm 0.06 & -0.40 \pm 0.09\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-1.51 \pm 0.13 & 1.16 \pm 0.11 & 0.74 \pm 0.11\\
-1.16 \pm 0.11 & 1.06 \pm 0.11 & 0.32 \pm 0.06\\
-0.74 \pm 0.11 & 0.32 \pm 0.06 & 0.75 \pm 0.10\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.41 \pm 0.08 & -0.47 \pm 0.07 & -0.48 \pm 0.06\\
+1.26 \pm 0.12 & 1.25 \pm 0.13 & 0.77 \pm 0.11\\
+1.25 \pm 0.13 & 1.47 \pm 0.18 & 0.43 \pm 0.10\\
+0.77 \pm 0.11 & 0.43 \pm 0.10 & 1.01 \pm 0.11\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+0.48 \pm 0.08 & 0.22 \pm 0.08 & 0.23 \pm 0.07\\
 \end{bmatrix}
@@
 \begin{bmatrix}
-1.13 \pm 0.15 & 1.42 \pm 0.20 & -0.06 \pm 0.08\\
-1.42 \pm 0.20 & 2.16 \pm 0.25 & -0.58 \pm 0.09\\
--0.06 \pm 0.08 & -0.58 \pm 0.09 & 0.74 \pm 0.09\\
-\end{bmatrix}
-\]
-\[
-\mu=
-\begin{bmatrix}
--0.47 \pm 0.07 & -0.72 \pm 0.10 & -0.26 \pm 0.06\\
+1.89 \pm 0.18 & 0.90 \pm 0.11 & 1.51 \pm 0.16\\
+0.90 \pm 0.11 & 0.68 \pm 0.07 & 0.41 \pm 0.10\\
+1.51 \pm 0.16 & 0.41 \pm 0.10 & 1.63 \pm 0.19\\
+\end{bmatrix}
+\]
+\[
+\mu=
+\begin{bmatrix}
+-0.49 \pm 0.09 & -0.55 \pm 0.06 & -0.40 \pm 0.09\\
 \end{bmatrix}

### 2018-05-16 paper/paper.tex
latest version

@@
 contours in the 2D scatter plots;
-while the right hand plot clearly places the MW observations at the
-border of the $3\sigma$ range in the joint distributions that involve
-the width $w$.
+while the right hand plot clearly places the MW observations outside
+the $2\sigma$ region in the joint distributions that involve the width
+$w$.
 
@@
 $97 \%$ of the total of points in the distribution.
-With this result in mind the $LG$ has the same degree of atypicality
+With this result in mind the LG has the same degree of atypicality
 as a $3\sigma$ outlier. 
@@
 
-For M31, between $5\%$ and $80\%$ of the pairs have a satellite
+For M31, up to $80\%$ of the pairs have a satellite
 distribution as aspherical as the one observed in M31.
 This fraction drops
-dramatically for the MW where only $0.02\%$ to $4\%$ of the satellites
+dramatically for the MW where only at most $4\%$ of the satellites
 are expected to have as extreme aspherical distributions as the MW.
@@
 
-\subsection{How to understand an atypical MW}
+\subsection{How to understand an atypical MW?}
 
@@
 recent results \citep{2012MNRAS.423.1109P,2015ApJ...815...19P}. 
-We estimated that with the M31 between $5\%$ and $80\%$ of the pairs
+We estimated that with the M31 up to $80\%$ of the pairs
 show aspherical characteristics larger than M31, while this fraction
